### 2015-07-13 paper.tex
template

\documentclass{article}

% For figures
\usepackage{graphicx} % more modern
%\usepackage{epsfig} % less modern
\usepackage{subfigure}

% For citations
\usepackage{natbib}

% For algorithms
\usepackage{algorithm}
\usepackage{algorithmic}

\usepackage{hyperref}
\newcommand{\theHalgorithm}{\arabic{algorithm}}

\usepackage[accepted]{icml2015}

% Header ======================================================================

\icmltitlerunning{Semi-supervised author disambiguation for scientific publications}

\begin{document}

\twocolumn[
\icmltitle{Semi-supervised author disambiguation for scientific publications}

\icmlauthor{Gilles Louppe}{g.louppe@cern.ch}
\icmlauthor{Hussein Al-Natsheh}{}
\icmlauthor{Mateusz Susik}{}
\icmladdress{CERN, CH-1211 Geneva 23, Switzerland}

\icmlkeywords{variable importances, random forest}

\vskip 0.3in
]

\begin{abstract}
The purpose of this document is to provide both the basic paper template and
submission guidelines.
\end{abstract}

% Background ==================================================================

\section{Background}
\label{background}

% Methods =====================================================================

\section{Methods}
\label{methods}

% Results and discussion ======================================================

\section{Results and discussion}
\label{results}

% Conclusions =================================================================

\section{Conclusions}
\label{conclusions}

% References ==================================================================
\nocite{langley00}

\bibliography{bib}
\bibliographystyle{icml2015}

\end{document}

### 2015-07-14 paper.tex
table of contents
abstract

@@
-\documentclass{article}
+\documentclass[11pt]{article}
+\usepackage[margin=1.2in]{geometry}
 
@@
 \usepackage{subfigure}
+\usepackage{color}
 
@@
 
-\usepackage[accepted]{icml2015}
+\usepackage{titlesec}
+\titleformat{\section}{\sf\large}{\thesection.}{1em}{}
+\titleformat{\subsection}{\sf}{\thesubsection}{1em}{}
+\titleformat{\subsubsection}{\sf \small}{\thesubsubsection}{1em}{\it }
+
+\newcommand{\glnote}[1]{\textcolor{red}{GL: #1}}
 
@@
 
-\icmltitlerunning{Semi-supervised author disambiguation for scientific publications}
+\title{Semi-supervised author disambiguation for large and partially annotated databases of scientific publications}
+\author{Gilles Louppe, Hussein Al-Natsheh and Mateusz Susik\\
+       \it{CERN, Geneva, Switzerland}}
+
+\date{}
+
+%\icmltitlerunning{Semi-supervised author disambiguation for large and partially annotated databases of scientific publications}
 
@@
 
-\twocolumn[
-\icmltitle{Semi-supervised author disambiguation for scientific publications}
-
-\icmlauthor{Gilles Louppe}{g.louppe@cern.ch}
-\icmlauthor{Hussein Al-Natsheh}{}
-\icmlauthor{Mateusz Susik}{}
-\icmladdress{CERN, CH-1211 Geneva 23, Switzerland}
-
-\icmlkeywords{variable importances, random forest}
-
-\vskip 0.3in
-]
+\maketitle
 
 \begin{abstract}
-The purpose of this document is to provide both the basic paper template and
-submission guidelines.
+
+Author name disambiguation in bibliographic databases is the problem of
+grouping together scientific publications written by a same person. This
+problem is difficult because (i) an author may use different spellings,
+variants or synonyms across her career and/or (ii) distinct authors may share
+the same name. Among solutions ot this problem, digital libraries are
+increasingly offering tools for authors to manually curate their publications
+and claim which ones are theirs. Indirectly, these tools allow for the
+inexpensive collection of large annotated training data that can be further
+leveraged to improve the overall accuracy of the system. In this context, we
+propose a semi-supervised machine learning disambiguation solution in the case
+large and partially annotated databases of scientific publications. We describe
+how this annotated data can be used to learn an accurate classifier for
+identifying corefering authors, guide the clustering of scientific publications
+by distinct authors and finally match the resulting clusters to existing
+profiles. Evaluation is carried out on a real-world database of 1 million
+annotated publications and demonstrates the very good accuracy of the proposed
+solution. In particular, our analysis of parameters and features reveal that...
+\glnote{To be completed with actual results.}
+
 \end{abstract}
 
-% Background ==================================================================
+% Introduction ==================================================================
 
-\section{Background}
-\label{background}
+\section{Introduction}
+\label{introduction}
+
+% general introduction to the disambiguation issues
+% summary of what we did
+% outline of the paper
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Phasellus malesuada
+eleifend pretium. Nulla semper aliquam arcu vel euismod. Curabitur dapibus
+tortor varius, pretium lectus at, tempus lectus. Mauris pellentesque, turpis
+vitae vulputate auctor, enim metus hendrerit nulla, ac elementum felis leo in
+nulla. Cras sed suscipit magna. Donec enim enim, egestas facilisis odio quis,
+laoreet maximus ligula. Nam vel metus at enim venenatis fringilla. Fusce nisl
+nunc, pellentesque eget arcu a, tempor interdum arcu. Duis non urna ligula.
+Vivamus consequat cursus auctor.
+
+% Related works ==================================================================
+
+\section{Related works}
+\label{relate-works}
+
+% levin
 
@@
 
-\section{Methods}
+\section{Semi-supervised author disambiguation}
 \label{methods}
+
+\subsection{Overview}
+% figure, notations, etc
+
+\subsection{Distance learning}
+% distance learning as a supervised problem
+% balancing difficult and easy cases
+
+\subsection{Blocking}
+% motivation
+% last name, first initial
+% phonetics something (dm)
+
+\subsection{Semi-supervised clustering}
+% hierarchical clustering
+% semi-supervised clustering
+% cold start problem (when no labels in a block)
+
+\subsection{Matching}
+% general description in a real system
+
+% Implementation ======================================================
+
+\section{Implementation}
+\label{implementation}
 
@@
 
-\section{Results and discussion}
-\label{results}
+\section{Experiments}
+\label{experiments}
+
+\subsection{Data}
+% source of the data, labels in the data, etc
+% release the data
+
+\subsection{Evaluation protocol}
+% measures (b^3, paired, size of clusters)
+% training / valid / test sets
+
+\subsection{Distance learning}
+% feature engineering
+% variable importance analysis
+% supervised learning model
+
+\subsection{Blocking}
+
+\subsection{Semi-supervised clustering}
+% compare agglomerative algorithms
+% compare threshold strategies
+% compare cold start solutions
+% talk about impact of small improvements in terms of citations statistics
 
@@
 
+% future improvements
+
 % References ==================================================================
-\nocite{langley00}
+\nocite{langley00} % todo remove
 
+\bibliographystyle{apalike}
 \bibliography{bib}
-\bibliographystyle{icml2015}
 

### 2015-07-14 paper.tex
abstract

@@
        \it{CERN, Geneva, Switzerland}}
-
 \date{}
-
-%\icmltitlerunning{Semi-supervised author disambiguation for large and partially annotated databases of scientific publications}
 
@@
 and claim which ones are theirs. Indirectly, these tools allow for the
-inexpensive collection of large annotated training data that can be further
-leveraged to improve the overall accuracy of the system. In this context, we
-propose a semi-supervised machine learning disambiguation solution in the case
-large and partially annotated databases of scientific publications. We describe
-how this annotated data can be used to learn an accurate classifier for
-identifying corefering authors, guide the clustering of scientific publications
-by distinct authors and finally match the resulting clusters to existing
-profiles. Evaluation is carried out on a real-world database of 1 million
-annotated publications and demonstrates the very good accuracy of the proposed
-solution. In particular, our analysis of parameters and features reveal that...
-\glnote{To be completed with actual results.}
+inexpensive collection of large annotated training data, which can be further
+leveraged to build an automated disambiguation system generalizing to
+unlabelled publications. In this context, we propose a semi-supervised machine
+learning disambiguation solution in the case large and partially annotated
+databases of scientific publications. We describe how this annotated data can
+be used to learn an accurate classifier for identifying corefering authors,
+guide the clustering of scientific publications by distinct authors and finally
+match the resulting clusters to existing profiles. Evaluation is carried out on
+a real-world database of 1 million manual annotations and demonstrates the
+very good accuracy of the proposed solution. In particular, our analysis of
+parameters and features reveal that... \glnote{To be completed with actual
+results.}
 

### 2015-07-15 paper.tex
template

@@
-\documentclass[11pt]{article}
-\usepackage[margin=1.2in]{geometry}
+\documentclass{article}
+%\usepackage[margin=1.2in]{geometry}
+
+\usepackage{nips15submit_e}
 
 % For figures
-\usepackage{graphicx} % more modern
-%\usepackage{epsfig} % less modern
+\usepackage{graphicx}
 \usepackage{subfigure}
@@
 
+% For links
 \usepackage{hyperref}
 \newcommand{\theHalgorithm}{\arabic{algorithm}}
-
-\usepackage{titlesec}
-\titleformat{\section}{\sf\large}{\thesection.}{1em}{}
-\titleformat{\subsection}{\sf}{\thesubsection}{1em}{}
-\titleformat{\subsubsection}{\sf \small}{\thesubsubsection}{1em}{\it }
 
@@
 
-\title{Semi-supervised author disambiguation for large and partially annotated databases of scientific publications}
-\author{Gilles Louppe, Hussein Al-Natsheh and Mateusz Susik\\
-       \it{CERN, Geneva, Switzerland}}
+\title{Semi-supervised author disambiguation of scientific publications}
+
+\author{Gilles Louppe\\
+        CERN, Switzerland\\
+        \texttt{g.louppe@cern.ch}\\
+\And Hussein Al-Natsheh\\
+        CERN, Switzerland\\
+        \texttt{hussein.al.natsheh@cern.ch }\\
+\And Mateusz Susik\\
+        CERN, Switzerland\\
+        \texttt{mateusz.susik@cern.ch }\\ }
 \date{}
+
+\nipsfinalcopy
 
@@
 databases of scientific publications. We describe how this annotated data can
-be used to learn an accurate classifier for identifying corefering authors,
-guide the clustering of scientific publications by distinct authors and finally
-match the resulting clusters to existing profiles. Evaluation is carried out on
-a real-world database of 1 million manual annotations and demonstrates the
-very good accuracy of the proposed solution. In particular, our analysis of
-parameters and features reveal that... \glnote{To be completed with actual
-results.}
+be used at several stages of disambiguation, to learn an accurate classifier
+for identifying corefering authors, to guide the clustering of scientific
+publications by distinct authors and finally to match the resulting clusters
+with existing profiles. Evaluation is carried out on a real-world database of 1
+million manual annotations and demonstrates the very good accuracy of the
+proposed solution. In particular, our analysis of parameters and features
+reveal that... \glnote{To be completed with actual results.}
 

### 2015-07-15 paper.tex
abstract

@@
 grouping together scientific publications written by a same person. This
-problem is difficult because (i) an author may use different spellings,
+problem is often difficult because (i) an author may use different spellings,
 variants or synonyms across her career and/or (ii) distinct authors may share
@@
 inexpensive collection of large annotated training data, which can be further
-leveraged to build an automated disambiguation system generalizing to
-unlabelled publications. In this context, we propose a semi-supervised machine
-learning disambiguation solution in the case large and partially annotated
-databases of scientific publications. We describe how this annotated data can
-be used at several stages of disambiguation, to learn an accurate classifier
-for identifying corefering authors, to guide the clustering of scientific
-publications by distinct authors and finally to match the resulting clusters
-with existing profiles. Evaluation is carried out on a real-world database of 1
-million manual annotations and demonstrates the very good accuracy of the
-proposed solution. In particular, our analysis of parameters and features
-reveal that... \glnote{To be completed with actual results.}
+leveraged to build an automated disambiguation system capable of inferring
+features or patterns for identifying publications written by a same person.  In
+this context, we propose a semi-supervised machine learning disambiguation
+solution in the case large and partially annotated databases of scientific
+publications. Using a real-world dataset of 1 million manual annotations, we
+demonstrate how to exploit this data to learn an accurate classifier for
+identifying corefering authors, to guide the clustering of scientific
+publications by distinct authors in a semi-supervised way and finally to match
+the resulting clusters with existing profiles.  Our analysis of parameters and
+features reveal that... \glnote{To be completed with actual results.}
 
@@
 % outline of the paper
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Phasellus malesuada
+eleifend pretium. Nulla semper aliquam arcu vel euismod. Curabitur dapibus
+tortor varius, pretium lectus at, tempus lectus. Mauris pellentesque, turpis
+vitae vulputate auctor, enim metus hendrerit nulla, ac elementum felis leo in
+nulla. Cras sed suscipit magna. Donec enim enim, egestas facilisis odio quis,
+laoreet maximus ligula. Nam vel metus at enim venenatis fringilla. Fusce nisl
+nunc, pellentesque eget arcu a, tempor interdum arcu. Duis non urna ligula.
+Vivamus consequat cursus auctor.
+
+Lorem ipsum dolor sit amet, consectetur adipiscing elit. Phasellus malesuada
+eleifend pretium. Nulla semper aliquam arcu vel euismod. Curabitur dapibus
+tortor varius, pretium lectus at, tempus lectus. Mauris pellentesque, turpis
+vitae vulputate auctor, enim metus hendrerit nulla, ac elementum felis leo in
+nulla. Cras sed suscipit magna. Donec enim enim, egestas facilisis odio quis,
+laoreet maximus ligula. Nam vel metus at enim venenatis fringilla. Fusce nisl
+nunc, pellentesque eget arcu a, tempor interdum arcu. Duis non urna ligula.
+Vivamus consequat cursus auctor.
 

### 2015-07-15 paper.tex
beginning of intro

@@
 grouping together scientific publications written by a same person. This
-problem is often difficult because (i) an author may use different spellings,
-variants or synonyms across her career and/or (ii) distinct authors may share
-the same name. Among solutions ot this problem, digital libraries are
-increasingly offering tools for authors to manually curate their publications
-and claim which ones are theirs. Indirectly, these tools allow for the
-inexpensive collection of large annotated training data, which can be further
-leveraged to build an automated disambiguation system capable of inferring
-features or patterns for identifying publications written by a same person.  In
-this context, we propose a semi-supervised machine learning disambiguation
-solution in the case large and partially annotated databases of scientific
-publications. Using a real-world dataset of 1 million manual annotations, we
-demonstrate how to exploit this data to learn an accurate classifier for
-identifying corefering authors, to guide the clustering of scientific
-publications by distinct authors in a semi-supervised way and finally to match
-the resulting clusters with existing profiles.  Our analysis of parameters and
+problem is often difficult because an author may use different spellings,
+variants or synonyms across her career and/or distinct authors may share the
+same name. Among solutions ot this problem, digital libraries are increasingly
+offering tools for authors to manually curate their publications and claim
+which ones are theirs. Indirectly, these tools allow for the inexpensive
+collection of large annotated training data, which can be further leveraged to
+build an automated disambiguation system capable of inferring features or
+patterns for identifying publications written by a same person.  In this
+context, we propose a semi-supervised machine learning disambiguation solution
+in the case large and partially annotated databases of scientific publications.
+Using a real-world dataset of 1 million manual annotations, we demonstrate how
+to exploit this data (i) to learn an accurate classifier for identifying
+corefering authors, (ii) to guide the clustering of scientific publications by
+distinct authors in a semi-supervised way and finally (iii) to match the
+resulting clusters with existing profiles.  Our analysis of parameters and
 features reveal that... \glnote{To be completed with actual results.}
@@
 % general introduction to the disambiguation issues
+% often based on small dataset or fully unsupervised
 % summary of what we did
 % outline of the paper
+
+In academic digital libraries, author name disambiguation is the problem of
+grouping together publications written by a same person.  With the fast growth
+of the scientific literature, this has become a pressing issue because the
+accuracy of information managed at the individual level directly affects the
+relevance search results (e.g., when querying for all publications written by a
+given individual), the reliability of bibliometrics (e.g., citation counts or
+other impact metrics) or the relevance of scientific network analysis. Author
+name disambiguation is often a difficult problem because an author may use
+different spellings, variants or synonyms across her career and/or distinct
+authors may share the same name. In particular, author disambiguation becomes
+even more critical for researchers from Eastern cultures, where personal names
+may be traditionally less diverse (leading to homonym issues) or for which
+transliteration to latin characters may not be unique (leading to synonym
+issues).
+
+Efforts and solutions to author disambiguation have been proposed in numerous
+fields.
+
+% Related works ==================================================================
+
+\section{Related works}
+\label{relate-works}
 
@@
 Vivamus consequat cursus auctor.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Phasellus malesuada
-eleifend pretium. Nulla semper aliquam arcu vel euismod. Curabitur dapibus
-tortor varius, pretium lectus at, tempus lectus. Mauris pellentesque, turpis
-vitae vulputate auctor, enim metus hendrerit nulla, ac elementum felis leo in
-nulla. Cras sed suscipit magna. Donec enim enim, egestas facilisis odio quis,
-laoreet maximus ligula. Nam vel metus at enim venenatis fringilla. Fusce nisl
-nunc, pellentesque eget arcu a, tempor interdum arcu. Duis non urna ligula.
-Vivamus consequat cursus auctor.
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Phasellus malesuada
-eleifend pretium. Nulla semper aliquam arcu vel euismod. Curabitur dapibus
-tortor varius, pretium lectus at, tempus lectus. Mauris pellentesque, turpis
-vitae vulputate auctor, enim metus hendrerit nulla, ac elementum felis leo in
-nulla. Cras sed suscipit magna. Donec enim enim, egestas facilisis odio quis,
-laoreet maximus ligula. Nam vel metus at enim venenatis fringilla. Fusce nisl
-nunc, pellentesque eget arcu a, tempor interdum arcu. Duis non urna ligula.
-Vivamus consequat cursus auctor.
-
-% Related works ==================================================================
-
-\section{Related works}
-\label{relate-works}
 

### 2015-07-16 paper.tex
autosave
added @eamonnmag

@@
 \author{Gilles Louppe\\
-        CERN, Switzerland\\
-        \texttt{g.louppe@cern.ch}\\
+        CERN\\
+        Switzerland\\
 \And Hussein Al-Natsheh\\
-        CERN, Switzerland\\
-        \texttt{hussein.al.natsheh@cern.ch }\\
+        CERN\\
+        Switzerland\\
 \And Mateusz Susik\\
-        CERN, Switzerland\\
-        \texttt{mateusz.susik@cern.ch }\\ }
+        CERN\\
+        Switzerland\\
+\And Eamonn Maguire\\
+        CERN\\
+        Switzerland}
 \date{}
@@
 Using a real-world dataset of 1 million manual annotations, we demonstrate how
-to exploit this data (i) to learn an accurate classifier for identifying
+we exploited this data (i) to learn an accurate classifier for identifying
 corefering authors, (ii) to guide the clustering of scientific publications by
@@
 resulting clusters with existing profiles.  Our analysis of parameters and
-features reveal that... \glnote{To be completed with actual results.}
+features on this large training set reveal that... \glnote{To be completed with
+actual results.}
 
@@
 of the scientific literature, this has become a pressing issue because the
-accuracy of information managed at the individual level directly affects the
-relevance search results (e.g., when querying for all publications written by a
-given individual), the reliability of bibliometrics (e.g., citation counts or
+accuracy of information managed at the level of individuals directly affects
+the relevance search results (e.g., when querying for all publications written
+by a given author), the reliability of bibliometrics (e.g., citation counts or
 other impact metrics) or the relevance of scientific network analysis. Author
@@
 
-Efforts and solutions to author disambiguation have been proposed in numerous
-fields.
+Efforts and solutions to author disambiguation have been proposed from various
+communities. On the one hand, libraries have maintained and developed
+authorship control with manual curation
 

### 2015-07-16 paper.tex
Adding content to Overview section

@@
 % figure, notations, etc
+Before presenting the methodology, we need to define some terminologies we will use to describe the data entities.
+An author's full name, or author name, is the string variation that was mention in the database record to refer to the author.
+The full name is a composition of the author last name and the author other names.
+For example, in the full name (Kerth, Leroy T.), the last name is Kerth and the other names will be (Leroy T.).
+We also use the terminology initials.
+In our full name example, the initials will be (L T).
+First initial then will be (L).
+So, grouping publications  What we refer to as the real author is the real person behind the publication.
+We will use the term signature as the entity that we apply clustering on.
+A signature is a unique combination between a publication and an author name as mentioned in the database.
+The term blocking means grouping the signature by a certain version of the author name.
+For example, blocking by the author last name and first name initial means grouping together all signatures that have in common the same author's last name and first name initial.
+In our example, grouping by the string (Kerth L).
+What we mean by claimed publications is the publications in which their real author identity were claimed.
+We use these claimed publications to generate our ground truth data.
+
+Our methodology consists in 4 main components: Distance learning, blocking, semi-supervised clustering and matching.
+A distance function is learned from a training set of signiture pairs sampled from ground-truth data.
+Each pair is labeled whether the 2 signatures are for the same real author or not.
+The learned distance function will then be used for computing the dissimilarity matrix of a block of signatures.
+A block of signatures is grouping signatures that have in common similar author names, for example same last name.
+This affinity matrix would be the main input of our semi-supervised clustering algorithm.
+The predicted clusters of each block will lastly be combined into a final predicted clusters result.
+Each cluster label represents the predicted single author of the publications in the cluster.
+Finally, we present a strategy for matching the predicted results with the publications in which their authors were claimed.
 

### 2015-07-16 paper.tex
autosave

--- 2015-07-16 paper.tex
@@
 Efforts and solutions to author disambiguation have been proposed from various
-communities. On the one hand, libraries have maintained and developed
-authorship control with manual curation
+communities \citep{liu2014author}. On the one hand, libraries have maintained
+authorship control through manual curation, either in a centralized way by
+hiring collaborators or by developing services inviting authors to register
+their publications themselves (e.g., Google Scholar, Inspire-HEP). Recently,
+efforts started to assign persistent digital identifiers to researchers (e.g.,
+ORCID, ResearchedID), with the further objective to embed these identifiers in
+the submission workflow of publishers or repositeries (e.g., Elsevier, arXiv,
+Inspire-HEP), thereby univocally solving any disambiguation issue. With the
+large cost of centralized manual authorship control or until the larger
+adoption of crowdsourced solutions, the impact of these efforts are
+unfortunately limited by the efficiency, motivation and integrity of their
+active contributors. For these reasons, fully automated machine learning-based
+methods have been proposed during the past decade to provide less costly and
+more efficient solutions to author disambiguation. In this work, ...
 
@@
 % References ==================================================================
-\nocite{langley00} % todo remove
 

### 2015-07-16 paper.tex
autosave

@@
 active contributors. For these reasons, fully automated machine learning-based
-methods have been proposed during the past decade to provide less costly and
-more efficient solutions to author disambiguation. In this work, ...
+methods have been proposed during the past decade \glnote{Add references} to provide less costly and
+more efficient solutions to author disambiguation. In this work, our goal is to
+explore and demonstrate how both approaches can coexist and benefit from each
+other.  In particular, we study how curated data obtained through manual
+curation (either centralized or crowdsourced) can be exploited (i) to learn an
+accurate classifier for identifying corefering authors, (ii) to guide the
+clustering of scientific publications by distinct authors in a semi-supervised
+way and finally (iii) to match the resulting clusters with existing profiles.
+Our analysis of parameters and features on this large training set reveal
+that... \glnote{To be completed with actual results.}
+
+The remaining of this report is structured as follows. In Section~\ref{related-works}, ...
 
@@
 \section{Related works}
-\label{relate-works}
-
-Lorem ipsum dolor sit amet, consectetur adipiscing elit. Phasellus malesuada
-eleifend pretium. Nulla semper aliquam arcu vel euismod. Curabitur dapibus
-tortor varius, pretium lectus at, tempus lectus. Mauris pellentesque, turpis
-vitae vulputate auctor, enim metus hendrerit nulla, ac elementum felis leo in
-nulla. Cras sed suscipit magna. Donec enim enim, egestas facilisis odio quis,
-laoreet maximus ligula. Nam vel metus at enim venenatis fringilla. Fusce nisl
-nunc, pellentesque eget arcu a, tempor interdum arcu. Duis non urna ligula.
-Vivamus consequat cursus auctor.
+\label{related-works}
 

### 2015-07-16 paper.tex
autosave

@@
 Author name disambiguation in bibliographic databases is the problem of
-grouping together scientific publications written by a same person. This
-problem is often difficult because an author may use different spellings,
-variants or synonyms across her career and/or distinct authors may share the
-same name. Among solutions ot this problem, digital libraries are increasingly
-offering tools for authors to manually curate their publications and claim
-which ones are theirs. Indirectly, these tools allow for the inexpensive
-collection of large annotated training data, which can be further leveraged to
-build an automated disambiguation system capable of inferring features or
-patterns for identifying publications written by a same person.  In this
-context, we propose a semi-supervised machine learning disambiguation solution
-in the case large and partially annotated databases of scientific publications.
-Using a real-world dataset of 1 million manual annotations, we demonstrate how
-we exploited this data (i) to learn an accurate classifier for identifying
-corefering authors, (ii) to guide the clustering of scientific publications by
-distinct authors in a semi-supervised way and finally (iii) to match the
-resulting clusters with existing profiles.  Our analysis of parameters and
-features on this large training set reveal that... \glnote{To be completed with
-actual results.}
+grouping together scientific publications written by a same person, accounting
+for potential homonyms and/or synonyms. Among solutions ot this problem, digital
+libraries are increasingly offering tools for authors to manually curate their
+publications and claim which ones are theirs. Indirectly, these tools allow for
+the inexpensive collection of large annotated training data, which can be
+further leveraged to build an automated disambiguation system capable of
+inferring features or patterns for identifying publications written by a same
+person.  In this context, we propose a semi-supervised machine learning
+disambiguation solution in the case large and partially annotated databases of
+scientific publications. Using a real-world dataset of 1 million manual
+annotations, we demonstrate how we exploited this data (i) to learn an accurate
+classifier for identifying corefering authors, (ii) to guide the clustering of
+scientific publications by distinct authors in a semi-supervised way and
+finally (iii) to match the resulting clusters with existing profiles.  Our
+analysis of parameters and features on this large training set reveal that...
+\glnote{To be completed with actual results.}
 
@@
 their publications themselves (e.g., Google Scholar, Inspire-HEP). Recently,
-efforts started to assign persistent digital identifiers to researchers (e.g.,
-ORCID, ResearchedID), with the further objective to embed these identifiers in
-the submission workflow of publishers or repositeries (e.g., Elsevier, arXiv,
-Inspire-HEP), thereby univocally solving any disambiguation issue. With the
-large cost of centralized manual authorship control or until the larger
-adoption of crowdsourced solutions, the impact of these efforts are
-unfortunately limited by the efficiency, motivation and integrity of their
-active contributors. For these reasons, fully automated machine learning-based
-methods have been proposed during the past decade \glnote{Add references} to provide less costly and
-more efficient solutions to author disambiguation. In this work, our goal is to
-explore and demonstrate how both approaches can coexist and benefit from each
-other.  In particular, we study how curated data obtained through manual
+efforts also started to assign persistent digital identifiers to researchers
+(e.g., ORCID, ResearchedID), with the further objective to embed these
+identifiers in the submission workflow of publishers or repositeries (e.g.,
+Elsevier, arXiv, Inspire-HEP), thereby univocally solving any disambiguation
+issue. With the large cost of centralized manual authorship control or until
+the larger adoption of crowdsourced solutions, the impact of these efforts are
+unfortunately limited by the efficiency, motivation or integrity of their
+active contributors. Similarly, the success of persistent digital identifier
+efforts is conditioned to a large and ubiquituous adoption by both reseachers and publishers.
+For these reasons, fully automated machine learning-based methods have been
+proposed during the past decade \glnote{Add references} to provide immediate, less costly
+and efficient solutions to author disambiguation. In this work, our goal
+is to explore and demonstrate how both approaches can coexist and benefit from
+each other.  In particular, we study how curated data obtained through manual
 curation (either centralized or crowdsourced) can be exploited (i) to learn an

### 2015-07-17 paper.tex
save

--- 2015-07-16 paper.tex
@@
 is to explore and demonstrate how both approaches can coexist and benefit from
-each other.  In particular, we study how curated data obtained through manual
+each other.  In particular, we study how labeled data obtained through manual
 curation (either centralized or crowdsourced) can be exploited (i) to learn an
@@
 \label{related-works}
+
+\glnote{I will take care of this}
 

### 2015-07-20 paper.tex
autosave

@@
 grouping together scientific publications written by a same person, accounting
-for potential homonyms and/or synonyms. Among solutions ot this problem, digital
+for potential homonyms and/or synonyms. Among solutions to this problem, digital
 libraries are increasingly offering tools for authors to manually curate their
@@
 authors may share the same name. In particular, author disambiguation becomes
-even more critical for researchers from Eastern cultures, where personal names
+even more critical for researchers from non-Western cultures, where personal names
 may be traditionally less diverse (leading to homonym issues) or for which
@@
 hiring collaborators or by developing services inviting authors to register
-their publications themselves (e.g., Google Scholar, Inspire-HEP). Recently,
-efforts also started to assign persistent digital identifiers to researchers
-(e.g., ORCID, ResearchedID), with the further objective to embed these
+their publications themselves (e.g., Google Scholar, Inspire-HEP, ...). Recently,
+efforts also started to create persistent digital identifiers assigned to researchers
+(e.g., ORCID, ResearchedID, ...), with the further objective to embed these
 identifiers in the submission workflow of publishers or repositeries (e.g.,
-Elsevier, arXiv, Inspire-HEP), thereby univocally solving any disambiguation
+Elsevier, arXiv, Inspire-HEP, ...), thereby univocally solving any disambiguation
 issue. With the large cost of centralized manual authorship control or until
@@
 active contributors. Similarly, the success of persistent digital identifier
-efforts is conditioned to a large and ubiquituous adoption by both reseachers and publishers.
+efforts is conditioned to a large and ubiquituous adoption by both researchers and publishers.
 For these reasons, fully automated machine learning-based methods have been
@@
 % figure, notations, etc
-Before presenting the methodology, we need to define some terminologies we will use to describe the data entities.
-An author's full name, or author name, is the string variation that was mention in the database record to refer to the author.
-The full name is a composition of the author last name and the author other names.
-For example, in the full name (Kerth, Leroy T.), the last name is Kerth and the other names will be (Leroy T.).
-We also use the terminology initials.
-In our full name example, the initials will be (L T).
-First initial then will be (L).
-So, grouping publications  What we refer to as the real author is the real person behind the publication.
-We will use the term signature as the entity that we apply clustering on.
-A signature is a unique combination between a publication and an author name as mentioned in the database.
-The term blocking means grouping the signature by a certain version of the author name.
-For example, blocking by the author last name and first name initial means grouping together all signatures that have in common the same author's last name and first name initial.
-In our example, grouping by the string (Kerth L).
-What we mean by claimed publications is the publications in which their real author identity were claimed.
-We use these claimed publications to generate our ground truth data.
 
-Our methodology consists in 4 main components: Distance learning, blocking, semi-supervised clustering and matching.
-A distance function is learned from a training set of signiture pairs sampled from ground-truth data.
-Each pair is labeled whether the 2 signatures are for the same real author or not.
-The learned distance function will then be used for computing the dissimilarity matrix of a block of signatures.
-A block of signatures is grouping signatures that have in common similar author names, for example same last name.
-This affinity matrix would be the main input of our semi-supervised clustering algorithm.
-The predicted clusters of each block will lastly be combined into a final predicted clusters result.
-Each cluster label represents the predicted single author of the publications in the cluster.
-Finally, we present a strategy for matching the predicted results with the publications in which their authors were claimed.
+Before presenting the methodology, we need to define some terminologies we will
+use to describe the data entities. An author's full name, or author name, is
+the string variation that was mention in the database record to refer to the
+author. The full name is a composition of the author last name and the author
+other names. For example, in the full name (Kerth, Leroy T.), the last name is
+Kerth and the other names will be (Leroy T.). We also use the terminology
+initials. In our full name example, the initials will be (L T). First initial
+then will be (L). So, grouping publications  What we refer to as the real
+author is the real person behind the publication. We will use the term
+signature as the entity that we apply clustering on.  A signature is a unique
+combination between a publication and an author name as mentioned in the
+database. The term blocking means grouping the signature by a certain version
+of the author name. For example, blocking by the author last name and first
+name initial means grouping together all signatures that have in common the
+same author's last name and first name initial. In our example, grouping by the
+string (Kerth L). What we mean by claimed publications is the publications in
+which their real author identity were claimed. We use these claimed
+publications to generate our ground truth data.
+
+Our methodology consists in 4 main components: Distance learning, blocking,
+semi-supervised clustering and matching. A distance function is learned from a
+training set of signiture pairs sampled from ground-truth data. Each pair is
+labeled whether the 2 signatures are for the same real author or not. The
+learned distance function will then be used for computing the dissimilarity
+matrix of a block of signatures. A block of signatures is grouping signatures
+that have in common similar author names, for example same last name. This
+affinity matrix would be the main input of our semi-supervised clustering
+algorithm. The predicted clusters of each block will lastly be combined into a
+final predicted clusters result. Each cluster label represents the predicted
+single author of the publications in the cluster. Finally, we present a
+strategy for matching the predicted results with the publications in which
+their authors were claimed.
 

### 2015-07-20 paper.tex
problem statement

@@
 
-Before presenting the methodology, we need to define some terminologies we will
-use to describe the data entities. An author's full name, or author name, is
-the string variation that was mention in the database record to refer to the
-author. The full name is a composition of the author last name and the author
-other names. For example, in the full name (Kerth, Leroy T.), the last name is
-Kerth and the other names will be (Leroy T.). We also use the terminology
-initials. In our full name example, the initials will be (L T). First initial
-then will be (L). So, grouping publications  What we refer to as the real
-author is the real person behind the publication. We will use the term
-signature as the entity that we apply clustering on.  A signature is a unique
-combination between a publication and an author name as mentioned in the
-database. The term blocking means grouping the signature by a certain version
-of the author name. For example, blocking by the author last name and first
-name initial means grouping together all signatures that have in common the
-same author's last name and first name initial. In our example, grouping by the
-string (Kerth L). What we mean by claimed publications is the publications in
-which their real author identity were claimed. We use these claimed
-publications to generate our ground truth data.
+Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
+p_{N-1}\}$ and a set of authors ${\cal A} = \{ a_0, ..., a_{M-1}\}$
+corresponding to individuals.  Let us define a signature $s \in p$ from a
+publication as a unique piece of information identifying one of the authors of
+$p$ (e.g., the author name, his affiliation, along with any other metadata can
+be derived from $p$). Let us denote by ${\cal S} = \{ s | s \in p, p \in {\cal
+P} \}$ the set of all signatures that can be extracted from all publications in
+${\cal P}$. In this context, the author disambiguation problem can be stated as
+the problem of finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of
+${\cal S}$ such that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$
+for all $i \neq j$, and where subsets $c_i$, or clusters, each corresponds to
+the set of all signatures belonging to the same individual $a_i$. Note that in
+practice, the set ${\cal A}$ often remains unknown and the task therefore boils
+down to finding a partition ${\cal C}$ such that subsets   $c_i$  each
+corresponds to the set of all signatures from a same individual.
 
-Our methodology consists in 4 main components: Distance learning, blocking,
-semi-supervised clustering and matching. A distance function is learned from a
-training set of signiture pairs sampled from ground-truth data. Each pair is
-labeled whether the 2 signatures are for the same real author or not. The
-learned distance function will then be used for computing the dissimilarity
-matrix of a block of signatures. A block of signatures is grouping signatures
-that have in common similar author names, for example same last name. This
-affinity matrix would be the main input of our semi-supervised clustering
-algorithm. The predicted clusters of each block will lastly be combined into a
-final predicted clusters result. Each cluster label represents the predicted
-single author of the publications in the cluster. Finally, we present a
-strategy for matching the predicted results with the publications in which
-their authors were claimed.
+% Before presenting the methodology, we need to define some terminologies we will
+% use to describe the data entities. An author's full name, or author name, is
+% the string variation that was mention in the database record to refer to the
+% author. The full name is a composition of the author last name and the author
+% other names. For example, in the full name (Kerth, Leroy T.), the last name is
+% Kerth and the other names will be (Leroy T.). We also use the terminology
+% initials. In our full name example, the initials will be (L T). First initial
+% then will be (L). So, grouping publications  What we refer to as the real
+% author is the real person behind the publication. We will use the term
+% signature as the entity that we apply clustering on.  A signature is a unique
+% combination between a publication and an author name as mentioned in the
+% database. The term blocking means grouping the signature by a certain version
+% of the author name. For example, blocking by the author last name and first
+% name initial means grouping together all signatures that have in common the
+% same author's last name and first name initial. In our example, grouping by the
+% string (Kerth L). What we mean by claimed publications is the publications in
+% which their real author identity were claimed. We use these claimed
+% publications to generate our ground truth data.
+
+% Our methodology consists in 4 main components: Distance learning, blocking,
+% semi-supervised clustering and matching. A distance function is learned from a
+% training set of signiture pairs sampled from ground-truth data. Each pair is
+% labeled whether the 2 signatures are for the same real author or not. The
+% learned distance function will then be used for computing the dissimilarity
+% matrix of a block of signatures. A block of signatures is grouping signatures
+% that have in common similar author names, for example same last name. This
+% affinity matrix would be the main input of our semi-supervised clustering
+% algorithm. The predicted clusters of each block will lastly be combined into a
+% final predicted clusters result. Each cluster label represents the predicted
+% single author of the publications in the cluster. Finally, we present a
+% strategy for matching the predicted results with the publications in which
+% their authors were claimed.
 

### 2015-07-20 paper.tex
autosave

@@
 \subsection{Overview}
-% figure, notations, etc
 
 Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
-p_{N-1}\}$ and a set of authors ${\cal A} = \{ a_0, ..., a_{M-1}\}$
-corresponding to individuals.  Let us define a signature $s \in p$ from a
-publication as a unique piece of information identifying one of the authors of
-$p$ (e.g., the author name, his affiliation, along with any other metadata can
-be derived from $p$). Let us denote by ${\cal S} = \{ s | s \in p, p \in {\cal
-P} \}$ the set of all signatures that can be extracted from all publications in
-${\cal P}$. In this context, the author disambiguation problem can be stated as
-the problem of finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of
-${\cal S}$ such that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$
-for all $i \neq j$, and where subsets $c_i$, or clusters, each corresponds to
-the set of all signatures belonging to the same individual $a_i$. Note that in
-practice, the set ${\cal A}$ often remains unknown and the task therefore boils
-down to finding a partition ${\cal C}$ such that subsets   $c_i$  each
-corresponds to the set of all signatures from a same individual.
+p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
+a_{M-1}\}$ having together authored all publications in ${\cal P}$.  Let us
+define a signature $s \in p$ from a publication as a unique piece of
+information identifying one of the authors of $p$ (e.g., the author name, his
+affiliation, along with any other metadata can be derived from $p$). Let us
+denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
+signatures that can be extracted from all publications in ${\cal P}$. In this
+context, the author disambiguation problem can be stated as the problem of
+finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
+that ${\cal S} = \cup_{i=0}^{M-1} c_i$, $c_i \cap c_j = \phi$ for all $i \neq
+j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
+signatures belonging to the same individual $a_i$. Note that in practice, the
+set ${\cal A}$ often remains unknown and the task therefore boils down to
+finding a partition ${\cal C}$ such that subsets   $c_i$  each corresponds to
+the set of all signatures from a same individual.
 

### 2015-07-20 paper.tex
save

@@
 
-\newcommand{\glnote}[1]{\textcolor{red}{GL: #1}}
+\newcommand{\glnote}[1]{\textcolor{red}{[GL: #1]}}
 
@@
 j$, and where subsets $c_i$, or clusters, each corresponds to the set of all
-signatures belonging to the same individual $a_i$. Note that in practice, the
-set ${\cal A}$ often remains unknown and the task therefore boils down to
-finding a partition ${\cal C}$ such that subsets   $c_i$  each corresponds to
-the set of all signatures from a same individual.
+signatures belonging to the same individual $a_i$. Alternatively, the set
+${\cal A}$ may remain (possibly partially) unknown, such that author
+disambiguation therefore boils down to finding a partition ${\cal C}$ where
+subsets $c_i$  each corresponds to the set of all signatures from a same
+individual. Finally, in the case of partially annotated databases as studied in
+this work, the setting extends with the partial knowledge of pairs $(a, s) \in
+{\cal A} \times {\cal S}$, each indicating that signature $s$ is known to
+belong to individual $a$.
+
+In this work, author disambiguation is cast into a semi-supervised clustering
+problem, as inspired from several previous works \glnote{Add references}.
+Our algorithm is made of four elements: ...
 
@@
 
-\subsection{Distance learning}
-% distance learning as a supervised problem
-% balancing difficult and easy cases
-
 \subsection{Blocking}
@@
 % phonetics something (dm)
+
+\subsection{Distance learning}
+% distance learning as a supervised problem
+% balancing difficult and easy cases
 
@@
 
+\subsection{Blocking}
+
 \subsection{Distance learning}
@@
 % supervised learning model
-
-\subsection{Blocking}
 

### 2015-07-20 paper.tex
save

@@
 signatures that can be extracted from all publications in ${\cal P}$. In this
-context, the author disambiguation problem can be stated as the problem of
+framework, author disambiguation can be stated as the problem of
 finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
@@
 ${\cal A}$ may remain (possibly partially) unknown, such that author
-disambiguation therefore boils down to finding a partition ${\cal C}$ where
+disambiguation boils down to finding a partition ${\cal C}$ where
 subsets $c_i$  each corresponds to the set of all signatures from a same

### 2015-08-05 paper.tex
save

@@
 further leveraged to build an automated disambiguation system capable of
-inferring features or patterns for identifying publications written by a same
+inferring patterns for identifying publications written by a same
 person.  In this context, we propose a semi-supervised machine learning
@@
 finally (iii) to match the resulting clusters with existing profiles.  Our
-analysis of parameters and features on this large training set reveal that...
+analysis on this large training set reveal that...
 \glnote{To be completed with actual results.}
@@
 In academic digital libraries, author name disambiguation is the problem of
-grouping together publications written by a same person.  With the fast growth
-of the scientific literature, this has become a pressing issue because the
-accuracy of information managed at the level of individuals directly affects
-the relevance search results (e.g., when querying for all publications written
-by a given author), the reliability of bibliometrics (e.g., citation counts or
-other impact metrics) or the relevance of scientific network analysis. Author
-name disambiguation is often a difficult problem because an author may use
-different spellings, variants or synonyms across her career and/or distinct
-authors may share the same name. In particular, author disambiguation becomes
-even more critical for researchers from non-Western cultures, where personal names
-may be traditionally less diverse (leading to homonym issues) or for which
-transliteration to latin characters may not be unique (leading to synonym
-issues).
+grouping together publications written by a same person.  Author name
+disambiguation is often a difficult problem because an author may use different
+spellings, variants or synonyms across her career and/or distinct authors may
+share the same name. Most notably, author disambiguation is often even more
+troublesome in the case of researchers from non-Western cultures, where
+personal names may be traditionally less diverse (leading to homonym issues) or
+for which transliteration to latin characters may not be unique (leading to
+synonym issues). With the fast growth of the scientific literature, author
+disambiguation has become a pressing issue because the accuracy of information
+managed at the level of individuals directly affects the relevance search
+results (e.g., when querying for all publications written by a given author),
+the reliability of bibliometrics (e.g., citation counts or other impact
+metrics) or the relevance of scientific network analysis.
 
@@
 information identifying one of the authors of $p$ (e.g., the author name, his
-affiliation, along with any other metadata can be derived from $p$). Let us
+affiliation, along with any other metadata that can be derived from $p$). Let us
 denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all

### 2015-08-05 paper.tex
save

@@
 
-\title{Semi-supervised author disambiguation of scientific publications}
+\title{Semi-supervised author disambiguation of large-scale collections of labeled scientific publications}
 
@@
 results (e.g., when querying for all publications written by a given author),
-the reliability of bibliometrics (e.g., citation counts or other impact
-metrics) or the relevance of scientific network analysis.
+the reliability of bibliometrics and author rankings (e.g., citation counts or other impact
+metrics, as studied in \citep{strotmann2012author}) or the relevance of scientific network analysis.
 
@@
 For these reasons, fully automated machine learning-based methods have been
-proposed during the past decade \glnote{Add references} to provide immediate, less costly
+proposed during the past decade (See Section~\ref{related-works}) to provide immediate, less costly
 and efficient solutions to author disambiguation. In this work, our goal
@@
 
-\glnote{I will take care of this}
+Depending on the type and amount of data available, machine learning approaches
+for author disambiguation are usually inventorized into three classes of
+algorithms \citep{smalheiser2009author,levin2012citation}.
 
@@
 Our algorithm is made of four elements: ...
-
-% Before presenting the methodology, we need to define some terminologies we will
-% use to describe the data entities. An author's full name, or author name, is
-% the string variation that was mention in the database record to refer to the
-% author. The full name is a composition of the author last name and the author
-% other names. For example, in the full name (Kerth, Leroy T.), the last name is
-% Kerth and the other names will be (Leroy T.). We also use the terminology
-% initials. In our full name example, the initials will be (L T). First initial
-% then will be (L). So, grouping publications  What we refer to as the real
-% author is the real person behind the publication. We will use the term
-% signature as the entity that we apply clustering on.  A signature is a unique
-% combination between a publication and an author name as mentioned in the
-% database. The term blocking means grouping the signature by a certain version
-% of the author name. For example, blocking by the author last name and first
-% name initial means grouping together all signatures that have in common the
-% same author's last name and first name initial. In our example, grouping by the
-% string (Kerth L). What we mean by claimed publications is the publications in
-% which their real author identity were claimed. We use these claimed
-% publications to generate our ground truth data.
 

### 2015-08-05 paper.tex
save

@@
 disambiguation is often a difficult problem because an author may use different
-spellings, variants or synonyms across her career and/or distinct authors may
-share the same name. Most notably, author disambiguation is often even more
+spellings or name variants across her career (synonymy) and/or distinct authors may
+share the same name (polysemy). Most notably, author disambiguation is often even more
 troublesome in the case of researchers from non-Western cultures, where
@@
 
-Depending on the type and amount of data available, machine learning approaches
-for author disambiguation are usually inventorized into three classes of
-algorithms \citep{smalheiser2009author,levin2012citation}.
-
-% levin
+As reviewed in
+\citep{smalheiser2009author,ferreira2012brief,levin2012citation}, author
+disambiguation algorithms are usually composed of two components: (i) a
+similarity function determining whether two publications have been written by a
+same author and (ii) a clustering algorithm producing clusters of publications
+assumed to be written by a same author. Approaches can be inventorized along
+several axes, depending on the type and amount of data available, the way the
+similarity function is learned or defined, or the clustering procedure used to
+group publications. Methods relying on supervised learning usually make use of
+hand-labeled pairs of publications identified as being either from the same or
+from different authors for learning automatically a similarity function between
+publications \citep{han2004two,huang2006efficient,
+culotta2007author,treeratpituk2009disambiguating,tran2014author}. Because
+training data is often not easily available, unsupervised approaches propose
+instead to use domain-specific similarity functions designed for author
+disambiguation
+\citep{malin2005unsupervised,mcrae2006also,song2007efficient,kang2009co,fan2011graph,schulz2014exploiting}.
+These later approaches have the advantage of requiring no hand-labeled data, but
+often do not perform as well as the supervised approaches. To reconcile
+both worlds, semi-supervised
 

### 2015-08-05 paper.tex
save

@@
 
-\title{Semi-supervised author disambiguation of large-scale collections of labeled scientific publications}
+\title{Author disambiguation of large-scale semi-labeled collections of scientific articles}
 
@@
 For these reasons, fully automated machine learning-based methods have been
-proposed during the past decade (See Section~\ref{related-works}) to provide immediate, less costly
+proposed during the past decade to provide immediate, less costly
 and efficient solutions to author disambiguation. In this work, our goal
@@
 training data is often not easily available, unsupervised approaches propose
-instead to use domain-specific similarity functions designed for author
-disambiguation
-\citep{malin2005unsupervised,mcrae2006also,song2007efficient,kang2009co,fan2011graph,schulz2014exploiting}.
-These later approaches have the advantage of requiring no hand-labeled data, but
-often do not perform as well as the supervised approaches. To reconcile
-both worlds, semi-supervised
+instead to use domain-specific similarity functions tailored for author
+disambiguation \citep{malin2005unsupervised,mcrae2006also,song2007efficient,
+soler2007separating, kang2009co,fan2011graph,schulz2014exploiting}. These later
+approaches have the advantage of not requiring  hand-labeled data, but often do
+not perform as well as the supervised approaches. To reconcile both worlds,
+semi-supervised methods make use of small, manually verified, clusters of
+publications and/or of high-precision domain-specific rules to build a training
+set of pairs of publications, from which a similarity function is then built
+using supervised learning
+\citep{ferreira2010effective,torvik2009author,levin2012citation}.
+Coincidentally, semi-supervised approaches also allow for the tuning of the
+clustering algorithm when the later is applied to a mixed set of labeled
+and unlabeled publications, e.g., by maximizing some clustering performance
+metric on the known clusters \citep{levin2012citation}.
+
+Because of the lack of a large and publicly available dataset of curated
+clusters of publications, studies on author disambiguation are usually
+constrained to validate their results on manually built datasets of limited
+size and scope (from a few hundreds to a few thousands of papers, with a sparse
+coverage of ambiguous cases), making the true performance of these methods
+often difficult to assess with high confidence. In addition, despite devoted
+efforts to construct them, these datasets are very rarely released publicly,
+making it even more difficult to compare methods on a common benchmark.
+
+In this context, we position the work presented in this paper as a
+semi-supervised  solution for author disambiguation, but with the significant
+advantage of having a very large collection of more than 1 million annotations
+of publications known to be from the same author. In particular, the extent and coverage
+of this data allows us to revisit, validate and nuance previous findings regarding
+supervised learning of similarity functions.
 
@@
 In this work, author disambiguation is cast into a semi-supervised clustering
-problem, as inspired from several previous works \glnote{Add references}.
+problem, as inspired from several previous works described in Section~\ref{related-works}.
 Our algorithm is made of four elements: ...

### 2015-08-06 paper.tex
save
typos

@@
 grouping together scientific publications written by a same person, accounting
-for potential homonyms and/or synonyms. Among solutions to this problem, digital
-libraries are increasingly offering tools for authors to manually curate their
-publications and claim which ones are theirs. Indirectly, these tools allow for
-the inexpensive collection of large annotated training data, which can be
-further leveraged to build an automated disambiguation system capable of
-inferring patterns for identifying publications written by a same
-person.  In this context, we propose a semi-supervised machine learning
-disambiguation solution in the case large and partially annotated databases of
-scientific publications. Using a real-world dataset of 1 million manual
-annotations, we demonstrate how we exploited this data (i) to learn an accurate
-classifier for identifying corefering authors, (ii) to guide the clustering of
-scientific publications by distinct authors in a semi-supervised way and
-finally (iii) to match the resulting clusters with existing profiles.  Our
-analysis on this large training set reveal that...
-\glnote{To be completed with actual results.}
+for potential homonyms and/or synonyms. Among solutions to this problem,
+digital libraries are increasingly offering tools for authors to manually
+curate their publications and claim which ones are theirs. Indirectly, these
+tools allow for the inexpensive collection of large annotated training data,
+which can be further leveraged to build an automated disambiguation system
+capable of inferring patterns for identifying publications written by a same
+person.  Using a real-world dataset of 1 million manual annotations, we propose
+and demonstrate how to exploit this data (i) to learn an accurate classifier
+for identifying corefering authors, (ii) to guide the clustering of scientific
+publications by distinct authors in a semi-supervised way and finally (iii) to
+match the resulting clusters with existing profiles. To the best of our
+knowledge, our analysis is the first to be carried out on data of this size and
+coverage. It reveals that... \glnote{To be completed with actual results.}
 
@@
 disambiguation has become a pressing issue because the accuracy of information
-managed at the level of individuals directly affects the relevance search
+managed at the level of individuals directly affects the relevance search of
 results (e.g., when querying for all publications written by a given author),
@@
 Elsevier, arXiv, Inspire-HEP, ...), thereby univocally solving any disambiguation
-issue. With the large cost of centralized manual authorship control or until
+issue. With the large cost of centralized manual authorship control, or until
 the larger adoption of crowdsourced solutions, the impact of these efforts are
-unfortunately limited by the efficiency, motivation or integrity of their
+unfortunately limited by the efficiency, motivation and integrity of their
 active contributors. Similarly, the success of persistent digital identifier
@@
 way and finally (iii) to match the resulting clusters with existing profiles.
-Our analysis of parameters and features on this large training set reveal
+Our analysis of parameters and features on this large training set reveals
 that... \glnote{To be completed with actual results.}
@@
 \subsection{Blocking}
+
+\glnote{By Mateusz}
+
 % motivation
@@
 
-\subsection{Distance learning}
+\subsection{Learning a similarity function}
 % distance learning as a supervised problem
@@
 
+\glnote{By Mateusz}
+
 % Results and discussion ======================================================
@@
 
-\subsection{Distance learning}
+\subsection{Learning a similarity function}
 % feature engineering

### 2015-08-06 paper.tex
save

@@
 
-The remaining of this report is structured as follows. In Section~\ref{related-works}, ...
+The remaining of this report is structured as follows. In Section~\ref{related-works},
+we first briefly review machine learning solutions for author disambiguation.
+The components of our method are then defined in Section~\ref{methods}
+and its implementation described in Section~\ref{implementation}. Experiments
+are carried out in Section~\ref{experiments}, where we explore and validate
+features for the supervised learning of a similarity function and compare
+strategies for the semi-supervised clustering of publications.
+Finally, conclusions and future works are discussed in Section~\ref{conclusions}.
 
@@
 \citep{smalheiser2009author,ferreira2012brief,levin2012citation}, author
-disambiguation algorithms are usually composed of two components: (i) a
+disambiguation algorithms are usually composed of two main components: (i) a
 similarity function determining whether two publications have been written by a
@@
 semi-supervised  solution for author disambiguation, but with the significant
-advantage of having a very large collection of more than 1 million annotations
+advantage of having a very large collection of more than 1 million crowdsourced annotations
 of publications known to be from the same author. In particular, the extent and coverage
 of this data allows us to revisit, validate and nuance previous findings regarding
-supervised learning of similarity functions.
+supervised learning of similarity functions and to better explore strategies
+for semi-supervised clustering. Additionally, by releasing the data publicly,
+we hope to set a benchmark on further research an author disambiguation
+and related topics can  build upon.
 
@@
 Our algorithm is made of four elements: ...
+
+\glnote{Figure required here (Eamonn)}
 
@@
 % compare cold start solutions
-% talk about impact of small improvements in terms of citations statistics
 

### 2015-08-06 paper.tex
save

@@
 for semi-supervised clustering. Additionally, by releasing the data publicly,
-we hope to set a benchmark on further research an author disambiguation
+we hope to set a benchmark on which further research on author disambiguation
 and related topics can  build upon.
@@
 
+% cite sklearn paper
+% cite sklearn api paper
+
 % Results and discussion ======================================================

### 2015-08-06 paper.tex
save

@@
 \newcommand{\glnote}[1]{\textcolor{red}{[GL: #1]}}
+\newcommand{\msnote}[1]{\textcolor{blue}{[MS: #1]}}
 
@@
 \end{abstract}
+
+\glnote{Note sure if we should talk about matching in this paper?}
 
@@
 this work, the setting extends with the partial knowledge of pairs $(a, s) \in
-{\cal A} \times {\cal S}$, each indicating that signature $s$ is known to
-belong to individual $a$.
+{\cal A} \times {\cal S}$, each indicating that signature $s$ is known with high confidence
+to belong to individual $a$.
 
 In this work, author disambiguation is cast into a semi-supervised clustering
-problem, as inspired from several previous works described in Section~\ref{related-works}.
-Our algorithm is made of four elements: ...
+problem, as inspired from several previous works described in Section~\ref
+{related-works}. Our algorithm is made of four elements: (i) a blocking
+function $b$ whose goal is to rhoughly pre-cluster signatures in order to
+reduce computational complexity; (ii) the construction of a similarity function
+$d$ between signatures using supervised learning algorithms; (iii) the
+semi-supervised clustering of all signatures within a same block, using $d$; (iv) the matching
+of predicted clusters to existing profiles in a database.
 
@@
 % balancing difficult and easy cases
+% sampling pairs from block only
 
@@
 \subsection{Blocking}
+% compare with torvik & smalheiser (2009) who argue that lnfi blocking has recall around 98%
 

### 2015-08-06 paper.tex
save

@@
 {related-works}. Our algorithm is made of four elements: (i) a blocking
-function $b$ whose goal is to rhoughly pre-cluster signatures in order to
+function $b$ whose goal is to rhoughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
 reduce computational complexity; (ii) the construction of a similarity function
-$d$ between signatures using supervised learning algorithms; (iii) the
+$d$ between signatures using supervised learning; (iii) the
 semi-supervised clustering of all signatures within a same block, using $d$; (iv) the matching
@@
 \glnote{Figure required here (Eamonn)}
-
-% Our methodology consists in 4 main components: Distance learning, blocking,
-% semi-supervised clustering and matching. A distance function is learned from a
-% training set of signiture pairs sampled from ground-truth data. Each pair is
-% labeled whether the 2 signatures are for the same real author or not. The
-% learned distance function will then be used for computing the dissimilarity
-% matrix of a block of signatures. A block of signatures is grouping signatures
-% that have in common similar author names, for example same last name. This
-% affinity matrix would be the main input of our semi-supervised clustering
-% algorithm. The predicted clusters of each block will lastly be combined into a
-% final predicted clusters result. Each cluster label represents the predicted
-% single author of the publications in the cluster. Finally, we present a
-% strategy for matching the predicted results with the publications in which
-% their authors were claimed.
 

### 2015-08-07 paper.tex
save

@@
 tools allow for the inexpensive collection of large annotated training data,
-which can be further leveraged to build an automated disambiguation system
+which can be further leveraged to build a complementary automated disambiguation system
 capable of inferring patterns for identifying publications written by a same
-person.  Using a real-world dataset of 1 million manual annotations, we propose
-and demonstrate how to exploit this data (i) to learn an accurate classifier
-for identifying corefering authors, (ii) to guide the clustering of scientific
-publications by distinct authors in a semi-supervised way and finally (iii) to
-match the resulting clusters with existing profiles. To the best of our
-knowledge, our analysis is the first to be carried out on data of this size and
-coverage. It reveals that... \glnote{To be completed with actual results.}
+person.  Building upon more than 1 million crowdsourced annotations, we
+propose a automated author disambiguation solution exploiting this data (i) to learn
+an accurate classifier for identifying corefering authors, (ii) to guide the
+clustering of scientific publications by distinct authors in a semi-supervised
+way and finally (iii) to match the resulting clusters with existing profiles.
+To the best of our knowledge, our analysis is the first to be carried out on
+data of this size and coverage. It reveals that... \glnote{To be completed with
+actual results.}
 
@@
 \glnote{Note sure if we should talk about matching in this paper?}
+\glnote{Insist on the complementarity of having both crowdsourced and automated disambiguation.}
 
@@
 metrics, as studied in \citep{strotmann2012author}) or the relevance of scientific network analysis.
+\glnote{Add more references.}
 
@@
 hiring collaborators or by developing services inviting authors to register
-their publications themselves (e.g., Google Scholar, Inspire-HEP, ...). Recently,
-efforts also started to create persistent digital identifiers assigned to researchers
-(e.g., ORCID, ResearchedID, ...), with the further objective to embed these
-identifiers in the submission workflow of publishers or repositeries (e.g.,
-Elsevier, arXiv, Inspire-HEP, ...), thereby univocally solving any disambiguation
-issue. With the large cost of centralized manual authorship control, or until
-the larger adoption of crowdsourced solutions, the impact of these efforts are
-unfortunately limited by the efficiency, motivation and integrity of their
-active contributors. Similarly, the success of persistent digital identifier
-efforts is conditioned to a large and ubiquituous adoption by both researchers and publishers.
-For these reasons, fully automated machine learning-based methods have been
-proposed during the past decade to provide immediate, less costly
-and efficient solutions to author disambiguation. In this work, our goal
-is to explore and demonstrate how both approaches can coexist and benefit from
-each other.  In particular, we study how labeled data obtained through manual
-curation (either centralized or crowdsourced) can be exploited (i) to learn an
-accurate classifier for identifying corefering authors, (ii) to guide the
-clustering of scientific publications by distinct authors in a semi-supervised
-way and finally (iii) to match the resulting clusters with existing profiles.
-Our analysis of parameters and features on this large training set reveals
-that... \glnote{To be completed with actual results.}
+their publications themselves (e.g., Google Scholar, Inspire-HEP, ...).
+Recently, efforts also started to create persistent digital identifiers
+assigned to researchers (e.g., ORCID, ResearchedID, ...), with the further
+objective to embed these identifiers in the submission workflow of publishers
+or repositeries (e.g., Elsevier, arXiv, Inspire-HEP, ...), thereby univocally
+solving any disambiguation issue. With the large cost of centralized manual
+authorship control, or until the larger adoption of crowdsourced solutions, the
+impact of these efforts are unfortunately limited by the efficiency, motivation
+and integrity of their active contributors. Similarly, the success of
+persistent digital identifier efforts is conditioned to a large and ubiquituous
+adoption by both researchers and publishers. For these reasons, fully automated
+machine learning-based methods have been proposed during the past decade to
+provide immediate, less costly and efficient solutions to author
+disambiguation. In this work, our goal is to explore and demonstrate how both
+approaches can coexist and benefit from each other.  In particular, we study
+how labeled data obtained through manual curation (either centralized or
+crowdsourced) can be exploited (i) to learn an accurate classifier for
+identifying corefering authors, (ii) to guide the clustering of scientific
+publications by distinct authors in a semi-supervised way and finally (iii) to
+match the resulting clusters with existing profiles. Our analysis of parameters
+and features on this large training set reveals that... \glnote{To be completed
+with actual results.} \glnote{Also mention error analysis, suggesting that
+uncertain disambiguation results should be suggested to human curators, thereby
+closing the loop and creating a vertuous circle.}
 
@@
 group publications. Methods relying on supervised learning usually make use of
+a small set of
 hand-labeled pairs of publications identified as being either from the same or
@@
 advantage of having a very large collection of more than 1 million crowdsourced annotations
-of publications known to be from the same author. In particular, the extent and coverage
+of publications whose true authors are identified. In particular, the extent and coverage
 of this data allows us to revisit, validate and nuance previous findings regarding
@@
 \subsection{Learning a similarity function}
+
+\glnote{By Gilles}
+
 % distance learning as a supervised problem
@@
 \subsection{Data}
+
+\glnote{By Gilles}
+
 % source of the data, labels in the data, etc
@@
 \subsection{Evaluation protocol}
+
 % measures (b^3, paired, size of clusters)

### 2015-08-07 paper.tex
save

@@
 person.  Building upon more than 1 million crowdsourced annotations, we
-propose a automated author disambiguation solution exploiting this data (i) to learn
+propose an automated author disambiguation solution exploiting this data (i) to learn
 an accurate classifier for identifying corefering authors, (ii) to guide the

### 2015-08-14 paper.tex
blocking and implementation
Signed-off-by: Mateusz Susik <mateusz.susik@cern.ch>

@@
 \usepackage{algorithm}
-\usepackage{algorithmic}
+\usepackage{algorithmicx}
+\usepackage[noend]{algpseudocode}
 
@@
 \newcommand{\theHalgorithm}{\arabic{algorithm}}
+
+% For "Jabłoński"
+\usepackage[utf8]{inputenc}
+
+% For placing tables in correct place
+\usepackage{placeins}
 
@@
 
-\glnote{By Mateusz}
+If the goal of the algorithm is to disambiguate millions of signatures and the algorithm
+complexity is $\Omega{(n^2)}$ in terms of the number of signatures due to pairwise
+comparisons, the disambiguation might take weeks or months to finish. In order to prevent
+that, we \textit{block} the signatures \citep{fellegi69}. The simplest strategy groups the
+signatures together if they share the same surnames and first given name initial (e.g.,
+"Wang, Z"). As the clustering will be performed only within the
+blocks, such strategy might prevent the further steps of the algorithm from assigning
+correctly two signatures to the same author. We extracted from our training set all pairs
+where the signatures belong to different blocks and the same author after the last name and
+first initial strategy was used. We observed that we can classify majority of these pairs
+into few categories:
+\begin{enumerate}
+  \item Author has multiple surnames and on some of his signatures all the surnames but the
+  last one are contained within given names (e.g., "Martinez Torres, A." and "Torres, A.
+  Martinez").
+  \item Author has multiple surnames and on some of his signatures only the first surname is
+  present (e.g., "Smith-Jones, A." and "Smith, A.")
+  \item Author comes from a country that doesn't use latin alphabet and there are different
+  ways of transcripting his name or his name sometimes contains a typo on the signatures
+  (e.g., "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
+  \item Author sometimes uses on the signature a different name than his first one (e.g.,
+  "Smith, Jack" and "Smith, A.J.")
+  \item Author changed his surname (e.g., because of marrying somebody).
+\end{enumerate}
 
-% motivation
-% last name, first initial
-% phonetics something (dm)
+We tackled first four categories\msnote{Should I mention why not all of them?} and
+implemented a blocking strategy that produces less pairs with signatures from the same
+author but different blocks, and the blocks output by the algorithm are small. Before
+performing blocking, the names on the signatures are \textit{normalized}: the accents are
+removed (e.g., "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and common affixes are removed
+(e.g., "van der Waals, J. D."  $\rightarrow$ "Waals, J. D.")\msnote{Better explanation of
+"affix" needed?}.
+\begin{algorithm}
+  \caption{Blocking using phonetic algorithm}
+  \begin{algorithmic}[1]
+    \newcommand{\myindent}[1]{
+        \newline\makebox[#1cm]{}
+    }
+    \Require{$S$ - set of signatures. The names on the signatures should be
+             \textit{normalized},
+             \myindent{0}$phonetic\_surnames$ - functions that outputs phonetic
+             representation of surnames from \myindent{1.38}given signature,
+             \myindent{0}$given\_names$ - function that ouputs all the given names from
+             given signature.}
+
+    \Function{Phonetic blocking}{$S$}
+      \State $blocks\gets \emptyset$
+      \Comment{Blocks are indexed by a phonetic representation of a surname}
+      \ForAll{$s$ in $S$ with single surname}
+         \myindent{0.92}assign $s$ to the block of $phonetic\_surnames(s)[0]$
+      \EndFor
+      \ForAll{$s$ in $S$ with multiple surnames}
+         \If{block of $phonetic\_surnames(s)[-1]$ contains a signature $t$
+         \myindent{1.84}where $phonetic\_surnames(s)[0] = given\_names(t)[-1]$}
+         \myindent{1.38}assign $s$ to the block of $phonetc\_surnames(s)[-1]$
+         \ElsIf{block of $phonetic\_surnames(s)[0]$ exists}
+          \myindent{1.38}assign $s$ to the block of $phonetic\_surnames(s)[0]$
+         \Else
+          \myindent{1.38}assign $s$ to the block of $phonetic\_surnames(s)[-1]$
+         \EndIf
+      \EndFor
+      \Return $blocks$
+    \EndFunction
+  \end{algorithmic}
+\end{algorithm}
+
+\msnote{Should I explain that if the block does not exist, an empty one is created?}
+
+After this algorithm is finished, all the blocks from the result of the function above can
+be additionally split over the first given name initial.
 
 \subsection{Learning a similarity function}
-
 \glnote{By Gilles}
@@
 \glnote{By Mateusz}
+\msnote{If the matching is not described in this paper, change appearances of "four elements"}
 
-% cite sklearn paper
-% cite sklearn api paper
+Having the algorithm split into four elements, we implemented each of them separately.
+Learning a similarity function and semi-supervised clustering steps required sophisticated
+machine learning algorithms which implementations transcended the scope of this project.
+Thus, we used ready-to-go \textit{Scikit-learn} library \citep{scikit-learn} and
+semi-supervised clustering from \textit{SciPy} \citep{scipy}. In order to keep the code
+maintainable and abstract, we followed practices introduces by \textit{Scikit-learn API}
+\citep{scikit-learn-API}.
+
+Performance-wise, the clustering step appeared to be the bottleneck. We improved the
+algorithmic efficiency by parallelizing it. Having $n$ cores available, one can run the
+semi-supervised clustering for $n$ different blocks in the same moment. In the production
+systems the disambiguation often need not be run on the whole dataset. Once the dataset has
+been disambiguated once, it is possible to avoid rerunning the whole algorithm when the new
+signatures arrive in the digital library. First of all, the similarity function can be
+reused. Moreover, the clustering has to be applied only to the blocks the new signatures are
+contained within.
+
+\msnote{Fill the table with times}
+\msnote{Add times for clustering with phonetic blockings if they prove to be better}
+
+\FloatBarrier
+\begin{table}[H]
+\caption{Time performance (2 GHz per CPU core, 32GB RAM)}
+\centering
+\begin{tabular}{|l|l|}
+  \hline
+  \textbf{algorithm} & \textbf{time}\\
+  \hline
+  blocking 1200000 signatures & dfsf \\
+  \hline
+  learning similarity function on 1000 pairs on reduced set of features & w1k2\\
+  \hline
+  learning similarity function on 1000000 pairs on reduced set of features & w2k2 \\
+  \hline
+  learning similarity function on 1000000 pairs on full set of features & sdfsdf \\
+  \hline
+  clustering 1200000 signatures on reduced set of features using 16 cores & asdsda \\
+  \hline
+  clustering 1200000 signatures on reduced set of features using 1 cores & aasdfs \\
+  \hline
+  clustering 1200000 signatures on full set of features using 16 cores & ssesdf \\
+  \hline
+  matching clusters from 1200000 signatures with the old onews & asdsd \\
+  \hline
+\end{tabular}
+\end{table}
 
@@
 
+\subsection{Base experiment}
+
+The starting point of our analysis is an algorithm that blocks the signatures using the last
+name and first initial strategy, samples the pairs in balanced way, uses gradient boosting
+with all features included for learning the similarity function and clusters using
+semi-supervised hierarchical approach.
+
+\FloatBarrier
+\begin{table}[H]
+\caption{Base experiment evaluation)}
+\centering
+\begin{tabular}{|r|r|l|l|l|}
+  \hline
+  Evaluation & Set & Precision & Recall & F-score \\
+  \hline
+  Pairwise & test & 0.9948 & 0.9738 & 0.9842 \\
+  \hline
+  Pairwise & train & 0.9976 & 0.9747 & 0.986 \\
+  \hline
+  Pairwise & overall & 0.9952 & 0.9739 & 0.9844 \\
+  \hline
+  $B^3$ & test & 0.9901 & 0.976 & 0.983 \\
+  \hline
+  $B^3$ & train & 0.997 & 0.979 & 0.9879 \\
+  \hline
+  $B^3$ & overall & 0.9907 & 0.9761 & 0.9834 \\
+  \hline
+\end{tabular}
+\end{table}
+
 \subsection{Blocking}
+
+Let us introduce a term \textit{blocking limited maximum recall} to describe the highest
+recall that the algorithm can theoretically reach after blocking is done.
+Formally, for the set of signatures ${\cal S}$, blocking function $F: \mathcal{S}
+\rightarrow \mathcal{B}$, where $ \mathcal{B} = \{s_{0}, \ldots{} , s_{N-1}\}$ is a
+partition of $\mathcal{S} $ , the recall function $\mathcal{R}: \mathcal{C}_{gold},
+\mathcal{C}_{predicted} \rightarrow \langle0,1\rangle$ where $\mathcal{C}_{gold}$ is the
+partition of $\mathcal{S}$ where for every author there is a set in $\mathcal{C}_{gold}$
+that contains only all the signatures of this author, $\mathcal{C}_{predicted}$ is the
+partition of $\mathcal{S}$ output by the algorithm, and $\mathcal{Q} = \{\cup_{i=0}^{N-1}
+q_i $ : $\forall_{i \in \langle0,N-1\rangle} q_i$ is a partition of $s_i$\}. Then
+\textit{blocking limited maximum recall} is defined as $\max_{q \in \mathcal{Q}}
+\mathcal{R}(\mathcal{C}_{gold}, q)$. For sanely defined recall functions, such as $B^{3}$
+recall or \textit{pairwise} recall \msnote{Further explanation needed, why it is
+equivalent?}, it is equivalent to $\mathcal{R}(\mathcal{C}_{gold}, \mathcal{B})$.
+
+The \textit{blocking limited maximum recall} for the last name and first initial blocking
+and $B^3$ scoring equals 0.9827. Comparing it to the $B^3$ recall of the base experiment,
+one can see that a huge part of errors comes from the blocking step which forbids some of
+the pairs to be merged together. To prevent that, we tried the phonetic blocking algorithm
+using three different phonetic algorithms: Double Metaphone \citep{doublemetaphone}, NYSIIS
+\citep{nysiis} and Soundex \citep{Soundex}. As Double Metaphone can return two results for a
+string, we always discarded the second one when we used this algorithm.
+
+\FloatBarrier
+\begin{table}[H]
+\caption{Blocking limited maximum recalls (BLMR) on the whole dataset without splitting over
+the first given name initial}
+\centering
+\begin{tabular}{|r|l|l|}
+  \hline
+  blocking function & BLMR with $B^{3}$ recall & BLMR with pairwise recall \\
+  \hline
+  last name and first initial & 0.9827 & 0.9776 \\
+  \hline
+  phonetic using double metaphone & 0.9967 & 0.9953 \\
+  \hline
+  phonetic using nysiis & 0.9961 & 0.9951 \\
+  \hline
+  phonetic using soundex & 0.9966 & 0.9953 \\
+  \hline
+\end{tabular}
+\end{table}
+
+\msnote{Mention two new features for this experiments, other than that everything is the
+same as in the base experiment}
+
+\FloatBarrier
+\begin{table}[H]
+\caption{Phonetic algorithm performance}
+\centering
+\begin{tabular}{|r|r|r|l|l|l|}
+  \hline
+  Phonetic Algorithm & Split over initial & Evaluation & Precision & Recall & F-score \\
+  \hline
+  Double Metaphone & yes & pairwise & 0.9934 & 0.982 & 0.9876 \\
+  \hline
+  Double Metaphone & yes & $B^3$ & 0.9867 & 0.983 & 0.9848 \\
+  \hline
+  Double Metaphone & no & pairwise & - & - & - \\
+  \hline
+  Double Metaphone & no & $B^3$ & - & - & - \\
+  \hline
+  NYSIIS & yes & pairwise & 0.9942 & 0.9818 & 0.9879 \\
+  \hline
+  NYSIIS & yes & $B^3$ & 0.9884 & 0.9828 & 0.9856 \\
+  \hline
+  NYSIIS & no & pairwise & - & - & - \\
+  \hline
+  NYSIIS & no & $B^3$ & - & - & - \\
+  \hline
+  Soundex & yes & pairwise & - & - & - \\
+  \hline
+  Soundex & yes & $B^3$ & - & - & - \\
+  \hline
+  Soundex & no & pairwise & - & - & - \\
+  \hline
+  Soundex & no & $B^3$ & - & - & - \\
+  \hline
+\end{tabular}
+\end{table}
+
+\msnote{Fill the table}
+
 % compare with torvik & smalheiser (2009) who argue that lnfi blocking has recall around 98%
+% MS - recall for lnfi (blocking only) 0.9776, lnfi (whole algorithm) 0.9739,
+% MS - all three results use pairwise scoring
 

### 2015-08-17 paper.tex
remove mentions of matching

@@
 tools allow for the inexpensive collection of large annotated training data,
-which can be further leveraged to build a complementary automated disambiguation system
-capable of inferring patterns for identifying publications written by a same
-person.  Building upon more than 1 million crowdsourced annotations, we
-propose an automated author disambiguation solution exploiting this data (i) to learn
-an accurate classifier for identifying corefering authors, (ii) to guide the
-clustering of scientific publications by distinct authors in a semi-supervised
-way and finally (iii) to match the resulting clusters with existing profiles.
-To the best of our knowledge, our analysis is the first to be carried out on
-data of this size and coverage. It reveals that... \glnote{To be completed with
-actual results.}
+which can be further leveraged to build a complementary automated
+disambiguation system capable of inferring patterns for identifying
+publications written by a same person.  Building upon more than 1 million
+crowdsourced annotations, we propose an automated author disambiguation
+solution exploiting this data (i) to learn an accurate classifier for
+identifying corefering authors and (ii) to guide the clustering of scientific
+publications by distinct authors in a semi-supervised way. To the best of our
+knowledge, our analysis is the first to be carried out on data of this size and
+coverage. It reveals that... \glnote{To be completed with actual results.}
 
@@
 
-\glnote{Note sure if we should talk about matching in this paper?}
 \glnote{Insist on the complementarity of having both crowdsourced and automated disambiguation.}
@@
 crowdsourced) can be exploited (i) to learn an accurate classifier for
-identifying corefering authors, (ii) to guide the clustering of scientific
-publications by distinct authors in a semi-supervised way and finally (iii) to
-match the resulting clusters with existing profiles. Our analysis of parameters
+identifying corefering authors and (ii) to guide the clustering of scientific
+publications by distinct authors in a semi-supervised way. Our analysis of parameters
 and features on this large training set reveals that... \glnote{To be completed
@@
 problem, as inspired from several previous works described in Section~\ref
-{related-works}. Our algorithm is made of four elements: (i) a blocking
+{related-works}. Our algorithm is made of three elements: (i) a blocking
 function $b$ whose goal is to rhoughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
@@
 $d$ between signatures using supervised learning; (iii) the
-semi-supervised clustering of all signatures within a same block, using $d$; (iv) the matching
-of predicted clusters to existing profiles in a database.
+semi-supervised clustering of all signatures within a same block, using $d$ as a pseudo distance metric.
 
@@
 
-\subsection{Matching}
+% \subsection{Matching}
 % general description in a real system
+% GL: out of scope, let us mention that in Conclusions instead
 

### 2015-08-17 paper.tex
example

@@
 \usepackage{color}
+\usepackage{amsmath}
 
@@
 information identifying one of the authors of $p$ (e.g., the author name, his
-affiliation, along with any other metadata that can be derived from $p$). Let us
+affiliation, along with any other metadata that can be derived from $p$, as illustrated in Figure~\ref{fig:signature}). Let us
 denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
-signatures that can be extracted from all publications in ${\cal P}$. In this
+signatures that can be extracted from all publications in ${\cal P}$ and
+by $S=|{\cal S}|$ the total number of signatures.
+
+\begin{figure}
+\label{fig:signature}
+\begin{tabular}{ l l l }
+  $s:$ & Title & Lorem ipsum dolor sit amet, consectetur adipiscing elit \\
+  & Author & Doe, John \\
+  & Affiliation & University of Foo \\
+  & Co-authors & Smith, John; Chen, Wang\\
+  & Year & 2015\\
+\end{tabular}
+
+\caption{An example of signature $s$ for "Doe, John". A \textit{signature} is
+defined as unique piece of information identifying an author on a publication,
+along with any other metadata that can be derived from it, such as publication
+title, co-authors or date of publication.}
+\end{figure}
+
+In this
 framework, author disambiguation can be stated as the problem of
@@
 
-\glnote{By Mateusz}
-\msnote{If the matching is not described in this paper, change appearances of "four elements"}
-
-Having the algorithm split into four elements, we implemented each of them separately.
+Having the algorithm split into three elements, we implemented each of them separately.
 Learning a similarity function and semi-supervised clustering steps required sophisticated
@@
   clustering 1200000 signatures on full set of features using 16 cores & ssesdf \\
-  \hline
-  matching clusters from 1200000 signatures with the old onews & asdsd \\
   \hline

### 2015-08-18 paper.tex
blocking (rewrite, wip)

@@
 
-In this work, author disambiguation is cast into a semi-supervised clustering
-problem, as inspired from several previous works described in Section~\ref
-{related-works}. Our algorithm is made of three elements: (i) a blocking
-function $b$ whose goal is to rhoughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
+As inspired from several previous works described in Section~\ref{related-works},
+we cast in this work author disambiguation into a semi-supervised clustering
+problem.  Our algorithm is made of three parts: (i) a blocking
+scheme whose goal is to rhoughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
 reduce computational complexity; (ii) the construction of a similarity function
@@
 \subsection{Blocking}
+\label{methods:blocking}
+
+As in previous works, the first part of our algorithm consists in grouping
+signatures ${\cal S}$ into disjoint subsets ${\cal S}_{b_0}, ..., {\cal
+S}_{b_{K-1}}$, or \textit{blocks} \citep{fellegi69}, and then to carry out
+author disambiguation independently on each one of these blocks. In doing so,
+computational complexity of clustering (see Section~\ref{methods:clustering})
+typically reduces from $O(S^2)$ to $O(\sum_b S_b^2)$, which becomes much more
+tractable as the number of signatures increases. Since disambiguation is
+performed independently per block, a good blocking strategy should also be
+designed such that signatures from the same author are all mapped to the same
+block, otherwise directly preventing their correct clustering in later stages. As a
+result, blocking should balance between reduced complexity and maximum recall.
+
+The simplest and most common strategy for blocking \glnote{add references}
+groups signatures together if they share the same surname(s) and the same first
+given name initial (e.g., "Doe, J").
+
+\vspace{3cm}
 
@@
 \subsection{Semi-supervised clustering}
+\label{methods:clustering}
+
 % hierarchical clustering

### 2015-08-18 paper.tex
blocking

@@
 groups signatures together if they share the same surname(s) and the same first
-given name initial (e.g., "Doe, J").
+given name initial (e.g., "Doe, J"). Despite satisfying performance, such
+a simple strategy fails in several cases, as listed below for
+pairs of signatures that should be clustered together but that are put into distinct
+blocks:
 
-\vspace{3cm}
+\begin{enumerate}
+  \item There are different
+  ways of transcripting an author name or some of signatures contain a typo
+  (e.g., "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
 
-If the goal of the algorithm is to disambiguate millions of signatures and the algorithm
-complexity is $\Omega{(n^2)}$ in terms of the number of signatures due to pairwise
-comparisons, the disambiguation might take weeks or months to finish. In order to prevent
-that, we \textit{block} the signatures \citep{fellegi69}. The simplest strategy groups the
-signatures together if they share the same surnames and first given name initial (e.g.,
-"Wang, Z"). As the clustering will be performed only within the
-blocks, such strategy might prevent the further steps of the algorithm from assigning
-correctly two signatures to the same author. We extracted from our training set all pairs
-where the signatures belong to different blocks and the same author after the last name and
-first initial strategy was used. We observed that we can classify majority of these pairs
-into few categories:
-\begin{enumerate}
-  \item Author has multiple surnames and on some of his signatures all the surnames but the
+  \item An author has multiple surnames and, on some of his signatures, all the surnames but the
   last one are contained within given names (e.g., "Martinez Torres, A." and "Torres, A.
   Martinez").
-  \item Author has multiple surnames and on some of his signatures only the first surname is
+
+  \item An author has multiple surnames and, on some of his signatures, only the first surname is
   present (e.g., "Smith-Jones, A." and "Smith, A.")
-  \item Author comes from a country that doesn't use latin alphabet and there are different
-  ways of transcripting his name or his name sometimes contains a typo on the signatures
-  (e.g., "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
-  \item Author sometimes uses on the signature a different name than his first one (e.g.,
-  "Smith, Jack" and "Smith, A.J.")
-  \item Author changed his surname (e.g., because of marrying somebody).
+
+  \item An author as multiple given names and they are not always mentioned on his signatures (e.g.,
+  "Smith, Jack" and "Smith, A. J.")
+
+  \item An author changed his surname (e.g., because of marrying somebody).
 \end{enumerate}
 
-We tackled first four categories\msnote{Should I mention why not all of them?} and
-implemented a blocking strategy that produces less pairs with signatures from the same
-author but different blocks, and the blocks output by the algorithm are small. Before
-performing blocking, the names on the signatures are \textit{normalized}: the accents are
-removed (e.g., "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and common affixes are removed
-(e.g., "van der Waals, J. D."  $\rightarrow$ "Waals, J. D.")\msnote{Better explanation of
-"affix" needed?}.
-\begin{algorithm}
-  \caption{Blocking using phonetic algorithm}
-  \begin{algorithmic}[1]
-    \newcommand{\myindent}[1]{
-        \newline\makebox[#1cm]{}
-    }
-    \Require{$S$ - set of signatures. The names on the signatures should be
-             \textit{normalized},
-             \myindent{0}$phonetic\_surnames$ - functions that outputs phonetic
-             representation of surnames from \myindent{1.38}given signature,
-             \myindent{0}$given\_names$ - function that ouputs all the given names from
-             given signature.}
+To account for these issues we propose instead to block signatures based on the
+phonetic representation of the normalized surname. Normalization consists in
+stripping accents (e.g., "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
+affixes that inconsistenly appear in signatures (e.g., "van der Waals, J. D."
+$\rightarrow$ "Waals, J. D."), while phonetization is based either on the
+Double Metaphone \citep{doublemetaphone}, the NYSIIS \citep{nysiis} or the
+Soundex \citep{Soundex} algorithms. Together, these processing steps allow to
+group most name variants of a same person in the same block while not
+significantly increasing computational complexity, thereby solving case 1.
 
-    \Function{Phonetic blocking}{$S$}
-      \State $blocks\gets \emptyset$
-      \Comment{Blocks are indexed by a phonetic representation of a surname}
-      \ForAll{$s$ in $S$ with single surname}
-         \myindent{0.92}assign $s$ to the block of $phonetic\_surnames(s)[0]$
-      \EndFor
-      \ForAll{$s$ in $S$ with multiple surnames}
-         \If{block of $phonetic\_surnames(s)[-1]$ contains a signature $t$
-         \myindent{1.84}where $phonetic\_surnames(s)[0] = given\_names(t)[-1]$}
-         \myindent{1.38}assign $s$ to the block of $phonetc\_surnames(s)[-1]$
-         \ElsIf{block of $phonetic\_surnames(s)[0]$ exists}
-          \myindent{1.38}assign $s$ to the block of $phonetic\_surnames(s)[0]$
-         \Else
-          \myindent{1.38}assign $s$ to the block of $phonetic\_surnames(s)[-1]$
-         \EndIf
-      \EndFor
-      \Return $blocks$
-    \EndFunction
-  \end{algorithmic}
-\end{algorithm}
+In the case of multiple surnames (cases 2 and 3), we further propose to block
+signatures in two phases. In the first phase, all the signatures with  one
+surname are clustered together. Every different surname token creates a new
+block. In the second phase, the signatures  with multiple surnames are compared
+with the blocks for the first and last surname.  If the first surnames of an
+author were already used as the last given names on some of the signatures, the
+new signature is assigned to the block of the last surname (case 2). Otherwise,
+the signature is assigned to the block of the first surname (case 3). Finally,
+to prevent the creation of too large blocks, signatures are further divided
+along their first given name initial.  Cases 4 and 5 are therefore not
+explicitly handled.
 
-\msnote{Should I explain that if the block does not exist, an empty one is created?}
-
-After this algorithm is finished, all the blocks from the result of the function above can
-be additionally split over the first given name initial.
+\glnote{I am not sure we need an explicit algorithm, but adding a few examples would help.}
 
 \subsection{Learning a similarity function}
+\label{methods:similarity}
 \glnote{By Gilles}
@@
 \label{methods:clustering}
+\glnote{By Gilles}
 
@@
 \label{implementation}
+
+\glnote{To proofread / improve}
 
@@
 
+\glnote{By Gilles}
+
 % measures (b^3, paired, size of clusters)
@@
 \subsection{Base experiment}
+
+\glnote{To proofread / improve}
 
@@
 \subsection{Blocking}
+
+\glnote{To proofread / improve}
 

### 2015-08-18 paper.tex
save

@@
   \item There are different
-  ways of transcripting an author name or some of signatures contain a typo
+  ways of transcripting an author name or signatures contain a typo
   (e.g., "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
 
-  \item An author has multiple surnames and, on some of his signatures, all the surnames but the
+  \item An author has multiple surnames and, on some signatures, all the surnames but the
   last one are contained within given names (e.g., "Martinez Torres, A." and "Torres, A.
@@
 
-  \item An author has multiple surnames and, on some of his signatures, only the first surname is
+  \item An author has multiple surnames and, on some signatures, only the first surname is
   present (e.g., "Smith-Jones, A." and "Smith, A.")
 
-  \item An author as multiple given names and they are not always mentioned on his signatures (e.g.,
+  \item An author as multiple given names and they are not always all mentioned (e.g.,
   "Smith, Jack" and "Smith, A. J.")
@@
 to prevent the creation of too large blocks, signatures are further divided
-along their first given name initial.  Cases 4 and 5 are therefore not
+along their first given name initial.  Cases 4 and 5 are not
 explicitly handled.

### 2015-08-18 paper.tex
implementation

@@
 
-\glnote{To proofread / improve}
+As part of this work, we developed a stand-alone application for author
+disambiguation, publicly available
+online\footnote{\url{https://github.com/inveniosoftware/beard}} for free reuse
+or study.  Our implementation builds upon the Python scientific stack, making
+use of the Scikit-Learn library \citep{scikitlearn} for the supervised learning
+of the similarity function and of SciPy \citep{scipy} for clustering. All
+components of the disambiguation pipeline have been designed to follow the
+Scikit-Learn API \citep{scikitlearnAPI}, making them easy to maintain,
+understand and reuse.
 
-Having the algorithm split into three elements, we implemented each of them separately.
-Learning a similarity function and semi-supervised clustering steps required sophisticated
-machine learning algorithms which implementations transcended the scope of this project.
-Thus, we used ready-to-go \textit{Scikit-learn} library \citep{scikit-learn} and
-semi-supervised clustering from \textit{SciPy} \citep{scipy}. In order to keep the code
-maintainable and abstract, we followed practices introduces by \textit{Scikit-learn API}
-\citep{scikit-learn-API}.
+\glnote{Not sure we should talk about parallelization?}
+\glnote{Mention (future) deployment in Inspire?}
 
-Performance-wise, the clustering step appeared to be the bottleneck. We improved the
-algorithmic efficiency by parallelizing it. Having $n$ cores available, one can run the
-semi-supervised clustering for $n$ different blocks in the same moment. In the production
-systems the disambiguation often need not be run on the whole dataset. Once the dataset has
-been disambiguated once, it is possible to avoid rerunning the whole algorithm when the new
-signatures arrive in the digital library. First of all, the similarity function can be
-reused. Moreover, the clustering has to be applied only to the blocks the new signatures are
-contained within.
-
-\msnote{Fill the table with times}
-\msnote{Add times for clustering with phonetic blockings if they prove to be better}
-
-\FloatBarrier
-\begin{table}[H]
-\caption{Time performance (2 GHz per CPU core, 32GB RAM)}
-\centering
-\begin{tabular}{|l|l|}
-  \hline
-  \textbf{algorithm} & \textbf{time}\\
-  \hline
-  blocking 1200000 signatures & dfsf \\
-  \hline
-  learning similarity function on 1000 pairs on reduced set of features & w1k2\\
-  \hline
-  learning similarity function on 1000000 pairs on reduced set of features & w2k2 \\
-  \hline
-  learning similarity function on 1000000 pairs on full set of features & sdfsdf \\
-  \hline
-  clustering 1200000 signatures on reduced set of features using 16 cores & asdsda \\
-  \hline
-  clustering 1200000 signatures on reduced set of features using 1 cores & aasdfs \\
-  \hline
-  clustering 1200000 signatures on full set of features using 16 cores & ssesdf \\
-  \hline
-\end{tabular}
-\end{table}
+% Performance-wise, the clustering step appeared to be the bottleneck. We improved the
+% algorithmic efficiency by parallelizing it. Having $n$ cores available, one can run the
+% semi-supervised clustering for $n$ different blocks in the same moment. In the production
+% systems the disambiguation often need not be run on the whole dataset. Once the dataset has
+% been disambiguated once, it is possible to avoid rerunning the whole algorithm when the new
+% signatures arrive in the digital library. First of all, the similarity function can be
+% reused. Moreover, the clustering has to be applied only to the blocks the new signatures are
+% contained within.
 
@@
 
-\glnote{To proofread / improve}
+\glnote{To review}
 

### 2015-08-19 paper.tex
save

@@
 
-As in previous works, the first part of our algorithm consists in grouping
+As in previous works, the first part of our algorithm consists in dividing
 signatures ${\cal S}$ into disjoint subsets ${\cal S}_{b_0}, ..., {\cal
@@
 tractable as the number of signatures increases. Since disambiguation is
-performed independently per block, a good blocking strategy should also be
+performed independently per block, a good blocking strategy should ideally be
 designed such that signatures from the same author are all mapped to the same
@@
 % distance learning as a supervised problem
+% describe all features
 % balancing difficult and easy cases
@@
 use of the Scikit-Learn library \citep{scikitlearn} for the supervised learning
-of the similarity function and of SciPy \citep{scipy} for clustering. All
+of a similarity function and of SciPy \citep{scipy} for clustering. All
 components of the disambiguation pipeline have been designed to follow the

### 2015-08-19 paper.tex
supervised learning

@@
 \usepackage[utf8]{inputenc}
-
-% For placing tables in correct place
-\usepackage{placeins}
 
@@
 are carried out in Section~\ref{experiments}, where we explore and validate
-features for the supervised learning of a similarity function and compare
+features for the supervised learning of a linkage function and compare
 strategies for the semi-supervised clustering of publications.
@@
 disambiguation algorithms are usually composed of two main components: (i) a
-similarity function determining whether two publications have been written by a
+linkage function determining whether two publications have been written by a
 same author and (ii) a clustering algorithm producing clusters of publications
@@
 several axes, depending on the type and amount of data available, the way the
-similarity function is learned or defined, or the clustering procedure used to
+linkage function is learned or defined, or the clustering procedure used to
 group publications. Methods relying on supervised learning usually make use of
@@
 hand-labeled pairs of publications identified as being either from the same or
-from different authors for learning automatically a similarity function between
+from different authors for learning automatically a linkage function between
 publications \citep{han2004two,huang2006efficient,
@@
 training data is often not easily available, unsupervised approaches propose
-instead to use domain-specific similarity functions tailored for author
+instead to use domain-specific linkage functions tailored for author
 disambiguation \citep{malin2005unsupervised,mcrae2006also,song2007efficient,
@@
 publications and/or of high-precision domain-specific rules to build a training
-set of pairs of publications, from which a similarity function is then built
+set of pairs of publications, from which a linakge function is then built
 using supervised learning
@@
 of this data allows us to revisit, validate and nuance previous findings regarding
-supervised learning of similarity functions and to better explore strategies
+supervised learning of linkage functions and to better explore strategies
 for semi-supervised clustering. Additionally, by releasing the data publicly,
@@
 scheme whose goal is to rhoughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
-reduce computational complexity; (ii) the construction of a similarity function
+reduce computational complexity; (ii) the construction of a linkage function
 $d$ between signatures using supervised learning; (iii) the
@@
 
-\subsection{Learning a similarity function}
-\label{methods:similarity}
-\glnote{By Gilles}
+\subsection{Linkage function}
+\label{methods:linkage}
+
+\textit{Supervised classification.} The second part of the algorithm is the
+automatic construction of a pair-wise linkage function between signatures, for
+later reuse during clustering to group all signatures from a same author.
+Formally, the goal is to build a function $d: {\cal S} \times {\cal S} \mapsto
+[0, 1]$, such that $d(s_1, s_2)$ tends to $0$ if both signatures $s_1$ and
+$s_2$ belong to the same author, and $1$ otherwise.
+
+As in previous works on author disambiguation, we cast this problem as a
+classification task, where inputs are pairs of signatures and outputs are
+classes $0$ (same authors) and $1$ (distinct authors).
+
+\textit{Features engineering.}
+
+\textit{Building a training set.}
+% cite https://hpi.de/naumann/projects/repeatability/datasets/dblp-dataset.html
 
@@
 use of the Scikit-Learn library \citep{scikitlearn} for the supervised learning
-of a similarity function and of SciPy \citep{scipy} for clustering. All
+of a linkage function and of SciPy \citep{scipy} for clustering. All
 components of the disambiguation pipeline have been designed to follow the
@@
 
-\FloatBarrier
 \begin{table}[H]
@@
 
-\subsection{Learning a similarity function}
+\subsection{Learning a linkage function}
 % feature engineering

### 2015-08-19 paper.tex
save

@@
 \usepackage{color}
+
+% Maths
 \usepackage{amsmath}
+\usepackage{amsfonts}
 
@@
 training data is often not easily available, unsupervised approaches propose
-instead to use domain-specific linkage functions tailored for author
+instead to use domain-specific, often manually designed, linkage functions tailored for author
 disambiguation \citep{malin2005unsupervised,mcrae2006also,song2007efficient,
@@
 automatic construction of a pair-wise linkage function between signatures, for
-later reuse during clustering to group all signatures from a same author.
+later use during clustering to group all signatures from a same author.
 Formally, the goal is to build a function $d: {\cal S} \times {\cal S} \mapsto
@@
 
-\textit{Features engineering.}
+\textit{Input features.} In most cases, supervised learning algorithms assume
+the input space ${\cal X}$ to be numeric (e.g., $\mathbb{R}^p$), making them
+not directly applicable to structured input spaces such as ${\cal S} \times
+{\cal S}$. Following previous works, pairs of signatures $(s_1, s_2)$ are
+transformed to vectors $v \in \mathbb{R}^p$ by building so-called similarity
+profiles \citep{treeratpituk2009disambiguating} on which supervised learning is
+then carried on. In this work, we design and evaluate 15 standard input features based
+on the comparison of signature fields, as reported in Table~\ref{table:features}.
+As an illustrative example, the \textit{Full name} feature corresponds to ...
+
+\begin{table}
+\caption{Input features}
+\label{table:features}
+\centering
+\begin{tabular}{|l|l|}
+  \hline
+  \textbf{Feature} & \textbf{Comparator}\\
+  \hline
+  \hline
+  Full name & Cosine similarity of TF-IDF\\
+  Given names & Cosine similarity of TF-IDF\\
+  First given name & Jaro-Winkler distance\\
+  Second given name & Jaro-Winkler distance\\
+  Given name initial & Equality\\
+  Affiliation & Cosine similarity of TF-IDF\\
+  Co-authors & Cosine similarity of TF-IDF\\
+  Title & Cosine similarity of TF-IDF\\
+  Journal & Cosine similarity of TF-IDF\\
+  Abstract & Cosine similarity of TF-IDF\\
+  Keywords & Cosine similarity of TF-IDF\\
+  Collaborations & Cosine similarity of TF-IDF\\
+  References & Cosine similarity of TF-IDF\\
+  Subject & Cosine similarity of TF-IDF\\
+  Year difference & Absolute difference\\
+  \hline
+\end{tabular}
+\end{table}
+
+% ethnicity features
 

### 2015-08-19 paper.tex
save

@@
 [0, 1]$, such that $d(s_1, s_2)$ tends to $0$ if both signatures $s_1$ and
-$s_2$ belong to the same author, and $1$ otherwise.
-
-As in previous works on author disambiguation, we cast this problem as a
-classification task, where inputs are pairs of signatures and outputs are
-classes $0$ (same authors) and $1$ (distinct authors).
+$s_2$ belong to the same author, and $1$ otherwise. Coincidentally, this
+problem can be cast as a standard supervised classification task, where inputs
+are pairs of signatures and outputs are classes $0$ (same authors) and $1$
+(distinct authors).
 
@@
 not directly applicable to structured input spaces such as ${\cal S} \times
-{\cal S}$. Following previous works, pairs of signatures $(s_1, s_2)$ are
-transformed to vectors $v \in \mathbb{R}^p$ by building so-called similarity
-profiles \citep{treeratpituk2009disambiguating} on which supervised learning is
-then carried on. In this work, we design and evaluate 15 standard input features based
-on the comparison of signature fields, as reported in Table~\ref{table:features}.
-As an illustrative example, the \textit{Full name} feature corresponds to ...
+{\cal S}$. Following previous works \glnote{add references}, pairs of
+signatures $(s_1, s_2)$ are therefore first transformed to vectors $v \in
+\mathbb{R}^p$ by building so-called similarity profiles
+\citep{treeratpituk2009disambiguating}, and on which supervised learning is
+then carried on. In this work, we design and evaluate 15 standard input
+features based on the comparison of signature fields, as reported in the first
+half of Table~\ref{table:features}. As an illustrative example, the
+\textit{Full name} feature corresponds to the similarity between the (full)
+author name fields of the two signatures, as measured using the cosine
+similarity between their respective TF-IDF vector representations as
+comparator. Similarly, the \textit{Year difference} feature measures the
+absolute difference between the publication date of the articles to which the
+two signatures respectively belong.
+
+Observing that author names from different cultures or origins are likely to be
+disambiguated using different strategies (e.g., pairs of signatures with French
+author names versus pairs of signatures with Chinese author names), and as
+corroborated in \citep{treeratpituk2012name} or \citep{chin2014effective}, we
+propose to complement our feature set with 7 additional new features, each
+evaluating the degree of belonging of both signatures to several ethnic groups,
+as reported in the second half of Table~\ref{table:features}. More
+specifically, using census data extracted from \citep{rugglesintegrated}, we
+built a logistic regression classifier for mapping the TF-IDF representation of
+an author name to one of the 7 ethnic groups reported in that dataset. Given a
+pair of signatures $(s_1, s_2)$, the proposed ethnicity features are each
+computed as the estimated probability of $s_1$ to belong to the respective
+ethnic group, multiplied by the estimated probability of $s_2$ to belong to the
+same group. In doing so, the expectation is for the linkage function to become
+sensitive to the actual origin of the authors depending on the values of these
+features.
 
 \begin{table}
-\caption{Input features}
+\caption{Input features for learning a linkage function}
 \label{table:features}
@@
   \hline
+  White & Product of estimated probabilities\\
+  Black & Product of estimated probabilities\\
+  American Indian or Alaska Native & Product of estimated probabilities\\
+  Chinese & Product of estimated probabilities\\
+  Japanese & Product of estimated probabilities\\
+  Other Asian or Pacific Islander & Product of estimated probabilities\\
+  Others & Product of estimated probabilities\\
+  \hline
 \end{tabular}
 \end{table}
-
-% ethnicity features
 

### 2015-08-19 paper.tex
save

@@
 personal names may be traditionally less diverse (leading to homonym issues) or
-for which transliteration to latin characters may not be unique (leading to
+for which transliteration to Latin characters may not be unique (leading to
 synonym issues). With the fast growth of the scientific literature, author
@@
 objective to embed these identifiers in the submission workflow of publishers
-or repositeries (e.g., Elsevier, arXiv, Inspire-HEP, ...), thereby univocally
+or repositories (e.g., Elsevier, arXiv, Inspire-HEP, ...), thereby univocally
 solving any disambiguation issue. With the large cost of centralized manual
@@
 and integrity of their active contributors. Similarly, the success of
-persistent digital identifier efforts is conditioned to a large and ubiquituous
+persistent digital identifier efforts is conditioned to a large and ubiquitous
 adoption by both researchers and publishers. For these reasons, fully automated
@@
 uncertain disambiguation results should be suggested to human curators, thereby
-closing the loop and creating a vertuous circle.}
+closing the loop and creating a virtuous circle.}
 
@@
 same author and (ii) a clustering algorithm producing clusters of publications
-assumed to be written by a same author. Approaches can be inventorized along
+assumed to be written by a same author. Approaches can be inventoried along
 several axes, depending on the type and amount of data available, the way the
@@
 publications and/or of high-precision domain-specific rules to build a training
-set of pairs of publications, from which a linakge function is then built
+set of pairs of publications, from which a linkage function is then built
 using supervised learning
@@
 problem.  Our algorithm is made of three parts: (i) a blocking
-scheme whose goal is to rhoughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
+scheme whose goal is to roughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
 reduce computational complexity; (ii) the construction of a linkage function
@@
 stripping accents (e.g., "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
-affixes that inconsistenly appear in signatures (e.g., "van der Waals, J. D."
+affixes that inconsistently appear in signatures (e.g., "van der Waals, J. D."
 $\rightarrow$ "Waals, J. D."), while phonetization is based either on the
@@
 {\cal S}$. Following previous works \glnote{add references}, pairs of
-signatures $(s_1, s_2)$ are therefore first transformed to vectors $v \in
+signatures $(s_1, s_2)$ are first transformed to vectors $v \in
 \mathbb{R}^p$ by building so-called similarity profiles
@@
 specifically, using census data extracted from \citep{rugglesintegrated}, we
-built a logistic regression classifier for mapping the TF-IDF representation of
+build a logistic regression classifier for mapping the TF-IDF representation of
 an author name to one of the 7 ethnic groups reported in that dataset. Given a
@@
   \hline
-  \textbf{Feature} & \textbf{Comparator}\\
+  \textbf{Feature} & \textbf{Combination operator}\\
   \hline

### 2015-08-19 paper.tex
save

@@
 
-\glnote{Insist on the complementarity of having both crowdsourced and automated disambiguation.}
-
 % Introduction ==================================================================
@@
 publications by distinct authors in a semi-supervised way. Our analysis of parameters
-and features on this large training set reveals that... \glnote{To be completed
-with actual results.} \glnote{Also mention error analysis, suggesting that
+and features on this large training set reveals that...
+
+\glnote{To be completed with actual results.}\\
+\glnote{Also mention error analysis, suggesting that
 uncertain disambiguation results should be suggested to human curators, thereby
-closing the loop and creating a virtuous circle.}
+closing the loop and creating a virtuous circle.}\\
+\glnote{New idea: phonetization in blocking}\\
+\glnote{New idea: ethnicity features}
 
@@
 {\cal S}$. Following previous works \glnote{add references}, pairs of
-signatures $(s_1, s_2)$ are first transformed to vectors $v \in
-\mathbb{R}^p$ by building so-called similarity profiles
+signatures $(s_1, s_2)$ are first transformed to vectors $v \in \mathbb{R}^p$
+by building so-called similarity profiles
 \citep{treeratpituk2009disambiguating}, and on which supervised learning is
@@
 \textit{Full name} feature corresponds to the similarity between the (full)
-author name fields of the two signatures, as measured using the cosine
-similarity between their respective TF-IDF vector representations as
-comparator. Similarly, the \textit{Year difference} feature measures the
+author name fields of the two signatures, as measured using as combination
+operator the cosine similarity between their respective TF-IDF vector
+representations. Similarly, the \textit{Year difference} feature measures the
 absolute difference between the publication date of the articles to which the
@@
 \end{table}
+
+\glnote{Add a few examples of transformed pairs?}
 

### 2015-08-20 paper.tex
save

@@
 are pairs of signatures and outputs are classes $0$ (same authors) and $1$
-(distinct authors).
+(distinct authors). In this work, we evaluate Random Forests \citep{breiman2001random},
+Gradient Boosted Regression Trees \citep{friedman2001greedy} and Logistic Regression \glnote{add ref} as classifiers.
 
@@
 author name fields of the two signatures, as measured using as combination
-operator the cosine similarity between their respective TF-IDF vector
-representations. Similarly, the \textit{Year difference} feature measures the
-absolute difference between the publication date of the articles to which the
-two signatures respectively belong.
+operator the cosine similarity between their respective $(n,m)$-TF-IDF vector
+representations\footnote{$(n,m)$ denotes that the TF-IDF vectors are computed
+from character $n$, $n+1$, ..., $m$-grams. When not specified, TF-IDF vector
+are otherwise computed from words.}. Similarly, the \textit{Year difference}
+feature measures the absolute difference between the publication date of the
+articles to which the two signatures respectively belong.
 
@@
 specifically, using census data extracted from \citep{rugglesintegrated}, we
-build a logistic regression classifier for mapping the TF-IDF representation of
+build a logistic regression classifier for mapping the $(1,5)$-TF-IDF representation of
 an author name to one of the 7 ethnic groups reported in that dataset. Given a
@@
   \hline
-  Full name & Cosine similarity of TF-IDF\\
-  Given names & Cosine similarity of TF-IDF\\
+  Full name & Cosine similarity of $(2,4)$-TF-IDF\\
+  Given names & Cosine similarity of $(2,4)$-TF-IDF\\
   First given name & Jaro-Winkler distance\\
@@
   Given name initial & Equality\\
-  Affiliation & Cosine similarity of TF-IDF\\
+  Affiliation & Cosine similarity of $(2,4)$-TF-IDF\\
   Co-authors & Cosine similarity of TF-IDF\\
-  Title & Cosine similarity of TF-IDF\\
-  Journal & Cosine similarity of TF-IDF\\
+  Title & Cosine similarity of $(2,4)$-TF-IDF\\
+  Journal & Cosine similarity of $(2,4)$-TF-IDF\\
   Abstract & Cosine similarity of TF-IDF\\

### 2015-08-20 paper.tex
save

@@
 representations\footnote{$(n,m)$ denotes that the TF-IDF vectors are computed
-from character $n$, $n+1$, ..., $m$-grams. When not specified, TF-IDF vector
+from character $n$, $n+1$, ..., $m$-grams. When not specified, TF-IDF vectors
 are otherwise computed from words.}. Similarly, the \textit{Year difference}
@@
 specifically, using census data extracted from \citep{rugglesintegrated}, we
-build a logistic regression classifier for mapping the $(1,5)$-TF-IDF representation of
-an author name to one of the 7 ethnic groups reported in that dataset. Given a
-pair of signatures $(s_1, s_2)$, the proposed ethnicity features are each
-computed as the estimated probability of $s_1$ to belong to the respective
-ethnic group, multiplied by the estimated probability of $s_2$ to belong to the
-same group. In doing so, the expectation is for the linkage function to become
-sensitive to the actual origin of the authors depending on the values of these
-features.
+build a logistic regression classifier for mapping the $(1,5)$-TF-IDF
+representation of an author name to one of the 7 ethnic groups reported in that
+dataset. Given a pair of signatures $(s_1, s_2)$, the proposed ethnicity
+features are each computed as the estimated probability of $s_1$ to belong to
+the corresponding ethnic group, multiplied by the estimated probability of
+$s_2$ to belong to the same group. In doing so, the expectation is for the
+linkage function to become sensitive to the actual origin of the authors
+depending on the values of these features. Indirectly, let us also note that these
+features hold discriminative power since, if author names are predicted
+to belong to different ethnic groups, then they are also likely to correspond to
+distinct actual persons.
 
@@
 
-% distance learning as a supervised problem
-% describe all features
 % balancing difficult and easy cases

### 2015-08-20 paper.tex
save

@@
 \documentclass{article}
-%\usepackage[margin=1.2in]{geometry}
-
 \usepackage{nips15submit_e}
@@
 \usepackage[noend]{algpseudocode}
+\newcommand{\theHalgorithm}{\arabic{algorithm}}
 
@@
 \usepackage{hyperref}
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
 
@@
 (distinct authors). In this work, we evaluate Random Forests \citep{breiman2001random},
-Gradient Boosted Regression Trees \citep{friedman2001greedy} and Logistic Regression \glnote{add ref} as classifiers.
+Gradient Boosted Regression Trees \citep{friedman2001greedy} and Logistic Regression \citep{fan2008liblinear} as classifiers.
 
@@
 
-\textit{Building a training set.}
-% cite https://hpi.de/naumann/projects/repeatability/datasets/dblp-dataset.html
+\textit{Building a training set.} The distinctive aspect of our work is the
+knowledge of more than 1 million of crowdsourced annotations ${\cal C} = \{(a,
+s) \in {\cal A} \times {\cal S}\}$, each indicating that signature $s$ is known
+to correspond to individual $a$. In particular, this data can be used to
+generate positive pairs $(x=(s_1, s_2), y=0)$ for all $(s_1, a_1)$, $(s_2, a_2)
+\in {\cal C}$ such that $a_1=a_2$. Similarly, negative pairs $(x=(s_1, s_2), y=1)$
+can be extracted for all $(s_1, a_1)$, $(s_2, a_2)
+\in {\cal C}$ such that $a_1 \neq a_2$.
+
+The most straightforward approach for building a training set on which to learn
+a linkage function is to sample an equal number of positive and negative pairs,
+as suggested above. By observing that the linkage function $d$ will eventually
+be used only on pairs of signatures from the same block $S_b$, a further
+refinement for building a training set is to restrict  positive and negative
+pairs $(s_1, s_2)$ to only those for which $s_1$ and $s_2$ belong to the same
+block. In doing so, the trained classifier is forced to learn intra-block
+discriminative patterns rather than inter-block differences. Furthermore, as
+noted in \citep{lange2011frequency}, pairs of signatures are in the vast
+majority non-ambiguous: if both signatures share the same author names, then
+they correspond to the same individual, otherwise they do not. Rather than
+sampling pairs uniformly at random, we therefore propose to  oversample
+difficult cases when building the training set (i.e., pairs of signatures with
+different author names corresponding to same individual, and pairs of
+signatures with identical author names but corresponding to distinct
+individuals) in order to improve the overall accuracy of the linkage function.
 

### 2015-08-20 paper.tex
added data
save

@@
 individual. Finally, in the case of partially annotated databases as studied in
-this work, the setting extends with the partial knowledge of pairs $(a, s) \in
-{\cal A} \times {\cal S}$, each indicating that signature $s$ is known with high confidence
-to belong to individual $a$.
+this work, the setting extends with the partial knowledge of pairs ${\cal C} = \{ (a, s) \in
+{\cal A} \times {\cal S} \}$, each indicating that signature $s$ is known with high confidence
+to belong to individual $a$. Equivalently, ${\cal C}$ can be seen as a set of partial
+clusters $c_a$, each including all signatures $s$ for which $(s, a) \in {\cal C}$.
 
@@
 
-\glnote{I am not sure we need an explicit algorithm, but adding a few examples would help.}
+%\glnote{I am not sure we need an explicit algorithm, but adding a few examples would help.}
 
@@
 
-% balancing difficult and easy cases
-% sampling pairs from block only
-
 \subsection{Semi-supervised clustering}
 \label{methods:clustering}
-\glnote{By Gilles}
+
+The last component of our author disambiguation pipeline is clustering, that is
+the process of grouping together, within a block, all signatures from the same
+individual (and only those). As for many other works on author disambiguation,
+we make use of hierarchical clustering \citep{ward1963hierarchical} for
+building clusters of signatures in a bottom-up fashion. The method consists in
+iteratively merging together the two most similar clusters until all clusters
+are eventually merged together at the top of the hierarchy. Similarity between
+clusters is evaluated using either complete, single or average linkage, using
+as pseudo-distance metric the probability that $s_1$ and $s_2$ correspond to
+distinct authors, as calculated from the custom linkage function $d$.
+
+To form flat clusters out of the hierarchy, one must decide on a maximum
+distance threshold above which clusters are considered to correspond to
+distinct authors.  Exploiting knowledge from the partial clusters known in
+${\cal C}$, we evaluate three cut-off strategies:
+\begin{itemize}
+\item No cut: all signatures from the same block are assumed to be from the same author;
+\item Global cut: the threshold is chosen globally over all blocks, as the one maximizing some score $f({\cal C}, \hat{{\cal C}}_t)$;
+\item Block cut: the threshold is chosen locally at each block $b$, as the one maximizing some score $f({\cal C}^b, \hat{{\cal C}}^b_t)$;
+\end{itemize}
+where $\hat{{\cal C}}_t$ denotes the predicted clusters,
+restricted to the signatures in ${\cal C}$, when cutting the hierarchy at threshold $t$, and
+where ${\cal C}^b$ is the subset of ${\cal C}$ including only those signatures from block $b$.
 

### 2015-08-20 paper.tex
save

@@
 \begin{itemize}
-\item No cut: all signatures from the same block are assumed to be from the same author;
-\item Global cut: the threshold is chosen globally over all blocks, as the one maximizing some score $f({\cal C}, \hat{{\cal C}}_t)$;
-\item Block cut: the threshold is chosen locally at each block $b$, as the one maximizing some score $f({\cal C}^b, \hat{{\cal C}}^b_t)$;
+\item \textit{No cut:} all signatures from the same block are assumed to be from the same author.
+\item \textit{Global cut:} the threshold is chosen globally over all blocks, as the one maximizing some score $f({\cal C}, \hat{{\cal C}}_t)$.
+\item \textit{Block cut:} the threshold is chosen locally at each block $b$, as the one maximizing some score $f({\cal C}^b, \hat{{\cal C}}^b_t)$. In case ${\cal C}^b$ is empty, then
+                 all signatures from $b$ are clustered together.
 \end{itemize}
-where $\hat{{\cal C}}_t$ denotes the predicted clusters,
-restricted to the signatures in ${\cal C}$, when cutting the hierarchy at threshold $t$, and
-where ${\cal C}^b$ is the subset of ${\cal C}$ including only those signatures from block $b$.
+Where $\hat{{\cal C}}_t$ denotes the predicted clusters, restricted to the
+signatures in ${\cal C}$, when cutting the hierarchy at threshold $t$, and
+where ${\cal C}^b$ is the subset of ${\cal C}$ including only those signatures
+from block $b$.
 

### 2015-08-20 paper.tex
save

@@
 subsets $c_i$  each corresponds to the set of all signatures from a same
-individual. Finally, in the case of partially annotated databases as studied in
+individual (without knowing who). Finally, in the case of partially annotated databases as studied in
 this work, the setting extends with the partial knowledge of pairs ${\cal C} = \{ (a, s) \in
@@
 to belong to individual $a$. Equivalently, ${\cal C}$ can be seen as a set of partial
-clusters $c_a$, each including all signatures $s$ for which $(s, a) \in {\cal C}$.
+clusters $c_a$, each including all signatures $s$ for which $(s, a) \in {\cal C}$. \glnote{Change notations for ${\cal C}$!!}
 
@@
 distinct authors.  Exploiting knowledge from the partial clusters known in
-${\cal C}$, we evaluate three cut-off strategies:
+${\cal C}$, we evaluate the following semi-supervised cut-off strategies:
 \begin{itemize}

### 2015-08-20 paper.tex
save

@@
 individual (without knowing who). Finally, in the case of partially annotated databases as studied in
-this work, the setting extends with the partial knowledge of pairs ${\cal C} = \{ (a, s) \in
-{\cal A} \times {\cal S} \}$, each indicating that signature $s$ is known with high confidence
-to belong to individual $a$. Equivalently, ${\cal C}$ can be seen as a set of partial
-clusters $c_a$, each including all signatures $s$ for which $(s, a) \in {\cal C}$. \glnote{Change notations for ${\cal C}$!!}
+this work, the setting extends with the partial knowledge $\bar{{\cal C}} = \{ \bar{c_0}, ..., \bar{c_{M-1}} \}$ of ${\cal C}$,
+such that $\bar{c_i} \subseteq c_i$, with $\bar{c_i}$ possibly empty.
+Or put otherwise, the setting extends with the knowledge that all signatures
+$s \in \bar{c_i}$ belong to author $a_i$.
 
@@
 \textit{Building a training set.} The distinctive aspect of our work is the
-knowledge of more than 1 million of crowdsourced annotations ${\cal C} = \{(a,
-s) \in {\cal A} \times {\cal S}\}$, each indicating that signature $s$ is known
-to correspond to individual $a$. In particular, this data can be used to
-generate positive pairs $(x=(s_1, s_2), y=0)$ for all $(s_1, a_1)$, $(s_2, a_2)
-\in {\cal C}$ such that $a_1=a_2$. Similarly, negative pairs $(x=(s_1, s_2), y=1)$
-can be extracted for all $(s_1, a_1)$, $(s_2, a_2)
-\in {\cal C}$ such that $a_1 \neq a_2$.
+knowledge of more than 1 million of crowdsourced annotations $\bar{\cal C} = \{
+\bar{c_0}, ..., \bar{c_{M-1}} \}$, indicating together that all signature $s \in
+\bar{c_i}$ are known to correspond to the same individual $a_i$. In particular,
+this data can be used to generate positive pairs $(x=(s_1, s_2), y=0)$ for all
+$s_1, s_2 \in \bar{c_i}$, for all $i$. Similarly, negative pairs $(x=(s_1,
+s_2), y=1)$ can be extracted for all $s_1 \in \bar{c_i}, s_2 \in \bar{c_j}$, for
+all $i \neq j$.
 

### 2015-08-20 paper.tex
save

@@
 distinct authors.  Exploiting knowledge from the partial clusters known in
-${\cal C}$, we evaluate the following semi-supervised cut-off strategies:
+$\bar{{\cal C}}$, we evaluate the following semi-supervised cut-off strategies:
 \begin{itemize}
 \item \textit{No cut:} all signatures from the same block are assumed to be from the same author.
-\item \textit{Global cut:} the threshold is chosen globally over all blocks, as the one maximizing some score $f({\cal C}, \hat{{\cal C}}_t)$.
-\item \textit{Block cut:} the threshold is chosen locally at each block $b$, as the one maximizing some score $f({\cal C}^b, \hat{{\cal C}}^b_t)$. In case ${\cal C}^b$ is empty, then
-                 all signatures from $b$ are clustered together.
+\item \textit{Global cut:} the threshold is chosen globally over all blocks,
+    as the one maximizing some score $f(\bar{{\cal C}}, \widehat{\bar{{\cal C}}}_t)$.
+\item \textit{Block cut:} the threshold is chosen locally at each block $b$,
+    as the one maximizing some score $f(\bar{{\cal C}}^b, \widehat{\bar{{\cal C}}^b_t})$.
+    In case $\bar{{\cal C}}^b$ is empty, then all signatures from $b$ are clustered together.
 \end{itemize}
-Where $\hat{{\cal C}}_t$ denotes the predicted clusters, restricted to the
-signatures in ${\cal C}$, when cutting the hierarchy at threshold $t$, and
-where ${\cal C}^b$ is the subset of ${\cal C}$ including only those signatures
-from block $b$.
+Where $\widehat{\bar{{\cal C}}}_t$ denotes the predicted clusters, restricted to the
+signatures in $\bar{{\cal C}}$, when cutting the hierarchy at threshold $t$, and
+where $\bar{{\cal C}^b}$ is limited to signatures of $\bar{{\cal C}}$ in block $b$.
 

### 2015-08-20 paper.tex
save

@@
 Or put otherwise, the setting extends with the knowledge that all signatures
-$s \in \bar{c_i}$ belong to author $a_i$.
+$s \in \bar{c_i}$ belong to the same author.
 
@@
 
+\glnote{Notations should be improved and be made more explicit}
+
 % hierarchical clustering

### 2015-08-21 paper.tex
save

@@
 distance threshold above which clusters are considered to correspond to
-distinct authors.  Exploiting knowledge from the partial clusters known in
-$\bar{{\cal C}}$, we evaluate the following semi-supervised cut-off strategies:
+distinct authors. Let us denote by $\bar{{\cal S}} = \{ s | s \in \bar{c}, \bar{c}
+\in \bar{\cal C} \}$ the set of all signatures for which partial clusters are
+known. Let us also denote by $\widehat{\cal C} = \{ \widehat{c}_i | i = 0, ...,
+K-1 \}$ the predicted clusters for all signatures in ${\cal S}$, and by
+$\widehat{\overline{\cal C}} = \{ \widehat{c}_i \cap \bar{{\cal S}} | i = 0,
+..., K-1 \}$ the predicted clusters restricted to signatures for which partial
+clusters are known. From these, we evaluate the following semi-supervised cut-off strategies:
 \begin{itemize}
@@
 \item \textit{Global cut:} the threshold is chosen globally over all blocks,
-    as the one maximizing some score $f(\bar{{\cal C}}, \widehat{\bar{{\cal C}}}_t)$.
+    as the one maximizing some score $f(\bar{\cal C}, \widehat{\overline{\cal C}})$.
 \item \textit{Block cut:} the threshold is chosen locally at each block $b$,
-    as the one maximizing some score $f(\bar{{\cal C}}^b, \widehat{\bar{{\cal C}}^b_t})$.
-    In case $\bar{{\cal C}}^b$ is empty, then all signatures from $b$ are clustered together.
+    as the one maximizing some score $f(\bar{\cal C}_b, \widehat{\overline{\cal C}}_b)$.
+    In case $\bar{\cal C}_b$ is empty, then all signatures from $b$ are clustered together.
 \end{itemize}
-Where $\widehat{\bar{{\cal C}}}_t$ denotes the predicted clusters, restricted to the
-signatures in $\bar{{\cal C}}$, when cutting the hierarchy at threshold $t$, and
-where $\bar{{\cal C}^b}$ is limited to signatures of $\bar{{\cal C}}$ in block $b$.
 
-\glnote{Notations should be improved and be made more explicit}
+\glnote{Add a figure showing the three possible splits}
 

### 2015-08-21 paper.tex
isave

@@
 \label{methods}
-
-\subsection{Overview}
 
@@
 K-1 \}$ the predicted clusters for all signatures in ${\cal S}$, and by
-$\widehat{\overline{\cal C}} = \{ \widehat{c}_i \cap \bar{{\cal S}} | i = 0,
-..., K-1 \}$ the predicted clusters restricted to signatures for which partial
+$\widehat{\overline{\cal C}} = \{ \widehat{c} \cap \bar{{\cal S}} | \widehat{c} \in \widehat{\cal C} \}$ the predicted clusters restricted to signatures for which partial
 clusters are known. From these, we evaluate the following semi-supervised cut-off strategies:
@@
 \subsection{Data}
-
-\glnote{By Gilles}
 

### 2015-08-21 paper.tex
data

@@
 \in \bar{\cal C} \}$ the set of all signatures for which partial clusters are
-known. Let us also denote by $\widehat{\cal C} = \{ \widehat{c}_i | i = 0, ...,
-K-1 \}$ the predicted clusters for all signatures in ${\cal S}$, and by
-$\widehat{\overline{\cal C}} = \{ \widehat{c} \cap \bar{{\cal S}} | \widehat{c} \in \widehat{\cal C} \}$ the predicted clusters restricted to signatures for which partial
+known. Let us also denote by $\smash{\widehat{\cal C}}$  the predicted clusters for all signatures in ${\cal S}$, and by
+$\smash{\widehat{\overline{\cal C}} = \{ \widehat{c} \cap \bar{{\cal S}} | \widehat{c} \in \widehat{\cal C} \}}$
+the predicted clusters restricted to signatures for which partial
 clusters are known. From these, we evaluate the following semi-supervised cut-off strategies:
@@
 disambiguation, publicly available
-online\footnote{\url{https://github.com/inveniosoftware/beard}} for free reuse
+online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
 or study.  Our implementation builds upon the Python scientific stack, making
@@
 \subsection{Data}
+
+The author disambiguation solution proposed in this work, along with its
+enhancements, are evaluated on data extracted from the INSPIRE portal
+\citep{gentil2009information}, a digital library for scientific literature in
+high-energy physics. Overall, the portal holds more than 1 million
+publications, forming in total a set ${\cal S}$ of more than 10 millions
+signatures. Out of these, around 13\% have been \textit{claimed} by their
+original authors or marked as such by professional curators. Together, they
+constitute a trusted set $\bar{\cal C}$ of 15388 distinct individuals sharing
+36340 unique author names. This data covers  several decades in time and dozens of
+author nationalities worldwide.
+
+Following INSPIRE terms of use, the data is released
+online\footnote{\url{https://github.com/glouppe/paper-author-disambiguation}}
+under the CC0 license. To the best of our knowledge, data of this size and
+coverage is the first to be publicly released in the scope of author
+disambiguation research.
 

### 2015-08-21 paper.tex
save

@@
 constitute a trusted set $\bar{\cal C}$ of 15388 distinct individuals sharing
-36340 unique author names. This data covers  several decades in time and dozens of
-author nationalities worldwide.
+36340 unique author names spread within 1201763 signatures on 360066
+publications. This data covers several decades in time and dozens of author
+nationalities worldwide.
 
-Following INSPIRE terms of use, the data is released
+Following INSPIRE terms of use, the dataset $\bar{\cal C}$ is released
 online\footnote{\url{https://github.com/glouppe/paper-author-disambiguation}}
@@
 
-% source of the data, labels in the data, etc
-% release the data
-
 \subsection{Evaluation protocol}
-
-\glnote{By Gilles}
 
@@
 
-\glnote{To review}
+% \glnote{To review}
 
-The starting point of our analysis is an algorithm that blocks the signatures using the last
-name and first initial strategy, samples the pairs in balanced way, uses gradient boosting
-with all features included for learning the similarity function and clusters using
-semi-supervised hierarchical approach.
+% The starting point of our analysis is an algorithm that blocks the signatures using the last
+% name and first initial strategy, samples the pairs in balanced way, uses gradient boosting
+% with all features included for learning the similarity function and clusters using
+% semi-supervised hierarchical approach.
 
-\begin{table}[H]
-\caption{Base experiment evaluation)}
-\centering
-\begin{tabular}{|r|r|l|l|l|}
-  \hline
-  Evaluation & Set & Precision & Recall & F-score \\
-  \hline
-  Pairwise & test & 0.9948 & 0.9738 & 0.9842 \\
-  \hline
-  Pairwise & train & 0.9976 & 0.9747 & 0.986 \\
-  \hline
-  Pairwise & overall & 0.9952 & 0.9739 & 0.9844 \\
-  \hline
-  $B^3$ & test & 0.9901 & 0.976 & 0.983 \\
-  \hline
-  $B^3$ & train & 0.997 & 0.979 & 0.9879 \\
-  \hline
-  $B^3$ & overall & 0.9907 & 0.9761 & 0.9834 \\
-  \hline
-\end{tabular}
-\end{table}
+% \begin{table}[H]
+% \caption{Base experiment evaluation)}
+% \centering
+% \begin{tabular}{|r|r|l|l|l|}
+%   \hline
+%   Evaluation & Set & Precision & Recall & F-score \\
+%   \hline
+%   Pairwise & test & 0.9948 & 0.9738 & 0.9842 \\
+%   \hline
+%   Pairwise & train & 0.9976 & 0.9747 & 0.986 \\
+%   \hline
+%   Pairwise & overall & 0.9952 & 0.9739 & 0.9844 \\
+%   \hline
+%   $B^3$ & test & 0.9901 & 0.976 & 0.983 \\
+%   \hline
+%   $B^3$ & train & 0.997 & 0.979 & 0.9879 \\
+%   \hline
+%   $B^3$ & overall & 0.9907 & 0.9761 & 0.9834 \\
+%   \hline
+% \end{tabular}
+% \end{table}
 
@@
 
-\glnote{To review}
+% \glnote{To review}
 
-Let us introduce a term \textit{blocking limited maximum recall} to describe the highest
-recall that the algorithm can theoretically reach after blocking is done.
-Formally, for the set of signatures ${\cal S}$, blocking function $F: \mathcal{S}
-\rightarrow \mathcal{B}$, where $ \mathcal{B} = \{s_{0}, \ldots{} , s_{N-1}\}$ is a
-partition of $\mathcal{S} $ , the recall function $\mathcal{R}: \mathcal{C}_{gold},
-\mathcal{C}_{predicted} \rightarrow \langle0,1\rangle$ where $\mathcal{C}_{gold}$ is the
-partition of $\mathcal{S}$ where for every author there is a set in $\mathcal{C}_{gold}$
-that contains only all the signatures of this author, $\mathcal{C}_{predicted}$ is the
-partition of $\mathcal{S}$ output by the algorithm, and $\mathcal{Q} = \{\cup_{i=0}^{N-1}
-q_i $ : $\forall_{i \in \langle0,N-1\rangle} q_i$ is a partition of $s_i$\}. Then
-\textit{blocking limited maximum recall} is defined as $\max_{q \in \mathcal{Q}}
-\mathcal{R}(\mathcal{C}_{gold}, q)$. For sanely defined recall functions, such as $B^{3}$
-recall or \textit{pairwise} recall \msnote{Further explanation needed, why it is
-equivalent?}, it is equivalent to $\mathcal{R}(\mathcal{C}_{gold}, \mathcal{B})$.
+% Let us introduce a term \textit{blocking limited maximum recall} to describe the highest
+% recall that the algorithm can theoretically reach after blocking is done.
+% Formally, for the set of signatures ${\cal S}$, blocking function $F: \mathcal{S}
+% \rightarrow \mathcal{B}$, where $ \mathcal{B} = \{s_{0}, \ldots{} , s_{N-1}\}$ is a
+% partition of $\mathcal{S} $ , the recall function $\mathcal{R}: \mathcal{C}_{gold},
+% \mathcal{C}_{predicted} \rightarrow \langle0,1\rangle$ where $\mathcal{C}_{gold}$ is the
+% partition of $\mathcal{S}$ where for every author there is a set in $\mathcal{C}_{gold}$
+% that contains only all the signatures of this author, $\mathcal{C}_{predicted}$ is the
+% partition of $\mathcal{S}$ output by the algorithm, and $\mathcal{Q} = \{\cup_{i=0}^{N-1}
+% q_i $ : $\forall_{i \in \langle0,N-1\rangle} q_i$ is a partition of $s_i$\}. Then
+% \textit{blocking limited maximum recall} is defined as $\max_{q \in \mathcal{Q}}
+% \mathcal{R}(\mathcal{C}_{gold}, q)$. For sanely defined recall functions, such as $B^{3}$
+% recall or \textit{pairwise} recall \msnote{Further explanation needed, why it is
+% equivalent?}, it is equivalent to $\mathcal{R}(\mathcal{C}_{gold}, \mathcal{B})$.
 
-The \textit{blocking limited maximum recall} for the last name and first initial blocking
-and $B^3$ scoring equals 0.9827. Comparing it to the $B^3$ recall of the base experiment,
-one can see that a huge part of errors comes from the blocking step which forbids some of
-the pairs to be merged together. To prevent that, we tried the phonetic blocking algorithm
-using three different phonetic algorithms: Double Metaphone \citep{doublemetaphone}, NYSIIS
-\citep{nysiis} and Soundex \citep{Soundex}. As Double Metaphone can return two results for a
-string, we always discarded the second one when we used this algorithm.
+% The \textit{blocking limited maximum recall} for the last name and first initial blocking
+% and $B^3$ scoring equals 0.9827. Comparing it to the $B^3$ recall of the base experiment,
+% one can see that a huge part of errors comes from the blocking step which forbids some of
+% the pairs to be merged together. To prevent that, we tried the phonetic blocking algorithm
+% using three different phonetic algorithms: Double Metaphone \citep{doublemetaphone}, NYSIIS
+% \citep{nysiis} and Soundex \citep{Soundex}. As Double Metaphone can return two results for a
+% string, we always discarded the second one when we used this algorithm.
 
-\begin{table}[H]
-\caption{Blocking limited maximum recalls (BLMR) on the whole dataset without splitting over
-the first given name initial}
-\centering
-\begin{tabular}{|r|l|l|}
-  \hline
-  blocking function & BLMR with $B^{3}$ recall & BLMR with pairwise recall \\
-  \hline
-  last name and first initial & 0.9827 & 0.9776 \\
-  \hline
-  phonetic using double metaphone & 0.9967 & 0.9953 \\
-  \hline
-  phonetic using nysiis & 0.9961 & 0.9951 \\
-  \hline
-  phonetic using soundex & 0.9966 & 0.9953 \\
-  \hline
-\end{tabular}
-\end{table}
+% \begin{table}[H]
+% \caption{Blocking limited maximum recalls (BLMR) on the whole dataset without splitting over
+% the first given name initial}
+% \centering
+% \begin{tabular}{|r|l|l|}
+%   \hline
+%   blocking function & BLMR with $B^{3}$ recall & BLMR with pairwise recall \\
+%   \hline
+%   last name and first initial & 0.9827 & 0.9776 \\
+%   \hline
+%   phonetic using double metaphone & 0.9967 & 0.9953 \\
+%   \hline
+%   phonetic using nysiis & 0.9961 & 0.9951 \\
+%   \hline
+%   phonetic using soundex & 0.9966 & 0.9953 \\
+%   \hline
+% \end{tabular}
+% \end{table}
 
-\msnote{Mention two new features for this experiments, other than that everything is the
-same as in the base experiment}
+% \msnote{Mention two new features for this experiments, other than that everything is the
+% same as in the base experiment}
 
-\begin{table}[H]
-\caption{Phonetic algorithm performance}
-\centering
-\begin{tabular}{|r|r|r|l|l|l|}
-  \hline
-  Phonetic Algorithm & Split over initial & Evaluation & Precision & Recall & F-score \\
-  \hline
-  Double Metaphone & yes & pairwise & 0.9934 & 0.982 & 0.9876 \\
-  \hline
-  Double Metaphone & yes & $B^3$ & 0.9867 & 0.983 & 0.9848 \\
-  \hline
-  Double Metaphone & no & pairwise & - & - & - \\
-  \hline
-  Double Metaphone & no & $B^3$ & - & - & - \\
-  \hline
-  NYSIIS & yes & pairwise & 0.9942 & 0.9818 & 0.9879 \\
-  \hline
-  NYSIIS & yes & $B^3$ & 0.9884 & 0.9828 & 0.9856 \\
-  \hline
-  NYSIIS & no & pairwise & - & - & - \\
-  \hline
-  NYSIIS & no & $B^3$ & - & - & - \\
-  \hline
-  Soundex & yes & pairwise & - & - & - \\
-  \hline
-  Soundex & yes & $B^3$ & - & - & - \\
-  \hline
-  Soundex & no & pairwise & - & - & - \\
-  \hline
-  Soundex & no & $B^3$ & - & - & - \\
-  \hline
-\end{tabular}
-\end{table}
+% \begin{table}[H]
+% \caption{Phonetic algorithm performance}
+% \centering
+% \begin{tabular}{|r|r|r|l|l|l|}
+%   \hline
+%   Phonetic Algorithm & Split over initial & Evaluation & Precision & Recall & F-score \\
+%   \hline
+%   Double Metaphone & yes & pairwise & 0.9934 & 0.982 & 0.9876 \\
+%   \hline
+%   Double Metaphone & yes & $B^3$ & 0.9867 & 0.983 & 0.9848 \\
+%   \hline
+%   Double Metaphone & no & pairwise & - & - & - \\
+%   \hline
+%   Double Metaphone & no & $B^3$ & - & - & - \\
+%   \hline
+%   NYSIIS & yes & pairwise & 0.9942 & 0.9818 & 0.9879 \\
+%   \hline
+%   NYSIIS & yes & $B^3$ & 0.9884 & 0.9828 & 0.9856 \\
+%   \hline
+%   NYSIIS & no & pairwise & - & - & - \\
+%   \hline
+%   NYSIIS & no & $B^3$ & - & - & - \\
+%   \hline
+%   Soundex & yes & pairwise & - & - & - \\
+%   \hline
+%   Soundex & yes & $B^3$ & - & - & - \\
+%   \hline
+%   Soundex & no & pairwise & - & - & - \\
+%   \hline
+%   Soundex & no & $B^3$ & - & - & - \\
+%   \hline
+% \end{tabular}
+% \end{table}
 
-\msnote{Fill the table}
+% \msnote{Fill the table}
 

### 2015-08-21 paper.tex
eval

@@
 individual (without knowing who). Finally, in the case of partially annotated databases as studied in
-this work, the setting extends with the partial knowledge $\bar{{\cal C}} = \{ \bar{c_0}, ..., \bar{c_{M-1}} \}$ of ${\cal C}$,
-such that $\bar{c_i} \subseteq c_i$, with $\bar{c_i}$ possibly empty.
+this work, the setting extends with the partial knowledge ${\cal C}^\prime = \{ c_0^\prime, ..., c_{M-1}^\prime \}$ of ${\cal C}$,
+such that $c_i^\prime \subseteq c_i$, with $c_i^\prime$ possibly empty.
 Or put otherwise, the setting extends with the knowledge that all signatures
-$s \in \bar{c_i}$ belong to the same author.
+$s \in c_i^\prime$ belong to the same author.
 
@@
 \textit{Building a training set.} The distinctive aspect of our work is the
-knowledge of more than 1 million of crowdsourced annotations $\bar{\cal C} = \{
-\bar{c_0}, ..., \bar{c_{M-1}} \}$, indicating together that all signature $s \in
-\bar{c_i}$ are known to correspond to the same individual $a_i$. In particular,
+knowledge of more than 1 million of crowdsourced annotations ${\cal C}^\prime = \{
+c_0^\prime, ..., c_{M-1}^\prime \}$, indicating together that all signature $s \in
+c_i^\prime$ are known to correspond to the same individual $a_i$. In particular,
 this data can be used to generate positive pairs $(x=(s_1, s_2), y=0)$ for all
-$s_1, s_2 \in \bar{c_i}$, for all $i$. Similarly, negative pairs $(x=(s_1,
-s_2), y=1)$ can be extracted for all $s_1 \in \bar{c_i}, s_2 \in \bar{c_j}$, for
+$s_1, s_2 \in c_i^\prime$, for all $i$. Similarly, negative pairs $(x=(s_1,
+s_2), y=1)$ can be extracted for all $s_1 \in c_i^\prime, s_2 \in c_j^\prime$, for
 all $i \neq j$.
@@
 distance threshold above which clusters are considered to correspond to
-distinct authors. Let us denote by $\bar{{\cal S}} = \{ s | s \in \bar{c}, \bar{c}
-\in \bar{\cal C} \}$ the set of all signatures for which partial clusters are
+distinct authors. Let us denote by ${\cal S}^\prime = \{ s | s \in c^\prime, c^\prime
+\in {\cal C}^\prime \}$ the set of all signatures for which partial clusters are
 known. Let us also denote by $\smash{\widehat{\cal C}}$  the predicted clusters for all signatures in ${\cal S}$, and by
-$\smash{\widehat{\overline{\cal C}} = \{ \widehat{c} \cap \bar{{\cal S}} | \widehat{c} \in \widehat{\cal C} \}}$
+$\smash{\widehat{\cal C}^\prime} = \{ \widehat{c} \cap {\cal S}^\prime | \widehat{c} \in \widehat{\cal C} \}$
 the predicted clusters restricted to signatures for which partial
@@
 \item \textit{Global cut:} the threshold is chosen globally over all blocks,
-    as the one maximizing some score $f(\bar{\cal C}, \widehat{\overline{\cal C}})$.
+    as the one maximizing some score $f({\cal C}^\prime, \widehat{\cal C}^\prime)$.
 \item \textit{Block cut:} the threshold is chosen locally at each block $b$,
-    as the one maximizing some score $f(\bar{\cal C}_b, \widehat{\overline{\cal C}}_b)$.
-    In case $\bar{\cal C}_b$ is empty, then all signatures from $b$ are clustered together.
+    as the one maximizing some score $f({\cal C}_b^\prime, \widehat{\cal C}_b^\prime)$.
+    In case ${\cal C}_b^\prime$ is empty, then all signatures from $b$ are clustered together.
 \end{itemize}
@@
 original authors or marked as such by professional curators. Together, they
-constitute a trusted set $\bar{\cal C}$ of 15388 distinct individuals sharing
+constitute a trusted set ${\cal C}^\prime$ of 15388 distinct individuals sharing
 36340 unique author names spread within 1201763 signatures on 360066
@@
 
-Following INSPIRE terms of use, the dataset $\bar{\cal C}$ is released
+Following INSPIRE terms of use, the signatures ${\cal S}^\prime$ and their
+corresponding clusters ${\cal C}^\prime$ are released
 online\footnote{\url{https://github.com/glouppe/paper-author-disambiguation}}
@@
 \subsection{Evaluation protocol}
+
+Experiments carried out to study the impact of the proposed algorithmic
+components and refinements, as described in Section~\ref{methods}, follow a
+standard 3-fold cross-validation protocol, using ${\cal S}^\prime$ as ground-
+truth dataset. To mimic the $|{\cal S}^\prime| / |{\cal S}| \approx 13\%$ ratio
+of claimed signatures with respect to the total set of signatures, as on the
+INSPIRE platform, cross-validation folds are constructed by sampling a training
+set ${\cal S}_\text{train}^\prime \subseteq {\cal S}^\prime$ of 13\% of claimed
+signatures and using the remaining signatures for testing. Accordingly, ${\cal
+C}_\text{train}^\prime = \{ c^\prime \cap {\cal S}_\text{train}^\prime |
+c^\prime \in {\cal C}^\prime \}$ is used to represent the partial known
+clusters on the training fold.
+
+We evaluate the predicted clusters over training data ${\cal
+C}_\text{train}^\prime$, testing data ${\cal C}_\text{test}^\prime$ and the
+whole data ${\cal C}^\prime$, using both B3 and pairwise precision, recall
+and F1-measures, as defined below:
+
+\begin{align}
+P_\text{B3}({\cal C}, \widehat{\cal C}) &= \\
+R_\text{B3}({\cal C}, \widehat{\cal C}) &= \\
+F_\text{B3}({\cal C}, \widehat{\cal C}) &= \frac{2 P_\text{B3}({\cal C}, \widehat{\cal C}) R_\text{B3}({\cal C}, \widehat{\cal C})}{P_\text{B3}({\cal C}, \widehat{\cal C}) + P_\text{B3}({\cal C}, \widehat{\cal C})}\\
+P_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \\
+R_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \\
+F_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{2 P_\text{pairwise}({\cal C}, \widehat{\cal C}) R_\text{pairwise}({\cal C}, \widehat{\cal C})}{P_\text{pairwise}({\cal C}, \widehat{\cal C}) + R_\text{pairwise}({\cal C}, \widehat{\cal C})}
+\end{align}
 

### 2015-08-21 paper.tex
save

@@
 components and refinements, as described in Section~\ref{methods}, follow a
-standard 3-fold cross-validation protocol, using ${\cal S}^\prime$ as ground-
-truth dataset. To mimic the $|{\cal S}^\prime| / |{\cal S}| \approx 13\%$ ratio
+standard 3-fold cross-validation protocol, using ${\cal S}^\prime$ as
+ground-truth dataset. To mimic the $|{\cal S}^\prime| / |{\cal S}| \approx 13\%$ ratio
 of claimed signatures with respect to the total set of signatures, as on the
@@
 
-We evaluate the predicted clusters over training data ${\cal
+As commonly used in author disambiguation research \citep{levin2012citation},
+we evaluate the predicted clusters over training data ${\cal
 C}_\text{train}^\prime$, testing data ${\cal C}_\text{test}^\prime$ and the
-whole data ${\cal C}^\prime$, using both B3 and pairwise precision, recall
-and F1-measures, as defined below:
-
+whole data ${\cal C}^\prime$, using both B3 \glnote{add ref} and pairwise \glnote{add ref} precision, recall
+and F-measure, as defined below:
 \begin{align}
-P_\text{B3}({\cal C}, \widehat{\cal C}) &= \\
-R_\text{B3}({\cal C}, \widehat{\cal C}) &= \\
-F_\text{B3}({\cal C}, \widehat{\cal C}) &= \frac{2 P_\text{B3}({\cal C}, \widehat{\cal C}) R_\text{B3}({\cal C}, \widehat{\cal C})}{P_\text{B3}({\cal C}, \widehat{\cal C}) + P_\text{B3}({\cal C}, \widehat{\cal C})}\\
-P_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \\
-R_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \\
+P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|\widehat{c}(s)|} \\
+R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|c(s)|}\\
+F_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{2 P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}{P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) + P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}\\
+P_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p(\widehat{\cal C})|}\\
+R_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p({\cal C})|}\\
 F_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{2 P_\text{pairwise}({\cal C}, \widehat{\cal C}) R_\text{pairwise}({\cal C}, \widehat{\cal C})}{P_\text{pairwise}({\cal C}, \widehat{\cal C}) + R_\text{pairwise}({\cal C}, \widehat{\cal C})}
 \end{align}
+where $c(s)$ (resp. $\widehat{c}(s)$) is the cluster $c \in {\cal C}$ such that
+$s \in c$ (resp. the cluster $\widehat{c} \in \widehat{\cal C}$ such that $s
+\in \widehat{c}$), and where $p({\cal C}) = \cup_{c \in {\cal C}} \{ (s_1, s_2)
+| s_1, s_2 \in c, s_1 \neq s_2 \}$ is the set of all pairs of signatures from
+the same clusters in ${\cal C}$. Intuitively, precision evaluates if signatures
+are grouped only with signatures from the same true clusters, while recall
+measures the extent to which all signatures from the same true clusters are
+effectively grouped together. The F-measure is the harmonic mean between these
+two quantities. In the analysis below, we rely primarily on B3 measures for discussing
+the results, as pairwise measures tend to favor large clusters (because the number of pairs is quadratic with the cluster size),
+hence unfairly giving preference to authors with many publications.
 

### 2015-08-21 paper.tex
save

@@
 standard 3-fold cross-validation protocol, using ${\cal S}^\prime$ as
-ground-truth dataset. To mimic the $|{\cal S}^\prime| / |{\cal S}| \approx 13\%$ ratio
+ground-truth dataset. To replicate the $|{\cal S}^\prime| / |{\cal S}| \approx 13\%$ ratio
 of claimed signatures with respect to the total set of signatures, as on the
@@
 set ${\cal S}_\text{train}^\prime \subseteq {\cal S}^\prime$ of 13\% of claimed
-signatures and using the remaining signatures for testing. Accordingly, ${\cal
+signatures, and by using the remaining signatures ${\cal S}_\text{test}^\prime = {\cal S}^\prime \setminus {\cal S}_\text{train}^\prime$ for testing. Accordingly, ${\cal
 C}_\text{train}^\prime = \{ c^\prime \cap {\cal S}_\text{train}^\prime |
-c^\prime \in {\cal C}^\prime \}$ is used to represent the partial known
-clusters on the training fold.
+c^\prime \in {\cal C}^\prime \}$ represents the partial known
+clusters on the training fold, while ${\cal C}_\text{test}^\prime$ are those
+used for testing.
 
-As commonly used in author disambiguation research \citep{levin2012citation},
+As commonly done in author disambiguation research \citep{levin2012citation},
 we evaluate the predicted clusters over training data ${\cal
@@
 the results, as pairwise measures tend to favor large clusters (because the number of pairs is quadratic with the cluster size),
-hence unfairly giving preference to authors with many publications.
+hence unfairly giving preference to authors with many publications. By contrast,
+B3 measures weight clusters linearly with respect to their size.
 
-% measures (b^3, paired, size of clusters)
-% training / valid / test sets
+\subsection{Results and discussion}
 
-\subsection{Base experiment}
+\textit{Baseline.}
+
+\glnote{Describe baseline}\\
+\glnote{Add an uber table of results}
 
@@
 
-\subsection{Blocking}
+\textit{Blocking.}
+
+\glnote{Discuss baseline + different blocking strategies}\\
+\glnote{Discuss blocking in terms of maximum recall}
 
@@
 
-\subsection{Learning a linkage function}
+\textit{Linkage function.}
 % feature engineering
@@
 
-\subsection{Semi-supervised clustering}
+\textit{Semi-supervised clustering.}
 % compare agglomerative algorithms

### 2015-08-22 paper.tex
save

@@
 \usepackage{natbib}
-
-% For algorithms
-\usepackage{algorithm}
-\usepackage{algorithmicx}
-\usepackage[noend]{algpseudocode}
-\newcommand{\theHalgorithm}{\arabic{algorithm}}
 
@@
 original authors or marked as such by professional curators. Together, they
-constitute a trusted set ${\cal C}^\prime$ of 15388 distinct individuals sharing
+constitute a trusted set $({\cal S}^\prime, {\cal C}^\prime)$ of 15388 distinct individuals sharing
 36340 unique author names spread within 1201763 signatures on 360066
@@
 components and refinements, as described in Section~\ref{methods}, follow a
-standard 3-fold cross-validation protocol, using ${\cal S}^\prime$ as
+standard 3-fold cross-validation protocol, using $({\cal S}^\prime, {\cal C}^\prime)$ as
 ground-truth dataset. To replicate the $|{\cal S}^\prime| / |{\cal S}| \approx 13\%$ ratio
@@
 \end{align}
-where $c(s)$ (resp. $\widehat{c}(s)$) is the cluster $c \in {\cal C}$ such that
+and where $c(s)$ (resp. $\widehat{c}(s)$) is the cluster $c \in {\cal C}$ such that
 $s \in c$ (resp. the cluster $\widehat{c} \in \widehat{\cal C}$ such that $s
@@
 
-\textit{Baseline.}
+\textit{Baseline.} Results presented in this section are all discussed with
+respect to a baseline solution using the following combination of components:
+\begin{itemize}
+\item Blocking: same surname and the same first given name initial strategy;
+\item Linkage function: all 22 features defined in Table~\ref{table:features},
+    gradient boosted regression trees as supervised learning algorithm
+    and a training set of pairs built by balancing easy and difficult cases.
+\item Clustering: agglomerative clustering using average linkage and
+    block cuts found to maximize $F_\text{B3}({\cal C}_\text{train}^\prime, \widehat{\cal C}_\text{train}^\prime, {\cal S}_\text{train}^\prime)$.
+\end{itemize}
 
-\glnote{Describe baseline}\\
 \glnote{Add an uber table of results}
-
-% \glnote{To review}
-
-% The starting point of our analysis is an algorithm that blocks the signatures using the last
-% name and first initial strategy, samples the pairs in balanced way, uses gradient boosting
-% with all features included for learning the similarity function and clusters using
-% semi-supervised hierarchical approach.
 

### 2015-08-22 paper.tex
save

@@
 
-The simplest and most common strategy for blocking \glnote{add references}
+The simplest and most common strategy for blocking, further denoted to as SFI,
 groups signatures together if they share the same surname(s) and the same first
@@
 
+\begin{table}
+\caption{Average precision, recall and f-measure scores on test folds.}
+\label{table:results}
+\centering
+\begin{tabular}{|l|c c c|c c c|}
+  \hline
+                       & \multicolumn{3}{|c|}{\textbf{B3}} & \multicolumn{3}{|c|}{\textbf{Pairwise}} \\
+  \textbf{Description} & \textit{P} & \textit{R} & \textit{F} & \textit{P} & \textit{R} & \textit{F}\\
+  \hline
+  \hline
+  Baseline & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+  \hline
+  Blocking SFI & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+  Blocking Double metaphone & 0.9856 & 0.9827 & 0.9841 & 0.9927 & 0.9817 & 0.9871 \\
+  Blocking NYSIIS & 0.9875 & 0.9826 & 0.9850 & 0.9936 & 0.9814 & 0.9875 \\
+  Blocking Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
+  \hline
+\end{tabular}
+\end{table}
+
 \textit{Baseline.} Results presented in this section are all discussed with
@@
 \end{itemize}
-
-\glnote{Add an uber table of results}
 

### 2015-08-22 paper.tex
results

@@
 \hline
-  Blocking SFI & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
-  Blocking Double metaphone & 0.9856 & 0.9827 & 0.9841 & 0.9927 & 0.9817 & 0.9871 \\
-  Blocking NYSIIS & 0.9875 & 0.9826 & 0.9850 & 0.9936 & 0.9814 & 0.9875 \\
-  Blocking Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
+Blocking = SFI & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841 & 0.9927 & 0.9817 & 0.9871 \\
+Blocking = NYSIIS & 0.9875 & 0.9826 & 0.9850 & 0.9936 & 0.9814 & 0.9875 \\
+Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
+\hline
+Classifier = GBRT & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+Classifier = Random Forests & 0.9909 & 0.9783 & 0.9846 & 0.9957 & 0.9752 & 0.9854 \\
+Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666 & 0.9717 & 0.9569 & 0.9643 \\
+\hline
+Training pairs = Non-blocked, uniform & 0.9793 & 0.9630 & 0.9711 & 0.9756 & 0.9629 & 0.9692 \\
+Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786 & 0.9850 & 0.9707 & 0.9778 \\
+Training pairs = Blocked, balanced & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+\hline
+Clustering = Average linkage & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671 & 0.9543 & 0.9626 & 0.9584 \\
+Clustering = Complete linkage & 0.9862 & 0.9709 & 0.9785 & 0.9920 & 0.9688 & 0.9803 \\
+\hline
+No cut & 0.9024 & 0.9828 & 0.9409 & 0.8298 & 0.9776 & 0.8977 \\
+Global cut & -- & -- & -- & -- & -- & -- \\
+Block cut & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+\hline
+No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
   \hline
@@
 \begin{itemize}
-\item Blocking: same surname and the same first given name initial strategy;
+\item Blocking: same surname and the same first given name initial strategy (SFI);
 \item Linkage function: all 22 features defined in Table~\ref{table:features},

### 2015-08-22 paper.tex
max recall table

@@
 As commonly done in author disambiguation research \citep{levin2012citation},
-we evaluate the predicted clusters over training data ${\cal
-C}_\text{train}^\prime$, testing data ${\cal C}_\text{test}^\prime$ and the
-whole data ${\cal C}^\prime$, using both B3 \glnote{add ref} and pairwise \glnote{add ref} precision, recall
+we evaluate the predicted clusters over testing data  ${\cal C}_\text{test}^\prime$,
+using both B3 \glnote{add ref} and pairwise \glnote{add ref} precision, recall
 and F-measure, as defined below:
@@
                        & \multicolumn{3}{|c|}{\textbf{B3}} & \multicolumn{3}{|c|}{\textbf{Pairwise}} \\
-  \textbf{Description} & \textit{P} & \textit{R} & \textit{F} & \textit{P} & \textit{R} & \textit{F}\\
+  \textbf{Description} & $P$ & $R$ & $F$ & $P$ & $R$ & $F$\\
   \hline
@@
 Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
+\hline
+No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
 \hline
@@
   \hline
-No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
-  \hline
 \end{tabular}
@@
 
-% \begin{table}[H]
-% \caption{Base experiment evaluation)}
-% \centering
-% \begin{tabular}{|r|r|l|l|l|}
-%   \hline
-%   Evaluation & Set & Precision & Recall & F-score \\
-%   \hline
-%   Pairwise & test & 0.9948 & 0.9738 & 0.9842 \\
-%   \hline
-%   Pairwise & train & 0.9976 & 0.9747 & 0.986 \\
-%   \hline
-%   Pairwise & overall & 0.9952 & 0.9739 & 0.9844 \\
-%   \hline
-%   $B^3$ & test & 0.9901 & 0.976 & 0.983 \\
-%   \hline
-%   $B^3$ & train & 0.997 & 0.979 & 0.9879 \\
-%   \hline
-%   $B^3$ & overall & 0.9907 & 0.9761 & 0.9834 \\
-%   \hline
-% \end{tabular}
-% \end{table}
-
 \textit{Blocking.}
@@
 \glnote{Discuss blocking in terms of maximum recall}
+
+\begin{table}
+\caption{Maximum recall of blocking strategies.}
+\label{table:results}
+\centering
+\begin{tabular}{|l|c|c|}
+  \hline
+  \textbf{Blocking} & $R_\text{B3}^*$ & $R_\text{pairwise}^*$ \\
+  \hline
+  \hline
+    SFI & 0.9828 & 0.9776 \\
+    Double metaphone & 0.9907 & 0.9863 \\
+    NYSIIS & 0.9902 & 0.9861 \\
+    Soundex & 0.9906 & 0.9863 \\
+  \hline
+\end{tabular}
+\end{table}
 
@@
 
-% \begin{table}[H]
-% \caption{Blocking limited maximum recalls (BLMR) on the whole dataset without splitting over
-% the first given name initial}
-% \centering
-% \begin{tabular}{|r|l|l|}
-%   \hline
-%   blocking function & BLMR with $B^{3}$ recall & BLMR with pairwise recall \\
-%   \hline
-%   last name and first initial & 0.9827 & 0.9776 \\
-%   \hline
-%   phonetic using double metaphone & 0.9967 & 0.9953 \\
-%   \hline
-%   phonetic using nysiis & 0.9961 & 0.9951 \\
-%   \hline
-%   phonetic using soundex & 0.9966 & 0.9953 \\
-%   \hline
-% \end{tabular}
-% \end{table}
-
 % \msnote{Mention two new features for this experiments, other than that everything is the
 % same as in the base experiment}
-
-% \begin{table}[H]
-% \caption{Phonetic algorithm performance}
-% \centering
-% \begin{tabular}{|r|r|r|l|l|l|}
-%   \hline
-%   Phonetic Algorithm & Split over initial & Evaluation & Precision & Recall & F-score \\
-%   \hline
-%   Double Metaphone & yes & pairwise & 0.9934 & 0.982 & 0.9876 \\
-%   \hline
-%   Double Metaphone & yes & $B^3$ & 0.9867 & 0.983 & 0.9848 \\
-%   \hline
-%   Double Metaphone & no & pairwise & - & - & - \\
-%   \hline
-%   Double Metaphone & no & $B^3$ & - & - & - \\
-%   \hline
-%   NYSIIS & yes & pairwise & 0.9942 & 0.9818 & 0.9879 \\
-%   \hline
-%   NYSIIS & yes & $B^3$ & 0.9884 & 0.9828 & 0.9856 \\
-%   \hline
-%   NYSIIS & no & pairwise & - & - & - \\
-%   \hline
-%   NYSIIS & no & $B^3$ & - & - & - \\
-%   \hline
-%   Soundex & yes & pairwise & - & - & - \\
-%   \hline
-%   Soundex & yes & $B^3$ & - & - & - \\
-%   \hline
-%   Soundex & no & pairwise & - & - & - \\
-%   \hline
-%   Soundex & no & $B^3$ & - & - & - \\
-%   \hline
-% \end{tabular}
-% \end{table}
-
-% \msnote{Fill the table}
 

### 2015-08-22 paper.tex
save

@@
 No cut & 0.9024 & 0.9828 & 0.9409 & 0.8298 & 0.9776 & 0.8977 \\
-Global cut & -- & -- & -- & -- & -- & -- \\
+Global cut \glnote{TODO} & -- & -- & -- & -- & -- & -- \\
 Block cut & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
@@
 
-\textit{Baseline.} Results presented in this section are all discussed with
+\textit{Baseline.} Results presented in Table~\ref{table:results} are all discussed with
 respect to a baseline solution using the following combination of components:
@@
 
-\textit{Blocking.}
+\textit{Blocking.} The very good precision of the baseline ($0.9901$) but its
+lower recall ($0.9760$) suggests that the blocking strategy might be the
+limiting factor to further overall improvements. As Table~\ref{table:blocking}
+indeed indicates, the maximum recall (i.e., if within a block, all signatures
+were clustered optimally) for SFI is $0.9828$ , hence not letting much more
+room for improvement. At the price of fewer and therefore slightly larger
+blocks (as reported in the right column of Table~\ref{table:blocking}), the
+proposed phonetic-based blocking strategies show better maximum recall (all
+around $0.9905$), thereby pushing further the upper bound on the maximum overall
+performance of author disambiguation. As Table~\ref{table:results} indeed shows,
+switching to either Double metaphone or NYSIIS phonetic-based blocking allows
+to improve the overall F-measure score, trading precision for recall. In particular,
+the NYSIIS-based phonetic blocking shows to be the most effective when applied
+to the baseline (with an F-measure of $0.9850$) while also being the most
+efficient computationally (with 10857 blocks versus 12978 for the baseline).
 
-\glnote{Discuss baseline + different blocking strategies}\\
-\glnote{Discuss blocking in terms of maximum recall}
+Finally, let us also note that Table~\ref{table:blocking} corroborates the
+estimation of \citep{torvik2009author}, stating that SFI blocking has a recall
+around $98\%$ on real data.
 
 \begin{table}
-\caption{Maximum recall of blocking strategies.}
-\label{table:results}
+\caption{Maximum recall of blocking strategies, and their number of blocks on ${\cal S}^\prime$.}
+\label{table:blocking}
 \centering
-\begin{tabular}{|l|c|c|}
+\begin{tabular}{|l|cc|c|}
   \hline
-  \textbf{Blocking} & $R_\text{B3}^*$ & $R_\text{pairwise}^*$ \\
+  \textbf{Blocking} & $R_\text{B3}^*$ & $R_\text{pairwise}^*$ & \# blocks \\
   \hline
   \hline
-    SFI & 0.9828 & 0.9776 \\
-    Double metaphone & 0.9907 & 0.9863 \\
-    NYSIIS & 0.9902 & 0.9861 \\
-    Soundex & 0.9906 & 0.9863 \\
+    SFI & 0.9828 & 0.9776 & 12978 \\
+    Double metaphone & 0.9907 & 0.9863 & 9753 \\
+    NYSIIS & 0.9902 & 0.9861 & 10857 \\
+    Soundex & 0.9906 & 0.9863 & 9403 \\
   \hline
@@
 
-% \glnote{To review}
-
-% Let us introduce a term \textit{blocking limited maximum recall} to describe the highest
-% recall that the algorithm can theoretically reach after blocking is done.
-% Formally, for the set of signatures ${\cal S}$, blocking function $F: \mathcal{S}
-% \rightarrow \mathcal{B}$, where $ \mathcal{B} = \{s_{0}, \ldots{} , s_{N-1}\}$ is a
-% partition of $\mathcal{S} $ , the recall function $\mathcal{R}: \mathcal{C}_{gold},
-% \mathcal{C}_{predicted} \rightarrow \langle0,1\rangle$ where $\mathcal{C}_{gold}$ is the
-% partition of $\mathcal{S}$ where for every author there is a set in $\mathcal{C}_{gold}$
-% that contains only all the signatures of this author, $\mathcal{C}_{predicted}$ is the
-% partition of $\mathcal{S}$ output by the algorithm, and $\mathcal{Q} = \{\cup_{i=0}^{N-1}
-% q_i $ : $\forall_{i \in \langle0,N-1\rangle} q_i$ is a partition of $s_i$\}. Then
-% \textit{blocking limited maximum recall} is defined as $\max_{q \in \mathcal{Q}}
-% \mathcal{R}(\mathcal{C}_{gold}, q)$. For sanely defined recall functions, such as $B^{3}$
-% recall or \textit{pairwise} recall \msnote{Further explanation needed, why it is
-% equivalent?}, it is equivalent to $\mathcal{R}(\mathcal{C}_{gold}, \mathcal{B})$.
-
-% The \textit{blocking limited maximum recall} for the last name and first initial blocking
-% and $B^3$ scoring equals 0.9827. Comparing it to the $B^3$ recall of the base experiment,
-% one can see that a huge part of errors comes from the blocking step which forbids some of
-% the pairs to be merged together. To prevent that, we tried the phonetic blocking algorithm
-% using three different phonetic algorithms: Double Metaphone \citep{doublemetaphone}, NYSIIS
-% \citep{nysiis} and Soundex \citep{Soundex}. As Double Metaphone can return two results for a
-% string, we always discarded the second one when we used this algorithm.
-
-% \msnote{Mention two new features for this experiments, other than that everything is the
-% same as in the base experiment}
-
-% compare with torvik & smalheiser (2009) who argue that lnfi blocking has recall around 98%
-% MS - recall for lnfi (blocking only) 0.9776, lnfi (whole algorithm) 0.9739,
-% MS - all three results use pairwise scoring
+\textit{Normalization.} As discussed before, the seemingly anodyne step of
+normalizing author names (stripping accents, removing affixes), as done in the
+baseline, reveals to be quite significant. Results of Table~\ref{table:results}
+indeed clearly suggests that not normalizing significantly reduces performance
+(yielding an F-measure of $0.9830$ when normalizing, but decreasing to $0.9791$
+when raw author name strings are used instead).
 

### 2015-08-22 paper.tex
title

@@
 
-\title{Author disambiguation of large-scale semi-labeled collections of scientific articles}
+\title{Ethnicity sensitive author disambiguation of semi-labeled corpora of scientific articles}
 
@@
 Scikit-Learn API \citep{scikitlearnAPI}, making them easy to maintain,
-understand and reuse.
-
-\glnote{Not sure we should talk about parallelization?}
-\glnote{Mention (future) deployment in Inspire?}
-
-% Performance-wise, the clustering step appeared to be the bottleneck. We improved the
-% algorithmic efficiency by parallelizing it. Having $n$ cores available, one can run the
-% semi-supervised clustering for $n$ different blocks in the same moment. In the production
-% systems the disambiguation often need not be run on the whole dataset. Once the dataset has
-% been disambiguated once, it is possible to avoid rerunning the whole algorithm when the new
-% signatures arrive in the digital library. First of all, the similarity function can be
-% reused. Moreover, the clustering has to be applied only to the blocks the new signatures are
-% contained within.
+understand and reuse. Our implementation is made to be efficient, exploiting
+parallelization when available, making it ready for production environments.
 
@@
 
-\textit{Normalization.} As discussed before, the seemingly anodyne step of
+\textit{Name normalization.} As discussed before, the seemingly anodyne step of
 normalizing author names (stripping accents, removing affixes), as done in the

### 2015-08-22 paper.tex
save

@@
 
-Observing that author names from different cultures or origins are likely to be
+Observing that author names from different cultures, origins or ethnic groups are likely to be
 disambiguated using different strategies (e.g., pairs of signatures with French

### 2015-08-23 paper.tex
save

@@
 hence unfairly giving preference to authors with many publications. By contrast,
-B3 measures weight clusters linearly with respect to their size.
+B3 measures weight clusters linearly with respect to their size. General conclusions
+drawn below remain however consistent for pairwise measures.
 
@@
 \hline
+Standard features & -- & -- & -- & -- & -- & -- \\
+Standard + Ethnicity features & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+\hline
 Clustering = Average linkage & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
@@
 No cut & 0.9024 & 0.9828 & 0.9409 & 0.8298 & 0.9776 & 0.8977 \\
-Global cut \glnote{TODO} & -- & -- & -- & -- & -- & -- \\
+Global cut & -- & -- & -- & -- & -- & -- \\
 Block cut & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
@@
 normalizing author names (stripping accents, removing affixes), as done in the
-baseline, reveals to be quite significant. Results of Table~\ref{table:results}
+baseline, reveals to be quite important. Results of Table~\ref{table:results}
 indeed clearly suggests that not normalizing significantly reduces performance
@@
 
-\textit{Linkage function.}
+\textit{Linkage function.} Let us first comment on the results regarding the
+supervised algorithm used to learn the linkage function. As
+Table~\ref{table:results} indicates, both tree-based algorithms appear to be
+significantly better fit than Linear Regression ($0.9830$ and $0.9846$ for GBRT
+and Random Forests versus $0.9666$ for Linear Regression). This result is
+consistent with \citep{treeratpituk2009disambiguating} which evaluated the use
+Random Forests for author disambiguation, but contradicts results of
+\citep{levin2012citation} for which Logistic Regression appeared to be the best
+classifier. Provided hyper-parameters are properly tuned, the superiority of
+tree-based methods is in our opinion not surprising. Indeed, given the fact
+that the optimal linkage function is likely to be non-linear, non-parametric
+methods are expected to yield better results, as the experiments here confirm.
+
+Next, properly constructing a training set of positive and negative pairs of
+signatures from which to learn a linkage function reveals to yield quite an
+improvement. A random sampling of positive and negative pairs, without taking
+blocking into account, significantly impacts the overall performance
+($0.9711$). When pairs are drawn from only from blocks, performance increases
+($0.9786$), which confirms our intuition that $d$ should be built only from
+pairs it will be used to eventually cluster. Finally, making the classification
+problem more difficult by oversampling complex cases proves to be relevant,
+by further improving the disambiguation results ($0.9830$).
+
 % feature engineering
@@
 
+\glnote{Mention Hussein's thesis for further experiments}
+
 % References ==================================================================

### 2015-08-23 paper.tex
save

@@
 are pairs of signatures and outputs are classes $0$ (same authors) and $1$
-(distinct authors). In this work, we evaluate Random Forests \citep{breiman2001random},
-Gradient Boosted Regression Trees \citep{friedman2001greedy} and Logistic Regression \citep{fan2008liblinear} as classifiers.
+(distinct authors). In this work, we evaluate Random Forests (RF, \cite{breiman2001random}),
+Gradient Boosted Regression Trees (GBRT, \cite{friedman2001greedy}) and Logistic Regression \citep{fan2008liblinear} as classifiers.
 
@@
 
-Next, properly constructing a training set of positive and negative pairs of
+Second, properly constructing a training set of positive and negative pairs of
 signatures from which to learn a linkage function reveals to yield quite an
@@
 by further improving the disambiguation results ($0.9830$).
+
+\begin{figure}
+\centering
+\label{fig:rfe}
+\includegraphics[scale=0.5]{figures/rfe.pdf}
+\caption{\glnote{todo}}
+\end{figure}
+
+Using Recursive Feature Elimination \cite{guyon2002gene} combined
+with feature importances \citep{louppe2013understanding} extracted from GBRT,
+we next evaluate the usefulness of all 15 standard and 7
+additional ethnicity features used together for learning the linkage function.
 

### 2015-08-23 paper.tex
save

@@
 \centering
+\caption{Recursive Feature Elimimation analysis. }
 \label{fig:rfe}
 \includegraphics[scale=0.5]{figures/rfe.pdf}
-\caption{\glnote{todo}}
 \end{figure}
 
-Using Recursive Feature Elimination \cite{guyon2002gene} combined
-with feature importances \citep{louppe2013understanding} extracted from GBRT,
-we next evaluate the usefulness of all 15 standard and 7
-additional ethnicity features used together for learning the linkage function.
+Using Recursive Feature Elimination \cite{guyon2002gene}, we next evaluate the
+usefulness of all 15 standard and 7 additional ethnicity features for learning
+the linkage function. The analysis consists in using the baseline algorithm
+first using all 22 features, to determine the least discriminative from feature
+importances \citep{louppe2013understanding}, and then re-learn the baseline
+using all but that one feature. That process is repeated recursively until
+eventually only one feature remains. Results are presented in
+Figure~\ref{fig:rfe} for one the three folds, starting from the far right with
+the baseline and \textit{Second given name} being the least important feature,
+and ending on the left with all features eliminated but \textit{Chinese}. As
+the figure illustrates, the most important features are ethnic-based features
+(\textit{Chinese}, \textit{Other Asian}, \textit{Black}) along with
+\textit{Co-authors}, \textit{Affiliation} and \textit{Full name}. Adding the remaining
+other features only brings marginal improvements, with \textit{Journal},
+\textit{Abstract}, \textit{Collaborations}, \textit{References} \textit{Given
+name initial} and \textit{Second given name} being almost insignificant.
+Overall, these results highlight the added value of the proposed ehtnic-based
+features. Their duality in modeling both the similarity between author names
+and their origins make them very strong predictors for author disambiguation.
+The results also corroborates results from \citep{ferreira2010effective}, who
+found that the similarity between co-authors was a highly discriminative
+feature. It indeed appears in 4th in our ranking and brings very significant
+improvements. In case computational complexity is a concern, this analysis also
+underline the fact that decent performance can be achieved using only a very
+limited set of features, as also observed in
+\citep{treeratpituk2009disambiguating} or \citep{levin2012citation}.
 
@@
 
-\textit{Semi-supervised clustering.}
+\textit{Semi-supervised clustering.} The last part of our experiments concerns
+the study of agglomerative clustering and the best way to find a cut-off
+threshold to form clusters.
+
 % compare agglomerative algorithms

### 2015-08-23 paper.tex
save

@@
 \label{fig:rfe}
-\includegraphics[scale=0.5]{figures/rfe.pdf}
+\includegraphics[width=\textwidth]{figures/rfe.pdf}
 \end{figure}
@@
 and their origins make them very strong predictors for author disambiguation.
+\glnote{Add note for Table.}
 The results also corroborates results from \citep{ferreira2010effective}, who
@@
 improvements. In case computational complexity is a concern, this analysis also
-underline the fact that decent performance can be achieved using only a very
-limited set of features, as also observed in
+underlines the fact that decent performance can be achieved using only a very
+small set of features, as also observed in
 \citep{treeratpituk2009disambiguating} or \citep{levin2012citation}.
-
-% feature engineering
-% variable importance analysis
-% supervised learning model
 
@@
 the study of agglomerative clustering and the best way to find a cut-off
-threshold to form clusters.
+threshold to form clusters. Results from Table~\ref{table:results}
+first clearly indicates that average linkage is significantly better than
+both single and complete linkage.
+
+\glnote{compare threshold strategies} \\
+\glnote{comment on the fact that not clustering is not that bad}
 

### 2015-08-24 paper.tex
save

@@
 \hline
-Standard features & -- & -- & -- & -- & -- & -- \\
-Standard + Ethnicity features & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
-\hline
 Clustering = Average linkage & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
@@
 No cut & 0.9024 & 0.9828 & 0.9409 & 0.8298 & 0.9776 & 0.8977 \\
-Global cut & -- & -- & -- & -- & -- & -- \\
+Global cut & 0.9892 & 0.9737 & 0.9814 & 0.9940 & 0.9727 & 0.9832 \\
 Block cut & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
@@
 
-\textit{Linkage function.} Let us first comment on the results regarding the
+\textit{Linkage function.} Let us first comment the results regarding the
 supervised algorithm used to learn the linkage function. As
@@
 blocking into account, significantly impacts the overall performance
-($0.9711$). When pairs are drawn from only from blocks, performance increases
+($0.9711$). When pairs are drawn only from blocks, performance increases
 ($0.9786$), which confirms our intuition that $d$ should be built only from
@@
 and their origins make them very strong predictors for author disambiguation.
-\glnote{Add note for Table.}
 The results also corroborates results from \citep{ferreira2010effective}, who
@@
 feature. It indeed appears in 4th in our ranking and brings very significant
-improvements. In case computational complexity is a concern, this analysis also
+improvements as the figure illustrates. In case computational complexity is a concern, this analysis also
 underlines the fact that decent performance can be achieved using only a very
@@
 
-\glnote{compare threshold strategies} \\
-\glnote{comment on the fact that not clustering is not that bad}
-
-% compare agglomerative algorithms
-% compare threshold strategies
-% compare cold start solutions
+Clustering together all signatures from the same block is the least effective
+strategy ($0.9409$), but yields anyhow surprisingly decent accuracy, given the
+fact it requires almost no computation (i.e., both learning a linkage function
+and running agglomerative clustering can be skipped -- only the blocking
+function is needed to group signatures). In particular, this result reveals
+that author names are not ambiguous in most cases\footnote{This holds for the
+data we extracted, but may in the future, with the rise of non-Western
+researchers, be an underestimate of the ambiguous cases.} and that only a small
+fraction of them requires advanced disambiguation procedures. On the other
+hand, both global and block cut thresholding strategies give very good results,
+with a slight advantage for block cuts ($0.9814$ versus $0.9830$), as expected.
+In case ${\cal S}^\prime_b$ is empty (e.g., because it corresponds to a young
+researcher at the beginning of his career), this therefore suggests that using
+a cut-off threshold learned globally from the known data would in general give
+satisfactory results, only marginally worse than if claimed signatures had been
+known.
 

### 2015-08-24 paper/paper.tex
structure

--- 2015-08-24 paper.tex
@@
 disambiguation system capable of inferring patterns for identifying
-publications written by a same person.  Building upon more than 1 million
-crowdsourced annotations, we propose an automated author disambiguation
-solution exploiting this data (i) to learn an accurate classifier for
-identifying corefering authors and (ii) to guide the clustering of scientific
-publications by distinct authors in a semi-supervised way. To the best of our
-knowledge, our analysis is the first to be carried out on data of this size and
-coverage. It reveals that... \glnote{To be completed with actual results.}
+publications written by a same person.  Building upon more than 1 million of
+publicly released crowdsourced annotations, we propose an automated author
+disambiguation solution exploiting this data (i) to learn an accurate
+classifier for identifying corefering authors and (ii) to guide the clustering
+of scientific publications by distinct authors in a semi-supervised way. To the
+best of our knowledge, our analysis is the first to be carried out on data of
+this size and coverage. With respect to the state of the art, we validate the
+general pipeline used in most existing solutions, and improve by proposing
+phonetic-based blocking strategies, thereby increasing recall, and strong
+ethnicity-sensitive features for learning a linkage function, thereby tailoring
+disambiguation to non-Western author names whenever necessary.
 
@@
 publications by distinct authors in a semi-supervised way. Our analysis of parameters
-and features on this large training set reveals that...
-
-\glnote{To be completed with actual results.}\\
-\glnote{Also mention error analysis, suggesting that
-uncertain disambiguation results should be suggested to human curators, thereby
-closing the loop and creating a virtuous circle.}\\
-\glnote{New idea: phonetization in blocking}\\
-\glnote{New idea: ethnicity features}
+and features on this large dataset reveals that the general pipeline
+commonly used in existing solutions is an effective solution for author disambiguation.
+In addition, and  as validated
+by experimental results, we propose alternative strategies for blocking based on the
+phonetization of author names, thereby increasing recall. We also propose
+effective ethnicity-sensitive features for learning a linkage function,
+thereby tailoring author
+disambiguation to non-Western author names whenever necessary.
 

### 2015-08-24 paper/paper.tex
save

@@
 general pipeline used in most existing solutions, and improve by proposing
-phonetic-based blocking strategies, thereby increasing recall, and strong
+phonetic-based blocking strategies, thereby increasing recall, along with strong
 ethnicity-sensitive features for learning a linkage function, thereby tailoring
@@
 the reliability of bibliometrics and author rankings (e.g., citation counts or other impact
-metrics, as studied in \citep{strotmann2012author}) or the relevance of scientific network analysis.
-\glnote{Add more references.}
+metrics, as studied in \citep{strotmann2012author}) or the relevance of scientific network analysis
+\citep{newman2001structure}.
 
@@
 machine learning-based methods have been proposed during the past decade to
-provide immediate, less costly and efficient solutions to author
+provide immediate, less costly and satisfactory solutions to author
 disambiguation. In this work, our goal is to explore and demonstrate how both
@@
 and features on this large dataset reveals that the general pipeline
-commonly used in existing solutions is an effective solution for author disambiguation.
+commonly used in existing solutions is an effective approach for author disambiguation.
 In addition, and  as validated
@@
 and their origins make them very strong predictors for author disambiguation.
-The results also corroborates results from \citep{ferreira2010effective}, who
+The results also corroborates results from \citep{kang2009co} or \citep{ferreira2010effective}, who
 found that the similarity between co-authors was a highly discriminative

### 2015-08-24 paper/paper.tex
save

@@
 culotta2007author,treeratpituk2009disambiguating,tran2014author}. Because
-training data is often not easily available, unsupervised approaches propose
-instead to use domain-specific, often manually designed, linkage functions tailored for author
+training data is usually not easily available, unsupervised approaches propose
+instead to use domain-specific,  manually designed, linkage functions tailored for author
 disambiguation \citep{malin2005unsupervised,mcrae2006also,song2007efficient,
@@
 In this context, we position the work presented in this paper as a
-semi-supervised  solution for author disambiguation, but with the significant
+semi-supervised  solution for author disambiguation, with the significant
 advantage of having a very large collection of more than 1 million crowdsourced annotations
@@
 \begin{figure}
-\label{fig:signature}
 \begin{tabular}{ l l l }
@@
 title, co-authors or date of publication.}
+\label{fig:signature}
 \end{figure}
@@
 groups signatures together if they share the same surname(s) and the same first
-given name initial (e.g., "Doe, J"). Despite satisfying performance, such
+given name initial (e.g., SFI("Doe, John") $==$ "Doe, J"). Despite satisfactory performance, such
 a simple strategy fails in several cases, as listed below for
@@
 In the case of multiple surnames (cases 2 and 3), we further propose to block
-signatures in two phases. In the first phase, all the signatures with  one
+signatures in two phases. In the first phase, all the signatures with a single
 surname are clustered together. Every different surname token creates a new
@@
 not directly applicable to structured input spaces such as ${\cal S} \times
-{\cal S}$. Following previous works \glnote{add references}, pairs of
+{\cal S}$. Following previous works, pairs of
 signatures $(s_1, s_2)$ are first transformed to vectors $v \in \mathbb{R}^p$
@@
 \textit{Building a training set.} The distinctive aspect of our work is the
-knowledge of more than 1 million of crowdsourced annotations ${\cal C}^\prime = \{
+knowledge of more than 1 million crowdsourced annotations ${\cal C}^\prime = \{
 c_0^\prime, ..., c_{M-1}^\prime \}$, indicating together that all signature $s \in

### 2015-08-24 paper/paper.tex
save

@@
 understand and reuse. Our implementation is made to be efficient, exploiting
-parallelization when available, making it ready for production environments.
+parallelization when available and making it ready for production environments.
 
@@
 high-energy physics. Overall, the portal holds more than 1 million
-publications, forming in total a set ${\cal S}$ of more than 10 millions
+publications ${\cal P}$, forming in total a set ${\cal S}$ of more than 10 millions
 signatures. Out of these, around 13\% have been \textit{claimed} by their
@@
 components and refinements, as described in Section~\ref{methods}, follow a
-standard 3-fold cross-validation protocol, using $({\cal S}^\prime, {\cal C}^\prime)$ as
-ground-truth dataset. To replicate the $|{\cal S}^\prime| / |{\cal S}| \approx 13\%$ ratio
-of claimed signatures with respect to the total set of signatures, as on the
-INSPIRE platform, cross-validation folds are constructed by sampling a training
-set ${\cal S}_\text{train}^\prime \subseteq {\cal S}^\prime$ of 13\% of claimed
-signatures, and by using the remaining signatures ${\cal S}_\text{test}^\prime = {\cal S}^\prime \setminus {\cal S}_\text{train}^\prime$ for testing. Accordingly, ${\cal
-C}_\text{train}^\prime = \{ c^\prime \cap {\cal S}_\text{train}^\prime |
-c^\prime \in {\cal C}^\prime \}$ represents the partial known
-clusters on the training fold, while ${\cal C}_\text{test}^\prime$ are those
-used for testing.
+standard 3-fold cross-validation protocol, using $({\cal S}^\prime, {\cal
+C}^\prime)$ as ground-truth dataset. To replicate the $|{\cal S}^\prime| /
+|{\cal S}| \approx 13\%$ ratio of claimed signatures with respect to the total
+set of signatures, as on the INSPIRE platform, cross-validation folds are
+constructed by sampling 13\% of claimed signatures to form a training set ${\cal
+S}_\text{train}^\prime \subseteq {\cal S}^\prime$, and by using the remaining
+signatures ${\cal S}_\text{test}^\prime = {\cal S}^\prime \setminus {\cal
+S}_\text{train}^\prime$ for testing. Accordingly, ${\cal C}_\text{train}^\prime
+= \{ c^\prime \cap {\cal S}_\text{train}^\prime | c^\prime \in {\cal C}^\prime
+\}$ represents the partial known clusters on the training fold, while ${\cal
+C}_\text{test}^\prime$ are those used for testing.
 
-As commonly done in author disambiguation research \citep{levin2012citation},
+As commonly done in author disambiguation research,
 we evaluate the predicted clusters over testing data  ${\cal C}_\text{test}^\prime$,
-using both B3 \glnote{add ref} and pairwise \glnote{add ref} precision, recall
+using both B3 and pairwise precision, recall
 and F-measure, as defined below:
@@
 | s_1, s_2 \in c, s_1 \neq s_2 \}$ is the set of all pairs of signatures from
-the same clusters in ${\cal C}$. Intuitively, precision evaluates if signatures
+the same clusters in ${\cal C}$. Intuitively, precision evaluates whether signatures
 are grouped only with signatures from the same true clusters, while recall
@@
 effectively grouped together. The F-measure is the harmonic mean between these
-two quantities. In the analysis below, we rely primarily on B3 measures for discussing
-the results, as pairwise measures tend to favor large clusters (because the number of pairs is quadratic with the cluster size),
+two quantities. In the analysis below, we rely primarily on the B3 F-measure for discussing
+results, as the pairwise variant tends to favor large clusters (because the number of pairs is quadratic with the cluster size),
 hence unfairly giving preference to authors with many publications. By contrast,
-B3 measures weight clusters linearly with respect to their size. General conclusions
-drawn below remain however consistent for pairwise measures.
+the B3 F-measure weights clusters linearly with respect to their size. General conclusions
+drawn below remain however consistent for pairwise F.
 
@@
 \hline
+\hline
 Blocking = SFI & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
 Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841 & 0.9927 & 0.9817 & 0.9871 \\
-Blocking = NYSIIS & 0.9875 & 0.9826 & 0.9850 & 0.9936 & 0.9814 & 0.9875 \\
+Blocking = NYSIIS & 0.9875 & 0.9826 & \textbf{0.9850} & 0.9936 & 0.9814 & \textbf{0.9875} \\
 Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
@@
 No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
+Name normalization & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
 \hline
 Classifier = GBRT & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
-Classifier = Random Forests & 0.9909 & 0.9783 & 0.9846 & 0.9957 & 0.9752 & 0.9854 \\
+Classifier = Random Forests & 0.9909 & 0.9783 & \textbf{0.9846} & 0.9957 & 0.9752 & \textbf{0.9854} \\
 Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666 & 0.9717 & 0.9569 & 0.9643 \\
@@
 Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786 & 0.9850 & 0.9707 & 0.9778 \\
-Training pairs = Blocked, balanced & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+Training pairs = Blocked, balanced & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
 \hline
-Clustering = Average linkage & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+Clustering = Average linkage & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
 Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671 & 0.9543 & 0.9626 & 0.9584 \\
@@
 Global cut & 0.9892 & 0.9737 & 0.9814 & 0.9940 & 0.9727 & 0.9832 \\
-Block cut & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
+Block cut & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
   \hline
@@
     gradient boosted regression trees as supervised learning algorithm
-    and a training set of pairs built by balancing easy and difficult cases.
+    and a training set of pairs built from $({\cal S}_\text{train}^\prime, {\cal C}_\text{train}^\prime)$, by balancing easy and difficult cases.
 \item Clustering: agglomerative clustering using average linkage and
@@
 proposed phonetic-based blocking strategies show better maximum recall (all
-around $0.9905$), thereby pushing further the upper bound on the maximum overall
+around $0.9905$), thereby pushing further the upper bound on the maximum
 performance of author disambiguation. As Table~\ref{table:results} indeed shows,
@@
 \glnote{Mention Hussein's thesis for further experiments}
+\glnote{Virtuous circle}
 

### 2015-08-24 paper/paper.tex
save

@@
 
-% future improvements
+In this work, we have revisited and validated the general author disambiguation
+pipeline introduced in previous and independent research works. The generic
+approach is made of three components, whose design and tuning are all critical
+to get good performance: (i) a blocking function for pre-clustering signatures
+and reducing computational complexity, (ii) a linkage function for identifying
+signatures with corefering authors and (iii) the agglomerative clustering of
+signatures. Making use of a distinctively large dataset of more than 1 million
+crowdsourced annotations, we experimentally study all three components and
+propose further improvements. With regards to blocking, we suggest to use
+phonetization of author names to increase recall while maintaining low
+computational complexity. For the linkage function, we introduce
+ethnicity-sensitive features for the automatic tailoring of disambiguation to non-Western
+author names whenever necessary. Finally, we explore semi-supervised cut-off
+threshold strategies for agglomerative clustering. For all three components,
+experiments show that our refinements all yield significantly better author
+disambiguation accuracy, thereby encouraging further research in these directions.
 
-\glnote{Mention Hussein's thesis for further experiments}
-\glnote{Virtuous circle}
+As part of this study, we also publicly release the annotated data extracted
+from the INSPIRE platform, and on which our experiments are based on. To the
+best of our knowledge, data of this size and coverage is the first to be
+available in  author disambiguation research. By releasing the data publicly,
+we hope to set a benchmark on which further research on author disambiguation
+and related topics can  build upon.
+
+\section*{Acknowledgements}
+
+\glnote{todo}
 

### 2015-08-24 paper/paper.tex
save
Added in figure

--- 2015-08-24 paper/paper.tex
@@
 
-\begin{figure}
-\begin{tabular}{ l l l }
-  $s:$ & Title & Lorem ipsum dolor sit amet, consectetur adipiscing elit \\
-  & Author & Doe, John \\
-  & Affiliation & University of Foo \\
-  & Co-authors & Smith, John; Chen, Wang\\
-  & Year & 2015\\
-\end{tabular}
-
-\caption{An example of signature $s$ for "Doe, John". A \textit{signature} is
+\begin{figure*}[ht!]
+\centering
+\includegraphics[width=\textwidth]{figures/pub-to-signature}
+\caption{An example signature $s$ for "Doe, John". A \textit{signature} is
 defined as unique piece of information identifying an author on a publication,
@@
 \label{fig:signature}
-\end{figure}
+\end{figure*}
 
@@
 semi-supervised clustering of all signatures within a same block, using $d$ as a pseudo distance metric.
-
-\glnote{Figure required here (Eamonn)}
+%
+%\begin{figure*}[ht!]
+%\centering
+%\includegraphics[width=\textwidth]{figures/workflow}
+%\caption{Something workflowy...}
+%\label{fig:workflow}
+%\end{figure*}
 

### 2015-08-24 paper/paper.tex

--- 2015-08-24 paper/paper.tex
@@
 
-\begin{figure}
-\begin{tabular}{ l l l }
-  $s:$ & Title & Lorem ipsum dolor sit amet, consectetur adipiscing elit \\
-  & Author & Doe, John \\
-  & Affiliation & University of Foo \\
-  & Co-authors & Smith, John; Chen, Wang\\
-  & Year & 2015\\
-\end{tabular}
-
-\caption{An example of signature $s$ for "Doe, John". A \textit{signature} is
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=\textwidth]{figures/pub-to-signature}
+\caption{An example signature $s$ for "Doe, John". A \textit{signature} is
 defined as unique piece of information identifying an author on a publication,
@@
 
-\glnote{Figure required here (Eamonn)}
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=\textwidth]{figures/workflow}
+\caption{Something workflowy...}
+\label{fig:workflow}
+\end{figure*}
 
@@
 
-\glnote{Add a figure showing the three possible splits}
+\begin{figure*}[t!]
+\centering
+\includegraphics[width=\textwidth]{figures/cuts}
+\caption{Something cutty}
+\label{fig:cuts}
+\end{figure*}
 
@@
 As part of this study, we also publicly release the annotated data extracted
-from the INSPIRE platform, and on which our experiments are based on. To the
+from the INSPIRE platform, on which our experiments are based on. To the
 best of our knowledge, data of this size and coverage is the first to be
@@
 
-\section*{Acknowledgements}
+% \section*{Acknowledgements}
 
-\glnote{todo}
+% \glnote{todo}
 

### 2015-08-25 paper/paper.tex
captions and refs

@@
 
-\begin{figure*}[t!]
+\begin{figure}
 \centering
@@
 \label{fig:signature}
-\end{figure*}
+\end{figure}
 
@@
 we cast in this work author disambiguation into a semi-supervised clustering
-problem.  Our algorithm is made of three parts: (i) a blocking
+problem.  Our algorithm is made of three parts, as sketched in Figure~\ref{fig:workflow}: (i) a blocking
 scheme whose goal is to roughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
@@
 
-\begin{figure*}[t!]
+\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{figures/workflow}
-\caption{Something workflowy...}
+\caption{General pipeline for author disambiguation: (a)
+signatures are \textit{blocked} to reduce computational complexity, (b) a linkage
+function is built with supervised learning, (c) signatures within the same block
+are grouped using agglomerative clustering.}
 \label{fig:workflow}
-\end{figure*}
+\end{figure}
 
@@
 explicitly handled.
-
-%\glnote{I am not sure we need an explicit algorithm, but adding a few examples would help.}
 
@@
 the predicted clusters restricted to signatures for which partial
-clusters are known. From these, we evaluate the following semi-supervised cut-off strategies:
+clusters are known. From these, we evaluate the following semi-supervised cut-off strategies, as illustrated in Figure~\ref{fig:cuts}:
 \begin{itemize}
@@
 
-\begin{figure*}[t!]
+\begin{figure}
 \centering
 \includegraphics[width=\textwidth]{figures/cuts}
-\caption{Something cutty}
+\caption{Semi-supervised cut-off strategies to form flat clusters of signatures.}
 \label{fig:cuts}
-\end{figure*}
+\end{figure}
 

### 2015-08-25 paper/paper.tex
save

@@
 \includegraphics[width=\textwidth]{figures/workflow}
-\caption{General pipeline for author disambiguation: (a)
+\caption{Pipeline for author disambiguation: (a)
 signatures are \textit{blocked} to reduce computational complexity, (b) a linkage
-function is built with supervised learning, (c) signatures within the same block
+function is built with supervised learning, (c) independently within each block, signatures
 are grouped using agglomerative clustering.}
@@
 
-\glnote{Add a few examples of transformed pairs?}
+%\glnote{Add a few examples of transformed pairs?}
 

### 2015-08-25 paper/paper.tex
notations

@@
 denote by ${\cal S} = \{ s | s \in p, p \in {\cal P} \}$ the set of all
-signatures that can be extracted from all publications in ${\cal P}$ and
-by $S=|{\cal S}|$ the total number of signatures.
+signatures that can be extracted from all publications in ${\cal P}$.
 
@@
 computational complexity of clustering (see Section~\ref{methods:clustering})
-typically reduces from $O(S^2)$ to $O(\sum_b S_b^2)$, which becomes much more
+typically reduces from $O(|{\cal S}|^2)$ to $O(\sum_b |{\cal S}_b|^2)$, which becomes much more
 tractable as the number of signatures increases. Since disambiguation is

### 2015-08-25 paper/paper.tex
First pass on abstract, introduction, and related work.

--- 2015-08-25 paper/paper.tex
@@
 \usepackage{amsfonts}
+\usepackage{xspace}
 
@@
 \newcommand{\msnote}[1]{\textcolor{blue}{[MS: #1]}}
+\newcommand{\etal}{\emph{et al.}\xspace}
+\newcommand{\ie}{\emph{i.e.}\xspace}
+\newcommand{\eg}{\emph{e.g.}\xspace}
+\newcommand{\Eg}{\emph{E.g.}\xspace}
 
@@
 Author name disambiguation in bibliographic databases is the problem of
-grouping together scientific publications written by a same person, accounting
-for potential homonyms and/or synonyms. Among solutions to this problem,
-digital libraries are increasingly offering tools for authors to manually
-curate their publications and claim which ones are theirs. Indirectly, these
-tools allow for the inexpensive collection of large annotated training data,
-which can be further leveraged to build a complementary automated
+grouping together scientific publications written by the same person, accounting
+for potential homonyms and/or synonyms.
+Among solutions to this problem, digital libraries are increasingly offering tools 
+for authors to manually curate their publications and claim those that are theirs. 
+Indirectly, these tools allow for the inexpensive collection of large annotated training 
+data, which can be further leveraged to build a complementary automated
 disambiguation system capable of inferring patterns for identifying
-publications written by a same person.  Building upon more than 1 million of
-publicly released crowdsourced annotations, we propose an automated author
-disambiguation solution exploiting this data (i) to learn an accurate
-classifier for identifying corefering authors and (ii) to guide the clustering
-of scientific publications by distinct authors in a semi-supervised way. To the
-best of our knowledge, our analysis is the first to be carried out on data of
-this size and coverage. With respect to the state of the art, we validate the
-general pipeline used in most existing solutions, and improve by proposing
-phonetic-based blocking strategies, thereby increasing recall, along with strong
-ethnicity-sensitive features for learning a linkage function, thereby tailoring
-disambiguation to non-Western author names whenever necessary.
+publications written by the same person.
+Building on more than 1 million publicly released crowdsourced annotations, 
+we propose an automated author disambiguation solution exploiting this data (i) to learn 
+an accurate classifier for identifying coreferring authors and (ii) to guide the clustering
+of scientific publications by distinct authors in a semi-supervised way.
+To the best of our knowledge, our analysis is the first to be carried out on data of
+this size and coverage.
+With respect to the state of the art, we validate the general pipeline used in most existing 
+solutions, and improve by: (i) proposing phonetic-based blocking strategies, thereby 
+increasing recall; and (ii) adding strong ethnicity-sensitive features for learning a linkage 
+function, thereby tailoring disambiguation to non-Western author names whenever necessary.
 
@@
 In academic digital libraries, author name disambiguation is the problem of
-grouping together publications written by a same person.  Author name
-disambiguation is often a difficult problem because an author may use different
-spellings or name variants across her career (synonymy) and/or distinct authors may
-share the same name (polysemy). Most notably, author disambiguation is often even more
-troublesome in the case of researchers from non-Western cultures, where
-personal names may be traditionally less diverse (leading to homonym issues) or
-for which transliteration to Latin characters may not be unique (leading to
-synonym issues). With the fast growth of the scientific literature, author
-disambiguation has become a pressing issue because the accuracy of information
-managed at the level of individuals directly affects the relevance search of
-results (e.g., when querying for all publications written by a given author),
-the reliability of bibliometrics and author rankings (e.g., citation counts or other impact
-metrics, as studied in \citep{strotmann2012author}) or the relevance of scientific network analysis
+grouping together publications written by the same person.
+Author name disambiguation is often a difficult problem because an author may use different
+spellings or name variants across their career (synonymy) and/or distinct authors may
+share the same name (polysemy).
+Most notably, author disambiguation is often more troublesome for researchers 
+from non-Western cultures, where personal names may be traditionally less diverse (leading to 
+homonym issues) or for which transliteration to Latin characters may not be unique (leading to
+synonym issues). 
+With the fast growth of the scientific literature, author disambiguation has become a pressing 
+issue since the accuracy of information managed at the level of individuals directly affects: 
+the relevance search of results (\eg, when querying for all publications written by a given author);
+the reliability of bibliometrics and author rankings (\eg, citation counts or other impact
+metrics, as studied in \citep{strotmann2012author}); and/or the relevance of scientific network analysis
 \citep{newman2001structure}.
@@
 authorship control through manual curation, either in a centralized way by
-hiring collaborators or by developing services inviting authors to register
-their publications themselves (e.g., Google Scholar, Inspire-HEP, ...).
-Recently, efforts also started to create persistent digital identifiers
-assigned to researchers (e.g., ORCID, ResearchedID, ...), with the further
-objective to embed these identifiers in the submission workflow of publishers
-or repositories (e.g., Elsevier, arXiv, Inspire-HEP, ...), thereby univocally
-solving any disambiguation issue. With the large cost of centralized manual
-authorship control, or until the larger adoption of crowdsourced solutions, the
-impact of these efforts are unfortunately limited by the efficiency, motivation
-and integrity of their active contributors. Similarly, the success of
-persistent digital identifier efforts is conditioned to a large and ubiquitous
-adoption by both researchers and publishers. For these reasons, fully automated
-machine learning-based methods have been proposed during the past decade to
-provide immediate, less costly and satisfactory solutions to author
+hiring collaborators or through developing services that invite authors to register
+their publications themselves (\eg, Google Scholar, and Inspire-HEP).
+Recent efforts to create persistent digital identifiers assigned to researchers (\eg, ORCID, and ResearchedID), 
+with the objective to embed these identifiers in the submission workflow of publishers
+or repositories (\eg, Elsevier, arXiv, Inspire-HEP), would univocally solve any disambiguation issue.
+With the large cost of centralized manual authorship control, or until crowdsourced solutions are more 
+widely adopted, the impact of these efforts are unfortunately limited by the efficiency, motivation
+and integrity of their active contributors. Similarly, the success of persistent digital identifier efforts 
+is conditioned to a large and ubiquitous adoption by both researchers and publishers.
+For these reasons, fully automated machine learning-based methods have been proposed during the past decade to
+provide immediate, less costly, and satisfactory solutions to author
 disambiguation. In this work, our goal is to explore and demonstrate how both
-approaches can coexist and benefit from each other.  In particular, we study
-how labeled data obtained through manual curation (either centralized or
+approaches can coexist and benefit from each other.
+In particular, we study how labeled data obtained through manual curation (either centralized or
 crowdsourced) can be exploited (i) to learn an accurate classifier for
-identifying corefering authors and (ii) to guide the clustering of scientific
-publications by distinct authors in a semi-supervised way. Our analysis of parameters
-and features on this large dataset reveals that the general pipeline
+identifying coreferring authors, and (ii) to guide the clustering of scientific
+publications by distinct authors in a semi-supervised way.
+Our analysis of parameters and features of this large dataset reveal that the general pipeline
 commonly used in existing solutions is an effective approach for author disambiguation.
-In addition, and  as validated
-by experimental results, we propose alternative strategies for blocking based on the
-phonetization of author names, thereby increasing recall. We also propose
-effective ethnicity-sensitive features for learning a linkage function,
-thereby tailoring author
-disambiguation to non-Western author names whenever necessary.
+Additionally, we propose alternative strategies for blocking based on the
+phonetization of author names to increase recall.
+We also propose ethnicity-sensitive features for learning a linkage function,
+thereby tailoring author disambiguation to non-Western author names whenever necessary.
 
-The remaining of this report is structured as follows. In Section~\ref{related-works},
-we first briefly review machine learning solutions for author disambiguation.
+The remainder of this report is structured as follows. In Section~\ref{related-works},
+we briefly review machine learning solutions for author disambiguation.
 The components of our method are then defined in Section~\ref{methods}
@@
 
-As reviewed in
-\citep{smalheiser2009author,ferreira2012brief,levin2012citation}, author
+As reviewed in \citep{smalheiser2009author,ferreira2012brief,levin2012citation}, author
 disambiguation algorithms are usually composed of two main components: (i) a
-linkage function determining whether two publications have been written by a
-same author and (ii) a clustering algorithm producing clusters of publications
-assumed to be written by a same author. Approaches can be inventoried along
-several axes, depending on the type and amount of data available, the way the
-linkage function is learned or defined, or the clustering procedure used to
-group publications. Methods relying on supervised learning usually make use of
-a small set of
-hand-labeled pairs of publications identified as being either from the same or
-from different authors for learning automatically a linkage function between
-publications \citep{han2004two,huang2006efficient,
-culotta2007author,treeratpituk2009disambiguating,tran2014author}. Because
-training data is usually not easily available, unsupervised approaches propose
-instead to use domain-specific,  manually designed, linkage functions tailored for author
+linkage function determining whether two publications have been written by the
+same author; and (ii) a clustering algorithm producing clusters of publications
+assumed to be written by the same author.
+Approaches can be classified along several axes, depending on the type and 
+amount of data available, the way the linkage function is learned or defined, or the 
+clustering procedure used to group publications.
+Methods relying on supervised learning usually make use of a small set of hand-labeled pairs 
+of publications identified as being either from the same or different authors to automatically learn a linkage
+function between publications \citep{han2004two,huang2006efficient, culotta2007author,treeratpituk2009disambiguating,tran2014author}.
+
+Training data is usually not easily available, therefore unsupervised approaches propose
+use of domain-specific, manually designed linkage functions tailored towards author
 disambiguation \citep{malin2005unsupervised,mcrae2006also,song2007efficient,
-soler2007separating, kang2009co,fan2011graph,schulz2014exploiting}. These later
-approaches have the advantage of not requiring  hand-labeled data, but often do
-not perform as well as the supervised approaches. To reconcile both worlds,
-semi-supervised methods make use of small, manually verified, clusters of
-publications and/or of high-precision domain-specific rules to build a training
-set of pairs of publications, from which a linkage function is then built
-using supervised learning
+soler2007separating, kang2009co,fan2011graph,schulz2014exploiting}.
+These approaches have the advantage of not requiring hand-labeled data, but generally do
+not perform as well as supervised approaches.
+To reconcile both worlds, semi-supervised methods make use of small, manually verified, clusters of
+publications and/or high-precision domain-specific rules to build a training
+set of pairs of publications, from which a linkage function is then built using supervised learning
 \citep{ferreira2010effective,torvik2009author,levin2012citation}.
-Coincidentally, semi-supervised approaches also allow for the tuning of the
+
+Semi-supervised approaches also allow for the tuning of the
 clustering algorithm when the later is applied to a mixed set of labeled
-and unlabeled publications, e.g., by maximizing some clustering performance
+and unlabeled publications, \eg, by maximizing some clustering performance
 metric on the known clusters \citep{levin2012citation}.
 
-Because of the lack of a large and publicly available dataset of curated
+Due to the lack of large and publicly available datasets of curated
 clusters of publications, studies on author disambiguation are usually
-constrained to validate their results on manually built datasets of limited
-size and scope (from a few hundreds to a few thousands of papers, with a sparse
+constrained to validating their results on manually built datasets of limited
+size and scope (from a few hundred to a few thousand papers, with sparse
 coverage of ambiguous cases), making the true performance of these methods
-often difficult to assess with high confidence. In addition, despite devoted
-efforts to construct them, these datasets are very rarely released publicly,
-making it even more difficult to compare methods on a common benchmark.
+often difficult to assess with high confidence.
+Additionally, despite devoted efforts to construct them, these datasets are rarely public,
+making it even more difficult to compare methods using a common benchmark.
 
@@
 advantage of having a very large collection of more than 1 million crowdsourced annotations
-of publications whose true authors are identified. In particular, the extent and coverage
-of this data allows us to revisit, validate and nuance previous findings regarding
-supervised learning of linkage functions and to better explore strategies
-for semi-supervised clustering. Additionally, by releasing the data publicly,
-we hope to set a benchmark on which further research on author disambiguation
-and related topics can  build upon.
+of publications whose true authors are identified.
+The extent and coverage of this data allows us to revisit, validate and nuance previous 
+findings regarding supervised learning of linkage functions, and to better explore strategies
+for semi-supervised clustering.
+Furthermore, by releasing our data in to the public domain, we hope to provide a benchmark on 
+which further research on author disambiguation and related topics can be built.
 
@@
 define a signature $s \in p$ from a publication as a unique piece of
-information identifying one of the authors of $p$ (e.g., the author name, his
+information identifying one of the authors of $p$ (\eg, the author name, his
 affiliation, along with any other metadata that can be derived from $p$, as illustrated in Figure~\ref{fig:signature}). Let us
@@
 disambiguation boils down to finding a partition ${\cal C}$ where
-subsets $c_i$  each corresponds to the set of all signatures from a same
+subsets $c_i$  each corresponds to the set of all signatures from the same
 individual (without knowing who). Finally, in the case of partially annotated databases as studied in
@@
 $d$ between signatures using supervised learning; (iii) the
-semi-supervised clustering of all signatures within a same block, using $d$ as a pseudo distance metric.
+semi-supervised clustering of all signatures within the same block, using $d$ as a pseudo distance metric.
 
@@
 groups signatures together if they share the same surname(s) and the same first
-given name initial (e.g., SFI("Doe, John") $==$ "Doe, J"). Despite satisfactory performance, such
+given name initial (\eg, SFI("Doe, John") $==$ "Doe, J"). Despite satisfactory performance, such
 a simple strategy fails in several cases, as listed below for
@@
   ways of transcripting an author name or signatures contain a typo
-  (e.g., "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
+  (\eg, "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
 
   \item An author has multiple surnames and, on some signatures, all the surnames but the
-  last one are contained within given names (e.g., "Martinez Torres, A." and "Torres, A.
+  last one are contained within given names (\eg, "Martinez Torres, A." and "Torres, A.
   Martinez").
@@
   \item An author has multiple surnames and, on some signatures, only the first surname is
-  present (e.g., "Smith-Jones, A." and "Smith, A.")
+  present (\eg, "Smith-Jones, A." and "Smith, A.")
 
-  \item An author as multiple given names and they are not always all mentioned (e.g.,
+  \item An author as multiple given names and they are not always all mentioned (\eg,
   "Smith, Jack" and "Smith, A. J.")
 
-  \item An author changed his surname (e.g., because of marrying somebody).
+  \item An author changed his surname (\eg, because of marrying somebody).
 \end{enumerate}
@@
 phonetic representation of the normalized surname. Normalization consists in
-stripping accents (e.g., "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
-affixes that inconsistently appear in signatures (e.g., "van der Waals, J. D."
+stripping accents (\eg, "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
+affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."
 $\rightarrow$ "Waals, J. D."), while phonetization is based either on the
@@
 Soundex \citep{Soundex} algorithms. Together, these processing steps allow to
-group most name variants of a same person in the same block while not
+group most name variants of the same person in the same block while not
 significantly increasing computational complexity, thereby solving case 1.
@@
 automatic construction of a pair-wise linkage function between signatures, for
-later use during clustering to group all signatures from a same author.
+later use during clustering to group all signatures from the same author.
 Formally, the goal is to build a function $d: {\cal S} \times {\cal S} \mapsto
@@
 \textit{Input features.} In most cases, supervised learning algorithms assume
-the input space ${\cal X}$ to be numeric (e.g., $\mathbb{R}^p$), making them
+the input space ${\cal X}$ to be numeric (\eg, $\mathbb{R}^p$), making them
 not directly applicable to structured input spaces such as ${\cal S} \times
@@
 Observing that author names from different cultures, origins or ethnic groups are likely to be
-disambiguated using different strategies (e.g., pairs of signatures with French
+disambiguated using different strategies (\eg, pairs of signatures with French
 author names versus pairs of signatures with Chinese author names), and as
@@
 with a slight advantage for block cuts ($0.9814$ versus $0.9830$), as expected.
-In case ${\cal S}^\prime_b$ is empty (e.g., because it corresponds to a young
+In case ${\cal S}^\prime_b$ is empty (\eg, because it corresponds to a young
 researcher at the beginning of his career), this therefore suggests that using
@@
 and reducing computational complexity, (ii) a linkage function for identifying
-signatures with corefering authors and (iii) the agglomerative clustering of
+signatures with coreferring authors and (iii) the agglomerative clustering of
 signatures. Making use of a distinctively large dataset of more than 1 million

### 2015-08-25 paper/paper.tex
corrections

@@
 
-\title{Ethnicity sensitive author disambiguation of semi-labeled corpora of scientific articles}
+\title{Ethnicity sensitive author dissambiguation using semi-supervised learning}
 
@@
 
-\section{Related works}
+\section{Related work}
 \label{related-works}
@@
 
-In this context, we position the work presented in this paper as a
+In this context, we position the work in this paper as a
 semi-supervised solution for author disambiguation, with the significant
@@
 disambiguation boils down to finding a partition ${\cal C}$ where
-subsets $c_i$  each corresponds to the set of all signatures from the same
+subsets $c_i$  each correspond to the set of all signatures from the same
 individual (without knowing who). Finally, in the case of partially annotated databases as studied in
-this work, the setting extends with the partial knowledge ${\cal C}^\prime = \{ c_0^\prime, ..., c_{M-1}^\prime \}$ of ${\cal C}$,
-such that $c_i^\prime \subseteq c_i$, with $c_i^\prime$ possibly empty.
-Or put otherwise, the setting extends with the knowledge that all signatures
+this work, the set extends with the partial knowledge ${\cal C}^\prime = \{ c_0^\prime, ..., c_{M-1}^\prime \}$ of ${\cal C}$,
+such that $c_i^\prime \subseteq c_i$, where $c_i^\prime$ may be empty.
+Or put otherwise, the set extends with the assumption that all signatures
 $s \in c_i^\prime$ belong to the same author.
 
-As inspired from several previous works described in Section~\ref{related-works},
+Inspired by several previous works described in Section~\ref{related-works},
 we cast in this work author disambiguation into a semi-supervised clustering
-problem.  Our algorithm is made of three parts, as sketched in Figure~\ref{fig:workflow}: (i) a blocking
+problem. 
+Our algorithm is composed of three parts, as sketched in Figure~\ref{fig:workflow}: (i) a blocking
 scheme whose goal is to roughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
 reduce computational complexity; (ii) the construction of a linkage function
-$d$ between signatures using supervised learning; (iii) the
+$d$ between signatures using supervised learning; and (iii) the
 semi-supervised clustering of all signatures within the same block, using $d$ as a pseudo distance metric.
@@
 
-As in previous works, the first part of our algorithm consists in dividing
+As in previous works, the first part of our algorithm consists of dividing
 signatures ${\cal S}$ into disjoint subsets ${\cal S}_{b_0}, ..., {\cal
-S}_{b_{K-1}}$, or \textit{blocks} \citep{fellegi69}, and then to carry out
-author disambiguation independently on each one of these blocks. In doing so,
-computational complexity of clustering (see Section~\ref{methods:clustering})
-typically reduces from $O(|{\cal S}|^2)$ to $O(\sum_b |{\cal S}_b|^2)$, which becomes much more
-tractable as the number of signatures increases. Since disambiguation is
-performed independently per block, a good blocking strategy should ideally be
+S}_{b_{K-1}}$, or \textit{blocks} \citep{fellegi69}, followed by carrying out
+author disambiguation on each one of these blocks independently.
+By doing so, the computational complexity of clustering (see Section~\ref{methods:clustering})
+typically reduces from $O(|{\cal S}|^2)$ to $O(\sum_b |{\cal S}_b|^2)$, which is much more
+tractable as the number of signatures increases.
+Since disambiguation is performed independently per block, a good blocking strategy should be
 designed such that signatures from the same author are all mapped to the same
-block, otherwise directly preventing their correct clustering in later stages. As a
-result, blocking should balance between reduced complexity and maximum recall.
+block, otherwise their correct clustering would not be possible in later stages of the workflow.
+As a result, blocking should be a balance between reduced complexity and maximum recall.
 
-The simplest and most common strategy for blocking, further denoted to as SFI,
+The simplest and most common strategy for blocking, referred to hereon in as \emph{SFI},
 groups signatures together if they share the same surname(s) and the same first
-given name initial (\eg, SFI("Doe, John") $==$ "Doe, J"). Despite satisfactory performance, such
-a simple strategy fails in several cases, as listed below for
-pairs of signatures that should be clustered together but that are put into distinct
-blocks:
+given name initial (\eg, \emph{SFI}("Doe, John") $==$ "Doe, J").
+Despite satisfactory performance, there are several cases where this simple strategy fails to cluster related pairs of signatures together, including:
 
@@
   \item There are different
-  ways of transcripting an author name or signatures contain a typo
+  ways of writing an author name, or signatures contain a typo
   (\eg, "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
 
-  \item An author has multiple surnames and, on some signatures, all the surnames but the
-  last one are contained within given names (\eg, "Martinez Torres, A." and "Torres, A.
-  Martinez").
+  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (\eg, "Martinez Torres, A." and "Torres, A. Martinez").
 
@@
 
-  \item An author as multiple given names and they are not always all mentioned (\eg,
+  \item An author as multiple given names and they are not always all recorded (\eg,
   "Smith, Jack" and "Smith, A. J.")
 
-  \item An author changed his surname (\eg, because of marrying somebody).
+  \item An authors surname changed (\eg, due to marriage).
 \end{enumerate}
@@
 To account for these issues we propose instead to block signatures based on the
-phonetic representation of the normalized surname. Normalization consists in
-stripping accents (\eg, "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
+phonetic representation of the normalized surname.
+Normalization involves stripping accents (\eg, "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
 affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."
@@
 Double Metaphone \citep{doublemetaphone}, the NYSIIS \citep{nysiis} or the
-Soundex \citep{Soundex} algorithms. Together, these processing steps allow to
-group most name variants of the same person in the same block while not
-significantly increasing computational complexity, thereby solving case 1.
+Soundex \citep{Soundex} algorithms.
+Together, these processing steps allow for grouping of most name variants of the same
+person in the same block with a small increase in the overall computational complexity, thereby solving case 1.
 
-In the case of multiple surnames (cases 2 and 3), we further propose to block
-signatures in two phases. In the first phase, all the signatures with a single
-surname are clustered together. Every different surname token creates a new
-block. In the second phase, the signatures  with multiple surnames are compared
-with the blocks for the first and last surname.  If the first surnames of an
-author were already used as the last given names on some of the signatures, the
-new signature is assigned to the block of the last surname (case 2). Otherwise,
-the signature is assigned to the block of the first surname (case 3). Finally,
-to prevent the creation of too large blocks, signatures are further divided
-along their first given name initial.  Cases 4 and 5 are not
-explicitly handled.
+In the case of multiple surnames (cases 2 and 3), we propose to block
+signatures in two phases.
+In the first phase, all the signatures with a single surname are clustered together.
+Every different surname token creates a new block.
+In the second phase, the signatures with multiple surnames are compared
+with the blocks for the first and last surname.
+If the first surnames of an author were already used as the last given names on some of the signatures, the
+new signature is assigned to the block of the last surname (case 2).
+Otherwise, the signature is assigned to the block of the first surname (case 3).
+Finally, to prevent the creation of too large blocks, signatures are further divided
+along their first given name initial.
+Cases 4 and 5 are not explicitly handled.
 
@@
 \textit{Supervised classification.} The second part of the algorithm is the
-automatic construction of a pair-wise linkage function between signatures, for
-later use during clustering to group all signatures from the same author.
+automatic construction of a pair-wise linkage function between signatures for use 
+during the clustering step which grouping all signatures from the same author.
+
 Formally, the goal is to build a function $d: {\cal S} \times {\cal S} \mapsto
-[0, 1]$, such that $d(s_1, s_2)$ tends to $0$ if both signatures $s_1$ and
-$s_2$ belong to the same author, and $1$ otherwise. Coincidentally, this
-problem can be cast as a standard supervised classification task, where inputs
-are pairs of signatures and outputs are classes $0$ (same authors) and $1$
+[0, 1]$, such that $d(s_1, s_2)$ approaches $0$ if both signatures $s_1$ and
+$s_2$ belong to the same author, and $1$ otherwise.
+This problem can be cast as a standard supervised classification task, where inputs
+are pairs of signatures and outputs are classes $0$ (same authors), and $1$
 (distinct authors). In this work, we evaluate Random Forests (RF, \cite{breiman2001random}),
-Gradient Boosted Regression Trees (GBRT, \cite{friedman2001greedy}) and Logistic Regression \citep{fan2008liblinear} as classifiers.
+Gradient Boosted Regression Trees (GBRT, \cite{friedman2001greedy}), 
+and Logistic Regression \citep{fan2008liblinear} as classifiers.
 
@@
 not directly applicable to structured input spaces such as ${\cal S} \times
-{\cal S}$. Following previous works, pairs of
-signatures $(s_1, s_2)$ are first transformed to vectors $v \in \mathbb{R}^p$
-by building so-called similarity profiles
-\citep{treeratpituk2009disambiguating}, and on which supervised learning is
-then carried on. In this work, we design and evaluate 15 standard input
+{\cal S}$.
+Following previous works, pairs of signatures $(s_1, s_2)$ are first transformed to vectors $v \in \mathbb{R}^p$
+by building so-called similarity profiles \citep{treeratpituk2009disambiguating} on which supervised learning is carried out.
+In this work, we design and evaluate fifteen standard input
 features based on the comparison of signature fields, as reported in the first
-half of Table~\ref{table:features}. As an illustrative example, the
-\textit{Full name} feature corresponds to the similarity between the (full)
+half of Table~\ref{table:features}.
+As an illustrative example, the \textit{Full name} feature corresponds to the similarity between the (full)
 author name fields of the two signatures, as measured using as combination
-operator the cosine similarity between their respective $(n,m)$-TF-IDF vector
-representations\footnote{$(n,m)$ denotes that the TF-IDF vectors are computed
-from character $n$, $n+1$, ..., $m$-grams. When not specified, TF-IDF vectors
-are otherwise computed from words.}. Similarly, the \textit{Year difference}
-feature measures the absolute difference between the publication date of the
+operator the cosine similarity between their respective $(n,m)$-\emph{TF-IDF} vector
+representations\footnote{$(n,m)$ denotes that the \emph{TF-IDF} vectors are computed
+from character $n$, $n+1$, ..., $m$-grams.
+When not specified, \emph{TF-IDF} vectors are otherwise computed from words.}.
+Similarly, the \textit{Year difference} feature measures the absolute difference between the publication date of the
 articles to which the two signatures respectively belong.
 
-Observing that author names from different cultures, origins or ethnic groups are likely to be
+Author names from different cultures, origins or ethnic groups are likely to be
 disambiguated using different strategies (\eg, pairs of signatures with French
-author names versus pairs of signatures with Chinese author names), and as
-corroborated in \citep{treeratpituk2012name} or \citep{chin2014effective}, we
-propose to complement our feature set with 7 additional new features, each
-evaluating the degree of belonging of both signatures to several ethnic groups,
-as reported in the second half of Table~\ref{table:features}. More
-specifically, using census data extracted from \citep{rugglesintegrated}, we
+author names versus pairs of signatures with Chinese author names) \citep{treeratpituk2012name, chin2014effective}.
+To support our disambiguation algorithm, we added seven features to our feature set, with each
+evaluating the degree of belonging of both signatures to an ethnic group,
+as reported in the second half of Table~\ref{table:features}.
+
+More specifically, using census data extracted from \citep{rugglesintegrated}, we
 build a logistic regression classifier for mapping the $(1,5)$-TF-IDF
-representation of an author name to one of the 7 ethnic groups reported in that
-dataset. Given a pair of signatures $(s_1, s_2)$, the proposed ethnicity
+representation of an author name to one of the seven ethnic groups.
+Given a pair of signatures $(s_1, s_2)$, the proposed ethnicity
 features are each computed as the estimated probability of $s_1$ to belong to
@@
 linkage function to become sensitive to the actual origin of the authors
-depending on the values of these features. Indirectly, let us also note that these
-features hold discriminative power since, if author names are predicted
-to belong to different ethnic groups, then they are also likely to correspond to
-distinct actual persons.
+depending on the values of these features.
+Indirectly, let us also note that these features hold discriminative power since 
+if author names are predicted to belong to different ethnic groups, then they 
+are also likely to correspond to distinct people.
 
@@
 c_0^\prime, ..., c_{M-1}^\prime \}$, indicating together that all signature $s \in
-c_i^\prime$ are known to correspond to the same individual $a_i$. In particular,
-this data can be used to generate positive pairs $(x=(s_1, s_2), y=0)$ for all
+c_i^\prime$ are known to correspond to the same individual $a_i$.
+In particular, this data can be used to generate positive pairs $(x=(s_1, s_2), y=0)$ for all
 $s_1, s_2 \in c_i^\prime$, for all $i$. Similarly, negative pairs $(x=(s_1,
@@
 a linkage function is to sample an equal number of positive and negative pairs,
-as suggested above. By observing that the linkage function $d$ will eventually
+as suggested above.
+By observing that the linkage function $d$ will eventually
 be used only on pairs of signatures from the same block $S_b$, a further
@@
 block. In doing so, the trained classifier is forced to learn intra-block
-discriminative patterns rather than inter-block differences. Furthermore, as
-noted in \citep{lange2011frequency}, pairs of signatures are in the vast
-majority non-ambiguous: if both signatures share the same author names, then
-they correspond to the same individual, otherwise they do not. Rather than
-sampling pairs uniformly at random, we therefore propose to  oversample
-difficult cases when building the training set (i.e., pairs of signatures with
+discriminative patterns rather than inter-block differences.
+Furthermore, as noted in \citep{lange2011frequency}, most signature pairs are non-ambiguous: 
+if both signatures share the same author names, then
+they correspond to the same individual, otherwise they do not.
+Rather than sampling pairs uniformly at random, we propose to oversample
+difficult cases when building the training set (\ie, pairs of signatures with
 different author names corresponding to same individual, and pairs of
@@
 the process of grouping together, within a block, all signatures from the same
-individual (and only those). As for many other works on author disambiguation,
-we make use of hierarchical clustering \citep{ward1963hierarchical} for
-building clusters of signatures in a bottom-up fashion. The method consists in
-iteratively merging together the two most similar clusters until all clusters
-are eventually merged together at the top of the hierarchy. Similarity between
-clusters is evaluated using either complete, single or average linkage, using
-as pseudo-distance metric the probability that $s_1$ and $s_2$ correspond to
-distinct authors, as calculated from the custom linkage function $d$.
+individual (and only those).
+As for many other works on author disambiguation, we make use of hierarchical clustering \citep{ward1963hierarchical} for
+building clusters of signatures in a bottom-up fashion.
+The method involves iteratively merging together the two most similar clusters until all clusters
+are merged together at the top of the hierarchy.
+Similarity between clusters is evaluated using either complete, single or average linkage, using
+as a pseudo-distance metric the probability that $s_1$ and $s_2$ correspond to
+distinct authors, as calculated from the custom linkage function $d$ from Section \ref{methods:linkage}.
 
-To form flat clusters out of the hierarchy, one must decide on a maximum
+To form flat clusters from the hierarchy, one must decide on a maximum
 distance threshold above which clusters are considered to correspond to
-distinct authors. Let us denote by ${\cal S}^\prime = \{ s | s \in c^\prime, c^\prime
+distinct authors.
+Let us denote by ${\cal S}^\prime = \{ s | s \in c^\prime, c^\prime
 \in {\cal C}^\prime \}$ the set of all signatures for which partial clusters are
-known. Let us also denote by $\smash{\widehat{\cal C}}$  the predicted clusters for all signatures in ${\cal S}$, and by
+known.
+Let us also denote by $\smash{\widehat{\cal C}}$ the predicted clusters for all signatures in ${\cal S}$, and by
 $\smash{\widehat{\cal C}^\prime} = \{ \widehat{c} \cap {\cal S}^\prime | \widehat{c} \in \widehat{\cal C} \}$
-the predicted clusters restricted to signatures for which partial
-clusters are known. From these, we evaluate the following semi-supervised cut-off strategies, as illustrated in Figure~\ref{fig:cuts}:
+the predicted clusters restricted to signatures for which partial clusters are known.
+From these, we evaluate the following semi-supervised cut-off strategies, as illustrated in Figure~\ref{fig:cuts}:
 \begin{itemize}
+
 \item \textit{No cut:} all signatures from the same block are assumed to be from the same author.
+
 \item \textit{Global cut:} the threshold is chosen globally over all blocks,
     as the one maximizing some score $f({\cal C}^\prime, \widehat{\cal C}^\prime)$.
+
 \item \textit{Block cut:} the threshold is chosen locally at each block $b$,
@@
 As part of this work, we developed a stand-alone application for author
-disambiguation, publicly available
-online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
-or study.  Our implementation builds upon the Python scientific stack, making
+disambiguation, publicly available online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
+or study.
+Our implementation builds upon the Python scientific stack, making
 use of the Scikit-Learn library \citep{scikitlearn} for the supervised learning
-of a linkage function and of SciPy \citep{scipy} for clustering. All
-components of the disambiguation pipeline have been designed to follow the
+of a linkage function and of SciPy \citep{scipy} for clustering.
+All components of the disambiguation pipeline have been designed to follow the
 Scikit-Learn API \citep{scikitlearnAPI}, making them easy to maintain,
-understand and reuse. Our implementation is made to be efficient, exploiting
-parallelization when available and making it ready for production environments.
+understand and reuse.
+Our implementation is made to be efficient, exploiting parallelization when available and
+making it ready for production environments.
 
@@
 The author disambiguation solution proposed in this work, along with its
-enhancements, are evaluated on data extracted from the INSPIRE portal
+enhancements, are evaluated on data extracted from the \emph{INSPIRE} portal
 \citep{gentil2009information}, a digital library for scientific literature in
-high-energy physics. Overall, the portal holds more than 1 million
-publications ${\cal P}$, forming in total a set ${\cal S}$ of more than 10 millions
-signatures. Out of these, around 13\% have been \textit{claimed} by their
-original authors or marked as such by professional curators. Together, they
-constitute a trusted set $({\cal S}^\prime, {\cal C}^\prime)$ of 15388 distinct individuals sharing
+high-energy physics.
+Overall, the portal holds more than 1 million publications ${\cal P}$, 
+forming in total a set ${\cal S}$ of more than 10 million signatures.
+Out of these, around 13\% have been \textit{claimed} by their
+original authors or marked as such by professional curators.
+Together, they constitute a trusted set $({\cal S}^\prime, {\cal C}^\prime)$ of 15388 distinct individuals sharing
 36340 unique author names spread within 1201763 signatures on 360066
@@
 
-Following INSPIRE terms of use, the signatures ${\cal S}^\prime$ and their
+Following the \emph{INSPIRE} terms of use, the signatures ${\cal S}^\prime$ and their
 corresponding clusters ${\cal C}^\prime$ are released
 online\footnote{\url{https://github.com/glouppe/paper-author-disambiguation}}
-under the CC0 license. To the best of our knowledge, data of this size and
-coverage is the first to be publicly released in the scope of author
-disambiguation research.
+under the CC0 license.
+To the best of our knowledge, data of this size and coverage is the first to be publicly 
+released in the scope of author disambiguation research.
 
@@
 constructed by sampling 13\% of claimed signatures to form a training set ${\cal
-S}_\text{train}^\prime \subseteq {\cal S}^\prime$, and by using the remaining
-signatures ${\cal S}_\text{test}^\prime = {\cal S}^\prime \setminus {\cal
-S}_\text{train}^\prime$ for testing. Accordingly, ${\cal C}_\text{train}^\prime
-= \{ c^\prime \cap {\cal S}_\text{train}^\prime | c^\prime \in {\cal C}^\prime
+S}_\text{train}^\prime \subseteq {\cal S}^\prime$.
+The remaining signatures ${\cal S}_\text{test}^\prime = {\cal S}^\prime \setminus {\cal
+S}_\text{train}^\prime$ are used for testing.
+Therefore, ${\cal C}_\text{train}^\prime = \{ c^\prime \cap {\cal S}_\text{train}^\prime | c^\prime \in {\cal C}^\prime
 \}$ represents the partial known clusters on the training fold, while ${\cal
@@
 
-As commonly done in author disambiguation research,
+As commonly performed in author disambiguation research,
 we evaluate the predicted clusters over testing data  ${\cal C}_\text{test}^\prime$,
@@
 | s_1, s_2 \in c, s_1 \neq s_2 \}$ is the set of all pairs of signatures from
-the same clusters in ${\cal C}$. Intuitively, precision evaluates whether signatures
-are grouped only with signatures from the same true clusters, while recall
-measures the extent to which all signatures from the same true clusters are
-effectively grouped together. The F-measure is the harmonic mean between these
-two quantities. In the analysis below, we rely primarily on the B3 F-measure for discussing
-results, as the pairwise variant tends to favor large clusters (because the number of pairs is quadratic with the cluster size),
-hence unfairly giving preference to authors with many publications. By contrast,
-the B3 F-measure weights clusters linearly with respect to their size. General conclusions
-drawn below remain however consistent for pairwise F.
+the same clusters in ${\cal C}$.
+Precision evaluates whether signatures are grouped only with signatures from the same true clusters, 
+while recall measures the extent to which all signatures from the same true clusters are
+effectively grouped together.
+The F-measure is the harmonic mean between these two quantities.
+In the analysis below, we rely primarily on the B3 F-measure for discussing results, as the pairwise variant 
+tends to favor large clusters (because the number of pairs is quadratic with the cluster size),
+hence unfairly giving preference to authors with many publications.
+By contrast, the B3 F-measure weights clusters linearly with respect to their size.
+General conclusions drawn below remain however consistent for pairwise F.
 
@@
 
-\textit{Baseline.} Results presented in Table~\ref{table:results} are all discussed with
+\textit{Baseline.} Results presented in Table~\ref{table:results} are discussed with
 respect to a baseline solution using the following combination of components:
@@
 
-\textit{Blocking.} The very good precision of the baseline ($0.9901$) but its
-lower recall ($0.9760$) suggests that the blocking strategy might be the
-limiting factor to further overall improvements. As Table~\ref{table:blocking}
-indeed indicates, the maximum recall (i.e., if within a block, all signatures
-were clustered optimally) for SFI is $0.9828$ , hence not letting much more
-room for improvement. At the price of fewer and therefore slightly larger
-blocks (as reported in the right column of Table~\ref{table:blocking}), the
+\textit{Blocking.} The good precision of the baseline ($0.9901$), but its
+lower recall ($0.9760$) suggest that the blocking strategy might be the
+limiting factor to further overall improvements.
+As shown in Table~\ref{table:blocking}, the maximum recall (\ie, if within a block, all signatures were clustered optimally) for SFI is $0.9828$.
+At the price of fewer and therefore slightly larger blocks (as reported in the right column of Table~\ref{table:blocking}), the
 proposed phonetic-based blocking strategies show better maximum recall (all
 around $0.9905$), thereby pushing further the upper bound on the maximum
-performance of author disambiguation. As Table~\ref{table:results} indeed shows,
-switching to either Double metaphone or NYSIIS phonetic-based blocking allows
-to improve the overall F-measure score, trading precision for recall. In particular,
-the NYSIIS-based phonetic blocking shows to be the most effective when applied
+performance of author disambiguation.
+As Table~\ref{table:results} shows, switching to either Double metaphone or NYSIIS phonetic-based blocking allows
+to improve the overall F-measure score, trading precision for recall.
+In particular, the NYSIIS-based phonetic blocking shows to be the most effective when applied
 to the baseline (with an F-measure of $0.9850$) while also being the most
@@
 
-\textit{Name normalization.} As discussed before, the seemingly anodyne step of
-normalizing author names (stripping accents, removing affixes), as done in the
-baseline, reveals to be quite important. Results of Table~\ref{table:results}
-indeed clearly suggests that not normalizing significantly reduces performance
-(yielding an F-measure of $0.9830$ when normalizing, but decreasing to $0.9791$
-when raw author name strings are used instead).
+\textit{Name normalization.} As discussed previously, the seemingly insignificant step of
+normalizing author names (stripping accents, removing affixes), as performed in the
+baseline, is shown to be important. Results from Table~\ref{table:results} clearly suggest that not
+normalizing significantly reduces performance (yielding an F-measure of $0.9830$ when normalizing, 
+but decreasing to $0.9791$ when raw author name strings are used instead).
 
-\textit{Linkage function.} Let us first comment the results regarding the
-supervised algorithm used to learn the linkage function. As
-Table~\ref{table:results} indicates, both tree-based algorithms appear to be
+\textit{Linkage function.} Let us first comment on the results regarding the
+supervised algorithm used to learn the linkage function.
+As Table~\ref{table:results} indicates, both tree-based algorithms appear to be
 significantly better fit than Linear Regression ($0.9830$ and $0.9846$ for GBRT
@@
 \citep{levin2012citation} for which Logistic Regression appeared to be the best
-classifier. Provided hyper-parameters are properly tuned, the superiority of
-tree-based methods is in our opinion not surprising. Indeed, given the fact
-that the optimal linkage function is likely to be non-linear, non-parametric
+classifier.
+Provided hyper-parameters are properly tuned, the superiority of
+tree-based methods is in our opinion not surprising.
+Indeed, given the fact that the optimal linkage function is likely to be non-linear, non-parametric
 methods are expected to yield better results, as the experiments here confirm.
@@
 Second, properly constructing a training set of positive and negative pairs of
-signatures from which to learn a linkage function reveals to yield quite an
-improvement. A random sampling of positive and negative pairs, without taking
+signatures from which to learn a linkage function yields a significant
+improvement.
+A random sampling of positive and negative pairs, without taking
 blocking into account, significantly impacts the overall performance
-($0.9711$). When pairs are drawn only from blocks, performance increases
+($0.9711$). When pairs are drawn only from blocks, performance increases to
 ($0.9786$), which confirms our intuition that $d$ should be built only from
@@
 \centering
-\caption{Recursive Feature Elimimation analysis. }
+\caption{Recursive Feature Elimination analysis. }
 \label{fig:rfe}
@@
 Using Recursive Feature Elimination \cite{guyon2002gene}, we next evaluate the
-usefulness of all 15 standard and 7 additional ethnicity features for learning
+usefulness of all fifteen standard and seven additional ethnicity features for learning
 the linkage function. The analysis consists in using the baseline algorithm
-first using all 22 features, to determine the least discriminative from feature
+first using all twenty two features, to determine the least discriminative from feature
 importances \citep{louppe2013understanding}, and then re-learn the baseline
@@
 name initial} and \textit{Second given name} being almost insignificant.
-Overall, these results highlight the added value of the proposed ehtnic-based
-features. Their duality in modeling both the similarity between author names
+Overall, these results highlight the added value of the proposed ethnicity
+features.
+Their duality in modeling both the similarity between author names
 and their origins make them very strong predictors for author disambiguation.
-The results also corroborates results from \citep{kang2009co} or \citep{ferreira2010effective}, who
+The results also corroborate those from \citep{kang2009co} or \citep{ferreira2010effective}, who
 found that the similarity between co-authors was a highly discriminative
-feature. It indeed appears in 4th in our ranking and brings very significant
-improvements as the figure illustrates. In case computational complexity is a concern, this analysis also
-underlines the fact that decent performance can be achieved using only a very
+feature.
+If computational complexity is a concern, this analysis also
+shows how decent performance can be achieved using only a very
 small set of features, as also observed in
@@
 
-\textit{Semi-supervised clustering.} The last part of our experiments concerns
+\textit{Semi-supervised clustering.} The last part of our experiment concerns
 the study of agglomerative clustering and the best way to find a cut-off
@@
 strategy ($0.9409$), but yields anyhow surprisingly decent accuracy, given the
-fact it requires almost no computation (i.e., both learning a linkage function
+fact it requires almost no computation (\ie, both learning a linkage function
 and running agglomerative clustering can be skipped -- only the blocking
@@
 In this work, we have revisited and validated the general author disambiguation
-pipeline introduced in previous and independent research works. The generic
-approach is made of three components, whose design and tuning are all critical
-to get good performance: (i) a blocking function for pre-clustering signatures
+pipeline introduced in previous independent research work.
+The generic approach is composed of three components, whose design and tuning are all critical
+to good performance: (i) a blocking function for pre-clustering signatures
 and reducing computational complexity, (ii) a linkage function for identifying
@@
 As part of this study, we also publicly release the annotated data extracted
-from the INSPIRE platform, on which our experiments are based on. To the
-best of our knowledge, data of this size and coverage is the first to be
+from the \emph{INSPIRE} platform, on which our experiments are based.
+To the best of our knowledge, data of this size and coverage is the first to be
 available in author disambiguation research. By releasing the data publicly,
-we hope to set a benchmark on which further research on author disambiguation
-and related topics can  build upon.
+we hope to provide the basis for further research on author disambiguation
+and related topics.
 

### 2015-08-25 paper/paper.tex
title
save

@@
 
-\title{Ethnicity sensitive author dissambiguation using semi-supervised learning}
+\title{Ethnicity sensitive author disambiguation using semi-supervised learning}
 
@@
 authorship control through manual curation, either in a centralized way by
-hiring collaborators or through developing services that invite authors to register
-their publications themselves (\eg, Google Scholar, and Inspire-HEP).
-Recent efforts to create persistent digital identifiers assigned to researchers (\eg, ORCID, and ResearchedID), 
+hiring professional collaborators or through developing services that invite authors to register
+their publications themselves (\eg, Google Scholar or Inspire-HEP).
+Recent efforts to create persistent digital identifiers assigned to researchers (\eg, ORCID or ResearchedID),
 with the objective to embed these identifiers in the submission workflow of publishers
-or repositories (\eg, Elsevier, arXiv, Inspire-HEP), would univocally solve any disambiguation issue.
+or repositories (\eg, Elsevier, arXiv or Inspire-HEP), would univocally solve any disambiguation issue.
 With the large cost of centralized manual authorship control, or until crowdsourced solutions are more
@@
 Training data is usually not easily available, therefore unsupervised approaches propose
-use of domain-specific, manually designed linkage functions tailored towards author
+the use of domain-specific, manually designed, linkage functions tailored towards author
 disambiguation \citep{malin2005unsupervised,mcrae2006also,song2007efficient,
@@
 for semi-supervised clustering.
-Furthermore, by releasing our data in to the public domain, we hope to provide a benchmark on 
+Furthermore, by releasing our data in the public domain, we hope to provide a benchmark on
 which further research on author disambiguation and related topics can be built.
@@
 
-The simplest and most common strategy for blocking, referred to hereon in as \emph{SFI},
+The simplest and most common strategy for blocking, referred to hereon as \emph{SFI},
 groups signatures together if they share the same surname(s) and the same first
@@
 automatic construction of a pair-wise linkage function between signatures for use
-during the clustering step which grouping all signatures from the same author.
+during the clustering step which groups all signatures from the same author.
 
@@
 blocking into account, significantly impacts the overall performance
-($0.9711$). When pairs are drawn only from blocks, performance increases to
+($0.9711$). When pairs are drawn only from blocks, performance increases
 ($0.9786$), which confirms our intuition that $d$ should be built only from

### 2015-08-26 paper/paper.tex
save

@@
 
-The simplest and most common strategy for blocking, referred to hereon as \emph{SFI},
+The simplest and most common strategy for blocking, referred to hereon in as \emph{SFI},
 groups signatures together if they share the same surname(s) and the same first

### 2015-08-26 paper/paper.tex
save

@@
 Semi-supervised approaches also allow for the tuning of the
-clustering algorithm when the later is applied to a mixed set of labeled
+clustering algorithm when the latter is applied to a mixed set of labeled
 and unlabeled publications, \eg, by maximizing some clustering performance
@@
 \hline
-\hline
 Blocking = SFI & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\

### 2015-08-27 paper/paper.tex
further imp
incremental disambiguation
Hussein's changes

@@
 along with any other metadata that can be derived from it, such as publication
-title, co-authors or date of publication.}
+title, co-authors or date of publication \glnote{Remove a) and b.}}
 \label{fig:signature}
@@
 function is built with supervised learning, (c) independently within each block, signatures
-are grouped using agglomerative clustering.}
+are grouped using hierarchical agglomerative clustering.}
 \label{fig:workflow}
@@
 
-The simplest and most common strategy for blocking, referred to hereon in as \emph{SFI},
+The simplest and most common strategy for blocking, referred to hereon in as \textit{Surname and First Initial (SFI)},
 groups signatures together if they share the same surname(s) and the same first
@@
 
-More specifically, using census data extracted from \citep{rugglesintegrated}, we
-build a logistic regression classifier for mapping the $(1,5)$-TF-IDF
-representation of an author name to one of the seven ethnic groups.
-Given a pair of signatures $(s_1, s_2)$, the proposed ethnicity
-features are each computed as the estimated probability of $s_1$ to belong to
-the corresponding ethnic group, multiplied by the estimated probability of
-$s_2$ to belong to the same group. In doing so, the expectation is for the
-linkage function to become sensitive to the actual origin of the authors
-depending on the values of these features.
-Indirectly, let us also note that these features hold discriminative power since
-if author names are predicted to belong to different ethnic groups, then they
-are also likely to correspond to distinct people.
+More specifically, using census data extracted from \citep{rugglesintegrated},
+we build a support vector machine classifier (using a linear kernel and
+one-versus-all scheme for multi-class classification) for mapping the
+ $(1,5)$-TF-IDF representation of an author name to one of the seven ethnic groups. Given a
+pair of signatures $(s_1, s_2)$, the proposed ethnicity features are each
+computed as the estimated probability of $s_1$ to belong to the corresponding
+ethnic group, multiplied by the estimated probability of $s_2$ to belong to the
+same group. In doing so, the expectation is for the linkage function to become
+sensitive to the actual origin of the authors depending on the values of these
+features. Indirectly, let us also note that these features hold discriminative
+power since if author names are predicted to belong to different ethnic groups,
+then they are also likely to correspond to distinct people.
 
@@
 making it ready for production environments.
+It is also designed be runnable
+in an incremental fashion, by enabling disambiguation only on specified blocks if desired,
+instead of having to run the disambiguation process on the whole signature set.
 
@@
 \hline
+Combined best settings  & 0.9910 & 0.9780 & \textbf{0.9845} & 0.9959 & 0.9750 & \textbf{0.9853} \\
+  \hline
 \end{tabular}
@@
 \begin{table}
-\caption{Maximum recall of blocking strategies, and their number of blocks on ${\cal S}^\prime$.}
+\caption{Maximum recall $R_\text{B3}^*$ and $R_\text{pairwise}^*$ of blocking strategies, and their number of blocks on ${\cal S}^\prime$.}
 \label{table:blocking}
@@
 In case ${\cal S}^\prime_b$ is empty (\eg, because it corresponds to a young
-researcher at the beginning of his career), this therefore suggests that using
-a cut-off threshold learned globally from the known data would in general give
+researcher at the beginning of his career), this therefore suggests that either using
+a cut-off threshold learned globally from the known data or using SFI would in general give
 satisfactory results, only marginally worse than if claimed signatures had been
 known.
+
+\textit{Combined best settings.} \glnote{todo}
 
@@
 
+Further improvements include ... \glnote{TODO}
+
 As part of this study, we also publicly release the annotated data extracted

### 2015-08-27 paper/paper.tex
combined best results

@@
 along with any other metadata that can be derived from it, such as publication
-title, co-authors or date of publication \glnote{Remove a) and b.}}
+title, co-authors or date of publication.}
 \label{fig:signature}
@@
 we build a support vector machine classifier (using a linear kernel and
-one-versus-all scheme for multi-class classification) for mapping the
+one-versus-all classification scheme) for mapping the
  $(1,5)$-TF-IDF representation of an author name to one of the seven ethnic groups. Given a
@@
 
-\textit{Combined best settings.} \glnote{todo}
+\textit{Combined best settings.} When all best settings are combined (\ie,
+Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
+pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
+performance saturates at $0.9845$, which shows not to be better than the best
+reported results ($0.9850$). Since the only difference between these two
+solutions is the use of Random Forests instead of GBRT as classifiers, this
+result suggests there appears to be no significant gain in using one rather
+the other. Both tree-based methods show equally good performance.
 

### 2015-08-28 paper/paper.tex
further works

@@
 understand and reuse.
-Our implementation is made to be efficient, exploiting parallelization when available and
-making it ready for production environments.
+Our implementation is made to be efficient, exploiting parallelization when available, and ready for production environments.
 It is also designed be runnable
@@
 solutions is the use of Random Forests instead of GBRT as classifiers, this
-result suggests there appears to be no significant gain in using one rather
+final result suggests that there appears to be no significant gain in using one rather
 the other. Both tree-based methods show equally good performance.
@@
 experiments show that our refinements all yield significantly better author
-disambiguation accuracy, thereby encouraging further research in these directions.
+disambiguation accuracy.
 
-Further improvements include ... \glnote{TODO}
+Overall, these results all encourage further improvements and research. For
+blocking, one of the open challenges is to manage signatures with inconsistent
+surnames or inconsistent first given names (cases 4 and 5, as described in
+Section~\ref{methods:blocking}) while maintaining blocks to a tractable size.
+For the linkage function, the good results of the proposed features pave the
+way for further research  in ethnicity-sensitive author disambiguation. The
+automatic fitting of the pipeline to cultures and ethnic groups for which
+standard author disambiguation is known to be less efficient (\eg, Chinese
+authors with many homonyms)  indeed constitutes a direction of research with
+great potential benefits for the concerned scientific communities.
 

### 2015-08-28 paper/paper.tex
save
move figures around
isave

@@
 \centering
-\includegraphics[width=\textwidth]{figures/pub-to-signature}
+\includegraphics[width=\textwidth]{fig-pub-to-signature}
 \caption{An example signature $s$ for "Doe, John". A \textit{signature} is
@@
 \centering
-\includegraphics[width=\textwidth]{figures/workflow}
+\includegraphics[width=\textwidth]{fig-workflow}
 \caption{Pipeline for author disambiguation: (a)
@@
 
-  \item An author as multiple given names and they are not always all recorded (\eg,
+  \item An author has multiple given names and they are not always all recorded (\eg,
   "Smith, Jack" and "Smith, A. J.")
@@
 pair of signatures $(s_1, s_2)$, the proposed ethnicity features are each
-computed as the estimated probability of $s_1$ to belong to the corresponding
-ethnic group, multiplied by the estimated probability of $s_2$ to belong to the
+computed as the estimated probability of $s_1$ belonging to the corresponding
+ethnic group, multiplied by the estimated probability of $s_2$ belonging to the
 same group. In doing so, the expectation is for the linkage function to become
@@
 \centering
-\includegraphics[width=\textwidth]{figures/cuts}
+\includegraphics[width=\textwidth]{fig-cuts}
 \caption{Semi-supervised cut-off strategies to form flat clusters of signatures.}
@@
 
+Note that the maximum recalls of blocking strategies using phonetization are
+raised also due to the better handling of multiple given names cases described in Section \ref{methods:blocking}.
+
 \textit{Name normalization.} As discussed previously, the seemingly insignificant step of
@@
 and Random Forests versus $0.9666$ for Linear Regression). This result is
-consistent with \citep{treeratpituk2009disambiguating} which evaluated the use
+consistent with \citep{treeratpituk2009disambiguating} which evaluated the use of
 Random Forests for author disambiguation, but contradicts results of
@@
 \label{fig:rfe}
-\includegraphics[width=\textwidth]{figures/rfe.pdf}
+\includegraphics[width=\textwidth]{fig-rfe.pdf}
 \end{figure}
@@
 other features only brings marginal improvements, with \textit{Journal},
-\textit{Abstract}, \textit{Collaborations}, \textit{References} \textit{Given
+\textit{Abstract}, \textit{Collaborations}, \textit{References}, \textit{Given
 name initial} and \textit{Second given name} being almost insignificant.
@@
 final result suggests that there appears to be no significant gain in using one rather
-the other. Both tree-based methods show equally good performance.
+the other. Both tree-based methods show equally good performance. \glnote{Experiment was run incorrectly!! Results are being recomputed...}
 
@@
 Section~\ref{methods:blocking}) while maintaining blocks to a tractable size.
-For the linkage function, the good results of the proposed features pave the
-way for further research  in ethnicity-sensitive author disambiguation. The
-automatic fitting of the pipeline to cultures and ethnic groups for which
-standard author disambiguation is known to be less efficient (\eg, Chinese
-authors with many homonyms)  indeed constitutes a direction of research with
-great potential benefits for the concerned scientific communities.
+As Double Metaphone, NYSIIS or Soundex are far from being perfect in the
+context of author disambiguation, another direction  for further work is the design of better
+phonetization functions, tailored for personal names. For the linkage function,
+the good results of the proposed features pave the way for further research  in
+ethnicity-sensitive author disambiguation. The automatic fitting of the
+pipeline to cultures and ethnic groups for which standard author disambiguation
+is known to be less efficient (\eg, Chinese authors with many homonyms)  indeed
+constitutes a direction of research with great potential benefits for the
+concerned scientific communities.
 

### 2015-08-28 paper/paper.tex
small change

@@
 Note that the maximum recalls of blocking strategies using phonetization are
-raised also due to the better handling of multiple given names cases described in Section \ref{methods:blocking}.
+also raised due to the better handling of multiple given names cases, as described in Section \ref{methods:blocking}.
 

### 2015-08-28 paper/paper.tex
save

--- 2015-08-28 paper/paper.tex
@@
 performance of author disambiguation.
+Let us remind however that the reported maximum recalls for the blocking strategies using phonetization are
+also raised due to the better handling of multiple surnames, as described in Section \ref{methods:blocking}.
+
 As Table~\ref{table:results} shows, switching to either Double metaphone or NYSIIS phonetic-based blocking allows
@@
 \end{table}
-
-Note that the maximum recalls of blocking strategies using phonetization are
-raised also due to the better handling of multiple given names cases described in Section \ref{methods:blocking}.
 

### 2015-08-28 paper/paper.tex
save

@@
 Double Metaphone \citep{doublemetaphone}, the NYSIIS \citep{nysiis} or the
-Soundex \citep{Soundex} algorithms.
+Soundex \citep{Soundex} phonetic algorithms for mapping author names to their pronunciations.
 Together, these processing steps allow for grouping of most name variants of the same
@@
 Section~\ref{methods:blocking}) while maintaining blocks to a tractable size.
-As Double Metaphone, NYSIIS or Soundex are far from being perfect in the
-context of author disambiguation, another direction  for further work is the design of better
-phonetization functions, tailored for personal names. For the linkage function,
+As phonetic algorithms are not yet perfect, another direction  for further work is the design of better
+phonetization functions, tailored for author disambiguation. For the linkage function,
 the good results of the proposed features pave the way for further research  in

### 2015-08-29 paper/paper.tex
save

@@
 \hline
-Combined best settings  & 0.9910 & 0.9780 & \textbf{0.9845} & 0.9959 & 0.9750 & \textbf{0.9853} \\
+Combined best settings & 0.9897 & 0.9827 & \textbf{0.9862} & 0.9954 & 0.9805 & \textbf{0.9879} \\
   \hline
@@
 pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
-performance saturates at $0.9845$, which shows not to be better than the best
-reported results ($0.9850$). Since the only difference between these two
-solutions is the use of Random Forests instead of GBRT as classifiers, this
-final result suggests that there appears to be no significant gain in using one rather
-the other. Both tree-based methods show equally good performance. \glnote{Experiment was run incorrectly!! Results are being recomputed...}
+performance reaches  $0.9862$, combining the high recall of NYSIIS blocking
+with the better precision of Random Forests.
 

### 2015-08-29 paper/paper.tex
save

@@
 pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
-performance reaches  $0.9862$, combining the high recall of NYSIIS blocking
-with the better precision of Random Forests.
+performance reaches $0.9862$, \ie, the best of all reported results. In particular,
+this combination exhibits both the high recall of phonetic blocking based on the NYSIIS algorithm
+and the high precision of Random Forests.
 

### 2015-08-31 paper/paper.tex
save

@@
 Out of these, around 13\% have been \textit{claimed} by their
-original authors or marked as such by professional curators.
+original authors, marked as such by professional curators or automatically assigned to their true authors thanks
+to persistent identifiers provided by publishers or other sources.
 Together, they constitute a trusted set $({\cal S}^\prime, {\cal C}^\prime)$ of 15388 distinct individuals sharing

### 2015-09-01 paper/paper.tex
typos

@@
 their publications themselves (\eg, Google Scholar or Inspire-HEP).
-Recent efforts to create persistent digital identifiers assigned to researchers (\eg, ORCID or ResearchedID),
+Recent efforts to create persistent digital identifiers assigned to researchers (\eg, ORCID or ResearcherID),
 with the objective to embed these identifiers in the submission workflow of publishers
@@
 Our implementation is made to be efficient, exploiting parallelization when available, and ready for production environments.
-It is also designed be runnable
+It is also designed to be runnable
 in an incremental fashion, by enabling disambiguation only on specified blocks if desired,
@@
 eventually only one feature remains. Results are presented in
-Figure~\ref{fig:rfe} for one the three folds, starting from the far right with
+Figure~\ref{fig:rfe} for one of the three folds, starting from the far right with
 the baseline and \textit{Second given name} being the least important feature,
@@
 threshold to form clusters. Results from Table~\ref{table:results}
-first clearly indicates that average linkage is significantly better than
+first clearly indicate that average linkage is significantly better than
 both single and complete linkage.

### 2015-10-05 paper/author_disambiguaton.tex
ICDE paper format

--- 2015-09-01 paper/paper.tex
@@
-\documentclass{article}
-\usepackage{nips15submit_e}
-
-% For figures
-\usepackage{graphicx}
-\usepackage{subfigure}
-\usepackage{color}
-
-% Maths
-\usepackage{amsmath}
-\usepackage{amsfonts}
+%% bare_conf.tex
+%% V1.3
+%% 2007/01/11
+%% by Michael Shell
+%% See:
+%% http://www.michaelshell.org/
+%% for current contact information.
+%%
+%% This is a skeleton file demonstrating the use of IEEEtran.cls
+%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
+%%
+%% Support sites:
+%% http://www.michaelshell.org/tex/ieeetran/
+%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
+%% and
+%% http://www.ieee.org/
+
+%%*************************************************************************
+%% Legal Notice:
+%% This code is offered as-is without any warranty either expressed or
+%% implied; without even the implied warranty of MERCHANTABILITY or
+%% FITNESS FOR A PARTICULAR PURPOSE! 
+%% User assumes all risk.
+%% In no event shall IEEE or any contributor to this code be liable for
+%% any damages or losses, including, but not limited to, incidental,
+%% consequential, or any other damages, resulting from the use or misuse
+%% of any information contained here.
+%%
+%% All comments are the opinions of their respective authors and are not
+%% necessarily endorsed by the IEEE.
+%%
+%% This work is distributed under the LaTeX Project Public License (LPPL)
+%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
+%% distributed and modified. A copy of the LPPL, version 1.3, is included
+%% in the base LaTeX documentation of all distributions of LaTeX released
+%% 2003/12/01 or later.
+%% Retain all contribution notices and credits.
+%% ** Modified files should be clearly indicated as such, including  **
+%% ** renaming them and changing author support contact information. **
+%%
+%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
+%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
+%%*************************************************************************
+
+% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
+% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
+% *** with production work. IEEE's font choices can trigger bugs that do  ***
+% *** not appear when using other class files.                            ***
+% The testflow support page is at:
+% http://www.michaelshell.org/tex/testflow/
+
+% Note that the a4paper option is mainly intended so that authors in
+% countries using A4 can easily print to A4 and see how their papers will
+% look in print - the typesetting of the document will not typically be
+% affected with changes in paper size (but the bottom and side margins will).
+% Use the testflow package mentioned above to verify correct handling of
+% both paper sizes by the user's LaTeX system.
+%
+% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
+% should be used if it is desired that the figures are to be displayed in
+% draft mode.
+%
+\documentclass[conference]{IEEEtran}
+% Add the compsoc option for Computer Society conferences.
+%
+% If IEEEtran.cls has not been installed into the LaTeX system files,
+% manually specify the path to it like:
+% \documentclass[conference]{../sty/IEEEtran}
+
+% Some very useful LaTeX packages include:
+% (uncomment the ones you want to load)
+
+% *** MISC UTILITY PACKAGES ***
+%
+%\usepackage{ifpdf}
+% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
+% compilation based on whether the output is pdf or dvi.
+% usage:
+% \ifpdf
+%   % pdf code
+% \else
+%   % dvi code
+% \fi
+% The latest version of ifpdf.sty can be obtained from:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
+% Also, note that IEEEtran.cls V1.7 and later provides a builtin
+% \ifCLASSINFOpdf conditional that works the same way.
+% When switching from latex to pdflatex and vice-versa, the compiler may
+% have to be run twice to clear warning/error messages.
+
 \usepackage{xspace}
-
-% For citations
-\usepackage{natbib}
-
-% For links
 \usepackage{hyperref}
-
-% For "Jabłoński"
-\usepackage[utf8]{inputenc}
-
-\newcommand{\glnote}[1]{\textcolor{red}{[GL: #1]}}
-\newcommand{\msnote}[1]{\textcolor{blue}{[MS: #1]}}
 \newcommand{\etal}{\emph{et al.}\xspace}
@@
 
-% Header ======================================================================
-
+% *** CITATION PACKAGES ***
+%
+%\usepackage{cite}
+% cite.sty was written by Donald Arseneau
+% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
+% \cite{} output to follow that of IEEE. Loading the cite package will
+% result in citation numbers being automatically sorted and properly
+% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
+% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
+% \cite will automatically add leading space, if needed. Use cite.sty's
+% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
+% cite.sty is already installed on most LaTeX systems. Be sure and use
+% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
+% not currently provide for hyperlinked citations.
+% The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
+% The documentation is contained in the cite.sty file itself.
+
+% *** GRAPHICS RELATED PACKAGES ***
+%
+\ifCLASSINFOpdf
+  \usepackage[pdftex]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../pdf/}{../jpeg/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
+\else
+  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
+  % will default to the driver specified in the system graphics.cfg if no
+  % driver is specified.
+  \usepackage[dvips]{graphicx}
+  % declare the path(s) where your graphic files are
+  % \graphicspath{{../eps/}}
+  % and their extensions so you won't have to specify these with
+  % every instance of \includegraphics
+  % \DeclareGraphicsExtensions{.eps}
+\fi
+% graphicx was written by David Carlisle and Sebastian Rahtz. It is
+% required if you want graphics, photos, etc. graphicx.sty is already
+% installed on most LaTeX systems. The latest version and documentation can
+% be obtained at: 
+% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
+% Another good source of documentation is "Using Imported Graphics in
+% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
+% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
+%
+% latex, and pdflatex in dvi mode, support graphics in encapsulated
+% postscript (.eps) format. pdflatex in pdf mode supports graphics
+% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
+% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
+% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
+% which can result in "jaggedy"/blurry rendering of lines and letters as
+% well as large increases in file sizes.
+%
+% You can find documentation about the pdfTeX application at:
+% http://www.tug.org/applications/pdftex
+
+% *** MATH PACKAGES ***
+%
+\usepackage[cmex10]{amsmath}
+\usepackage{amsfonts}
+% A popular package from the American Mathematical Society that provides
+% many useful and powerful commands for dealing with mathematics. If using
+% it, be sure to load this package with the cmex10 option to ensure that
+% only type 1 fonts will utilized at all point sizes. Without this option,
+% it is possible that some math symbols, particularly those within
+% footnotes, will be rendered in bitmap form which will result in a
+% document that can not be IEEE Xplore compliant!
+%
+% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
+% thus preventing page breaks from occurring within multiline equations. Use:
+\interdisplaylinepenalty=2500
+% after loading amsmath to restore such page breaks as IEEEtran.cls normally
+% does. amsmath.sty is already installed on most LaTeX systems. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
+
+% *** SPECIALIZED LIST PACKAGES ***
+%
+%\usepackage{algorithmic}
+% algorithmic.sty was written by Peter Williams and Rogerio Brito.
+% This package provides an algorithmic environment fo describing algorithms.
+% You can use the algorithmic environment in-text or within a figure
+% environment to provide for a floating algorithm. Do NOT use the algorithm
+% floating environment provided by algorithm.sty (by the same authors) or
+% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
+% algorithm float types and packages that provide these will not provide
+% correct IEEE style captions. The latest version and documentation of
+% algorithmic.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
+% There is also a support site at:
+% http://algorithms.berlios.de/index.html
+% Also of interest may be the (relatively newer and more customizable)
+% algorithmicx.sty package by Szasz Janos:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
+
+% *** ALIGNMENT PACKAGES ***
+%
+%\usepackage{array}
+% Frank Mittelbach's and David Carlisle's array.sty patches and improves
+% the standard LaTeX2e array and tabular environments to provide better
+% appearance and additional user controls. As the default LaTeX2e table
+% generation code is lacking to the point of almost being broken with
+% respect to the quality of the end results, all users are strongly
+% advised to use an enhanced (at the very least that provided by array.sty)
+% set of table tools. array.sty is already installed on most systems. The
+% latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/required/tools/
+
+%\usepackage{mdwmath}
+%\usepackage{mdwtab}
+% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
+% especially mdwmath.sty and mdwtab.sty which are used to format equations
+% and tables, respectively. The MDWtools set is already installed on most
+% LaTeX systems. The lastest version and documentation is available at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
+
+% IEEEtran contains the IEEEeqnarray family of commands that can be used to
+% generate multiline equations as well as matrices, tables, etc., of high
+% quality.
+
+%\usepackage{eqparbox}
+% Also of notable interest is Scott Pakin's eqparbox package for creating
+% (automatically sized) equal width boxes - aka "natural width parboxes".
+% Available at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
+
+% *** SUBFIGURE PACKAGES ***
+%\usepackage[tight,footnotesize]{subfigure}
+% subfigure.sty was written by Steven Douglas Cochran. This package makes it
+% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
+% work, it is a good idea to load it with the tight package option to reduce
+% the amount of white space around the subfigures. subfigure.sty is already
+% installed on most LaTeX systems. The latest version and documentation can
+% be obtained at:
+% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
+% subfigure.sty has been superceeded by subfig.sty.
+
+%\usepackage[caption=false]{caption}
+%\usepackage[font=footnotesize]{subfig}
+% subfig.sty, also written by Steven Douglas Cochran, is the modern
+% replacement for subfigure.sty. However, subfig.sty requires and
+% automatically loads Axel Sommerfeldt's caption.sty which will override
+% IEEEtran.cls handling of captions and this will result in nonIEEE style
+% figure/table captions. To prevent this problem, be sure and preload
+% caption.sty with its "caption=false" package option. This is will preserve
+% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
+% (recommended due to many improvements over 1.2) of subfig.sty supports
+% the caption=false option directly:
+%\usepackage[caption=false,font=footnotesize]{subfig}
+%
+% The latest version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
+% The latest version and documentation of caption.sty can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
+
+% *** FLOAT PACKAGES ***
+%
+%\usepackage{fixltx2e}
+% fixltx2e, the successor to the earlier fix2col.sty, was written by
+% Frank Mittelbach and David Carlisle. This package corrects a few problems
+% in the LaTeX2e kernel, the most notable of which is that in current
+% LaTeX2e releases, the ordering of single and double column floats is not
+% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
+% single column figure to be placed prior to an earlier double column
+% figure. The latest version and documentation can be found at:
+% http://www.ctan.org/tex-archive/macros/latex/base/
+
+%\usepackage{stfloats}
+% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
+% the ability to do double column floats at the bottom of the page as well
+% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
+% LaTeX2e). It also provides a command:
+%\fnbelowfloat
+% to enable the placement of footnotes below bottom floats (the standard
+% LaTeX2e kernel puts them above bottom floats). This is an invasive package
+% which rewrites many portions of the LaTeX2e float routines. It may not work
+% with other packages that modify the LaTeX2e float routines. The latest
+% version and documentation can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
+% Documentation is contained in the stfloats.sty comments as well as in the
+% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
+% does not allow \baselineskip to stretch. Authors submitting work to the
+% IEEE should note that IEEE rarely uses double column equations and
+% that authors should try to avoid such use. Do not be tempted to use the
+% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
+% not format its papers in such ways.
+
+% *** PDF, URL AND HYPERLINK PACKAGES ***
+%
+%\usepackage{url}
+% url.sty was written by Donald Arseneau. It provides better support for
+% handling and breaking URLs. url.sty is already installed on most LaTeX
+% systems. The latest version can be obtained at:
+% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
+% Read the url.sty source comments for usage information. Basically,
+% \url{my_url_here}.
+
+% *** Do not adjust lengths that control margins, column widths, etc. ***
+% *** Do not use packages that alter fonts (such as pslatex).         ***
+% There should be no need to do such things with IEEEtran.cls V1.6 and later.
+% (Unless specifically asked to do so by the journal or conference you plan
+% to submit to, of course. )
+
+% correct bad hyphenation here
+\hyphenation{op-tical net-works semi-conduc-tor}
+
+\begin{document}
+%
+% paper title
+% can use linebreaks \\ within to get better formatting as desired
 \title{Ethnicity sensitive author disambiguation using semi-supervised learning}
 
-\author{Gilles Louppe\\
-        CERN\\
-        Switzerland\\
-\And Hussein Al-Natsheh\\
-        CERN\\
-        Switzerland\\
-\And Mateusz Susik\\
-        CERN\\
-        Switzerland\\
-\And Eamonn Maguire\\
-        CERN\\
-        Switzerland}
-\date{}
-
-\nipsfinalcopy
-
-\begin{document}
-
+% author names and affiliations
+% use a multiple column layout for up to three different
+% affiliations
+
+\author{
+\IEEEauthorblockN{Gilles Louppe}
+\IEEEauthorblockA{CERN, Switzerland\\
+g.louppe@cern.ch}
+\and
+\IEEEauthorblockN{Hussein T. Al-Natsheh}
+\IEEEauthorblockA{CNRS, France \\
+hussein.al-natsheh@ish-lyon.cnrs.fr}
+\and
+\IEEEauthorblockN{Mateusz Susik}
+\IEEEauthorblockA{University of Warsaw\\
+msusik@student.uw.edu.pl}
+\and
+\IEEEauthorblockN{Eamonn Maguire}
+\IEEEauthorblockA{CERN, Switzerland\\
+eamonn.james.maguire@cern.ch }}
+
+% conference papers do not typically use \thanks and this command
+% is locked out in conference mode. If really needed, such as for
+% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
+% after \documentclass
+
+% for over three affiliations, or if they all won't fit within the width
+% of the page, use this alternative format:
+% 
+%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
+%Homer Simpson\IEEEauthorrefmark{2},
+%James Kirk\IEEEauthorrefmark{3}, 
+%Montgomery Scott\IEEEauthorrefmark{3} and
+%Eldon Tyrell\IEEEauthorrefmark{4}}
+%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
+%Georgia Institute of Technology,
+%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
+%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
+%Email: homer@thesimpsons.com}
+%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
+%Telephone: (800) 555--1212, Fax: (888) 555--1212}
+%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
+
+% use for special paper notices
+%\IEEEspecialpapernotice{(Invited Paper)}
+
+% make the title area
 \maketitle
@@
 \begin{abstract}
-
+%\boldmath
 Author name disambiguation in bibliographic databases is the problem of
@@
 function, thereby tailoring disambiguation to non-Western author names whenever necessary.
-
 \end{abstract}
-
-% Introduction ==================================================================
+% IEEEtran.cls defaults to using nonbold math in the Abstract.
+% This preserves the distinction between vectors and scalars. However,
+% if the conference you are submitting to favors bold math in the abstract,
+% then you can use LaTeX's standard command \boldmath at the very start
+% of the abstract to achieve this. Many IEEE journals/conferences frown on
+% math in the abstract anyway.
+
+% no keywords
+
+% For peer review papers, you can put extra information on the cover
+% page as needed:
+% \ifCLASSOPTIONpeerreview
+% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
+% \fi
+%
+% For peerreview papers, this IEEEtran command inserts a page break and
+% creates the second title. It will be ignored for other modes.
+\IEEEpeerreviewmaketitle
 
 \section{Introduction}
-\label{introduction}
-
-% general introduction to the disambiguation issues
-% often based on small dataset or fully unsupervised
-% summary of what we did
-% outline of the paper
-
 In academic digital libraries, author name disambiguation is the problem of
@@
 the reliability of bibliometrics and author rankings (\eg, citation counts or other impact
-metrics, as studied in \citep{strotmann2012author}); and/or the relevance of scientific network analysis
-\citep{newman2001structure}.
+metrics, as studied in \cite{strotmann2012author}); and/or the relevance of scientific network analysis
+\cite{newman2001structure}.
 
 Efforts and solutions to author disambiguation have been proposed from various
-communities \citep{liu2014author}. On the one hand, libraries have maintained
+communities \cite{liu2014author}. On the one hand, libraries have maintained
 authorship control through manual curation, either in a centralized way by
@@
 phonetization of author names to increase recall.
+
 We also propose ethnicity-sensitive features for learning a linkage function,
@@
 we briefly review machine learning solutions for author disambiguation.
-The components of our method are then defined in Section~\ref{methods}
-and its implementation described in Section~\ref{implementation}. Experiments
+The components of our method are then defined in Section~\ref{methods} and its implementation described in Section~\ref{implementation}.Experiments
 are carried out in Section~\ref{experiments}, where we explore and validate
@@
 
+% An example of a floating figure using the graphicx package.
+% Note that \label must occur AFTER (or within) \caption.
+% For figures, \caption should occur after the \includegraphics.
+% Note that IEEEtran v1.7 and later has special internal code that
+% is designed to preserve the operation of \label within \caption
+% even when the captionsoff option is in effect. However, because
+% of issues like this, it may be the safest practice to put all your
+% \label just after \caption rather than within \caption{}.
+%
+% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
+% option should be used if it is desired that the figures are to be
+% displayed while in draft mode.
+%
+%\begin{figure}[!t]
+%\centering
+%\includegraphics[width=2.5in]{myfigure}
+% where an .eps filename suffix will be assumed under latex, 
+% and a .pdf suffix will be assumed for pdflatex; or what has been declared
+% via \DeclareGraphicsExtensions.
+%\caption{Simulation Results}
+%\label{fig_sim}
+%\end{figure}
+
+% Note that IEEE typically puts floats only at the top, even when this
+% results in a large percentage of a column being occupied by floats.
+
+% An example of a double column floating figure using two subfigures.
+% (The subfig.sty package must be loaded for this to work.)
+% The subfigure \label commands are set within each subfloat command, the
+% \label for the overall figure must come after \caption.
+% \hfil must be used as a separator to get equal spacing.
+% The subfigure.sty package works much the same way, except \subfigure is
+% used instead of \subfloat.
+%
+%\begin{figure*}[!t]
+%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
+%\label{fig_first_case}}
+%\hfil
+%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
+%\label{fig_second_case}}}
+%\caption{Simulation results}
+%\label{fig_sim}
+%\end{figure*}
+%
+% Note that often IEEE papers with subfigures do not employ subfigure
+% captions (using the optional argument to \subfloat), but instead will
+% reference/describe all of them (a), (b), etc., within the main caption.
+
+% An example of a floating table. Note that, for IEEE style tables, the 
+% \caption command should come BEFORE the table. Table text will default to
+% \footnotesize as IEEE normally uses this smaller font for tables.
+% The \label must come after \caption as always.
+%
+%\begin{table}[!t]
+%% increase table row spacing, adjust to taste
+%\renewcommand{\arraystretch}{1.3}
+% if using array.sty, it might be a good idea to tweak the value of
+% \extrarowheight as needed to properly center the text within the cells
+%\caption{An Example of a Table}
+%\label{table_example}
+%\centering
+%% Some packages, such as MDW tools, offer better commands for making tables
+%% than the plain LaTeX2e tabular which is used here.
+%\begin{tabular}{|c||c|}
+%\hline
+%One & Two\\
+%\hline
+%Three & Four\\
+%\hline
+%\end{tabular}
+%\end{table}
+
+% Note that IEEE does not put floats in the very first column - or typically
+% anywhere on the first page for that matter. Also, in-text middle ("here")
+% positioning is not used. Most IEEE journals/conferences use top floats
+% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
+% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
+% command of the stfloats package.
 % Related works ==================================================================
@@
 
-As reviewed in \citep{smalheiser2009author,ferreira2012brief,levin2012citation}, author
+As reviewed in \cite{smalheiser2009author,ferreira2012brief,levin2012citation}, author
 disambiguation algorithms are usually composed of two main components: (i) a
@@
 of publications identified as being either from the same or different authors to automatically learn a linkage
-function between publications \citep{han2004two,huang2006efficient, culotta2007author,treeratpituk2009disambiguating,tran2014author}.
+function between publications \cite{han2004two,huang2006efficient, culotta2007author,treeratpituk2009disambiguating,tran2014author}.
 
@@
 the use of domain-specific, manually designed, linkage functions tailored towards author
-disambiguation \citep{malin2005unsupervised,mcrae2006also,song2007efficient,
+disambiguation \cite{malin2005unsupervised,mcrae2006also,song2007efficient,
 soler2007separating, kang2009co,fan2011graph,schulz2014exploiting}.
@@
 set of pairs of publications, from which a linkage function is then built using supervised learning
-\citep{ferreira2010effective,torvik2009author,levin2012citation}.
+\cite{ferreira2010effective,torvik2009author,levin2012citation}.
 
@@
 and unlabeled publications, \eg, by maximizing some clustering performance
-metric on the known clusters \citep{levin2012citation}.
+metric on the known clusters \cite{levin2012citation}.
 
@@
 \centering
-\includegraphics[width=\textwidth]{fig-pub-to-signature}
+\includegraphics[width=\linewidth]{fig-pub-to-signature}
 \caption{An example signature $s$ for "Doe, John". A \textit{signature} is
@@
 \centering
-\includegraphics[width=\textwidth]{fig-workflow}
+\includegraphics[width=\linewidth]{fig-workflow}
 \caption{Pipeline for author disambiguation: (a)
@@
 signatures ${\cal S}$ into disjoint subsets ${\cal S}_{b_0}, ..., {\cal
-S}_{b_{K-1}}$, or \textit{blocks} \citep{fellegi69}, followed by carrying out
+S}_{b_{K-1}}$, or \textit{blocks} \cite{fellegi69}, followed by carrying out
 author disambiguation on each one of these blocks independently.
@@
 phonetic representation of the normalized surname.
-Normalization involves stripping accents (\eg, "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
+Normalization involves stripping accents (\eg, "Jab?o?ski, ?" $\rightarrow$ "Jablonski, L") and name
 affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."
 $\rightarrow$ "Waals, J. D."), while phonetization is based either on the
-Double Metaphone \citep{doublemetaphone}, the NYSIIS \citep{nysiis} or the
-Soundex \citep{Soundex} phonetic algorithms for mapping author names to their pronunciations.
+Double Metaphone \cite{doublemetaphone}, the NYSIIS \cite{nysiis} or the
+Soundex \cite{Soundex} phonetic algorithms for mapping author names to their pronunciations.
 Together, these processing steps allow for grouping of most name variants of the same
@@
 Gradient Boosted Regression Trees (GBRT, \cite{friedman2001greedy}),
-and Logistic Regression \citep{fan2008liblinear} as classifiers.
+and Logistic Regression \cite{fan2008liblinear} as classifiers.
 
@@
 Following previous works, pairs of signatures $(s_1, s_2)$ are first transformed to vectors $v \in \mathbb{R}^p$
-by building so-called similarity profiles \citep{treeratpituk2009disambiguating} on which supervised learning is carried out.
+by building so-called similarity profiles \cite{treeratpituk2009disambiguating} on which supervised learning is carried out.
 In this work, we design and evaluate fifteen standard input
@@
 disambiguated using different strategies (\eg, pairs of signatures with French
-author names versus pairs of signatures with Chinese author names) \citep{treeratpituk2012name, chin2014effective}.
+author names versus pairs of signatures with Chinese author names) \cite{treeratpituk2012name, chin2014effective}.
 To support our disambiguation algorithm, we added seven features to our feature set, with each
@@
 
-More specifically, using census data extracted from \citep{rugglesintegrated},
+More specifically, using census data extracted from \cite{rugglesintegrated},
 we build a support vector machine classifier (using a linear kernel and
@@
 discriminative patterns rather than inter-block differences.
-Furthermore, as noted in \citep{lange2011frequency}, most signature pairs are non-ambiguous:
+Furthermore, as noted in \cite{lange2011frequency}, most signature pairs are non-ambiguous:
 if both signatures share the same author names, then
@@
 individual (and only those).
-As for many other works on author disambiguation, we make use of hierarchical clustering \citep{ward1963hierarchical} for
+As for many other works on author disambiguation, we make use of hierarchical clustering \cite{ward1963hierarchical} for
 building clusters of signatures in a bottom-up fashion.
@@
 \centering
-\includegraphics[width=\textwidth]{fig-cuts}
+\includegraphics[width=\linewidth]{fig-cuts}
 \caption{Semi-supervised cut-off strategies to form flat clusters of signatures.}
@@
 % GL: out of scope, let us mention that in Conclusions instead
-
 % Implementation ======================================================
@@
 Our implementation builds upon the Python scientific stack, making
-use of the Scikit-Learn library \citep{scikitlearn} for the supervised learning
-of a linkage function and of SciPy \citep{scipy} for clustering.
+use of the Scikit-Learn library \cite{scikitlearn} for the supervised learning
+of a linkage function and of SciPy \cite{scipy} for clustering.
 All components of the disambiguation pipeline have been designed to follow the
-Scikit-Learn API \citep{scikitlearnAPI}, making them easy to maintain,
+Scikit-Learn API \cite{scikitlearnAPI}, making them easy to maintain,
 understand and reuse.
@@
 enhancements, are evaluated on data extracted from the \emph{INSPIRE} portal
-\citep{gentil2009information}, a digital library for scientific literature in
+\cite{gentil2009information}, a digital library for scientific literature in
 high-energy physics.
@@
 \begin{table}
-\caption{Average precision, recall and f-measure scores on test folds.}
+\caption{Average precision, recall and B3 f-measure scores on test folds.}
 \label{table:results}
 \centering
-\begin{tabular}{|l|c c c|c c c|}
-  \hline
-                       & \multicolumn{3}{|c|}{\textbf{B3}} & \multicolumn{3}{|c|}{\textbf{Pairwise}} \\
-  \textbf{Description} & $P$ & $R$ & $F$ & $P$ & $R$ & $F$\\
-  \hline
-  \hline
-Baseline & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
-\hline
-Blocking = SFI & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
-Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841 & 0.9927 & 0.9817 & 0.9871 \\
-Blocking = NYSIIS & 0.9875 & 0.9826 & \textbf{0.9850} & 0.9936 & 0.9814 & \textbf{0.9875} \\
-Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
-\hline
-No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
-Name normalization & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
-\hline
-Classifier = GBRT & 0.9901 & 0.9760 & 0.9830 & 0.9948 & 0.9738 & 0.9842 \\
-Classifier = Random Forests & 0.9909 & 0.9783 & \textbf{0.9846} & 0.9957 & 0.9752 & \textbf{0.9854} \\
-Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666 & 0.9717 & 0.9569 & 0.9643 \\
-\hline
-Training pairs = Non-blocked, uniform & 0.9793 & 0.9630 & 0.9711 & 0.9756 & 0.9629 & 0.9692 \\
-Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786 & 0.9850 & 0.9707 & 0.9778 \\
-Training pairs = Blocked, balanced & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
-\hline
-Clustering = Average linkage & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
-Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671 & 0.9543 & 0.9626 & 0.9584 \\
-Clustering = Complete linkage & 0.9862 & 0.9709 & 0.9785 & 0.9920 & 0.9688 & 0.9803 \\
-\hline
-No cut & 0.9024 & 0.9828 & 0.9409 & 0.8298 & 0.9776 & 0.8977 \\
-Global cut & 0.9892 & 0.9737 & 0.9814 & 0.9940 & 0.9727 & 0.9832 \\
-Block cut & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842} \\
-\hline
-Combined best settings & 0.9897 & 0.9827 & \textbf{0.9862} & 0.9954 & 0.9805 & \textbf{0.9879} \\
+\begin{tabular}{|l|c c c|}
+  \hline
+                       & \multicolumn{3}{|c|}{\textbf{B3}} \\
+  \textbf{Description} & $P$ & $R$ & $F$ \\
+  \hline
+  \hline
+Baseline & 0.9901 & 0.9760 & 0.9830  \\
+\hline
+Blocking = SFI & 0.9901 & 0.9760 & 0.9830  \\
+Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841  \\
+Blocking = NYSIIS & 0.9875 & 0.9826 & \textbf{0.9850} \\
+Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 \\
+\hline
+No name normalization & 0.9887 & 0.9697 & 0.9791  \\
+Name normalization & 0.9901 & 0.9760 & \textbf{0.9830}  \\
+\hline
+Classifier = GBRT & 0.9901 & 0.9760 & 0.9830  \\
+Classifier = Random Forests & 0.9909 & 0.9783 & \textbf{0.9846}  \\
+Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666  \\
+\hline
+Training pairs = Non-blocked, uniform & 0.9793 & 0.9630 & 0.9711  \\
+Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786  \\
+Training pairs = Blocked, balanced & 0.9901 & 0.9760 & \textbf{0.9830}  \\
+\hline
+Clustering = Average linkage & 0.9901 & 0.9760 & \textbf{0.9830}  \\
+Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671  \\
+Clustering = Complete linkage & 0.9862 & 0.9709 & 0.9785  \\
+\hline
+No cut & 0.9024 & 0.9828 & 0.9409  \\
+Global cut & 0.9892 & 0.9737 & 0.9814  \\
+Block cut & 0.9901 & 0.9760 & \textbf{0.9830}  \\
+\hline
+Combined best settings & 0.9897 & 0.9827 & \textbf{0.9862}  \\
+  \hline
+\end{tabular}
+\end{table}
+
+\begin{table}
+\caption{Average precision, recall and pairwise f-measure scores on test folds.}
+\label{table:resultspw}
+\centering
+\begin{tabular}{|l|c c c|}
+  \hline
+                       & \multicolumn{3}{|c|}{\textbf{Pairwise}} \\
+  \textbf{Description} & $P$ & $R$ & $F$\\
+  \hline
+  \hline
+Baseline & 0.9948 & 0.9738 & 0.9842 \\
+\hline
+Blocking = SFI & 0.9948 & 0.9738 & 0.9842 \\
+Blocking = Double metaphone & 0.9927 & 0.9817 & 0.9871 \\
+Blocking = NYSIIS  & 0.9936 & 0.9814 & \textbf{0.9875} \\
+Blocking = Soundex & 0.9935 & 0.9725 & 0.9828 \\
+\hline
+No name normalization & 0.9931 & 0.9658 & 0.9793 \\
+Name normalization& 0.9948 & 0.9738 & \textbf{0.9842} \\
+\hline
+Classifier = GBRT & 0.9948 & 0.9738 & 0.9842 \\
+Classifier = Random Forests & 0.9957 & 0.9752 & \textbf{0.9854} \\
+Classifier = Linear Regression & 0.9717 & 0.9569 & 0.9643 \\
+\hline
+Training pairs = Non-blocked, uniform & 0.9756 & 0.9629 & 0.9692 \\
+Training pairs = Blocked, uniform & 0.9850 & 0.9707 & 0.9778 \\
+Training pairs = Blocked, balanced  & 0.9948 & 0.9738 & \textbf{0.9842} \\
+\hline
+Clustering = Average linkage& 0.9948 & 0.9738 & \textbf{0.9842} \\
+Clustering = Single linkage & 0.9543 & 0.9626 & 0.9584 \\
+Clustering = Complete linkage & 0.9920 & 0.9688 & 0.9803 \\
+\hline
+No cut& 0.8298 & 0.9776 & 0.8977 \\
+Global cut & 0.9940 & 0.9727 & 0.9832 \\
+Block cut& 0.9948 & 0.9738 & \textbf{0.9842} \\
+\hline
+Combined best settings & 0.9954 & 0.9805 & \textbf{0.9879} \\
   \hline
@@
 Finally, let us also note that Table~\ref{table:blocking} corroborates the
-estimation of \citep{torvik2009author}, stating that SFI blocking has a recall
+estimation of \cite{torvik2009author}, stating that SFI blocking has a recall
 around $98\%$ on real data.
@@
 and Random Forests versus $0.9666$ for Linear Regression). This result is
-consistent with \citep{treeratpituk2009disambiguating} which evaluated the use of
+consistent with \cite{treeratpituk2009disambiguating} which evaluated the use of
 Random Forests for author disambiguation, but contradicts results of
-\citep{levin2012citation} for which Logistic Regression appeared to be the best
+\cite{levin2012citation} for which Logistic Regression appeared to be the best
 classifier.
@@
 \label{fig:rfe}
-\includegraphics[width=\textwidth]{fig-rfe.pdf}
+\includegraphics[width=\linewidth]{fig-rfe.pdf}
 \end{figure}
@@
 first using all twenty two features, to determine the least discriminative from feature
-importances \citep{louppe2013understanding}, and then re-learn the baseline
+importances \cite{louppe2013understanding}, and then re-learn the baseline
 using all but that one feature. That process is repeated recursively until
@@
 and their origins make them very strong predictors for author disambiguation.
-The results also corroborate those from \citep{kang2009co} or \citep{ferreira2010effective}, who
+The results also corroborate those from \cite{kang2009co} or \cite{ferreira2010effective}, who
 found that the similarity between co-authors was a highly discriminative
@@
 small set of features, as also observed in
-\citep{treeratpituk2009disambiguating} or \citep{levin2012citation}.
+\cite{treeratpituk2009disambiguating} or \cite{levin2012citation}.
 
@@
 satisfactory results, only marginally worse than if claimed signatures had been
-known.
+known.Trying out 3 clustering methods, the results show that \textit {average linkage} was the best one.
 
@@
 
-% \section*{Acknowledgements}
-
-% \glnote{todo}
-
-% References ==================================================================
-
-\bibliographystyle{apalike}
+% conference papers do not normally have an appendix
+
+% use section* for acknowledgement
+%\section*{Acknowledgment}
+
+%The authors would like to thank...
+
+% trigger a \newpage just before the given reference
+% number - used to balance the columns on the last page
+% adjust value as needed - may need to be readjusted if
+% the document is modified later
+%\IEEEtriggeratref{8}
+% The "triggered" command can be changed if desired:
+%\IEEEtriggercmd{\enlargethispage{-5in}}
+
+% references section
+
+% can use a bibliography generated by BibTeX as a .bbl file
+% BibTeX documentation can be easily obtained at:
+% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
+% The IEEEtran BibTeX style support page is at:
+% http://www.michaelshell.org/tex/ieeetran/bibtex/
+\bibliographystyle{IEEEtran}
 \bibliography{bib}
 
+% argument is your BibTeX string definitions and bibliography database(s)
+%\bibliography{IEEEabrv,../bib/paper}
+%
+% <OR> manually copy in the resultant .bbl file
+% set second argument of \begin to the number of references
+% (used to reserve space for the reference number labels box)
+
+%%%%%%%%%%%%%%%%%%%%%
+%\begin{thebibliography}{1}
+
+%\bibitem{IEEEhowto:kopka}
+%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em %plus
+%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
+
+%\end{thebibliography}
+%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
+
+% that's all folks
 \end{document}

### 2015-10-06 paper/author_disambiguaton.tex
add a missing space

@@
 we briefly review machine learning solutions for author disambiguation.
-The components of our method are then defined in Section~\ref{methods} and its implementation described in Section~\ref{implementation}.Experiments
+The components of our method are then defined in Section~\ref{methods} and its implementation described in Section~\ref{implementation}. Experiments
 are carried out in Section~\ref{experiments}, where we explore and validate

### 2015-10-06 paper/author_disambiguaton.tex
adding missing spaces

@@
 we briefly review machine learning solutions for author disambiguation.
-The components of our method are then defined in Section~\ref{methods} and its implementation described in Section~\ref{implementation}. Experiments
+The components of our method are then defined in Section~\ref{methods} and its implementation described in Section~\ref{implementation}.
+Experiments
 are carried out in Section~\ref{experiments}, where we explore and validate
@@
 satisfactory results, only marginally worse than if claimed signatures had been
-known.Trying out 3 clustering methods, the results show that \textit {average linkage} was the best one.
+known. Trying out 3 clustering methods, the results show that \textit {average linkage} was the best one.
 

### 2015-10-06 paper/author_disambiguaton.tex
unicode characters

@@
 phonetic representation of the normalized surname.
-Normalization involves stripping accents (\eg, "Jab?o?ski, ?" $\rightarrow$ "Jablonski, L") and name
+Normalization involves stripping accents (\eg, "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
 affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."

### 2015-12-27 paper/author_disambiguaton.tex
span figures
adding missing inputenc dependency + rebuilt pdf
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>
SIGIR template
Using SIGIR ACM template and adding a short paragraph about the
execution time in the discussion section

@@
-%% bare_conf.tex
-%% V1.3
-%% 2007/01/11
-%% by Michael Shell
-%% See:
-%% http://www.michaelshell.org/
-%% for current contact information.
-%%
-%% This is a skeleton file demonstrating the use of IEEEtran.cls
-%% (requires IEEEtran.cls version 1.7 or later) with an IEEE conference paper.
-%%
-%% Support sites:
-%% http://www.michaelshell.org/tex/ieeetran/
-%% http://www.ctan.org/tex-archive/macros/latex/contrib/IEEEtran/
-%% and
-%% http://www.ieee.org/
-
-%%*************************************************************************
-%% Legal Notice:
-%% This code is offered as-is without any warranty either expressed or
-%% implied; without even the implied warranty of MERCHANTABILITY or
-%% FITNESS FOR A PARTICULAR PURPOSE! 
-%% User assumes all risk.
-%% In no event shall IEEE or any contributor to this code be liable for
-%% any damages or losses, including, but not limited to, incidental,
-%% consequential, or any other damages, resulting from the use or misuse
-%% of any information contained here.
-%%
-%% All comments are the opinions of their respective authors and are not
-%% necessarily endorsed by the IEEE.
-%%
-%% This work is distributed under the LaTeX Project Public License (LPPL)
-%% ( http://www.latex-project.org/ ) version 1.3, and may be freely used,
-%% distributed and modified. A copy of the LPPL, version 1.3, is included
-%% in the base LaTeX documentation of all distributions of LaTeX released
-%% 2003/12/01 or later.
-%% Retain all contribution notices and credits.
-%% ** Modified files should be clearly indicated as such, including  **
-%% ** renaming them and changing author support contact information. **
-%%
-%% File list of work: IEEEtran.cls, IEEEtran_HOWTO.pdf, bare_adv.tex,
-%%                    bare_conf.tex, bare_jrnl.tex, bare_jrnl_compsoc.tex
-%%*************************************************************************
-
-% *** Authors should verify (and, if needed, correct) their LaTeX system  ***
-% *** with the testflow diagnostic prior to trusting their LaTeX platform ***
-% *** with production work. IEEE's font choices can trigger bugs that do  ***
-% *** not appear when using other class files.                            ***
-% The testflow support page is at:
-% http://www.michaelshell.org/tex/testflow/
-
-% Note that the a4paper option is mainly intended so that authors in
-% countries using A4 can easily print to A4 and see how their papers will
-% look in print - the typesetting of the document will not typically be
-% affected with changes in paper size (but the bottom and side margins will).
-% Use the testflow package mentioned above to verify correct handling of
-% both paper sizes by the user's LaTeX system.
+% This file should be compiled with V2.5 of "sig-alternate.cls" May 2012
 %
-% Also note that the "draftcls" or "draftclsnofoot", not "draft", option
-% should be used if it is desired that the figures are to be displayed in
-% draft mode.
+% ----------------------------------------------------------------------------------------------------------------
+% This .tex file (and associated .cls V2.5) produces:
+%       1) The Permission Statement
+%       2) The Conference (location) Info information
+%       3) The Copyright Line with ACM data
+%       4) NO page numbers
 %
-\documentclass[conference]{IEEEtran}
-% Add the compsoc option for Computer Society conferences.
+% as against the acm_proc_article-sp.cls file which
+% DOES NOT produce 1) thru' 3) above.
 %
-% If IEEEtran.cls has not been installed into the LaTeX system files,
-% manually specify the path to it like:
-% \documentclass[conference]{../sty/IEEEtran}
-
-% Some very useful LaTeX packages include:
-% (uncomment the ones you want to load)
-
-% *** MISC UTILITY PACKAGES ***
+% Using 'sig-alternate.cls' you have control, however, from within
+% the source .tex file, over both the CopyrightYear
+% (defaulted to 200X) and the ACM Copyright Data
+% (defaulted to X-XXXXX-XX-X/XX/XX).
+% e.g.
+% \CopyrightYear{2007} will cause 2007 to appear in the copyright line.
+% \crdata{0-12345-67-8/90/12} will cause 0-12345-67-8/90/12 to appear in the copyright line.
 %
-%\usepackage{ifpdf}
-% Heiko Oberdiek's ifpdf.sty is very useful if you need conditional
-% compilation based on whether the output is pdf or dvi.
-% usage:
-% \ifpdf
-%   % pdf code
-% \else
-%   % dvi code
-% \fi
-% The latest version of ifpdf.sty can be obtained from:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/oberdiek/
-% Also, note that IEEEtran.cls V1.7 and later provides a builtin
-% \ifCLASSINFOpdf conditional that works the same way.
-% When switching from latex to pdflatex and vice-versa, the compiler may
-% have to be run twice to clear warning/error messages.
-
-\usepackage{xspace}
-\usepackage{hyperref}
-\newcommand{\etal}{\emph{et al.}\xspace}
-\newcommand{\ie}{\emph{i.e.}\xspace}
-\newcommand{\eg}{\emph{e.g.}\xspace}
-\newcommand{\Eg}{\emph{E.g.}\xspace}
-
-% *** CITATION PACKAGES ***
+% ---------------------------------------------------------------------------------------------------------------
+% This .tex source is an example which *does* use
+% the .bib file (from which the .bbl file % is produced).
+% REMEMBER HOWEVER: After having produced the .bbl file,
+% and prior to final submission, you *NEED* to 'insert'
+% your .bbl file into your source .tex file so as to provide
+% ONE 'self-contained' source file.
 %
-%\usepackage{cite}
-% cite.sty was written by Donald Arseneau
-% V1.6 and later of IEEEtran pre-defines the format of the cite.sty package
-% \cite{} output to follow that of IEEE. Loading the cite package will
-% result in citation numbers being automatically sorted and properly
-% "compressed/ranged". e.g., [1], [9], [2], [7], [5], [6] without using
-% cite.sty will become [1], [2], [5]--[7], [9] using cite.sty. cite.sty's
-% \cite will automatically add leading space, if needed. Use cite.sty's
-% noadjust option (cite.sty V3.8 and later) if you want to turn this off.
-% cite.sty is already installed on most LaTeX systems. Be sure and use
-% version 4.0 (2003-05-27) and later if using hyperref.sty. cite.sty does
-% not currently provide for hyperlinked citations.
-% The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/cite/
-% The documentation is contained in the cite.sty file itself.
-
-% *** GRAPHICS RELATED PACKAGES ***
+% ================= IF YOU HAVE QUESTIONS =======================
+% Questions regarding the SIGS styles, SIGS policies and
+% procedures, Conferences etc. should be sent to
+% Adrienne Griscti (griscti@acm.org)
 %
-\ifCLASSINFOpdf
-  \usepackage[pdftex]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../pdf/}{../jpeg/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.pdf,.jpeg,.png}
-\else
-  % or other class option (dvipsone, dvipdf, if not using dvips). graphicx
-  % will default to the driver specified in the system graphics.cfg if no
-  % driver is specified.
-  \usepackage[dvips]{graphicx}
-  % declare the path(s) where your graphic files are
-  % \graphicspath{{../eps/}}
-  % and their extensions so you won't have to specify these with
-  % every instance of \includegraphics
-  % \DeclareGraphicsExtensions{.eps}
-\fi
-% graphicx was written by David Carlisle and Sebastian Rahtz. It is
-% required if you want graphics, photos, etc. graphicx.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at: 
-% http://www.ctan.org/tex-archive/macros/latex/required/graphics/
-% Another good source of documentation is "Using Imported Graphics in
-% LaTeX2e" by Keith Reckdahl which can be found as epslatex.ps or
-% epslatex.pdf at: http://www.ctan.org/tex-archive/info/
+% Technical questions _only_ to
+% Gerald Murray (murray@hq.acm.org)
+% ===============================================================
 %
-% latex, and pdflatex in dvi mode, support graphics in encapsulated
-% postscript (.eps) format. pdflatex in pdf mode supports graphics
-% in .pdf, .jpeg, .png and .mps (metapost) formats. Users should ensure
-% that all non-photo figures use a vector format (.eps, .pdf, .mps) and
-% not a bitmapped formats (.jpeg, .png). IEEE frowns on bitmapped formats
-% which can result in "jaggedy"/blurry rendering of lines and letters as
-% well as large increases in file sizes.
-%
-% You can find documentation about the pdfTeX application at:
-% http://www.tug.org/applications/pdftex
-
-% *** MATH PACKAGES ***
-%
-\usepackage[cmex10]{amsmath}
-\usepackage{amsfonts}
-% A popular package from the American Mathematical Society that provides
-% many useful and powerful commands for dealing with mathematics. If using
-% it, be sure to load this package with the cmex10 option to ensure that
-% only type 1 fonts will utilized at all point sizes. Without this option,
-% it is possible that some math symbols, particularly those within
-% footnotes, will be rendered in bitmap form which will result in a
-% document that can not be IEEE Xplore compliant!
-%
-% Also, note that the amsmath package sets \interdisplaylinepenalty to 10000
-% thus preventing page breaks from occurring within multiline equations. Use:
-\interdisplaylinepenalty=2500
-% after loading amsmath to restore such page breaks as IEEEtran.cls normally
-% does. amsmath.sty is already installed on most LaTeX systems. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/amslatex/math/
-
-% *** SPECIALIZED LIST PACKAGES ***
-%
-%\usepackage{algorithmic}
-% algorithmic.sty was written by Peter Williams and Rogerio Brito.
-% This package provides an algorithmic environment fo describing algorithms.
-% You can use the algorithmic environment in-text or within a figure
-% environment to provide for a floating algorithm. Do NOT use the algorithm
-% floating environment provided by algorithm.sty (by the same authors) or
-% algorithm2e.sty (by Christophe Fiorio) as IEEE does not use dedicated
-% algorithm float types and packages that provide these will not provide
-% correct IEEE style captions. The latest version and documentation of
-% algorithmic.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithms/
-% There is also a support site at:
-% http://algorithms.berlios.de/index.html
-% Also of interest may be the (relatively newer and more customizable)
-% algorithmicx.sty package by Szasz Janos:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/algorithmicx/
-
-% *** ALIGNMENT PACKAGES ***
-%
-%\usepackage{array}
-% Frank Mittelbach's and David Carlisle's array.sty patches and improves
-% the standard LaTeX2e array and tabular environments to provide better
-% appearance and additional user controls. As the default LaTeX2e table
-% generation code is lacking to the point of almost being broken with
-% respect to the quality of the end results, all users are strongly
-% advised to use an enhanced (at the very least that provided by array.sty)
-% set of table tools. array.sty is already installed on most systems. The
-% latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/required/tools/
-
-%\usepackage{mdwmath}
-%\usepackage{mdwtab}
-% Also highly recommended is Mark Wooding's extremely powerful MDW tools,
-% especially mdwmath.sty and mdwtab.sty which are used to format equations
-% and tables, respectively. The MDWtools set is already installed on most
-% LaTeX systems. The lastest version and documentation is available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/mdwtools/
-
-% IEEEtran contains the IEEEeqnarray family of commands that can be used to
-% generate multiline equations as well as matrices, tables, etc., of high
-% quality.
-
-%\usepackage{eqparbox}
-% Also of notable interest is Scott Pakin's eqparbox package for creating
-% (automatically sized) equal width boxes - aka "natural width parboxes".
-% Available at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/eqparbox/
-
-% *** SUBFIGURE PACKAGES ***
-%\usepackage[tight,footnotesize]{subfigure}
-% subfigure.sty was written by Steven Douglas Cochran. This package makes it
-% easy to put subfigures in your figures. e.g., "Figure 1a and 1b". For IEEE
-% work, it is a good idea to load it with the tight package option to reduce
-% the amount of white space around the subfigures. subfigure.sty is already
-% installed on most LaTeX systems. The latest version and documentation can
-% be obtained at:
-% http://www.ctan.org/tex-archive/obsolete/macros/latex/contrib/subfigure/
-% subfigure.sty has been superceeded by subfig.sty.
-
-%\usepackage[caption=false]{caption}
-%\usepackage[font=footnotesize]{subfig}
-% subfig.sty, also written by Steven Douglas Cochran, is the modern
-% replacement for subfigure.sty. However, subfig.sty requires and
-% automatically loads Axel Sommerfeldt's caption.sty which will override
-% IEEEtran.cls handling of captions and this will result in nonIEEE style
-% figure/table captions. To prevent this problem, be sure and preload
-% caption.sty with its "caption=false" package option. This is will preserve
-% IEEEtran.cls handing of captions. Version 1.3 (2005/06/28) and later 
-% (recommended due to many improvements over 1.2) of subfig.sty supports
-% the caption=false option directly:
-%\usepackage[caption=false,font=footnotesize]{subfig}
-%
-% The latest version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/subfig/
-% The latest version and documentation of caption.sty can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/caption/
-
-% *** FLOAT PACKAGES ***
-%
-%\usepackage{fixltx2e}
-% fixltx2e, the successor to the earlier fix2col.sty, was written by
-% Frank Mittelbach and David Carlisle. This package corrects a few problems
-% in the LaTeX2e kernel, the most notable of which is that in current
-% LaTeX2e releases, the ordering of single and double column floats is not
-% guaranteed to be preserved. Thus, an unpatched LaTeX2e can allow a
-% single column figure to be placed prior to an earlier double column
-% figure. The latest version and documentation can be found at:
-% http://www.ctan.org/tex-archive/macros/latex/base/
-
-%\usepackage{stfloats}
-% stfloats.sty was written by Sigitas Tolusis. This package gives LaTeX2e
-% the ability to do double column floats at the bottom of the page as well
-% as the top. (e.g., "\begin{figure*}[!b]" is not normally possible in
-% LaTeX2e). It also provides a command:
-%\fnbelowfloat
-% to enable the placement of footnotes below bottom floats (the standard
-% LaTeX2e kernel puts them above bottom floats). This is an invasive package
-% which rewrites many portions of the LaTeX2e float routines. It may not work
-% with other packages that modify the LaTeX2e float routines. The latest
-% version and documentation can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/sttools/
-% Documentation is contained in the stfloats.sty comments as well as in the
-% presfull.pdf file. Do not use the stfloats baselinefloat ability as IEEE
-% does not allow \baselineskip to stretch. Authors submitting work to the
-% IEEE should note that IEEE rarely uses double column equations and
-% that authors should try to avoid such use. Do not be tempted to use the
-% cuted.sty or midfloat.sty packages (also by Sigitas Tolusis) as IEEE does
-% not format its papers in such ways.
-
-% *** PDF, URL AND HYPERLINK PACKAGES ***
-%
-%\usepackage{url}
-% url.sty was written by Donald Arseneau. It provides better support for
-% handling and breaking URLs. url.sty is already installed on most LaTeX
-% systems. The latest version can be obtained at:
-% http://www.ctan.org/tex-archive/macros/latex/contrib/misc/
-% Read the url.sty source comments for usage information. Basically,
-% \url{my_url_here}.
-
-% *** Do not adjust lengths that control margins, column widths, etc. ***
-% *** Do not use packages that alter fonts (such as pslatex).         ***
-% There should be no need to do such things with IEEEtran.cls V1.6 and later.
-% (Unless specifically asked to do so by the journal or conference you plan
-% to submit to, of course. )
-
-% correct bad hyphenation here
-\hyphenation{op-tical net-works semi-conduc-tor}
+% For tracking purposes - this is V2.0 - May 2012
+
+\documentclass{sig-alternate}
 
 \begin{document}
-%
+
+% Copyright
+\setcopyright{acmcopyright}
 % paper title
@@
 
-% author names and affiliations
-% use a multiple column layout for up to three different
-% affiliations
-
+\numberofauthors{4} 
 \author{
-\IEEEauthorblockN{Gilles Louppe}
-\IEEEauthorblockA{CERN, Switzerland\\
-g.louppe@cern.ch}
+\alignauthor
+Gilles Louppe\\
+       \affaddr{CERN, Switzerland}\\
+       \email{g.louppe@cern.ch}
+\alignauthor
+Hussein T. Al-Natsheh\\
+       \affaddr{ISH-LYON, CNRS, France}\\
+       \email{hussein.al-natsheh@ish-lyon.cnrs.fr}
+\alignauthor
+Mateusz Susik\\
+       \affaddr{University of Warsaw}\\
+       \email{msusik@student.uw.edu.pl}
+\alignauthor
 \and
-\IEEEauthorblockN{Hussein T. Al-Natsheh}
-\IEEEauthorblockA{CNRS, France \\
-hussein.al-natsheh@ish-lyon.cnrs.fr}
-\and
-\IEEEauthorblockN{Mateusz Susik}
-\IEEEauthorblockA{University of Warsaw\\
-msusik@student.uw.edu.pl}
-\and
-\IEEEauthorblockN{Eamonn Maguire}
-\IEEEauthorblockA{CERN, Switzerland\\
-eamonn.james.maguire@cern.ch }}
-
-% conference papers do not typically use \thanks and this command
-% is locked out in conference mode. If really needed, such as for
-% the acknowledgment of grants, issue a \IEEEoverridecommandlockouts
-% after \documentclass
-
-% for over three affiliations, or if they all won't fit within the width
-% of the page, use this alternative format:
-% 
-%\author{\IEEEauthorblockN{Michael Shell\IEEEauthorrefmark{1},
-%Homer Simpson\IEEEauthorrefmark{2},
-%James Kirk\IEEEauthorrefmark{3}, 
-%Montgomery Scott\IEEEauthorrefmark{3} and
-%Eldon Tyrell\IEEEauthorrefmark{4}}
-%\IEEEauthorblockA{\IEEEauthorrefmark{1}School of Electrical and Computer Engineering\\
-%Georgia Institute of Technology,
-%Atlanta, Georgia 30332--0250\\ Email: see http://www.michaelshell.org/contact.html}
-%\IEEEauthorblockA{\IEEEauthorrefmark{2}Twentieth Century Fox, Springfield, USA\\
-%Email: homer@thesimpsons.com}
-%\IEEEauthorblockA{\IEEEauthorrefmark{3}Starfleet Academy, San Francisco, California 96678-2391\\
-%Telephone: (800) 555--1212, Fax: (888) 555--1212}
-%\IEEEauthorblockA{\IEEEauthorrefmark{4}Tyrell Inc., 123 Replicant Street, Los Angeles, California 90210--4321}}
-
-% use for special paper notices
-%\IEEEspecialpapernotice{(Invited Paper)}
-
-% make the title area
+Eamonn Maguire\\
+       \affaddr{CERN, Switzerland}\\
+       \email{eamonn.james.maguire@cern.ch}
+}
+
 \maketitle
-
 \begin{abstract}
-%\boldmath
+
 Author name disambiguation in bibliographic databases is the problem of
@@
 \end{abstract}
-% IEEEtran.cls defaults to using nonbold math in the Abstract.
-% This preserves the distinction between vectors and scalars. However,
-% if the conference you are submitting to favors bold math in the abstract,
-% then you can use LaTeX's standard command \boldmath at the very start
-% of the abstract to achieve this. Many IEEE journals/conferences frown on
-% math in the abstract anyway.
-
-% no keywords
-
-% For peer review papers, you can put extra information on the cover
-% page as needed:
-% \ifCLASSOPTIONpeerreview
-% \begin{center} \bfseries EDICS Category: 3-BBND \end{center}
-% \fi
-%
-% For peerreview papers, this IEEEtran command inserts a page break and
-% creates the second title. It will be ignored for other modes.
-\IEEEpeerreviewmaketitle
 
@@
 issue since the accuracy of information managed at the level of individuals directly affects:
-the relevance search of results (\eg, when querying for all publications written by a given author);
-the reliability of bibliometrics and author rankings (\eg, citation counts or other impact
+the relevance search of results (e.g., when querying for all publications written by a given author);
+the reliability of bibliometrics and author rankings (e.g., citation counts or other impact
 metrics, as studied in \cite{strotmann2012author}); and/or the relevance of scientific network analysis
@@
 hiring professional collaborators or through developing services that invite authors to register
-their publications themselves (\eg, Google Scholar or Inspire-HEP).
-Recent efforts to create persistent digital identifiers assigned to researchers (\eg, ORCID or ResearcherID),
+their publications themselves (e.g., Google Scholar or Inspire-HEP).
+Recent efforts to create persistent digital identifiers assigned to researchers (e.g., ORCID or ResearcherID),
 with the objective to embed these identifiers in the submission workflow of publishers
-or repositories (\eg, Elsevier, arXiv or Inspire-HEP), would univocally solve any disambiguation issue.
+or repositories (e.g., Elsevier, arXiv or Inspire-HEP), would univocally solve any disambiguation issue.
 With the large cost of centralized manual authorship control, or until crowdsourced solutions are more
@@
 Finally, conclusions and future works are discussed in Section~\ref{conclusions}.
-
-% An example of a floating figure using the graphicx package.
-% Note that \label must occur AFTER (or within) \caption.
-% For figures, \caption should occur after the \includegraphics.
-% Note that IEEEtran v1.7 and later has special internal code that
-% is designed to preserve the operation of \label within \caption
-% even when the captionsoff option is in effect. However, because
-% of issues like this, it may be the safest practice to put all your
-% \label just after \caption rather than within \caption{}.
-%
-% Reminder: the "draftcls" or "draftclsnofoot", not "draft", class
-% option should be used if it is desired that the figures are to be
-% displayed while in draft mode.
-%
-%\begin{figure}[!t]
-%\centering
-%\includegraphics[width=2.5in]{myfigure}
-% where an .eps filename suffix will be assumed under latex, 
-% and a .pdf suffix will be assumed for pdflatex; or what has been declared
-% via \DeclareGraphicsExtensions.
-%\caption{Simulation Results}
-%\label{fig_sim}
-%\end{figure}
-
-% Note that IEEE typically puts floats only at the top, even when this
-% results in a large percentage of a column being occupied by floats.
-
-% An example of a double column floating figure using two subfigures.
-% (The subfig.sty package must be loaded for this to work.)
-% The subfigure \label commands are set within each subfloat command, the
-% \label for the overall figure must come after \caption.
-% \hfil must be used as a separator to get equal spacing.
-% The subfigure.sty package works much the same way, except \subfigure is
-% used instead of \subfloat.
-%
-%\begin{figure*}[!t]
-%\centerline{\subfloat[Case I]\includegraphics[width=2.5in]{subfigcase1}%
-%\label{fig_first_case}}
-%\hfil
-%\subfloat[Case II]{\includegraphics[width=2.5in]{subfigcase2}%
-%\label{fig_second_case}}}
-%\caption{Simulation results}
-%\label{fig_sim}
-%\end{figure*}
-%
-% Note that often IEEE papers with subfigures do not employ subfigure
-% captions (using the optional argument to \subfloat), but instead will
-% reference/describe all of them (a), (b), etc., within the main caption.
-
-% An example of a floating table. Note that, for IEEE style tables, the 
-% \caption command should come BEFORE the table. Table text will default to
-% \footnotesize as IEEE normally uses this smaller font for tables.
-% The \label must come after \caption as always.
-%
-%\begin{table}[!t]
-%% increase table row spacing, adjust to taste
-%\renewcommand{\arraystretch}{1.3}
-% if using array.sty, it might be a good idea to tweak the value of
-% \extrarowheight as needed to properly center the text within the cells
-%\caption{An Example of a Table}
-%\label{table_example}
-%\centering
-%% Some packages, such as MDW tools, offer better commands for making tables
-%% than the plain LaTeX2e tabular which is used here.
-%\begin{tabular}{|c||c|}
-%\hline
-%One & Two\\
-%\hline
-%Three & Four\\
-%\hline
-%\end{tabular}
-%\end{table}
-
-% Note that IEEE does not put floats in the very first column - or typically
-% anywhere on the first page for that matter. Also, in-text middle ("here")
-% positioning is not used. Most IEEE journals/conferences use top floats
-% exclusively. Note that, LaTeX2e, unlike IEEE journals/conferences, places
-% footnotes above bottom floats. This can be corrected via the \fnbelowfloat
-% command of the stfloats package.
 % Related works ==================================================================
@@
 clustering algorithm when the latter is applied to a mixed set of labeled
-and unlabeled publications, \eg, by maximizing some clustering performance
+and unlabeled publications, e.g., by maximizing some clustering performance
 metric on the known clusters \cite{levin2012citation}.
@@
 define a signature $s \in p$ from a publication as a unique piece of
-information identifying one of the authors of $p$ (\eg, the author name, his
+information identifying one of the authors of $p$ (e.g., the author name, his
 affiliation, along with any other metadata that can be derived from $p$, as illustrated in Figure~\ref{fig:signature}). Let us
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=\linewidth]{fig-pub-to-signature}
+\includegraphics[width=\textwidth]{fig-pub-to-signature}
 \caption{An example signature $s$ for "Doe, John". A \textit{signature} is
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=\linewidth]{fig-workflow}
+\includegraphics[width=\textwidth]{fig-workflow}
 \caption{Pipeline for author disambiguation: (a)
@@
 \label{fig:workflow}
-\end{figure}
+\end{figure*}
 
@@
 groups signatures together if they share the same surname(s) and the same first
-given name initial (\eg, \emph{SFI}("Doe, John") $==$ "Doe, J").
+given name initial (e.g., \emph{SFI}("Doe, John") $==$ "Doe, J").
 Despite satisfactory performance, there are several cases where this simple strategy fails to cluster related pairs of signatures together, including:
@@
   ways of writing an author name, or signatures contain a typo
-  (\eg, "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
-
-  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (\eg, "Martinez Torres, A." and "Torres, A. Martinez").
+  (e.g., "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
+
+  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (e.g., "Martinez Torres, A." and "Torres, A. Martinez").
 
   \item An author has multiple surnames and, on some signatures, only the first surname is
-  present (\eg, "Smith-Jones, A." and "Smith, A.")
-
-  \item An author has multiple given names and they are not always all recorded (\eg,
+  present (e.g., "Smith-Jones, A." and "Smith, A.")
+
+  \item An author has multiple given names and they are not always all recorded (e.g.,
   "Smith, Jack" and "Smith, A. J.")
 
-  \item An authors surname changed (\eg, due to marriage).
+  \item An authors surname changed (e.g., due to marriage).
 \end{enumerate}
@@
 phonetic representation of the normalized surname.
-Normalization involves stripping accents (\eg, "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
-affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."
+Normalization involves stripping accents (e.g., "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
+affixes that inconsistently appear in signatures (e.g., "van der Waals, J. D."
 $\rightarrow$ "Waals, J. D."), while phonetization is based either on the
@@
 \textit{Input features.} In most cases, supervised learning algorithms assume
-the input space ${\cal X}$ to be numeric (\eg, $\mathbb{R}^p$), making them
+the input space ${\cal X}$ to be numeric (e.g., $\mathbb{R}^p$), making them
 not directly applicable to structured input spaces such as ${\cal S} \times
@@
 Author names from different cultures, origins or ethnic groups are likely to be
-disambiguated using different strategies (\eg, pairs of signatures with French
+disambiguated using different strategies (e.g., pairs of signatures with French
 author names versus pairs of signatures with Chinese author names) \cite{treeratpituk2012name, chin2014effective}.
@@
 
-\begin{table}
+\begin{table*}
 \caption{Input features for learning a linkage function}
@@
 \end{tabular}
-\end{table}
+\end{table*}
 
@@
 Rather than sampling pairs uniformly at random, we propose to oversample
-difficult cases when building the training set (\ie, pairs of signatures with
+difficult cases when building the training set (e.g., pairs of signatures with
 different author names corresponding to same individual, and pairs of
@@
 
-\begin{figure}
+\begin{figure*}
 \centering
-\includegraphics[width=\linewidth]{fig-cuts}
+\includegraphics[width=\textwidth]{fig-cuts}
 \caption{Semi-supervised cut-off strategies to form flat clusters of signatures.}
 \label{fig:cuts}
-\end{figure}
+\end{figure*}
 
@@
 
-\begin{table}
+\begin{table*}
 \caption{Average precision, recall and B3 f-measure scores on test folds.}
@@
 \end{tabular}
-\end{table}
-
-\begin{table}
+\end{table*}
+
+\begin{table*}
 \caption{Average precision, recall and pairwise f-measure scores on test folds.}
@@
 limiting factor to further overall improvements.
-As shown in Table~\ref{table:blocking}, the maximum recall (\ie, if within a block, all signatures were clustered optimally) for SFI is $0.9828$.
+As shown in Table~\ref{table:blocking}, the maximum recall (e.g., if within a block, all signatures were clustered optimally) for SFI is $0.9828$.
 At the price of fewer and therefore slightly larger blocks (as reported in the right column of Table~\ref{table:blocking}), the
@@
 
-\begin{table}
+\begin{table*}
 \caption{Maximum recall $R_\text{B3}^*$ and $R_\text{pairwise}^*$ of blocking strategies, and their number of blocks on ${\cal S}^\prime$.}
@@
 strategy ($0.9409$), but yields anyhow surprisingly decent accuracy, given the
-fact it requires almost no computation (\ie, both learning a linkage function
+fact it requires almost no computation (e.g., both learning a linkage function
 and running agglomerative clustering can be skipped -- only the blocking
@@
 with a slight advantage for block cuts ($0.9814$ versus $0.9830$), as expected.
-In case ${\cal S}^\prime_b$ is empty (\eg, because it corresponds to a young
+In case ${\cal S}^\prime_b$ is empty (e.g., because it corresponds to a young
 researcher at the beginning of his career), this therefore suggests that either using
@@
 
-\textit{Combined best settings.} When all best settings are combined (\ie,
+\textit{Combined best settings.} When all best settings are combined (e.g.,
 Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
 pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
-performance reaches $0.9862$, \ie, the best of all reported results. In particular,
+performance reaches $0.9862$, e.g., the best of all reported results. In particular,
 this combination exhibits both the high recall of phonetic blocking based on the NYSIIS algorithm
 and the high precision of Random Forests.
+
+\textit{Execution time.} Our implementation takes around $20$ hours to process the complete set of the data (for 10M signatures, on a $16$ cores machine with $32$GB of RAM).
+Related work \cite{khabsa2014large} reports execution times around $24$ hours to cluster $4$M signatures.
+Note also that shorter execution times can be achieved, at the expense of worse results.
 
@@
 pipeline to cultures and ethnic groups for which standard author disambiguation
-is known to be less efficient (\eg, Chinese authors with many homonyms)  indeed
+is known to be less efficient (e.g., Chinese authors with many homonyms)  indeed
 constitutes a direction of research with great potential benefits for the
@@
 
-% conference papers do not normally have an appendix
-
-% use section* for acknowledgement
-%\section*{Acknowledgment}
-
-%The authors would like to thank...
-
-% trigger a \newpage just before the given reference
-% number - used to balance the columns on the last page
-% adjust value as needed - may need to be readjusted if
-% the document is modified later
-%\IEEEtriggeratref{8}
-% The "triggered" command can be changed if desired:
-%\IEEEtriggercmd{\enlargethispage{-5in}}
-
-% references section
-
-% can use a bibliography generated by BibTeX as a .bbl file
-% BibTeX documentation can be easily obtained at:
-% http://www.ctan.org/tex-archive/biblio/bibtex/contrib/doc/
-% The IEEEtran BibTeX style support page is at:
-% http://www.michaelshell.org/tex/ieeetran/bibtex/
-\bibliographystyle{IEEEtran}
+\bibliographystyle{abbrv}
 \bibliography{bib}
 
-% argument is your BibTeX string definitions and bibliography database(s)
-%\bibliography{IEEEabrv,../bib/paper}
-%
-% <OR> manually copy in the resultant .bbl file
-% set second argument of \begin to the number of references
-% (used to reserve space for the reference number labels box)
-
-%%%%%%%%%%%%%%%%%%%%%
-%\begin{thebibliography}{1}
-
-%\bibitem{IEEEhowto:kopka}
-%H.~Kopka and P.~W. Daly, \emph{A Guide to \LaTeX}, 3rd~ed.\hskip 1em %plus
-%  0.5em minus 0.4em\relax Harlow, England: Addison-Wesley, 1999.
-
-%\end{thebibliography}
-%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
-
-% that's all folks
 \end{document}

### 2016-01-11 paper/author_disambiguaton.tex
correct i.e. and e.g.

@@
 \documentclass{sig-alternate}
+
+\usepackage{xspace}
+\newcommand*{\eg}{e.g.\@\xspace}
+\newcommand*{\ie}{i.e.\@\xspace}
 
@@
 issue since the accuracy of information managed at the level of individuals directly affects:
-the relevance search of results (e.g., when querying for all publications written by a given author);
-the reliability of bibliometrics and author rankings (e.g., citation counts or other impact
+the relevance search of results (\eg, when querying for all publications written by a given author);
+the reliability of bibliometrics and author rankings (\eg, citation counts or other impact
 metrics, as studied in \cite{strotmann2012author}); and/or the relevance of scientific network analysis
@@
 hiring professional collaborators or through developing services that invite authors to register
-their publications themselves (e.g., Google Scholar or Inspire-HEP).
-Recent efforts to create persistent digital identifiers assigned to researchers (e.g., ORCID or ResearcherID),
+their publications themselves (\eg, Google Scholar or Inspire-HEP).
+Recent efforts to create persistent digital identifiers assigned to researchers (\eg, ORCID or ResearcherID),
 with the objective to embed these identifiers in the submission workflow of publishers
-or repositories (e.g., Elsevier, arXiv or Inspire-HEP), would univocally solve any disambiguation issue.
+or repositories (\eg, Elsevier, arXiv or Inspire-HEP), would univocally solve any disambiguation issue.
 With the large cost of centralized manual authorship control, or until crowdsourced solutions are more
@@
 clustering algorithm when the latter is applied to a mixed set of labeled
-and unlabeled publications, e.g., by maximizing some clustering performance
+and unlabeled publications, \eg, by maximizing some clustering performance
 metric on the known clusters \cite{levin2012citation}.
@@
 groups signatures together if they share the same surname(s) and the same first
-given name initial (e.g., \emph{SFI}("Doe, John") $==$ "Doe, J").
+given name initial (\eg, \emph{SFI}("Doe, John") $==$ "Doe, J").
 Despite satisfactory performance, there are several cases where this simple strategy fails to cluster related pairs of signatures together, including:
@@
   ways of writing an author name, or signatures contain a typo
-  (e.g., "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
+  (\eg, "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
 
-  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (e.g., "Martinez Torres, A." and "Torres, A. Martinez").
+  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (\eg, "Martinez Torres, A." and "Torres, A. Martinez").
 
   \item An author has multiple surnames and, on some signatures, only the first surname is
-  present (e.g., "Smith-Jones, A." and "Smith, A.")
+  present (\eg, "Smith-Jones, A." and "Smith, A.")
 
-  \item An author has multiple given names and they are not always all recorded (e.g.,
+  \item An author has multiple given names and they are not always all recorded (\eg,
   "Smith, Jack" and "Smith, A. J.")
 
-  \item An authors surname changed (e.g., due to marriage).
+  \item An authors surname changed (\eg, due to marriage).
 \end{enumerate}
@@
 phonetic representation of the normalized surname.
-Normalization involves stripping accents (e.g., "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
-affixes that inconsistently appear in signatures (e.g., "van der Waals, J. D."
+Normalization involves stripping accents (\eg, "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
+affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."
 $\rightarrow$ "Waals, J. D."), while phonetization is based either on the
@@
 Author names from different cultures, origins or ethnic groups are likely to be
-disambiguated using different strategies (e.g., pairs of signatures with French
+disambiguated using different strategies (\eg, pairs of signatures with French
 author names versus pairs of signatures with Chinese author names) \cite{treeratpituk2012name, chin2014effective}.
@@
 Rather than sampling pairs uniformly at random, we propose to oversample
-difficult cases when building the training set (e.g., pairs of signatures with
+difficult cases when building the training set (\ie, pairs of signatures with
 different author names corresponding to same individual, and pairs of
@@
 limiting factor to further overall improvements.
-As shown in Table~\ref{table:blocking}, the maximum recall (e.g., if within a block, all signatures were clustered optimally) for SFI is $0.9828$.
+As shown in Table~\ref{table:blocking}, the maximum recall (\ie, if within a block, all signatures were clustered optimally) for SFI is $0.9828$.
 At the price of fewer and therefore slightly larger blocks (as reported in the right column of Table~\ref{table:blocking}), the
@@
 strategy ($0.9409$), but yields anyhow surprisingly decent accuracy, given the
-fact it requires almost no computation (e.g., both learning a linkage function
+fact it requires almost no computation (\ie, both learning a linkage function
 and running agglomerative clustering can be skipped -- only the blocking
@@
 with a slight advantage for block cuts ($0.9814$ versus $0.9830$), as expected.
-In case ${\cal S}^\prime_b$ is empty (e.g., because it corresponds to a young
+In case ${\cal S}^\prime_b$ is empty (\eg, because it corresponds to a young
 researcher at the beginning of his career), this therefore suggests that either using
@@
 
-\textit{Combined best settings.} When all best settings are combined (e.g.,
-Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
+\textit{Combined best settings.} When all best settings are combined (\ie, Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
 pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
-performance reaches $0.9862$, e.g., the best of all reported results. In particular,
+performance reaches $0.9862$, \ie, the best of all reported results. In particular,
 this combination exhibits both the high recall of phonetic blocking based on the NYSIIS algorithm
@@
 pipeline to cultures and ethnic groups for which standard author disambiguation
-is known to be less efficient (e.g., Chinese authors with many homonyms)  indeed
+is known to be less efficient (\eg, Chinese authors with many homonyms)  indeed
 constitutes a direction of research with great potential benefits for the

### 2016-01-11 paper/author_disambiguaton.tex
modifying the abstract
Adding a few ideas to the abstract

@@
 Hussein T. Al-Natsheh\\
-       \affaddr{ISH-LYON, CNRS, France}\\
+       \affaddr{ISH-LYON (USR 3385), CNRS, France}\\
        \email{hussein.al-natsheh@ish-lyon.cnrs.fr}
@@
 increasing recall; and (ii) adding strong ethnicity-sensitive features for learning a linkage
-function, thereby tailoring disambiguation to non-Western author names whenever necessary.
+function, thereby tailoring disambiguation to non-Western author names whenever necessary. (iii) Showing the importance of balancing negative and positive examples when learning the linkage function.
+In addition to releasing the software implementation of our improved pipeline, we also published the verified dataset to ease the comparison with other researchers who are interested in further contribution.
 \end{abstract}

### 2016-01-12 paper/author_disambiguaton.tex
Further changes to the abstract

--- 2016-01-11 paper/author_disambiguaton.tex
@@
 
-Author name disambiguation in bibliographic databases is the problem of
-grouping together scientific publications written by the same person, accounting
-for potential homonyms and/or synonyms.
-Among solutions to this problem, digital libraries are increasingly offering tools
-for authors to manually curate their publications and claim those that are theirs.
-Indirectly, these tools allow for the inexpensive collection of large annotated training
-data, which can be further leveraged to build a complementary automated
-disambiguation system capable of inferring patterns for identifying
-publications written by the same person.
-Building on more than 1 million publicly released crowdsourced annotations,
-we propose an automated author disambiguation solution exploiting this data (i) to learn
-an accurate classifier for identifying coreferring authors and (ii) to guide the clustering
-of scientific publications by distinct authors in a semi-supervised way.
-To the best of our knowledge, our analysis is the first to be carried out on data of
-this size and coverage.
-With respect to the state of the art, we validate the general pipeline used in most existing
-solutions, and improve by: (i) proposing phonetic-based blocking strategies, thereby
-increasing recall; and (ii) adding strong ethnicity-sensitive features for learning a linkage
-function, thereby tailoring disambiguation to non-Western author names whenever necessary.
+Author name disambiguation in bibliographic databases is the problem of grouping
+together scientific publications written by the same person, accounting for
+potential homonyms and/or synonyms. Among solutions to this problem, digital
+libraries are increasingly offering tools for authors to manually curate their
+publications and claim those that are theirs. Indirectly, these tools allow for
+the inexpensive collection of large annotated training data, which can be
+further leveraged to build a complementary automated disambiguation system
+capable of inferring patterns for identifying publications written by the same
+person. Building on more than 1 million crowdsourced
+annotations that we publicly release, we propose an automated author disambiguation solution exploiting
+this data (i) to learn an accurate classifier for identifying coreferring
+authors and (ii) to guide the clustering of scientific publications by distinct
+authors in a semi-supervised way. To the best of our knowledge, our analysis is
+the first to be carried out on data of this size and coverage. With respect to
+the state of the art, we validate the general pipeline used in most existing
+solutions, and improve by: (i) proposing phonetic-based blocking strategies,
+thereby increasing recall; (ii) adding strong ethnicity-sensitive features for
+learning a linkage function, thereby tailoring disambiguation to non-Western
+author names whenever necessary; and (iii) showing the importance of balancing
+negative and positive examples when learning the linkage function.
+
 \end{abstract}

### 2016-01-12 paper/author_disambiguation.tex

--- 2016-01-12 paper/author_disambiguaton.tex
@@
 \usepackage{xspace}
+\usepackage[hidelinks]{hyperref}
 \newcommand*{\eg}{e.g.\@\xspace}
@@
        \email{hussein.al-natsheh@ish-lyon.cnrs.fr}
+\and
 \alignauthor
@@
 \alignauthor
-\and
 Eamonn Maguire\\
@@
 Finally, conclusions and future works are discussed in Section~\ref{conclusions}.
+
 % Related works ==================================================================
@@
 
-\section{Semi-supervised author disambiguation}
+\section{Semi-supervised\\ author disambiguation}
 \label{methods}
@@
 \centering
-\includegraphics[width=\textwidth]{fig-pub-to-signature}
+\includegraphics[width=\textwidth]{fig-pub-to-signature.pdf}
 \caption{An example signature $s$ for "Doe, John". A \textit{signature} is
@@
 \centering
-\includegraphics[width=\textwidth]{fig-workflow}
+\includegraphics[width=\textwidth]{fig-workflow.pdf}
 \caption{Pipeline for author disambiguation: (a)
@@
 phonetic representation of the normalized surname.
-Normalization involves stripping accents (\eg, "Jabłoński, Ł" $\rightarrow$ "Jablonski, L") and name
-affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."
+Normalization involves stripping accents (e.g., "Jab\l{}o\'nski, \L{}" $\rightarrow$ "Jablonski, L") and name
+affixes that inconsistently appear in signatures (e.g., "van der Waals, J. D."
 $\rightarrow$ "Waals, J. D."), while phonetization is based either on the
@@
 \centering
+{\small
 \begin{tabular}{|l|l|}
@@
   \hline
-\end{tabular}
+\end{tabular}}
 \end{table*}
@@
 \centering
-\includegraphics[width=\textwidth]{fig-cuts}
+\includegraphics[width=\textwidth]{fig-cuts.pdf}
 \caption{Semi-supervised cut-off strategies to form flat clusters of signatures.}

### 2016-01-12 paper/author_disambiguation.tex
Revert eg change
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

@@
 phonetic representation of the normalized surname.
-Normalization involves stripping accents (e.g., "Jab\l{}o\'nski, \L{}" $\rightarrow$ "Jablonski, L") and name
-affixes that inconsistently appear in signatures (e.g., "van der Waals, J. D."
+Normalization involves stripping accents (\eg, "Jab\l{}o\'nski, \L{}" $\rightarrow$ "Jablonski, L") and name
+affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."
 $\rightarrow$ "Waals, J. D."), while phonetization is based either on the

### 2016-01-18 paper/author_disambiguation.tex

@@
 
-Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
+Formally, let us assume a set of publications \\ ${\cal P} = \{ p_0, ...,
 p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
@@
 Our implementation is made to be efficient, exploiting parallelization when available, and ready for production environments.
-It is also designed to be runnable
-in an incremental fashion, by enabling disambiguation only on specified blocks if desired,
-instead of having to run the disambiguation process on the whole signature set.
+It is also designed to be runnable in an incremental fashion in which our approach is considered to be scalable.
+We adopt a divide-and-conquer strategy for clustering (called “blocking” in this line of work) in order to reduce the computational complexity from $O(N^2)$ to $O(\sum N_i^2)$, which in practice tends to ${O(N)}$ when $N_i << N$.
+This also means that instead of having to run the disambiguation process on the whole signature set, the process could be run only on specified blocks if desired.
 
@@
 \begin{table*}
-\caption{Average precision, recall and B3 f-measure scores on test folds.}
+\caption{Average precision, recall and f-measure scores on test folds.}
 \label{table:results}
 \centering
-\begin{tabular}{|l|c c c|}
+\begin{tabular}{|l|c c c | c c c|}
   \hline
-                       & \multicolumn{3}{|c|}{\textbf{B3}} \\
-  \textbf{Description} & $P$ & $R$ & $F$ \\
+                       & \multicolumn{3}{|c|}{\textbf{B3}} & \multicolumn{3}{|c|}{\textbf{Pairwise}}\\
+  \textbf{Description} & $P$ & $R$ & $F$ & $P$ & $R$ & $F$ \\
   \hline
   \hline
-Baseline & 0.9901 & 0.9760 & 0.9830  \\
+Baseline & 0.9024 & 0.9828 & 0.9409  & 0.8298 & 0.9776 & 0.8977 \\
 \hline
-Blocking = SFI & 0.9901 & 0.9760 & 0.9830  \\
-Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841  \\
-Blocking = NYSIIS & 0.9875 & 0.9826 & \textbf{0.9850} \\
-Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 \\
+\underline{Blocking = SFI} & 0.9901 & 0.9760 & 0.9830  & 0.9948 & 0.9738 & 0.9842\\
+Blocking = Double metaphone & 0.9856 & 0.9827 & 0.9841  & 0.9927 & 0.9817 & 0.9871 \\
+Blocking = NYSIIS & 0.9875 & 0.9826 & \textbf{0.9850}  & 0.9936 & 0.9814 & \textbf{0.9875} \\
+Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
 \hline
-No name normalization & 0.9887 & 0.9697 & 0.9791  \\
-Name normalization & 0.9901 & 0.9760 & \textbf{0.9830}  \\
+No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
+\underline{Name normalization} & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842}  \\
 \hline
-Classifier = GBRT & 0.9901 & 0.9760 & 0.9830  \\
-Classifier = Random Forests & 0.9909 & 0.9783 & \textbf{0.9846}  \\
-Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666  \\
 \hline
-Training pairs = Non-blocked, uniform & 0.9793 & 0.9630 & 0.9711  \\
-Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786  \\
-Training pairs = Blocked, balanced & 0.9901 & 0.9760 & \textbf{0.9830}  \\
+\underline{Classifier = GBRT} & 0.9901 & 0.9760 & 0.9830   & 0.9948 & 0.9738 & 0.9842 \\
+Classifier = Random Forests & 0.9909 & 0.9783 & \textbf{0.9846}  & 0.9957 & 0.9752 & \textbf{0.9854} \\
+Classifier = Linear Regression & 0.9749 & 0.9584 & 0.9666 & 0.9717 & 0.9569 & 0.9643 \\
 \hline
-Clustering = Average linkage & 0.9901 & 0.9760 & \textbf{0.9830}  \\
-Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671  \\
-Clustering = Complete linkage & 0.9862 & 0.9709 & 0.9785  \\
+Training pairs = Non-blocked, uniform & 0.9793 & 0.9630 & 0.9711  & 0.9756 & 0.9629 & 0.9692 \\
+Training pairs = Blocked, uniform & 0.9854 & 0.9720 & 0.9786  & 0.9850 & 0.9707 & 0.9778 \\
+\underline{Training pairs = Blocked, balanced} & 0.9901 & 0.9760 & \textbf{0.9830}  & 0.9948 & 0.9738 & \textbf{0.9842} \\
 \hline
-No cut & 0.9024 & 0.9828 & 0.9409  \\
-Global cut & 0.9892 & 0.9737 & 0.9814  \\
-Block cut & 0.9901 & 0.9760 & \textbf{0.9830}  \\
 \hline
-Combined best settings & 0.9897 & 0.9827 & \textbf{0.9862}  \\
+\underline{Clustering = Average linkage} & 0.9901 & 0.9760 & \textbf{0.9830}  & 0.9948 & 0.9738 & \textbf{0.9842} \\
+Clustering = Single linkage & 0.9741 & 0.9603 & 0.9671  & 0.9543 & 0.9626 & 0.9584 \\
+Clustering = Complete linkage & 0.9862 & 0.9709 & 0.9785  & 0.9920 & 0.9688 & 0.9803 \\
+\hline
+No cut (baseline) & 0.9024 & 0.9828 & 0.9409  & 0.8298 & 0.9776 & 0.8977 \\
+Global cut & 0.9892 & 0.9737 & 0.9814  & 0.9940 & 0.9727 & 0.9832 \\
+\underline{Block cut} & 0.9901 & 0.9760 & \textbf{0.9830}  & 0.9948 & 0.9738 & \textbf{0.9842} \\
+\hline
+\hline
+Combined best settings & 0.9897 & 0.9827 & \textbf{0.9862}  & 0.9954 & 0.9805 & \textbf{0.9879} \\
   \hline
@@
 
-\begin{table*}
-\caption{Average precision, recall and pairwise f-measure scores on test folds.}
-\label{table:resultspw}
-\centering
-\begin{tabular}{|l|c c c|}
-  \hline
-                       & \multicolumn{3}{|c|}{\textbf{Pairwise}} \\
-  \textbf{Description} & $P$ & $R$ & $F$\\
-  \hline
-  \hline
-Baseline & 0.9948 & 0.9738 & 0.9842 \\
-\hline
-Blocking = SFI & 0.9948 & 0.9738 & 0.9842 \\
-Blocking = Double metaphone & 0.9927 & 0.9817 & 0.9871 \\
-Blocking = NYSIIS  & 0.9936 & 0.9814 & \textbf{0.9875} \\
-Blocking = Soundex & 0.9935 & 0.9725 & 0.9828 \\
-\hline
-No name normalization & 0.9931 & 0.9658 & 0.9793 \\
-Name normalization& 0.9948 & 0.9738 & \textbf{0.9842} \\
-\hline
-Classifier = GBRT & 0.9948 & 0.9738 & 0.9842 \\
-Classifier = Random Forests & 0.9957 & 0.9752 & \textbf{0.9854} \\
-Classifier = Linear Regression & 0.9717 & 0.9569 & 0.9643 \\
-\hline
-Training pairs = Non-blocked, uniform & 0.9756 & 0.9629 & 0.9692 \\
-Training pairs = Blocked, uniform & 0.9850 & 0.9707 & 0.9778 \\
-Training pairs = Blocked, balanced  & 0.9948 & 0.9738 & \textbf{0.9842} \\
-\hline
-Clustering = Average linkage& 0.9948 & 0.9738 & \textbf{0.9842} \\
-Clustering = Single linkage & 0.9543 & 0.9626 & 0.9584 \\
-Clustering = Complete linkage & 0.9920 & 0.9688 & 0.9803 \\
-\hline
-No cut& 0.8298 & 0.9776 & 0.8977 \\
-Global cut & 0.9940 & 0.9727 & 0.9832 \\
-Block cut& 0.9948 & 0.9738 & \textbf{0.9842} \\
-\hline
-Combined best settings & 0.9954 & 0.9805 & \textbf{0.9879} \\
-  \hline
-\end{tabular}
-\end{table*}
+Our approach could be considered as an experimental design solution.
+Our goal is to find the best combination of design parameters.
+Such a solution could be reached by performing many experiments where in each experiment we fix all design parameters except one.
+Of course, what we found as a best choice in each experiment will be used for the proceeding one and so on.
+To initialize the process, we will use what have been reported by some related works as a best method.
 
-\textit{Baseline.} Results presented in Table~\ref{table:results} are discussed with
-respect to a baseline solution using the following combination of components:
+\textit{state-of-the-art.} Unfortunately, most methods proposed in related works have released neither their software, nor their data, making in practice a fair comparison very difficult.
+However, we believe state-of-the-art algorithms proposed in the literature could still be shown by categorizing the design parameters into the three categories; blocking strategy, linkage function, and clustering and compare the choices per each category.
+This categorization represents the three main phases in the pipeline.
+We believe that results for different settings somehow reflects some of these state-of-the-art choices as we will show in this section.
+Results presented in Table ~\ref{table:results} are discussed with
+respect to a state-of-the-art using the following parameter design setting per category.
+In Table ~\ref{table:results}, what we considered as state-of-the-art choice is underlined which are as follows:
+
 \begin{itemize}
-\item Blocking: same surname and the same first given name initial strategy (SFI);
+	\item Blocking: same surname and the same first given name initial strategy (SFI) and with name normalization;
 	\item Linkage function: all 22 features defined in Table~\ref{table:features},
@@
 	\item Clustering: agglomerative clustering using average linkage and
-    block cuts found to maximize $F_\text{B3}({\cal C}_\text{train}^\prime, \widehat{\cal C}_\text{train}^\prime, {\cal S}_\text{train}^\prime)$.
+	block cuts found to maximize \\ $F_\text{B3}({\cal C}_\text{train}^\prime, \widehat{\cal C}_\text{train}^\prime, {\cal S}_\text{train}^\prime)$.
 \end{itemize}
 
-\textit{Blocking.} The good precision of the baseline ($0.9901$), but its
+\textit{Baseline.} Using machine learning techniques should perform better than dealing with the problem with other simpler method.
+Accordingly, we have set our experiment baseline having neither linkage function nor clustering.
+Actually, This is the case of many digital library where they use a simple and very fast execution solution with acceptable performance.
+Accordingly, our baseline algorithm is simply to group the set of publications from author names that have common surname and first initial as denoted in section \ref{methods:blocking} by \textit{SFI} and label them with a distinct author.
+However, this baseline also considers \textit{Name Normalization} for the 5 cases that is also previously discussed in section \ref{methods:blocking}.
+The results of the baseline is reported in the top of  Table ~\ref{table:results}.
+
+In sections \ref{choices:blocking}, \ref{choices:linkage}, and \ref{choices:clustering}, we will discuss each group of design parameters in respect to the state-of-the-art choice of that group.
+Keep in mind that the results of each group uses the best of the other design parameters.
+
+\subsubsection{Blocking choices} 
+\label{choices:blocking}
+The good precision of the state-of-the-art ($0.9901$), but its
 lower recall ($0.9760$) suggest that the blocking strategy might be the
@@
 In particular, the NYSIIS-based phonetic blocking shows to be the most effective when applied
-to the baseline (with an F-measure of $0.9850$) while also being the most
+to the state-of-the-art (with an F-measure of $0.9850$) while also being the most
 efficient computationally (with 10857 blocks versus 12978 for the baseline).
@@
 normalizing author names (stripping accents, removing affixes), as performed in the
-baseline, is shown to be important. Results from Table~\ref{table:results} clearly suggest that not
+state-of-the-art, is shown to be important. Results from Table~\ref{table:results} clearly suggest that not
 normalizing significantly reduces performance (yielding an F-measure of $0.9830$ when normalizing,
@@
 
-\textit{Linkage function.} Let us first comment on the results regarding the
+\subsubsection{Linkage function choices} 
+\label{choices:linkage}
+Let us first comment on the results regarding the
 supervised algorithm used to learn the linkage function.
@@
 
-\begin{figure}
-\centering
-\caption{Recursive Feature Elimination analysis. }
-\label{fig:rfe}
-\includegraphics[width=\linewidth]{fig-rfe.pdf}
-\end{figure}
-
 Using Recursive Feature Elimination \cite{guyon2002gene}, we next evaluate the
 usefulness of all fifteen standard and seven additional ethnicity features for learning
-the linkage function. The analysis consists in using the baseline algorithm
+the linkage function. The analysis consists in using the state-of-the-art algorithm
 first using all twenty two features, to determine the least discriminative from feature
-importances \cite{louppe2013understanding}, and then re-learn the baseline
+importances \cite{louppe2013understanding}, and then re-learn the state-of-the-art algorithm
 using all but that one feature. That process is repeated recursively until
 eventually only one feature remains. Results are presented in
-Figure~\ref{fig:rfe} for one of the three folds, starting from the far right with
-the baseline and \textit{Second given name} being the least important feature,
+Figure~\ref{fig:rfe} for one of the three folds with
+the state-of-the-art, starting from the far right, \textit{Second given name} being the least important feature,
 and ending on the left with all features eliminated but \textit{Chinese}. As
@@
 
-\textit{Semi-supervised clustering.} The last part of our experiment concerns
+\begin{figure}
+	\centering
+	\caption{Recursive Feature Elimination analysis. }
+	\label{fig:rfe}
+	\includegraphics[width=\linewidth]{fig-rfe.pdf}
+\end{figure}
+
+\subsubsection{Semi-supervised clustering choices}  
+\label{choices:clustering}
+The last part of our experiment concerns
 the study of agglomerative clustering and the best way to find a cut-off
@@
 
-Clustering together all signatures from the same block is the least effective
+Clustering together all signatures from the same block (\ie, baseline) is the least effective
 strategy ($0.9409$), but yields anyhow surprisingly decent accuracy, given the
@@
 
-\textit{Combined best settings.} When all best settings are combined (\ie, Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
+\subsubsection{Combined best settings} When all best settings are combined (\ie, Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
 pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
@@
 
-\textit{Execution time.} Our implementation takes around $20$ hours to process the complete set of the data (for 10M signatures, on a $16$ cores machine with $32$GB of RAM).
+\subsubsection{Execution time} Our implementation takes around $20$ hours to process the complete set of the data (for 10M signatures, on a $16$ cores machine with $32$GB of RAM).
 Related work \cite{khabsa2014large} reports execution times around $24$ hours to cluster $4$M signatures.

### 2016-01-18 paper/author_disambiguation.tex
MSusik PR
as a new commit as the original PR has conflict

@@
 metrics, as studied in \cite{strotmann2012author}); and/or the relevance of scientific network analysis
-\cite{newman2001structure}.
+\cite{newman2001structure}. Thus, even small improvements in the field significantly improve the
++usability of the digital libraries to some users.
 
@@
 Related work \cite{khabsa2014large} reports execution times around $24$ hours to cluster $4$M signatures.
-Note also that shorter execution times can be achieved, at the expense of worse results.
+Note also that shorter execution times can be achieved, at the expense of worse results, by reducing the set of the features used.
 

### 2016-01-19 paper/author_disambiguation.tex
extra '+'
solving an extra '+' which was added by mistake
Rephrase things

@@
 metrics, as studied in \cite{strotmann2012author}); and/or the relevance of scientific network analysis
-\cite{newman2001structure}. Thus, even small improvements in the field significantly improve the
-+usability of the digital libraries to some users.
+\cite{newman2001structure}. Thus, even small improvements in the field significantly improve the usability of the digital libraries to some users.
 
@@
 R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|c(s)|}\\
-F_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{2 P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}{P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) + P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}\\
+F_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{2 P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}{P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) + P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}
+\end{align}
+\begin{align}
 P_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p(\widehat{\cal C})|}\\
@@
 \begin{table*}
-\caption{Average precision, recall and f-measure scores on test folds.}
+\caption{Average precision, recall and f-measure scores on test folds. Underlined components correspond together the state-of-the-art solution.}
 \label{table:results}
@@
 
-Our approach could be considered as an experimental design solution.
-Our goal is to find the best combination of design parameters.
-Such a solution could be reached by performing many experiments where in each experiment we fix all design parameters except one.
-Of course, what we found as a best choice in each experiment will be used for the proceeding one and so on.
-To initialize the process, we will use what have been reported by some related works as a best method.
+% Our approach could be considered as an experimental design solution. Our goal is
+% to find the best combination of design parameters. Such a solution could be
+% reached by performing many experiments where in each experiment we fix all
+% design parameters except one. Of course, what we found as a best choice in each
+% experiment will be used for the proceeding one and so on. To initialize the
+% process, we will use what have been reported by some related works as a best
+% method.
 
-\textit{state-of-the-art.} Unfortunately, most methods proposed in related works have released neither their software, nor their data, making in practice a fair comparison very difficult.
-However, we believe state-of-the-art algorithms proposed in the literature could still be shown by categorizing the design parameters into the three categories; blocking strategy, linkage function, and clustering and compare the choices per each category.
-This categorization represents the three main phases in the pipeline.
-We believe that results for different settings somehow reflects some of these state-of-the-art choices as we will show in this section.
-Results presented in Table ~\ref{table:results} are discussed with
-respect to a state-of-the-art using the following parameter design setting per category.
-In Table ~\ref{table:results}, what we considered as state-of-the-art choice is underlined which are as follows:
+\textit{Baseline.} The simplest baseline against which we compare our results
+consists in grouping all signatures sharing the same (normalized) surname(s) and
+the same (normalized) first given name initial. As it does not require the usage
+of any machine learning component, this baseline provides a simple and fast
+solution yielding decent results, as reported at the top of
+Table~\ref{table:results}
+
+\textit{State-of-the-art.} Most methods proposed in related works have released
+neither their software, nor their data, making a fair comparison very difficult.
+Yet, we believe solutions reported in the literature can be closely
+matched to our generic pipeline, provided the blocking strategy, the linkage
+function and the clustering algorithm are properly aligned. In particular,
+we consider hereon as the \textit{state-of-the-art} solution the following
+combination of components:
 
@@
 
-\textit{Baseline.} Using machine learning techniques should perform better than dealing with the problem with other simpler method.
-Accordingly, we have set our experiment baseline having neither linkage function nor clustering.
-Actually, This is the case of many digital library where they use a simple and very fast execution solution with acceptable performance.
-Accordingly, our baseline algorithm is simply to group the set of publications from author names that have common surname and first initial as denoted in section \ref{methods:blocking} by \textit{SFI} and label them with a distinct author.
-However, this baseline also considers \textit{Name Normalization} for the 5 cases that is also previously discussed in section \ref{methods:blocking}.
-The results of the baseline is reported in the top of  Table ~\ref{table:results}.
-
-In sections \ref{choices:blocking}, \ref{choices:linkage}, and \ref{choices:clustering}, we will discuss each group of design parameters in respect to the state-of-the-art choice of that group.
-Keep in mind that the results of each group uses the best of the other design parameters.
+Sections \ref{choices:blocking}, \ref{choices:linkage}, and
+\ref{choices:clustering} now study each component individually and discuss
+results with respect to the underlined state-of-the-art solution.
 
@@
 \label{choices:blocking}
+
 The good precision of the state-of-the-art ($0.9901$), but its
@@
 
-Finally, let us also note that Table~\ref{table:blocking} corroborates the
+Let us also note that Table~\ref{table:blocking} corroborates the
 estimation of \cite{torvik2009author}, stating that SFI blocking has a recall
@@
 
-\textit{Name normalization.} As discussed previously, the seemingly insignificant step of
+Finally, as discussed previously, the seemingly insignificant step of
 normalizing author names (stripping accents, removing affixes), as performed in the

### 2016-01-20 paper/author_disambiguation.tex
fix Tabel 2 title
Error rate discussion
Adding a paragraph discussing the importance of our approach enhancement

@@
 \begin{table*}
-\caption{Average precision, recall and f-measure scores on test folds. Underlined components correspond together the state-of-the-art solution.}
+\caption{Average precision, recall and f-measure scores on test folds. Underlined components correspond to the state-of-the-art choices.}
 \label{table:results}
@@
 
+The best combined settings reduces the error rate by $76.65\%$ in comparison with the baseline.
+This means that more than three quarters of ambiguous author names are predicted to be resolved using our approach in compare with using \textit{SFI} method a lone after applying \textit{Name Normalization}.
+In comparison with the state-of-the-art, the error rate reduction is $18.82\%$ which means about fifth of ambiguous author names (\ie, signatures) that is unsolved by the state-of-the-art would be addressed.
+When we deal with 10 millions of signatures(\ie, the case of the digital library we took the dataset from), this performance enhancements is equivalent to $453000$ more signatures to be resolved in comparison of the baseline which is expensive to resolve with manual curation.
+In comparison of the state-of-the-art, this is equivalent to $32000$ more signatures to be resolved.
+
 \subsubsection{Execution time} Our implementation takes around $20$ hours to process the complete set of the data (for 10M signatures, on a $16$ cores machine with $32$GB of RAM).

### 2016-01-20 paper/author_disambiguation.tex
modify the added paragraph
modify the added discussion of the combined best settings improvement

--- 2016-01-19 paper/author_disambiguation.tex
@@
 performance reaches $0.9862$, \ie, the best of all reported results. In particular,
-this combination exhibits both the high recall of phonetic blocking based on the NYSIIS algorithm
-and the high precision of Random Forests.
+this combination exhibits both the high recall of phonetic blocking based on the NYSIIS algorithm and the high precision of Random Forests.
+Our best combined settings solution achieves relative improvement of more than $76\%$ with respect to the baseline and about $19\%$ with respect to the state-of-the-art choices.
 

### 2016-04-23 paper/author_disambiguation.tex
kesw initial commit
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

--- 2016-01-19 paper/author_disambiguation.tex
@@
 
-\documentclass{sig-alternate}
+\documentclass[runningheads,a4paper]{llncs}
 
 \usepackage{xspace}
+\usepackage{graphicx}
+\usepackage{amsfonts}
+\usepackage{amssymb}
+\usepackage{epsfig}
+\usepackage{amsmath}
 \usepackage[hidelinks]{hyperref}
@@
 \newcommand*{\ie}{i.e.\@\xspace}
+\usepackage{color}
+\newcommand{\msnote}[1]{\textcolor{blue}{[MS: #1]}}
 
+\def\baselinestretch{0.95}
 \begin{document}
 
-% Copyright
-\setcopyright{acmcopyright}
 % paper title
@@
 
-\numberofauthors{4}
-\author{
-\alignauthor
-Gilles Louppe\\
-       \affaddr{CERN, Switzerland}\\
-       \email{g.louppe@cern.ch}
-\alignauthor
-Hussein T. Al-Natsheh\\
-       \affaddr{ISH-LYON (USR 3385), CNRS, France}\\
+\authorrunning{Gilles Louppe et al.}
+\author{Gilles Louppe\inst{1}\and Hussein T. Al-Natsheh\inst{2}\and Mateusz Susik\inst{3}\and\\ 
+Eamonn James Maguire\inst{1}}
+
+\institute{CERN, Switzerland,\\
+\email{\{g.louppe, eamonn.james.maguire\}@cern.ch},
+\and
+ISH-LYON (USR 3385), CNRS, France,\\
 \email{hussein.al-natsheh@ish-lyon.cnrs.fr}
 \and
-\alignauthor
-Mateusz Susik\\
-       \affaddr{University of Warsaw}\\
+University of Warsaw, Poland,\\
 \email{msusik@student.uw.edu.pl}
-\alignauthor
-Eamonn Maguire\\
-       \affaddr{CERN, Switzerland}\\
-       \email{eamonn.james.maguire@cern.ch}
 }
@@
 grouping together publications written by the same person.
-Author name disambiguation is often a difficult problem because an author may use different
+It is often difficult because an author may use different
 spellings or name variants across their career (synonymy) and/or distinct authors may
@@
 or repositories (\eg, Elsevier, arXiv or Inspire-HEP), would univocally solve any disambiguation issue.
-With the large cost of centralized manual authorship control, or until crowdsourced solutions are more
-widely adopted, the impact of these efforts are unfortunately limited by the efficiency, motivation
-and integrity of their active contributors. Similarly, the success of persistent digital identifier efforts
-is conditioned to a large and ubiquitous adoption by both researchers and publishers.
-For these reasons, fully automated machine learning-based methods have been proposed during the past decade to
+As the centralized manual authorship control is expensive and the success of persistent digital
+identifiers requires large and ubiquitous adoption by both researchers and publishers, fully
+automated machine learning-based methods have been proposed during the past decade to
 provide immediate, less costly, and satisfactory solutions to author
@@
 Additionally, we propose alternative strategies for blocking based on the
-phonetization of author names to increase recall.
-
-We also propose ethnicity-sensitive features for learning a linkage function,
-thereby tailoring author disambiguation to non-Western author names whenever necessary.
+phonetization of author names to increase recall and ethnicity-sensitive features for learning a
+linkage function which tailor our author disambiguation to non-Western author names whenever
+necessary.
 
@@
 
-\section{Semi-supervised\\ author disambiguation}
+\section{Semi-supervised author disambiguation}
 \label{methods}
 
-Formally, let us assume a set of publications \\ ${\cal P} = \{ p_0, ...,
+Formally, let us assume a set of publications ${\cal P} = \{ p_0, ...,
 p_{N-1}\}$ along with the set of unique individuals ${\cal A} = \{ a_0, ...,
@@
 
-Inspired by several previous works described in Section~\ref{related-works},
-we cast in this work author disambiguation into a semi-supervised clustering
-problem.
 Our algorithm is composed of three parts, as sketched in Figure~\ref{fig:workflow}: (i) a blocking
@@
   ways of writing an author name, or signatures contain a typo
-  (\eg, "Mueller, R." and "Muller, R.", "Tchaikovsky, P." and "Czajkowski, P.").
+  (\eg, "Mueller, R." and "Muller, R.").
 
@@
 When not specified, \emph{TF-IDF} vectors are otherwise computed from words.}.
-Similarly, the \textit{Year difference} feature measures the absolute difference between the publication date of the
-articles to which the two signatures respectively belong.
 
@@
 To support our disambiguation algorithm, we added seven features to our feature set, with each
-evaluating the degree of belonging of both signatures to an ethnic group,
-as reported in the second half of Table~\ref{table:features}.
+evaluating the degree of belonging of both signatures to an ethnic group.
+\msnote{Explain here ethnicity features (ethnicities come from some kind of US Census.
+Name those groups (as I removed them from the table))}
 
@@
   \hline
-	White & Product of estimated probabilities\\
-  Black & Product of estimated probabilities\\
-  American Indian or Alaska Native & Product of estimated probabilities\\
-  Chinese & Product of estimated probabilities\\
-  Japanese & Product of estimated probabilities\\
-  Other Asian or Pacific Islander & Product of estimated probabilities\\
-  Others & Product of estimated probabilities\\
+  Any ethnicity feature & Product of estimated probabilities\\
   \hline
@@
 use of the Scikit-Learn library \cite{scikitlearn} for the supervised learning
-of a linkage function and of SciPy \cite{scipy} for clustering.
+of a linkage function and of SciPy for clustering.
 All components of the disambiguation pipeline have been designed to follow the
@@
 Experiments carried out to study the impact of the proposed algorithmic
-components and refinements, as described in Section~\ref{methods}, follow a
+components and refinements, follow a
 standard 3-fold cross-validation protocol, using $({\cal S}^\prime, {\cal
@@
 and F-measure, as defined below:
+\begin{small}
 \begin{align}
@@
 R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|c(s)|}\\
-F_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{2 P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}{P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) + P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}
-\end{align}
-\begin{align}
+F_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{2 P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}{P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) + P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})} \\
 P_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p(\widehat{\cal C})|}\\
@@
 \end{align}
+\end{small}
 and where $c(s)$ (resp. $\widehat{c}(s)$) is the cluster $c \in {\cal C}$ such that
@@
 the same clusters in ${\cal C}$.
-Precision evaluates whether signatures are grouped only with signatures from the same true clusters,
-while recall measures the extent to which all signatures from the same true clusters are
-effectively grouped together.
 The F-measure is the harmonic mean between these two quantities.
@@
 
+% Our approach could be considered as an experimental design solution. Our goal is
+% to find the best combination of design parameters. Such a solution could be
+% reached by performing many experiments where in each experiment we fix all
+% design parameters except one. Of course, what we found as a best choice in each
+% experiment will be used for the proceeding one and so on. To initialize the
+% process, we will use what have been reported by some related works as a best
+% method.
+
 \begin{table*}
-\caption{Average precision, recall and f-measure scores on test folds. Underlined components correspond together the state-of-the-art solution.}
+\caption{Average precision, recall and f-measure scores on test folds. Underlined components correspond to the state-of-the-art choices.}
 \label{table:results}
@@
 
-% Our approach could be considered as an experimental design solution. Our goal is
-% to find the best combination of design parameters. Such a solution could be
-% reached by performing many experiments where in each experiment we fix all
-% design parameters except one. Of course, what we found as a best choice in each
-% experiment will be used for the proceeding one and so on. To initialize the
-% process, we will use what have been reported by some related works as a best
-% method.
-
 \textit{Baseline.} The simplest baseline against which we compare our results
@@
 
-Sections \ref{choices:blocking}, \ref{choices:linkage}, and
-\ref{choices:clustering} now study each component individually and discuss
+Below we study each component individually and discuss
 results with respect to the underlined state-of-the-art solution.
@@
 limiting factor to further overall improvements.
-As shown in Table~\ref{table:blocking}, the maximum recall (\ie, if within a block, all signatures were clustered optimally) for SFI is $0.9828$.
-At the price of fewer and therefore slightly larger blocks (as reported in the right column of Table~\ref{table:blocking}), the
+Our experiments showed the maximum $B3$ recall (\ie, if within a block, all signatures were clustered optimally) for SFI is $0.9828$, which corroborates the
+estimation of this technique on real data by \cite{torvik2009author}.
+At the price of fewer and therefore slightly larger blocks, the
 proposed phonetic-based blocking strategies show better maximum recall (all
@@
 
-Let us also note that Table~\ref{table:blocking} corroborates the
-estimation of \cite{torvik2009author}, stating that SFI blocking has a recall
-around $98\%$ on real data.
-
-\begin{table*}
-\caption{Maximum recall $R_\text{B3}^*$ and $R_\text{pairwise}^*$ of blocking strategies, and their number of blocks on ${\cal S}^\prime$.}
-\label{table:blocking}
-\centering
-\begin{tabular}{|l|cc|c|}
-  \hline
-  \textbf{Blocking} & $R_\text{B3}^*$ & $R_\text{pairwise}^*$ & \# blocks \\
-  \hline
-  \hline
-    SFI & 0.9828 & 0.9776 & 12978 \\
-    Double metaphone & 0.9907 & 0.9863 & 9753 \\
-    NYSIIS & 0.9902 & 0.9861 & 10857 \\
-    Soundex & 0.9906 & 0.9863 & 9403 \\
-  \hline
-\end{tabular}
-\end{table*}
+%\begin{table*}
+%\caption{Maximum recall $R_\text{B3}^*$ and $R_\text{pairwise}^*$ of blocking strategies, and %their number of blocks on ${\cal S}^\prime$.}
+%\label{table:blocking}
+%\centering
+%\begin{tabular}{|l|cc|c|}
+%  \hline
+%  \textbf{Blocking} & $R_\text{B3}^*$ & $R_\text{pairwise}^*$ & \# blocks \\
+%  \hline
+%  \hline
+%    SFI & 0.9828 & 0.9776 & 12978 \\
+%    Double metaphone & 0.9907 & 0.9863 & 9753 \\
+%    NYSIIS & 0.9902 & 0.9861 & 10857 \\
+%    Soundex & 0.9906 & 0.9863 & 9403 \\
+%  \hline
+%\end{tabular}
+%\end{table*}
 
@@
 
-\begin{figure}
+\begin{figure*}
   \centering
@@
   \includegraphics[width=\linewidth]{fig-rfe.pdf}
-\end{figure}
+\end{figure*}
 
@@
 performance reaches $0.9862$, \ie, the best of all reported results. In particular,
-this combination exhibits both the high recall of phonetic blocking based on the NYSIIS algorithm
-and the high precision of Random Forests.
+this combination exhibits both the high recall of phonetic blocking based on the NYSIIS algorithm and the high precision of Random Forests.
 

### 2016-04-24 paper/author_disambiguation.tex
kesw: fits in 15 pages.
* Removed table with maximum blocking recall
* Removed few citations to unsupervised clustering
* Shrunk the rfe figure

Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

@@
 \usepackage{amsmath}
+\usepackage{cite}
 \usepackage[hidelinks]{hyperref}
@@
 \usepackage{color}
+\setlength{\intextsep}{10pt plus 2pt minus 2pt}
 \newcommand{\msnote}[1]{\textcolor{blue}{[MS: #1]}}
@@
 
-\authorrunning{Gilles Louppe et al.}
+\authorrunning{G. Louppe, H. Al-Natsheh, M. Susik, E. Maguire}
 \author{Gilles Louppe\inst{1}\and Hussein T. Al-Natsheh\inst{2}\and Mateusz Susik\inst{3}\and\\ 
@@
 
-Efforts and solutions to author disambiguation have been proposed from various
+Solutions to author disambiguation have been proposed from various
 communities \cite{liu2014author}. On the one hand, libraries have maintained
@@
 identifiers requires large and ubiquitous adoption by both researchers and publishers, fully
-automated machine learning-based methods have been proposed during the past decade to
+automated machine learning-based methods have been proposed to
 provide immediate, less costly, and satisfactory solutions to author
-disambiguation. In this work, our goal is to explore and demonstrate how both
-approaches can coexist and benefit from each other.
-In particular, we study how labeled data obtained through manual curation (either centralized or
+disambiguation. In this work, we study how labeled data obtained through manual curation (either centralized or
 crowdsourced) can be exploited (i) to learn an accurate classifier for
@@
 commonly used in existing solutions is an effective approach for author disambiguation.
-Additionally, we propose alternative strategies for blocking based on the
+Moreover, we propose better strategies for blocking based on the
 phonetization of author names to increase recall and ethnicity-sensitive features for learning a
-linkage function which tailor our author disambiguation to non-Western author names whenever
-necessary.
+linkage function which tailor our author disambiguation to non-Western author names.
 
@@
 the use of domain-specific, manually designed, linkage functions tailored towards author
-disambiguation \cite{malin2005unsupervised,mcrae2006also,song2007efficient,
-soler2007separating, kang2009co,fan2011graph,schulz2014exploiting}.
+disambiguation \cite{malin2005unsupervised,song2007efficient, kang2009co,schulz2014exploiting}.
 These approaches have the advantage of not requiring hand-labeled data, but generally do
 not perform as well as supervised approaches.
-To reconcile both worlds, semi-supervised methods make use of small, manually verified, clusters of
+To reconcile both worlds, semi-supervised methods make use of small, manually verified clusters of
 publications and/or high-precision domain-specific rules to build a training
@@
 
-In this
-framework, author disambiguation can be stated as the problem of
+Author disambiguation can be stated as the problem of
 finding a partition ${\cal C} = \{ c_0, ..., c_{M-1} \}$ of ${\cal S}$ such
@@
 such that $c_i^\prime \subseteq c_i$, where $c_i^\prime$ may be empty.
-Or put otherwise, the set extends with the assumption that all signatures
-$s \in c_i^\prime$ belong to the same author.
 
-Our algorithm is composed of three parts, as sketched in Figure~\ref{fig:workflow}: (i) a blocking
-scheme whose goal is to roughly pre-cluster signatures ${\cal S}$ into smaller groups in order to
-reduce computational complexity; (ii) the construction of a linkage function
+Our algorithm is composed of three parts (Figure~\ref{fig:workflow}): (i) a blocking
+scheme whose goal is to pre-cluster signatures ${\cal S}$ into smaller groups; (ii) the construction of a linkage function
 $d$ between signatures using supervised learning; and (iii) the
@@
 By doing so, the computational complexity of clustering (see Section~\ref{methods:clustering})
-typically reduces from $O(|{\cal S}|^2)$ to $O(\sum_b |{\cal S}_b|^2)$, which is much more
-tractable as the number of signatures increases.
+typically reduces from $O(|{\cal S}|^2)$ to $O(\sum_b |{\cal S}_b|^2)$.
 Since disambiguation is performed independently per block, a good blocking strategy should be
@@
 groups signatures together if they share the same surname(s) and the same first
-given name initial (\eg, \emph{SFI}("Doe, John") $==$ "Doe, J").
+given name initial.
 Despite satisfactory performance, there are several cases where this simple strategy fails to cluster related pairs of signatures together, including:
@@
 
-\textit{Supervised classification.} The second part of the algorithm is the
+\subsubsection{Supervised classification.} The second part of the algorithm is the
 automatic construction of a pair-wise linkage function between signatures for use
@@
 $s_2$ belong to the same author, and $1$ otherwise.
-This problem can be cast as a standard supervised classification task, where inputs
+This problem can be cast as a supervised classification task, where inputs
 are pairs of signatures and outputs are classes $0$ (same authors), and $1$
@@
 
-\textit{Input features.} In most cases, supervised learning algorithms assume
-the input space ${\cal X}$ to be numeric (\eg, $\mathbb{R}^p$), making them
-not directly applicable to structured input spaces such as ${\cal S} \times
-{\cal S}$.
-Following previous works, pairs of signatures $(s_1, s_2)$ are first transformed to vectors $v \in \mathbb{R}^p$
+%In most cases, supervised learning algorithms assume
+%the input space ${\cal X}$ to be numeric (\eg, $\mathbb{R}^p$), making them
+%not directly applicable to structured input spaces such as ${\cal S} \times
+%{\cal S}$.
+
+\subsubsection{Input features.} Following previous works, pairs of signatures $(s_1, s_2)$ are first transformed to vectors $v \in \mathbb{R}^p$
 by building so-called similarity profiles \cite{treeratpituk2009disambiguating} on which supervised learning is carried out.
@@
 
-\subsection{Data}
-
-The author disambiguation solution proposed in this work, along with its
-enhancements, are evaluated on data extracted from the \emph{INSPIRE} portal
-\cite{gentil2009information}, a digital library for scientific literature in
+All the solutions proposed in this work sare evaluated on data extracted from
+the \emph{INSPIRE} portal \cite{gentil2009information}, a digital library for scientific literature in
 high-energy physics.
@@
 \begin{align}
-P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|\widehat{c}(s)|} \\
-R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|c(s)|}\\
+P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|\widehat{c}(s)|} \qquad
+R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) = \frac{1}{|{\cal S}|} \sum_{s \in {\cal S}} \frac{|c(s) \cap \widehat{c}(s)|}{|c(s)|}\\
 F_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) &= \frac{2 P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) R_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})}{P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S}) + P_\text{B3}({\cal C}, \widehat{\cal C}, {\cal S})} \\
-P_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p(\widehat{\cal C})|}\\
-R_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p({\cal C})|}\\
+P_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p(\widehat{\cal C})|} \qquad \qquad
+R_\text{pairwise}({\cal C}, \widehat{\cal C}) = \frac{|p({\cal C}) \cap p(\widehat{\cal C})|}{|p({\cal C})|}\\
 F_\text{pairwise}({\cal C}, \widehat{\cal C}) &= \frac{2 P_\text{pairwise}({\cal C}, \widehat{\cal C}) R_\text{pairwise}({\cal C}, \widehat{\cal C})}{P_\text{pairwise}({\cal C}, \widehat{\cal C}) + R_\text{pairwise}({\cal C}, \widehat{\cal C})}
@@
 consists in grouping all signatures sharing the same (normalized) surname(s) and
-the same (normalized) first given name initial. As it does not require the usage
-of any machine learning component, this baseline provides a simple and fast
+the same (normalized) first given name initial. It provides a simple and fast
 solution yielding decent results, as reported at the top of
@@
   \item Clustering: agglomerative clustering using average linkage and
-  block cuts found to maximize \\ $F_\text{B3}({\cal C}_\text{train}^\prime, \widehat{\cal C}_\text{train}^\prime, {\cal S}_\text{train}^\prime)$.
+  block cuts found to maximize $F_\text{B3}({\cal C}_\text{train}^\prime, \widehat{\cal C}_\text{train}^\prime, {\cal S}_\text{train}^\prime)$.
 \end{itemize}
@@
 
-Finally, as discussed previously, the seemingly insignificant step of
+Finally, as discussed previously, the step of
 normalizing author names (stripping accents, removing affixes), as performed in the

### 2016-04-26 paper/author_disambiguation.tex
kesw: first version. 16 pages
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

@@
 \usepackage{color}
-\setlength{\intextsep}{10pt plus 2pt minus 2pt}
+\usepackage{microtype}
+\setlength{\intextsep}{5pt plus 0pt minus 0pt}
 \newcommand{\msnote}[1]{\textcolor{blue}{[MS: #1]}}
 
-\def\baselinestretch{0.95}
+\def\baselinestretch{0.98}
+
+\newcommand{\longpage}{\enlargethispage{\baselineskip}}
+
 \begin{document}
@@
 
+\longpage
+
 As reviewed in \cite{smalheiser2009author,ferreira2012brief,levin2012citation}, author
@@
 set of pairs of publications, from which a linkage function is then built using supervised learning
-\cite{ferreira2010effective,torvik2009author,levin2012citation}.
-
-Semi-supervised approaches also allow for the tuning of the
+\cite{ferreira2010effective,torvik2009author,levin2012citation}. Semi-supervised approaches also allow for the tuning of the
 clustering algorithm when the latter is applied to a mixed set of labeled
@@
 
-In this context, we position the work in this paper as a
+In this context, we position this work as a
 semi-supervised solution for author disambiguation, with the significant
@@
 for semi-supervised clustering.
-Furthermore, by releasing our data in the public domain, we hope to provide a benchmark on
-which further research on author disambiguation and related topics can be built.
+Furthermore, by releasing our data in the public domain, we provide a benchmark on
+which further research on author disambiguation and related topics can be evaluated.
 
@@
 such that $c_i^\prime \subseteq c_i$, where $c_i^\prime$ may be empty.
+
+The distinctive aspect of our work is the
+knowledge of more than 1 million crowdsourced annotations, indicating together that all signature $s \in
+c_i^\prime$ are known to correspond to the same individual $a_i$.
+
+\longpage
 
@@
 \end{enumerate}
+
+\longpage
 
@@
 operator the cosine similarity between their respective $(n,m)$-\emph{TF-IDF} vector
-representations\footnote{$(n,m)$ denotes that the \emph{TF-IDF} vectors are computed
-from character $n$, $n+1$, ..., $m$-grams.
-When not specified, \emph{TF-IDF} vectors are otherwise computed from words.}.
+representations\footnote{$(n,m)-$\emph{TF-IDF} vectors are \emph{TF-IDF} vectors computed
+from $n$, $n+1$, ..., $m$-grams.}.
 
-Author names from different cultures, origins or ethnic groups are likely to be
+Authors from different origins or ethnic groups are likely to be
 disambiguated using different strategies (\eg, pairs of signatures with French
-author names versus pairs of signatures with Chinese author names) \cite{treeratpituk2012name, chin2014effective}.
+author names versus pairs of signatures with Chinese author names)
+\cite{treeratpituk2012name, chin2014effective}. For example, scientist coming from China
+might more/less often change affiliations, and this dependency, if learnt by the classifier, 
+should improve the fit.
 To support our disambiguation algorithm, we added seven features to our feature set, with each
 evaluating the degree of belonging of both signatures to an ethnic group.
-\msnote{Explain here ethnicity features (ethnicities come from some kind of US Census.
-Name those groups (as I removed them from the table))}
+
+\longpage
 
@@
 one-versus-all classification scheme) for mapping the
- $(1,5)$-TF-IDF representation of an author name to one of the seven ethnic groups. Given a
+$(1,5)$-TF-IDF representation of an author name to one of the ethnic groups, as
+defined in United States federal censuses. These groups are: \textit{White},
+\textit{Black of African American}, \textit{American Indian and Alaska Native},
+\textit{Asian}, \textit{Native Hawaiian and Other Pacific Islander},
+\textit{Japanese}, \textit{Chinese}, \textit{Others}. Given a
 pair of signatures $(s_1, s_2)$, the proposed ethnicity features are each
@@
 ethnic group, multiplied by the estimated probability of $s_2$ belonging to the
-same group. In doing so, the expectation is for the linkage function to become
+same group. Each of the seven races is used to create a single new feature.
+In doing so, the expectation is for the linkage function to become
 sensitive to the actual origin of the authors depending on the values of these
-features. Indirectly, let us also note that these features hold discriminative
+features. Indirectly, these features also hold discriminative
 power since if author names are predicted to belong to different ethnic groups,
@@
   \hline
-  Any ethnicity feature & Product of estimated probabilities\\
+  Any ethnicity feature & Product of probabilities estimated by SVM\\
   \hline
@@
 
-\textit{Building a training set.} The distinctive aspect of our work is the
-knowledge of more than 1 million crowdsourced annotations ${\cal C}^\prime = \{
-c_0^\prime, ..., c_{M-1}^\prime \}$, indicating together that all signature $s \in
-c_i^\prime$ are known to correspond to the same individual $a_i$.
-In particular, this data can be used to generate positive pairs $(x=(s_1, s_2), y=0)$ for all
+\textit{Building a training set.} 1 million of crowdsourced annotations (see Section \ref{methods}) can be used to generate positive pairs $(x=(s_1, s_2), y=0)$ for all
 $s_1, s_2 \in c_i^\prime$, for all $i$. Similarly, negative pairs $(x=(s_1,
@@
 
-The last component of our author disambiguation pipeline is clustering, that is
+\longpage
+
+The last component of our author disambiguation pipeline is clustering - 
 the process of grouping together, within a block, all signatures from the same
@@
 
+\longpage
+
 As part of this work, we developed a stand-alone application for author
@@
 It is also designed to be runnable in an incremental fashion in which our approach is considered to be scalable.
-We adopt a divide-and-conquer strategy for clustering (called “blocking” in this line of work) in order to reduce the computational complexity from $O(N^2)$ to $O(\sum N_i^2)$, which in practice tends to ${O(N)}$ when $N_i << N$.
+We adopt the blocking phase in order to reduce the computational complexity from $O(N^2)$ to $O(\sum N_i^2)$, which in practice tends to ${O(N)}$ when $N_i << N$.
 This also means that instead of having to run the disambiguation process on the whole signature set, the process could be run only on specified blocks if desired.
@@
 
-All the solutions proposed in this work sare evaluated on data extracted from
+All the solutions proposed in this work are evaluated on data extracted from
 the \emph{INSPIRE} portal \cite{gentil2009information}, a digital library for scientific literature in
@@
 
+\longpage
+
+\subsubsection{Baseline.} The simplest baseline against which we compare our results
+consists in grouping all signatures sharing the same (normalized) surname(s) and
+the same (normalized) first given name initial. It provides a simple and fast
+solution yielding decent results, as reported at the top of
+Table~\ref{table:results}
+
+\begin{small}
 \begin{table*}
@@
 \hline
-\hline
 \underline{Classifier = GBRT} & 0.9901 & 0.9760 & 0.9830   & 0.9948 & 0.9738 & 0.9842 \\
@@
 \underline{Training pairs = Blocked, balanced} & 0.9901 & 0.9760 & \textbf{0.9830}  & 0.9948 & 0.9738 & \textbf{0.9842} \\
-\hline
 \hline
@@
 \hline
-\hline
 Combined best settings & 0.9897 & 0.9827 & \textbf{0.9862}  & 0.9954 & 0.9805 & \textbf{0.9879} \\
+Best settings without ethnicity features & 0.9862 & 0.9819 & 0.9841 & 0.9937 & 0.9815 & 0.9876 \\
   \hline
@@
 \end{table*}
+\end{small}
 
-\textit{Baseline.} The simplest baseline against which we compare our results
-consists in grouping all signatures sharing the same (normalized) surname(s) and
-the same (normalized) first given name initial. It provides a simple and fast
-solution yielding decent results, as reported at the top of
-Table~\ref{table:results}
-
-\textit{State-of-the-art.} Most methods proposed in related works have released
+\subsubsection{State-of-the-art.} Most methods proposed in related works have released
 neither their software, nor their data, making a fair comparison very difficult.
@@
 
+\longpage
+
 The good precision of the state-of-the-art ($0.9901$), but its
@@
 As Table~\ref{table:results} shows, switching to either Double metaphone or NYSIIS phonetic-based blocking allows
-to improve the overall F-measure score, trading precision for recall.
+to improve the overall F-measure score.
 In particular, the NYSIIS-based phonetic blocking shows to be the most effective when applied
@@
 
+Moreover, we observed that the ethnicity features are an improvement. When these features were not
+included in the features set, using the best combined settings, the algorithm yields worse result
+($0.9841$).
+
 Using Recursive Feature Elimination \cite{guyon2002gene}, we next evaluate the
@@
 strategy ($0.9409$), but yields anyhow surprisingly decent accuracy, given the
-fact it requires almost no computation (\ie, both learning a linkage function
-and running agglomerative clustering can be skipped -- only the blocking
-function is needed to group signatures). In particular, this result reveals
+fact it requires no linkage function and no agglomerative clustering -- only the blocking
+function is needed to group signatures. In particular, this result reveals
 that author names are not ambiguous in most cases\footnote{This holds for the
@@
 fraction of them requires advanced disambiguation procedures. On the other
-hand, both global and block cut thresholding strategies give very good results,
-with a slight advantage for block cuts ($0.9814$ versus $0.9830$), as expected.
-In case ${\cal S}^\prime_b$ is empty (\eg, because it corresponds to a young
-researcher at the beginning of his career), this therefore suggests that either using
-a cut-off threshold learned globally from the known data or using SFI would in general give
-satisfactory results, only marginally worse than if claimed signatures had been
+hand, both global and block cut thresholding strategies give better results,
+with a slight advantage for the block cuts ($0.9814$ versus $0.9830$), as expected.
+In case ${\cal S}^\prime_b$ is empty (\ie partial clusters are not known for any of the signatures from the
+block), this therefore suggests that either using
+a cut-off threshold learned globally from the known data would in general give results only
+marginally worse than if the claimed signatures had been
 known. Trying out 3 clustering methods, the results show that \textit {average linkage} was the best one.
+
+\longpage
 
@@
 \label{conclusions}
+
+\longpage
 
@@
 
+Moreover, the techniques presented in this work can be easily adapted to the broader
+problem of named entity disambiguation and might improve accuracy of semantic search
+algorithms.
+
 As part of this study, we also publicly release the annotated data extracted

### 2016-04-29 paper/author_disambiguation.tex
kesw: first official version
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

@@
 \usepackage{microtype}
+
 \setlength{\intextsep}{5pt plus 0pt minus 0pt}
-\newcommand{\msnote}[1]{\textcolor{blue}{[MS: #1]}}
-
-\def\baselinestretch{0.98}
+\def\baselinestretch{0.99}
 
 \newcommand{\longpage}{\enlargethispage{\baselineskip}}
+\newcommand{\verylongpage}{\enlargethispage{2\baselineskip}}
 
@@
 Experiments
-are carried out in Section~\ref{experiments}, where we explore and validate
-features for the supervised learning of a linkage function and compare
-strategies for the semi-supervised clustering of publications.
+are carried out in Section~\ref{experiments}, where we compare
+approaches to the problem and explore feature choice.
 Finally, conclusions and future works are discussed in Section~\ref{conclusions}.
@@
 
-Due to the lack of large and publicly available datasets of curated
-clusters of publications, studies on author disambiguation are usually
-constrained to validating their results on manually built datasets of limited
-size and scope (from a few hundred to a few thousand papers, with sparse
-coverage of ambiguous cases), making the true performance of these methods
-often difficult to assess with high confidence.
-Additionally, despite devoted efforts to construct them, these datasets are rarely public,
-making it even more difficult to compare methods using a common benchmark.
+%Due to the lack of large and publicly available datasets of curated
+%clusters of publications, studies on author disambiguation are usually
+%constrained to validating their results on manually built datasets of limited
+%size and scope (from a few hundred to a few thousand papers, with sparse
+%coverage of ambiguous cases), making the true performance of these methods
+%often difficult to assess with high confidence.
+%Additionally, despite devoted efforts to construct them, these datasets are rarely public,
+%making it even more difficult to compare methods using a common benchmark.
 
@@
 \end{enumerate}
-
-\longpage
 
@@
 From these, we evaluate the following semi-supervised cut-off strategies, as illustrated in Figure~\ref{fig:cuts}:
+
 \begin{itemize}
@@
 solution yielding decent results, as reported at the top of
-Table~\ref{table:results}
+Table~\ref{table:results}.
 
@@
 \begin{table*}
-\caption{Average precision, recall and f-measure scores on test folds. Underlined components correspond to the state-of-the-art choices.}
+\caption{Average precision, recall and f-measure scores on test folds. - components correspond to the state-of-the-art choices.}
 \label{table:results}
@@
 Blocking = Soundex & 0.9886 & 0.9745 & 0.9815 & 0.9935 & 0.9725 & 0.9828 \\
-\hline
-No name normalization & 0.9887 & 0.9697 & 0.9791 & 0.9931 & 0.9658 & 0.9793 \\
-\underline{Name normalization} & 0.9901 & 0.9760 & \textbf{0.9830} & 0.9948 & 0.9738 & \textbf{0.9842}  \\
 \hline
@@
 \hline
-Combined best settings & 0.9897 & 0.9827 & \textbf{0.9862}  & 0.9954 & 0.9805 & \textbf{0.9879} \\
+Combined best settings & 0.9888 & 0.9848 & \textbf{0.9868}  & 0.9951 & 0.9831 & \textbf{0.9890} \\
 Best settings without ethnicity features & 0.9862 & 0.9819 & 0.9841 & 0.9937 & 0.9815 & 0.9876 \\
@@
 
+\longpage
+
 \begin{itemize}
-	\item Blocking: same surname and the same first given name initial strategy (SFI) and with name normalization;
+	\item Blocking: same surname and the same first given name initial strategy (SFI);
 	\item Linkage function: all 22 features defined in Table~\ref{table:features},
@@
 
-Finally, as discussed previously, the step of
-normalizing author names (stripping accents, removing affixes), as performed in the
-state-of-the-art, is shown to be important. Results from Table~\ref{table:results} clearly suggest that not
-normalizing significantly reduces performance (yielding an F-measure of $0.9830$ when normalizing,
-but decreasing to $0.9791$ when raw author name strings are used instead).
+%Finally, as discussed previously, the step of
+%normalizing author names (stripping accents, removing affixes), as performed in the
+%state-of-the-art, is shown to be important. Results from Table~\ref{table:results} clearly %suggest that not
+%normalizing significantly reduces performance (yielding an F-measure of $0.9830$ when %normalizing,
+%but decreasing to $0.9791$ when raw author name strings are used instead).
 
@@
 
-Moreover, we observed that the ethnicity features are an improvement. When these features were not
-included in the features set, using the best combined settings, the algorithm yields worse result
+Moreover, we observed that the ethnicity features serve a purpose. When these features were not
+included in the features set, using the best combined settings, the algorithm yields worse performance
 ($0.9841$).
@@
 
+\longpage
+
 Clustering together all signatures from the same block (\ie, baseline) is the least effective
@@
 marginally worse than if the claimed signatures had been
-known. Trying out 3 clustering methods, the results show that \textit {average linkage} was the best one.
+known.
 
-\longpage
-
-\subsubsection{Combined best settings} When all best settings are combined (\ie, Blocking = NYSIIS, Name normalization, Classifier = Random Forests, Training
+\subsubsection{Combined best settings} When all best settings are combined (\ie, Blocking = NYSIIS, Classifier = Random Forests, Training
 pairs = blocked and balanced, Clustering = Average linkage, Block cuts),
@@
 Overall, these results all encourage further improvements and research. For
-blocking, one of the open challenges is to manage signatures with inconsistent
-surnames or inconsistent first given names (cases 4 and 5, as described in
+blocking, one of the challenges is to manage signatures with inconsistent
+surnames or first given names (cases 4 and 5, as described in
 Section~\ref{methods:blocking}) while maintaining blocks to a tractable size.
@@
 
+\verylongpage
+
 \bibliographystyle{abbrv}

### 2016-04-29 paper/author_disambiguation.tex
double quotes

@@
 \includegraphics[width=\textwidth]{fig-pub-to-signature.pdf}
-\caption{An example signature $s$ for "Doe, John". A \textit{signature} is
+\caption{An example signature $s$ for ``Doe, John". A \textit{signature} is
 defined as unique piece of information identifying an author on a publication,
@@
   ways of writing an author name, or signatures contain a typo
-  (\eg, "Mueller, R." and "Muller, R.").
+  (\eg, ``Mueller, R." and ``Muller, R.").
 
-  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (\eg, "Martinez Torres, A." and "Torres, A. Martinez").
+  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (\eg, ``Martinez Torres, A." and ``Torres, A. Martinez").
 
   \item An author has multiple surnames and, on some signatures, only the first surname is
-  present (\eg, "Smith-Jones, A." and "Smith, A.")
+  present (\eg, ``Smith-Jones, A." and ``Smith, A.")
 
   \item An author has multiple given names and they are not always all recorded (\eg,
-  "Smith, Jack" and "Smith, A. J.")
+  ``Smith, Jack" and ``Smith, A. J.")
 
@@
 phonetic representation of the normalized surname.
-Normalization involves stripping accents (\eg, "Jab\l{}o\'nski, \L{}" $\rightarrow$ "Jablonski, L") and name
-affixes that inconsistently appear in signatures (\eg, "van der Waals, J. D."
-$\rightarrow$ "Waals, J. D."), while phonetization is based either on the
+Normalization involves stripping accents (\eg, ``Jab\l{}o\'nski, \L{}" $\rightarrow$ ``Jablonski, L") and name
+affixes that inconsistently appear in signatures (\eg, ``van der Waals, J. D."
+$\rightarrow$ ``Waals, J. D."), while phonetization is based either on the
 Double Metaphone \cite{doublemetaphone}, the NYSIIS \cite{nysiis} or the

### 2016-04-29 paper/author_disambiguation.tex
A few words about ethnicity dataset
A few words about ethnicity dataset as a motivation for futurework

@@
 
-Overall, these results all encourage further improvements and research. For
 blocking, one of the challenges is to manage signatures with inconsistent

### 2016-04-29 paper/author_disambiguation.tex
A few words about ethnicity dataset

--- 2016-04-29 paper/author_disambiguation.tex
@@
 
-Overall, these results all encourage further improvements and research. For
+Overall, these results all encourage further improvements and research.
+Because of the sensitivity of name-to-ethnicity data, it was not easy to obtain a sufficient coverage of names and ethnicities in the dataset.
+Even though, we observed some performance enhancements with the generated ethnicity estimator.
+This motivates working on building a better name-to-ethnicity dataset and measuring its impact on the performance.
+For
 blocking, one of the challenges is to manage signatures with inconsistent

### 2016-04-29 paper/author_disambiguation.tex
rephrase to keep 15 pages as before

--- 2016-04-29 paper/author_disambiguation.tex
@@
 disambiguation accuracy.
-
-Overall, these results all encourage further improvements and research. For
-blocking, one of the challenges is to manage signatures with inconsistent
-surnames or first given names (cases 4 and 5, as described in
-Section~\ref{methods:blocking}) while maintaining blocks to a tractable size.
-As phonetic algorithms are not yet perfect, another direction  for further work is the design of better
-phonetization functions, tailored for author disambiguation. For the linkage function,
-the good results of the proposed features pave the way for further research  in
-ethnicity-sensitive author disambiguation. The automatic fitting of the
-pipeline to cultures and ethnic groups for which standard author disambiguation
-is known to be less efficient (\eg, Chinese authors with many homonyms)  indeed
-constitutes a direction of research with great potential benefits for the
-concerned scientific communities.
-
+In general, the results encourage further improvements and research.
+For blocking, one of the challenges is to manage signatures with inconsistent surnames or first given names (cases 4 and 5, as described in Section~\ref{methods:blocking}) while maintaining blocks to a tractable size.
+As phonetic algorithms are not yet perfect, another direction  for further work is the design of better phonetization functions, tailored for author disambiguation.
+For the linkage function, the good results of the proposed features pave the way for further research in ethnicity-sensitive author disambiguation.
+The automatic fitting of the pipeline to ethnic groups is better that a standard one that is less efficient for author names with many homonyms (\eg,Chinese authors).
+Collecting a bigger name-to-ethnicity dataset with better coverage of names is another future work to consider.
 Moreover, the techniques presented in this work can be easily adapted to the broader

### 2016-04-29 paper/author_disambiguation.tex
inspirehep/beard

@@
 As part of this work, we developed a stand-alone application for author
-disambiguation, publicly available online\footnote{\url{https://github.com/glouppe/beard}} for free reuse
+disambiguation, publicly available online\footnote{\url{https://github.com/inspirehep/beard}} for free reuse
 or study.

### 2016-04-29 paper/author_disambiguation.tex
kesw: final rewording
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

@@
 \textit{Co-authors}, \textit{Affiliation} and \textit{Full name}. Adding the remaining
-other features only brings marginal improvements, with \textit{Journal},
-\textit{Abstract}, \textit{Collaborations}, \textit{References}, \textit{Given
-name initial} and \textit{Second given name} being almost insignificant.
+other features only brings marginal improvements.
 Overall, these results highlight the added value of the proposed ethnicity
@@
 disambiguation accuracy.
-In general, the results encourage further improvements and research.
-For blocking, one of the challenges is to manage signatures with inconsistent surnames or first given names (cases 4 and 5, as described in Section~\ref{methods:blocking}) while maintaining blocks to a tractable size.
-As phonetic algorithms are not yet perfect, another direction  for further work is the design of better phonetization functions, tailored for author disambiguation.
-For the linkage function, the good results of the proposed features pave the way for further research in ethnicity-sensitive author disambiguation.
-The automatic fitting of the pipeline to ethnic groups is better that a standard one that is less efficient for author names with many homonyms (\eg,Chinese authors).
-Collecting a bigger name-to-ethnicity dataset with better coverage of names is another future work to consider.
+In general, the results encourage further improvements and research. For blocking, one of the
+challenges is to manage signatures with inconsistent surnames or first given names (cases 4
+and 5, as described in Section~\ref{methods:blocking}) while maintaining blocks to a tractable
+size. As phonetic algorithms are not yet perfect, another direction  for further work is the
+design of better phonetization functions, tailored for author disambiguation. For the linkage
+function, the good results of the proposed features pave the way for further research in
+ethnicity-sensitivity. The automatic fitting of the
+pipeline to cultures and ethnic groups for which standard author disambiguation
+is known to be less efficient (\eg, Chinese authors with many homonyms) indeed
+constitutes a direction of research with great potential benefits for the
+concerned scientific communities. Exploring other name-to-ethnicity datasets with deeper 
+coverage of names is another future work worth considering.
+
 Moreover, the techniques presented in this work can be easily adapted to the broader
-problem of named entity disambiguation and might improve accuracy of semantic search
-algorithms.
+problem of named entity disambiguation and thus might significantly improve accuracy of
+semantic search algorithms.
 
@@
 
-\verylongpage
-
 \bibliographystyle{abbrv}

### 2016-06-27 paper/author_disambiguation.tex
Modify the affiliation line of Hussein
june 1 deadline
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

@@
 \setlength{\intextsep}{5pt plus 0pt minus 0pt}
-\def\baselinestretch{0.99}
+% \def\baselinestretch{0.99}
 
 \newcommand{\longpage}{\enlargethispage{\baselineskip}}
-\newcommand{\verylongpage}{\enlargethispage{2\baselineskip}}
 
@@
 % can use linebreaks \\ within to get better formatting as desired
-\title{Ethnicity sensitive author disambiguation using semi-supervised learning}
+\title{Ethnicity Sensitive Author Disambiguation Using Semi-supervised Learning}
 
@@
 \and
-ISH-LYON (USR 3385), CNRS, France,\\
+Univ Lyon, ISH Lyon, USR 3385, CNRS, and ERIC lab., EA 3083, Lyon 2, France,\\
 \email{hussein.al-natsheh@ish-lyon.cnrs.fr}
@@
 
-Author name disambiguation in bibliographic databases is the problem of grouping
-together scientific publications written by the same person, accounting for
-potential homonyms and/or synonyms. Among solutions to this problem, digital
-libraries are increasingly offering tools for authors to manually curate their
-publications and claim those that are theirs. Indirectly, these tools allow for
-the inexpensive collection of large annotated training data, which can be
-further leveraged to build a complementary automated disambiguation system
-capable of inferring patterns for identifying publications written by the same
-person. Building on more than 1 million crowdsourced
-annotations that we publicly release, we propose an automated author disambiguation solution exploiting
+Building on more than 1 million crowdsourced
+annotations that we publicly release, we propose a new automated disambiguation
+solution exploiting
 this data (i) to learn an accurate classifier for identifying coreferring
@@
 the state of the art, we validate the general pipeline used in most existing
-solutions, and improve by: (i) proposing phonetic-based blocking strategies,
+solutions, and improve by: (i) proposing new phonetic-based blocking strategies,
 thereby increasing recall; (ii) adding strong ethnicity-sensitive features for
@@
 
-\longpage
-
 Our algorithm is composed of three parts (Figure~\ref{fig:workflow}): (i) a blocking
@@
 along their first given name initial.
-Cases 4 and 5 are not explicitly handled.
+The biggest limitation of this method is leaving the cases 4 and 5 unhandled.
+This method might result in blocking together signatures from many different authors
+with similar names.
 
@@
 \label{methods:linkage}
+
+\longpage
 
@@
 In this work, we design and evaluate fifteen standard input
-features based on the comparison of signature fields, as reported in the first
+features \cite{ferreira2012brief, levin2012citation} based on the comparison of signature fields, as reported in the first
 half of Table~\ref{table:features}.
@@
 
-\longpage
-
 The last component of our author disambiguation pipeline is clustering - 
@@
 to persistent identifiers provided by publishers or other sources.
-Together, they constitute a trusted set $({\cal S}^\prime, {\cal C}^\prime)$ of 15388 distinct individuals sharing
-36340 unique author names spread within 1201763 signatures on 360066
+Together, they constitute a trusted set $({\cal S}^\prime, {\cal C}^\prime)$ of 15,388 distinct individuals sharing
+36,340 unique author names spread within 1,201,763 signatures on 360,066
 publications. This data covers several decades in time and dozens of author
@@
 
-\longpage
-
 \subsubsection{Baseline.} The simplest baseline against which we compare our results
@@
 \begin{table*}
-\caption{Average precision, recall and f-measure scores on test folds. - components correspond to the state-of-the-art choices.}
+\caption{Average precision, recall and f-measure scores on test folds. Components correspond to the state-of-the-art choices.}
 \label{table:results}
@@
 
-\longpage
-
 \begin{itemize}
@@
 proposed phonetic-based blocking strategies show better maximum recall (all
-around $0.9905$), thereby pushing further the upper bound on the maximum
-performance of author disambiguation.
-Let us remind however that the reported maximum recalls for the blocking strategies using phonetization are
+around $0.9905$). Better recall pushes further the upper bound on the maximum
+performance of author disambiguation, as the signatures that belong to the same author
+and different groups can not be clustered together by our algorithm.
+Let us remind that the reported maximum recalls for the blocking strategies using phonetization are
 also raised due to the better handling of multiple surnames, as described in Section \ref{methods:blocking}.
@@
 to the state-of-the-art (with an F-measure of $0.9850$) while also being the most
-efficient computationally (with 10857 blocks versus 12978 for the baseline).
+efficient computationally (with 10,857 blocks versus 12,978 for the baseline).
 
@@
 
+\longpage
+
 Second, properly constructing a training set of positive and negative pairs of
@@
 pairs it will be used to eventually cluster. Finally, making the classification
-problem more difficult by oversampling complex cases proves to be relevant,
+problem more difficult by oversampling complex cases (see \ref{methods:linkage}) proves to be relevant,
 by further improving the disambiguation results ($0.9830$).
@@
 
-\longpage
-
 Clustering together all signatures from the same block (\ie, baseline) is the least effective
@@
 \label{conclusions}
-
-\longpage
 

### 2016-06-27 paper/author_disambiguation.tex
other june 1 fixes
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

@@
 \setlength{\intextsep}{5pt plus 0pt minus 0pt}
-% \def\baselinestretch{0.99}
+%\def\baselinestretch{0.99}
 
-\newcommand{\longpage}{\enlargethispage{\baselineskip}}
+\newcommand{\longpage}{\enlargethispage{1.5\baselineskip}}
 
@@
 \label{related-works}
-
-\longpage
 
@@
 
-  \item An author has multiple surnames and some signatures place the first part of the surname within the given names (\eg, ``Martinez Torres, A." and ``Torres, A. Martinez").
+  \item An author has multiple surnames (or a patronymic) and some signatures place the first part of the surname within the given names (\eg, ``Martinez Torres, A." and ``Torres, A. Martinez").
 
@@
 \label{methods:linkage}
-
-\longpage
 
@@
 \includegraphics[width=\textwidth]{fig-cuts.pdf}
-\caption{Semi-supervised cut-off strategies to form flat clusters of signatures.}
+\caption{Semi-supervised cut-off strategies to form flat clusters of signatures. Every
+dendogram represents a single block.}
 \label{fig:cuts}
@@
 
-\longpage
-
 The good precision of the state-of-the-art ($0.9901$), but its
@@
 
+\longpage
+
 In this work, we have revisited and validated the general author disambiguation

### 2016-06-28 paper/author_disambiguation.tex
Shorter version of Hussein's affiliation
blocking and meta-data + small and compact title section

@@
 \usepackage{microtype}
+\usepackage[small,compact]{titlesec}
 
@@
 \and
-Univ Lyon, ISH Lyon, USR 3385, CNRS, and ERIC lab., EA 3083, Lyon 2, France,\\
+ISH, USR 3385, CNRS, and ERIC lab, EA 3083, Univ Lyon 2, France,\\
 \email{hussein.al-natsheh@ish-lyon.cnrs.fr}
@@
 with the objective to embed these identifiers in the submission workflow of publishers
-or repositories (\eg, Elsevier, arXiv or Inspire-HEP), would univocally solve any disambiguation issue.
+or repositories (\eg, Elsevier or arXiv), would univocally solve any disambiguation issue.
 As the centralized manual authorship control is expensive and the success of persistent digital
@@
 commonly used in existing solutions is an effective approach for author disambiguation.
-Moreover, we propose better strategies for blocking based on the
+Moreover, we propose better strategies for blocking (\ie, partitioning) based on the
 phonetization of author names to increase recall and ethnicity-sensitive features for learning a
@@
 signatures ${\cal S}$ into disjoint subsets ${\cal S}_{b_0}, ..., {\cal
-S}_{b_{K-1}}$, or \textit{blocks} \cite{fellegi69}, followed by carrying out
+S}_{b_{K-1}}$, or \textit{blocks} (\ie partitions) \cite{fellegi69}, followed by carrying out
 author disambiguation on each one of these blocks independently.
@@
 features \cite{ferreira2012brief, levin2012citation} based on the comparison of signature fields, as reported in the first
-half of Table~\ref{table:features}.
+half of Table~\ref{table:features}. Noteworthy, the author metadata, both provided or derived, are far more important than the publication content itself.
 As an illustrative example, the \textit{Full name} feature corresponds to the similarity between the (full)

### 2016-06-30 paper/author_disambiguation.tex
fit to 15 pages without titlesec
Signed-off-by: Mateusz Susik <mateuszsusik@gmail.com>

@@
 \usepackage{microtype}
-\usepackage[small,compact]{titlesec}
 
 \setlength{\intextsep}{5pt plus 0pt minus 0pt}
-%\def\baselinestretch{0.99}
+\def\baselinestretch{0.99}
 
-\newcommand{\longpage}{\enlargethispage{1.5\baselineskip}}
+\newcommand{\longpage}{\enlargethispage{1.4\baselineskip}}
 
@@
 
-Building on more than 1 million crowdsourced
+Building on more than one million crowdsourced
 annotations that we publicly release, we propose a new automated disambiguation
@@
 
-\longpage
-
 Second, properly constructing a training set of positive and negative pairs of
@@
 
-\longpage
-
 In this work, we have revisited and validated the general author disambiguation
